### 2020-11-18 article/article.tex
Moved to separate repo

%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham Universtiy, UK.

\documentclass{jors}

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

\begin{document}

{\bf Software paper for submission to the Journal of Open Research Software} \\

To complete this template, please replace the blue text with your own. The paper has three main sections: (1) Overview; (2) Availability; (3) Reuse potential. \\

Please submit the completed paper to: editor.jors@ubiquitypress.com

\rule{\textwidth}{1pt}

\section*{(1) Overview}

\vspace{0.5cm}

\section*{Title}
Spinsim: a GPU optimised solver of spin one and half quantum systems

\textcolor{blue}{The title of the software paper should focus on the software, e.g. “Text mining software from the X project”. If the software is closely linked to a specific research paper, then “Software from Paper Title” is appropriate. The title should be factual, relating to the functionality of the software and the area it relates to rather than making claims about the software, e.g. “Easy-to-use”.}

\section*{Paper Authors}
1. Tritt, Alexander;\\
2. Turner, Lincoln David;\\
3. Saunderson, James;\\
4. Morris, Joshua;\\
5. Hochstetter, Joel;\\

\textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
2. Last name, first name; etc.}

\section*{Paper Author Roles and Affiliations}
1. PhD student, School of physics and astronomy, Monash University\\
2. Supervisor, School of physics and astronomy, Monash University\\
3. Supervisor, Department of electrical and computer systems engineering, Monash University\\
4. Original writer of AtomicPy for spin half systems\\
5. Original writer of the spin one extension to AtomicPy\\

\textcolor{blue}{1. First author role and affiliation \\
2. Second author role and affiliation etc.}

\section*{Abstract}

\textcolor{blue}{A short (ca. 100 word) summary of the software being described: what problem the software addresses, how it was implemented and architected, where it is stored, and its reuse potential.}

\section*{Keywords}
Time dependent Schrödinger equation; Spin one; Spin half; Integrator; GPU;\\

\textcolor{blue}{keyword 1; keyword 2; etc. \\
Keywords should make it easy to identify who and what the software will be useful for.}

\section*{Introduction}
\subsection*{Motivation}
Spinsim is a package for python designed to simulate the spin one dynamics of Bose Einstein Condensates, specifically for the Spinor BEC lab group at Monash University.

\subsection*{Motivation}

\textcolor{blue}{An overview of the software, how it was produced, and the research for which it has been used, including references to relevant research articles. A short comparison with software which implements similar functionality should be included in this section. }

\section*{Implementation and architecture}

\textcolor{blue}{How the software was implemented, with details of the architecture where relevant. Use of relevant diagrams is appropriate. Please also describe any variants and associated implementation differences.}

\section*{Quality control}

\textcolor{blue}{Detail the level of testing that has been carried out on the code (e.g. unit, functional, load etc.), and in which environments. If not already included in the software documentation, provide details of how a user could quickly understand if the software is working (e.g. providing examples of running the software with sample input and output data). }

\section*{(2) Availability}
\vspace{0.5cm}
\section*{Operating system}

\textcolor{blue}{Please include minimum version compatibility.}

\section*{Programming language}

\textcolor{blue}{Please include minimum version compatibility.}

\section*{Additional system requirements}

\textcolor{blue}{E.g. memory, disk space, processor, input devices, output devices.}

\section*{Dependencies}

\textcolor{blue}{E.g. libraries, frameworks, incl. minimum version compatibility.}

\section*{List of contributors}

\textcolor{blue}{Please list anyone who helped to create the software (who may also not be an author of this paper), including their roles and affiliations.}

\section*{Software location:}

{\bf Archive} \textcolor{blue}{(e.g. institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Publisher:]  \textcolor{blue}{Name of the person who deposited the software.}
	\item[Version published:] \textcolor{blue}{The version number of the software archived.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

{\bf Code repository} \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

{\bf Emulation environment} \textcolor{blue}{(if appropriate)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

\section*{Language}

\textcolor{blue}{Language of repository, software and supporting files.}

\section*{(3) Reuse potential}

\textcolor{blue}{Please describe in as much detail as possible the ways in which the software could be reused by other researchers both within and outside of your field. This should include the use cases for the software, and also details of how the software might be modified or extended (including how contributors should contact you) if appropriate. Also you must include details of what support mechanisms are in place for this software (even if there is no support).}

\section*{Acknowledgements}

\textcolor{blue}{Please add any relevant acknowledgements to anyone else who supported the project in which the software was created, but did not work directly on the software itself.}

\section*{Funding statement}

\textcolor{blue}{If the software resulted from funded research please give the funder and grant number.}

\section*{Competing interests}

\textcolor{blue}{If any of the authors have any competing interests then these must be declared. The authors’ initials should be used to denote differing competing interests. For example: “BH has minority shares in [company name], which part funded the research grant for this project. All other authors have no competing interests." \\
If there are no competing interests, please add the statement:
“The authors declare that they have no competing interests.” }

\section*{References}

\textcolor{blue}{Please enter references in the Harvard style and include a DOI where available, citing them in the text with a number in square brackets, e.g. \\ }

\textcolor{blue}{[1] Piwowar, H A 2011 Who Shares? Who Doesn't? Factors Associated with Openly Archiving Raw Research Data. PLoS ONE 6(7): e18657. DOI: \\ http://dx.doi.org/10.1371/journal.pone.0018657.}

\vspace{2cm}

\rule{\textwidth}{1pt}

{ \bf Copyright Notice} \\
Authors who publish with this journal agree to the following terms: \\

Authors retain copyright and grant the journal right of first publication with the work simultaneously licensed under a  \href{http://creativecommons.org/licenses/by/3.0/}{Creative Commons Attribution License} that allows others to share the work with an acknowledgement of the work's authorship and initial publication in this journal. \\

Authors are able to enter into separate, additional contractual arrangements for the non-exclusive distribution of the journal's published version of the work (e.g., post it to an institutional repository or publish it in a book), with an acknowledgement of its initial publication in this journal. \\

By submitting this paper you agree to the terms of this Copyright Notice, which will apply to this submission if and when it is published by this journal.

\end{document}

### 2020-11-18 docs/source/_ext/numbadoc.py

@@ -1,0 +1,177 @@
+"""
+This sphinx extension aims to improve the documentation of numba-decorated
+functions. It it inspired by the design of Celery's sphinx extension
+'celery.contrib.sphinx'.
+
+Usage
+-----
+
+Add the extension to your :file:`conf.py` configuration module:
+
+.. code-block:: python
+
+    extensions = (...,
+                  'numbadoc')
+
+This extension adds two configuration fields, which determine the prefix
+printed before jitted functions in the reference documentation.
+Overwrite these values in your :file:`conf.py` to change this behaviour
+
+.. code-block:: python
+
+    #defaults
+    numba_jit_prefix = '@numba.jit'
+    numba_vectorize_prefix = '@numba.vectorize'
+    numba_cuda_jit_prefix = '@numba.cuda.jit'
+
+With the extension installed `autodoc` will automatically find
+numba decorated objects and generate the correct docs.
+
+If a vecotrized function with fixed signatures is found, these are injected
+into the docstring.
+"""
+from typing import List, Iterator
+from sphinx.domains.python import PyFunction
+from sphinx.ext.autodoc import FunctionDocumenter
+
+from numba.core.dispatcher import Dispatcher
+from numba.np.ufunc.dufunc import DUFunc
+from numba.cuda.compiler import AutoJitCUDAKernel
+from numba.cuda.compiler import DeviceFunctionTemplate
+
+class NumbaFunctionDocumenter(FunctionDocumenter):
+    """Document numba decorated functions."""
+
+    def import_object(self) -> bool:
+        """Import the object given by *self.modname* and *self.objpath* and set
+        it as *self.object*.
+
+        Returns True if successful, False if an error occurred.
+        """
+        success = super().import_object()
+        if success:
+            # Store away numba wrapper
+            self.jitobj = self.object
+            # And bend references to underlying python function
+            if hasattr(self.object, "py_func"):
+                self.object = self.object.py_func
+            elif hasattr(self.object, "_dispatcher") and \
+                 hasattr(self.object._dispatcher, "py_func"):
+                self.object = self.object._dispatcher.py_func
+            else:
+                success = False
+        return success
+
+    def process_doc(self, docstrings: List[List[str]]) -> Iterator[str]:
+        """Let the user process the docstrings before adding them."""
[…]

### 2020-11-18 docs/source/conf.py

@@ -1,0 +1,105 @@
+# Configuration file for the Sphinx documentation builder.
+#
+# This file only contains a selection of the most common options. For a full
+# list see the documentation:
+# https://www.sphinx-doc.org/en/master/usage/configuration.html
+
+# -- Path setup --------------------------------------------------------------
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#
+
+
+"""
+To init rst from comments:
+sphinx-apidoc -o source/ ../
+
+To build html from rst:
+make html
+"""
+
+import os
+import sys
+import sphinx_rtd_theme
+# from import exts.numbadoc
+sys.path.insert(0, os.path.abspath('../../'))
+sys.path.append(os.path.abspath("./_ext"))
+sys.path.append(os.path.abspath("../../../"))
+# sys.path.insert(1, os.path.abspath('exts\\'))
+# from exts import numbadoc
+# sys.path.append(os.path.abspath('exts\\'))
+
+
+# -- Project information -----------------------------------------------------
+
+project = 'spinsim'
+copyright = '2020, Alexander Tritt'
+author = 'Alexander Tritt'
+
+# The full version, including alpha/beta/rc tags
+release = '0.1'
+
+
+# -- General configuration ---------------------------------------------------
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = [
+    "sphinx.ext.autodoc",   # Generate documentation from code
+    "sphinx.ext.napoleon",  # Use numpy standard formatting
+    "sphinx_rtd_theme",     # Documentation theme
+    "numbadoc",             # Is able to document numba
+    "sphinx.ext.intersphinx"
+]
+
+autoclass_content = 'both'
+
+# Napoleon settings
+napoleon_google_docstring = False
+napoleon_numpy_docstring = True
+napoleon_include_init_with_doc = False
+napoleon_include_private_with_doc = False
+napoleon_include_special_with_doc = True
+napoleon_use_admonition_for_examples = False
+napoleon_use_admonition_for_notes = False
+napoleon_use_admonition_for_references = False
+napoleon_use_ivar = False
+napoleon_use_param = True
+napoleon_use_rtype = True
+napoleon_type_aliases = None
+
+# Add any paths that contain templates here, relative to this directory.
[…]

### 2020-11-18 example.py

@@ -1,0 +1,169 @@
+import colorama         # Colourful terminal
+colorama.init()
+
+import spinsim.spinsim as spinsim
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+"""
+Note: please see documentation for a full explanation of the source code.
+"""
+
+"""
+======================================
+Example 1: Spin half Larmor precession
+======================================
+"""
+# Define a numba.cuda compatible source sampling function
+def get_source_larmor(time_sample, simulation_index, source_sample):
+    source_sample[0] = 0            # Zero source in x direction
+    source_sample[1] = 0            # Zero source in y direction
+    source_sample[2] = 1000         # Split spin z eigenstates by 1kHz
+
+# Return a solver which uses this function
+simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
+
+# The resultion of the output of the simulation is 500ns
+time_step_coarse = 500e-9
+# The resultion of the integration in the simulation is 100ns
+time_step_fine = 100e-9
+# Run between times of 0ms and 100ms.
+time_end_points = np.asarray([0e-3, 100e-3], np.double)
+
+# The number of samples in the output
+time_index_max = int((time_end_points[1] - time_end_points[0])/time_step_coarse)
+# Define an empty array to write the time to
+time = np.empty(time_index_max, np.double)
+
+# Define the initial state of the system (eigenstate of spin x)
+state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
+# Define an empty array to write the state to
+state = np.empty((time_index_max, 2), np.cdouble)
+# Define an empty array to write the spin to
+spin = np.empty((time_index_max, 3), np.double)
+
+# Define an empty array to write the time evolution operator to
+time_evolution = np.empty((time_index_max, 2, 2), np.cdouble)
+
+# Find the time evolution operator using our settings
+simulator_larmor.get_time_evolution(0, time, time_end_points, time_step_fine, time_step_coarse, time_evolution)
+
+# Chain the time evolution operators together to find the state at each point in time
+simulator_larmor.get_state(state_init, state, time_evolution)
+
+# Calculate the spin at each point in time
+simulator_larmor.get_spin(state, spin)
+
+# Plot result
+plt.figure()
+plt.plot(time, spin)
+plt.legend(["x", "y", "z"])
[…]

### 2020-11-18 spinsim/__init__.py

@@ -1,0 +1,4 @@
+from .spinsim import *
+from . import utilities
+
+__all__ = ["spinsim"]

### 2020-11-18 spinsim/spinsim.py

@@ -1,0 +1,497 @@
+"""
+.. _overview_of_simulation_method:
+
+*********************************
+Overview of the simulation method
+*********************************
+
+The goal here is to evaluate the value of the spin, and thus the quantum state of a 3 level atom in a coarse grained time series with step :math:`\\mathrm{D}t`. The time evolution between time indices is
+
+.. math::
+   \\begin{align*}
+   \\psi(t + \\mathrm{D}t) &= U(t \\rightarrow t + \\mathrm{D}t) \\psi(t)\\\\
+   \\psi(t + \\mathrm{D}t) &= U(t) \\psi(t)
+   \\end{align*}
+
+Each :math:`U(t)` is completely independent of :math:`\\psi(t_0)` or :math:`U(t_0)` for any other time value :math:`t_0`. Therefore each :math:`U(t)` can be calculated independently of each other. This is done in parallel using a GPU kernel in the function :func:`getTimeEvolutionCommutatorFree4Rotating_wave()` (the highest performing variant of this solver). Afterwards, the final result of
+
+.. math::
+   \\psi(t + \\mathrm{D}t) = U(t) \\psi(t)
+
+is calculated sequentially for each :math:`t` in the function :func:`get_state()`. Afterwards, the spin at each time step is calculated in parallel in the function :func:`get_spin()`.
+
+All magnetic signals fed into the integrator in the form of sine waves, with varying amplitude, frequency, phase, and start and end times. This can be used to simulate anything from the bias and dressing fields, to the fake neural pulses, to AC line and DC detuning noise. These sinusoids are superposed and sampled at any time step needed to for the solver. The magnetic signals are written in high level as :class:`test_signal.TestSignal` objects, and are converted to a parametrisation readable to the integrator in the form of :class:`SourceProperties` objects.
+
+*********
+Reference
+*********
+"""
+from . import utilities
+
+from enum import Enum
+import numba as nb
+from numba import cuda
+import math
+
+sqrt2 = math.sqrt(2)
+sqrt3 = math.sqrt(3)
+
+class SpinQuantumNumber(Enum):
+    """
+    The spin quantum number of the system being simulated. 
+
+    Parameters
+    ----------
+    value : `int`
+        Dimension of the hilbert space the states belong to.
+    utility_set : `module`
+        The module for GPU device functions for that particular spin value.
+    label : `string`
+        What to write in the HDF5 archive file.
+    """
+
+    def __init__(self, value, dimension, utility_set, label):
[…]

### 2020-11-18 spinsim/utilities/__init__.py

@@ -1,0 +1,78 @@
+"""
+Some device functions for doing maths and interpolation with :mod:`numba.cuda`.
+"""
+
+import math
+import numpy as np
+import numba as nb
+from numba import cuda
+
+from . import scalar
+from . import spin_half
+from . import spin_one
+
+@cuda.jit(device = True, inline = True)
+def interpolate_source_linear(source, time_sample, time_step_source, source_sample):
+    """
+    Samples the source using linear interpolation.
+
+    Parameters
+    ----------
+    source : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index, time_source_index)
+        The input source of the environment of the spin system. In units of Hz.
+    time_sample : `float`
+        The time to be sampled.
+    time_step_source : `float`
+        The time step between source samples.
+    source_sample : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index)
+        The interpolated value of source.
+    """
+    time_sample = time_sample/time_step_source
+    time_index_source = int(time_sample)
+    time_sample -= time_index_source
+
+    time_index_source_next = time_index_source + 1
+    if time_index_source_next > source.shape[0] - 1:
+        time_index_source_next = source.shape[0] - 1
+
+    for spacial_index in range(source.shape[1]):
+        source_sample[spacial_index] = (time_sample*(source[time_index_source_next, spacial_index] - source[time_index_source, spacial_index]) + source[time_index_source, spacial_index])
+
+@cuda.jit(device = True, inline = True)
+def interpolate_source_cubic(source, time_sample, time_step_source, source_sample):
+    """
+    Samples the source using cubic interpolation.
+
+    Parameters
+    ----------
+    source : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index, time_source_index)
+        The input source of the environment of the spin system. In units of Hz.
+    time_sample : `float`
+        The time to be sampled.
+    time_step_source : `float`
+        The time step between source samples.
+    source_sample : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index)
+        The interpolated value of source.
+    """
+    time_sample = time_sample/time_step_source
+    time_index_source = int(time_sample)
+    time_sample -= time_index_source
+
+    time_index_source_next = time_index_source + 1
+    if time_index_source_next > source.shape[0] - 1:
+        time_index_source_next = source.shape[0] - 1
[…]

### 2020-11-18 spinsim/utilities/scalar.py

@@ -1,0 +1,54 @@
+"""
+Some device functions for doing complex scalar maths with :mod:`numba.cuda`.
+"""
+
+import math
+import numpy as np
+import numba as nb
+from numba import cuda
+
+@cuda.jit(device = True, inline = True)
+def conj(z):
+    """
+    Conjugate of a complex number.
+
+    .. math::
+        \\begin{align*}
+        (a + ib)^* &= a - ib\\\\
+         a, b &\\in \\mathbb{R}
+        \\end{align*}
+
+    Parameters
+    ----------
+    z : :class:`numpy.cdouble`
+        The complex number to take the conjugate of.
+    
+    Returns
+    -------
+    cz : :class:`numpy.cdouble`
+        The conjugate of z.
+    """
+    return (z.real - 1j*z.imag)
+
+@cuda.jit(device = True, inline = True)
+def complex_abs(z):
+    """
+    The absolute value of a complex number.
+
+    .. math::
+        \\begin{align*}
+        |a + ib| &= \\sqrt{a^2 + b^2}\\\\
+         a, b &\\in \\mathbb{R}
+        \\end{align*}
+    
+    Parameters
+    ----------
+    z : :class:`numpy.cdouble`
+        The complex number to take the absolute value of.
+    
+    Returns
+    -------
+    az : :class:`numpy.double`
+        The absolute value of z.
+    """
+    return math.sqrt(z.real**2 + z.imag**2)

### 2020-11-18 spinsim/utilities/spin_half.py

@@ -1,0 +1,525 @@
+"""
+Some device functions for doing spin one maths with :mod:`numba.cuda`.
+"""
+
+import math
+import numpy as np
+import numba as nb
+from numba import cuda
+from . import scalar
+
+# Important constants
+cuda_debug = False
+sqrt2 = math.sqrt(2)
+sqrt3 = math.sqrt(3)
+machine_epsilon = np.finfo(np.float64).eps*1000  # When to decide that vectors are parallel
+# trotter_cutoff = 52
+
+@cuda.jit(device = True, inline = True)
+def matrix_exponential_analytic(source_sample, result):
+    """
+    Calculates a :math:`su(2)` matrix exponential based on its analytic form.
+
+    Assumes the exponent is an imaginary  linear combination of :math:`su(2)`, being,
+
+    .. math::
+        \\begin{align*}
+            A &= -i(x F_x + y F_y + z F_z),
+        \\end{align*}
+    
+    with
+
+    .. math::
+        \\begin{align*}
+            F_x &= \\frac{1}{2}\\begin{pmatrix}
+                0 & 1 \\\\
+                1 & 0
+            \\end{pmatrix},&
+            F_y &= \\frac{1}{2}\\begin{pmatrix}
+                0 & -i \\\\
+                i &  0
+            \\end{pmatrix},&
+            F_z &= \\frac{1}{2}\\begin{pmatrix}
+                1 &  0  \\\\
+                0 & -1 
+            \\end{pmatrix}
+        \\end{align*}
+
+    Then the exponential can be calculated as
+
+    .. math::
+        \\begin{align*}
+            \\exp(A) &= \\exp(-ix F_x - iy F_y - iz F_z)\\\\
+            &= \\begin{pmatrix}
+                \\cos(\\frac{r}{2}) - i\\frac{z}{r}\\sin(\\frac{r}{2}) & -\\frac{y + ix}{r}\\sin(\\frac{r}{2})\\\\
+                 \\frac{y - ix}{r}\\sin(\\frac{r}{2}) & \\cos(\\frac{r}{2}) + i\\frac{z}{r}\\sin(\\frac{r}{2})
+            \\end{pmatrix}
+        \\end{align*}
+
+    with :math:`r = \\sqrt{x^2 + y^2 + z^2}`.
+
+    Parameters
[…]

### 2020-11-18 spinsim/utilities/spin_one.py

@@ -1,0 +1,910 @@
+"""
+Some device functions for doing spin one maths with :mod:`numba.cuda`.
+"""
+
+import math
+import numpy as np
+import numba as nb
+from numba import cuda
+from . import scalar
+
+# Important constants
+cuda_debug = False
+sqrt2 = math.sqrt(2)
+sqrt3 = math.sqrt(3)
+machine_epsilon = np.finfo(np.float64).eps*1000  # When to decide that vectors are parallel
+# trotter_cutoff = 52
+
+@cuda.jit(device = True, inline = True)
+def matrix_exponential_lie_trotter(source_sample, result, trotter_cutoff):
+    """
+    Calculates a matrix exponential based on the Lie Product Formula,
+
+    .. math::
+        \\exp(A + B) = \\lim_{c \\to \\infty} \\left(\\exp\\left(\\frac{1}{c}A\\right) \\exp\\left(\\frac{1}{c}B\\right)\\right)^c.
+
+    Assumes the exponent is an imaginary  linear combination of a subspace of :math:`su(3)`, being,
+
+    .. math::
+        \\begin{align*}
+            A &= -i(x F_x + y F_y + z F_z + q F_q),
+        \\end{align*}
+    
+    with
+
+    .. math::
+        \\begin{align*}
+            F_x &= \\frac{1}{\\sqrt{2}}\\begin{pmatrix}
+                0 & 1 & 0 \\\\
+                1 & 0 & 1 \\\\
+                0 & 1 & 0
+            \\end{pmatrix},&
+            F_y &= \\frac{1}{\\sqrt{2}}\\begin{pmatrix}
+                0 & -i &  0 \\\\
+                i &  0 & -i \\\\
+                0 &  i &  0
+            \\end{pmatrix},\\\\
+            F_z &= \\begin{pmatrix}
+                1 & 0 &  0 \\\\
+                0 & 0 &  0 \\\\
+                0 & 0 & -1
+            \\end{pmatrix},&
+            F_q &= \\frac{1}{3}\\begin{pmatrix}
+                1 &  0 & 0 \\\\
+                0 & -2 & 0 \\\\
+                0 &  0 & 1
+            \\end{pmatrix}
[…]

### 2020-11-18 example.py
Built package for first time

@@ -1,7 +1,7 @@
 import colorama         # Colourful terminal
 colorama.init()
 
-import spinsim.spinsim as spinsim
+import spinsim
 
 import numpy as np
 import matplotlib.pyplot as plt
@@ -76,7 +76,7 @@ import math
 
 def get_source_rabi(time_sample, simulation_index, source_sample):
     # Dress atoms from the x direction, Rabi flopping at 1kHz
-    source_sample[0] = 2000*np.cos(math.tau*20e3*simulation_index*time_sample)
+    source_sample[0] = 2000*math.cos(math.tau*20e3*simulation_index*time_sample)
     source_sample[1] = 0                        # Zero source in y direction
     source_sample[2] = 20e3*simulation_index    # Split spin z eigenstates by 700kHz
     source_sample[3] = 0                        # Zero quadratic shift, found in spin one systems

### 2020-11-18 docs/source/conf.py
Tutorial updated to match new architecture.

@@ -102,4 +102,4 @@ intersphinx_mapping = {
     'matplotlib': ('http://matplotlib.sourceforge.net/', None)
     }
 
-add_module_names = False
+# add_module_names = False

### 2020-11-18 example.py

@@ -16,7 +16,7 @@ Example 1: Spin half Larmor precession
 ======================================
 """
 # Define a numba.cuda compatible source sampling function
-def get_source_larmor(time_sample, simulation_index, source_sample):
+def get_source_larmor(time_sample, source_modifier, source_sample):
     source_sample[0] = 0            # Zero source in x direction
     source_sample[1] = 0            # Zero source in y direction
     source_sample[2] = 1000         # Split spin z eigenstates by 1kHz
@@ -74,11 +74,11 @@ Example 2: Spin one Rabi flopping
 # The math, or cmath library must be used over numpy for the source function to be cuda compilable
 import math
 
-def get_source_rabi(time_sample, simulation_index, source_sample):
+def get_source_rabi(time_sample, source_modifier, source_sample):
     # Dress atoms from the x direction, Rabi flopping at 1kHz
-    source_sample[0] = 2000*math.cos(math.tau*20e3*simulation_index*time_sample)
+    source_sample[0] = 2000*math.cos(math.tau*20e3*source_modifier*time_sample)
     source_sample[1] = 0                        # Zero source in y direction
-    source_sample[2] = 20e3*simulation_index    # Split spin z eigenstates by 700kHz
+    source_sample[2] = 20e3*source_modifier     # Split spin z eigenstates by 700kHz
     source_sample[3] = 0                        # Zero quadratic shift, found in spin one systems
 
 # Return a solver which uses this function

### 2020-11-18 spinsim/__init__.py

@@ -1,4 +1,498 @@
-from .spinsim import *
+"""
+.. _overview_of_simulation_method:
+
+*********************************
+Overview of the simulation method
+*********************************
+
+The goal here is to evaluate the value of the spin, and thus the quantum state of a 3 level atom in a coarse grained time series with step :math:`\\mathrm{D}t`. The time evolution between time indices is
+
+.. math::
+   \\begin{align*}
+   \\psi(t + \\mathrm{D}t) &= U(t \\rightarrow t + \\mathrm{D}t) \\psi(t)\\\\
+   \\psi(t + \\mathrm{D}t) &= U(t) \\psi(t)
+   \\end{align*}
+
+Each :math:`U(t)` is completely independent of :math:`\\psi(t_0)` or :math:`U(t_0)` for any other time value :math:`t_0`. Therefore each :math:`U(t)` can be calculated independently of each other. This is done in parallel using a GPU kernel in the function :func:`getTimeEvolutionCommutatorFree4Rotating_wave()` (the highest performing variant of this solver). Afterwards, the final result of
+
+.. math::
+   \\psi(t + \\mathrm{D}t) = U(t) \\psi(t)
+
+is calculated sequentially for each :math:`t` in the function :func:`get_state()`. Afterwards, the spin at each time step is calculated in parallel in the function :func:`get_spin()`.
+
+All magnetic signals fed into the integrator in the form of sine waves, with varying amplitude, frequency, phase, and start and end times. This can be used to simulate anything from the bias and dressing fields, to the fake neural pulses, to AC line and DC detuning noise. These sinusoids are superposed and sampled at any time step needed to for the solver. The magnetic signals are written in high level as :class:`test_signal.TestSignal` objects, and are converted to a parametrisation readable to the integrator in the form of :class:`SourceProperties` objects.
+
+*********
+Reference
+*********
+"""
+
 from . import utilities
 
-__all__ = ["spinsim"]
+from enum import Enum
+import numba as nb
+from numba import cuda
+import math
+
+sqrt2 = math.sqrt(2)
+sqrt3 = math.sqrt(3)
+
+class SpinQuantumNumber(Enum):
+    """
+    The spin quantum number of the system being simulated. 
+
+    Parameters
+    ----------
+    value : `int`
+        Dimension of the hilbert space the states belong to.
+    utility_set : `module`
+        The module for GPU device functions for that particular spin value.
+    label : `string`
+        What to write in the HDF5 archive file.
+    """
[…]

### 2020-11-18 spinsim/spinsim.py

@@ -1,497 +1,0 @@
-"""
-.. _overview_of_simulation_method:
-
-*********************************
-Overview of the simulation method
-*********************************
-
-The goal here is to evaluate the value of the spin, and thus the quantum state of a 3 level atom in a coarse grained time series with step :math:`\\mathrm{D}t`. The time evolution between time indices is
-
-.. math::
-   \\begin{align*}
-   \\psi(t + \\mathrm{D}t) &= U(t \\rightarrow t + \\mathrm{D}t) \\psi(t)\\\\
-   \\psi(t + \\mathrm{D}t) &= U(t) \\psi(t)
-   \\end{align*}
-
-Each :math:`U(t)` is completely independent of :math:`\\psi(t_0)` or :math:`U(t_0)` for any other time value :math:`t_0`. Therefore each :math:`U(t)` can be calculated independently of each other. This is done in parallel using a GPU kernel in the function :func:`getTimeEvolutionCommutatorFree4Rotating_wave()` (the highest performing variant of this solver). Afterwards, the final result of
-
-.. math::
-   \\psi(t + \\mathrm{D}t) = U(t) \\psi(t)
-
-is calculated sequentially for each :math:`t` in the function :func:`get_state()`. Afterwards, the spin at each time step is calculated in parallel in the function :func:`get_spin()`.
-
-All magnetic signals fed into the integrator in the form of sine waves, with varying amplitude, frequency, phase, and start and end times. This can be used to simulate anything from the bias and dressing fields, to the fake neural pulses, to AC line and DC detuning noise. These sinusoids are superposed and sampled at any time step needed to for the solver. The magnetic signals are written in high level as :class:`test_signal.TestSignal` objects, and are converted to a parametrisation readable to the integrator in the form of :class:`SourceProperties` objects.
-
-*********
-Reference
-*********
-"""
-from . import utilities
-
-from enum import Enum
-import numba as nb
-from numba import cuda
-import math
-
-sqrt2 = math.sqrt(2)
-sqrt3 = math.sqrt(3)
-
-class SpinQuantumNumber(Enum):
-    """
-    The spin quantum number of the system being simulated. 
-
-    Parameters
-    ----------
-    value : `int`
-        Dimension of the hilbert space the states belong to.
-    utility_set : `module`
-        The module for GPU device functions for that particular spin value.
-    label : `string`
-        What to write in the HDF5 archive file.
-    """
-
-    def __init__(self, value, dimension, utility_set, label):
[…]

### 2020-11-19 docs/source/conf.py
Updated documentation and version number

@@ -35,11 +35,11 @@ sys.path.append(os.path.abspath("../../../"))
 # -- Project information -----------------------------------------------------
 
 project = 'spinsim'
-copyright = '2020, Alexander Tritt'
+copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.1'
+release = '0.1.1'
 
 
 # -- General configuration ---------------------------------------------------
@@ -48,11 +48,12 @@ release = '0.1'
 # extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
 # ones.
 extensions = [
-    "sphinx.ext.autodoc",   # Generate documentation from code
-    "sphinx.ext.napoleon",  # Use numpy standard formatting
-    "sphinx_rtd_theme",     # Documentation theme
-    "numbadoc",             # Is able to document numba
-    "sphinx.ext.intersphinx"
+    "sphinx.ext.autodoc",       # Generate documentation from code
+    "sphinx.ext.napoleon",      # Use numpy standard formatting
+    "sphinx_rtd_theme",         # Documentation theme
+    "numbadoc",                 # Is able to document numba
+    "sphinx.ext.intersphinx",   # Link to other documentation
+    "sphinxcontrib.bibtex"      # Bibtex support
 ]
 
 autoclass_content = 'both'

### 2020-11-19 example.py

@@ -1,131 +1,37 @@
-import colorama         # Colourful terminal
-colorama.init()
-
 import spinsim
-
 import numpy as np
 import matplotlib.pyplot as plt
-
-"""
-Note: please see documentation for a full explanation of the source code.
-"""
-
-"""
-======================================
-Example 1: Spin half Larmor precession
-======================================
-"""
-# Define a numba.cuda compatible source sampling function
-def get_source_larmor(time_sample, source_modifier, source_sample):
-    source_sample[0] = 0            # Zero source in x direction
-    source_sample[1] = 0            # Zero source in y direction
-    source_sample[2] = 1000         # Split spin z eigenstates by 1kHz
-
-# Return a solver which uses this function
-simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
-
-# The resultion of the output of the simulation is 500ns
-time_step_coarse = 500e-9
-# The resultion of the integration in the simulation is 100ns
-time_step_fine = 100e-9
-# Run between times of 0ms and 100ms.
-time_end_points = np.asarray([0e-3, 100e-3], np.double)
-
-# The number of samples in the output
-time_index_max = int((time_end_points[1] - time_end_points[0])/time_step_coarse)
-# Define an empty array to write the time to
-time = np.empty(time_index_max, np.double)
-
-# Define the initial state of the system (eigenstate of spin x)
-state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
-# Define an empty array to write the state to
-state = np.empty((time_index_max, 2), np.cdouble)
-# Define an empty array to write the spin to
-spin = np.empty((time_index_max, 3), np.double)
-
-# Define an empty array to write the time evolution operator to
-time_evolution = np.empty((time_index_max, 2, 2), np.cdouble)
-
-# Find the time evolution operator using our settings
-simulator_larmor.get_time_evolution(0, time, time_end_points, time_step_fine, time_step_coarse, time_evolution)
-
-# Chain the time evolution operators together to find the state at each point in time
-simulator_larmor.get_state(state_init, state, time_evolution)
-
-# Calculate the spin at each point in time
-simulator_larmor.get_spin(state, spin)
-
-# Plot result
-plt.figure()
-plt.plot(time, spin)
-plt.legend(["x", "y", "z"])
-plt.xlim(0e-3, 2e-3)
[…]

### 2020-11-20 example.py
Added some information about the package

@@ -2,63 +2,37 @@ import spinsim
 import numpy as np
 import matplotlib.pyplot as plt
 import math
-from numba import cuda
 
-def get_source_rabi(time_sample, source_modifier, source_sample):
-   # Dress atoms from the x direction, Rabi flopping at 1kHz
-   source_sample[0] = 2000*math.cos(math.tau*20e3*source_modifier*time_sample)
-   source_sample[1] = 0                        # Zero source in y direction
-   source_sample[2] = 20e3*source_modifier     # Split spin z eigenstates by 700kHz
-   source_sample[3] = 0                        # Zero quadratic shift, found in spin one systems
+def get_source(time_sample, source_modifier, source_sample):
+   source_sample[0] = 2000*math.exp(-((time_sample - 0.05)/0.01)**2)*math.cos(math.tau*700e3*time_sample)
+   source_sample[1] = 0
+   source_sample[2] = 700e3
 
-simulator_rabi = spinsim.Simulator(get_source_rabi, spinsim.SpinQuantumNumber.ONE)
+simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
 
 time_step_coarse = 500e-9
 time_step_fine = 100e-9
 time_end_points = np.asarray([0e-3, 100e-3], np.double)
+
 time_index_max = int((time_end_points[1] - time_end_points[0])/time_step_coarse)
+time = np.empty(time_index_max, np.double)
 
-state_init = np.asarray([1, 0, 0], np.cdouble)
-state = np.empty((time_index_max, 3), np.cdouble)
+state_init = np.asarray([1, 0], np.cdouble)
+state = np.empty((time_index_max, 2), np.cdouble)
+spin = np.empty((time_index_max, 3), np.double)
+time_evolution = np.empty((time_index_max, 2, 2), np.cdouble)
 
-time_evolution = cuda.device_array((time_index_max, 3, 3), np.cdouble)
-time = cuda.device_array(time_index_max, np.double)
-spin = cuda.device_array((time_index_max, 3), np.double)
-
-simulator_rabi.get_time_evolution(1, time, cuda.to_device(time_end_points), time_step_fine, time_step_coarse, time_evolution)
-time = time.copy_to_host()
-time_evolution = time_evolution.copy_to_host()
[…]

### 2020-11-20 spinsim/__init__.py

@@ -1,30 +1,5 @@
 """
-.. _overview_of_simulation_method:
 
-*********************************
-Overview of the simulation method
-*********************************
-
-The goal here is to evaluate the value of the spin, and thus the quantum state of a 3 level atom in a coarse grained time series with step :math:`\\mathrm{D}t`. The time evolution between time indices is
-
-.. math::
-   \\begin{align*}
-   \\psi(t + \\mathrm{D}t) &= U(t \\rightarrow t + \\mathrm{D}t) \\psi(t)\\\\
-   \\psi(t + \\mathrm{D}t) &= U(t) \\psi(t)
-   \\end{align*}
-
-Each :math:`U(t)` is completely independent of :math:`\\psi(t_0)` or :math:`U(t_0)` for any other time value :math:`t_0`. Therefore each :math:`U(t)` can be calculated independently of each other. This is done in parallel using a GPU kernel in the function :func:`getTimeEvolutionCommutatorFree4Rotating_wave()` (the highest performing variant of this solver). Afterwards, the final result of
-
-.. math::
-   \\psi(t + \\mathrm{D}t) = U(t) \\psi(t)
-
-is calculated sequentially for each :math:`t` in the function :func:`get_state()`. Afterwards, the spin at each time step is calculated in parallel in the function :func:`get_spin()`.
-
-All magnetic signals fed into the integrator in the form of sine waves, with varying amplitude, frequency, phase, and start and end times. This can be used to simulate anything from the bias and dressing fields, to the fake neural pulses, to AC line and DC detuning noise. These sinusoids are superposed and sampled at any time step needed to for the solver. The magnetic signals are written in high level as :class:`test_signal.TestSignal` objects, and are converted to a parametrisation readable to the integrator in the form of :class:`SourceProperties` objects.
-
-*********
-Reference
-*********
 """
 
 from . import utilities

### 2020-11-23 article/article.tex
0.1.3, hides all GPU weird stuff from user

@@
 \section*{Paper Authors}
-1. Tritt, Alexander;\\
-2. Turner, Lincoln David;\\
-3. Saunderson, James;\\
-4. Morris, Joshua;\\
-5. Hochstetter, Joel;\\
+1. Tritt, Alex;\\
+2. Morris, Joshua;\\
+3. Hochstetter, Joel;\\
+4. Anderson, R. P.;\\
+5. Saunderson, James;\\
+6. Turner, L. D.;\\
 
@@
 \section*{Paper Author Roles and Affiliations}
-1. PhD student, School of physics and astronomy, Monash University\\
-2. Supervisor, School of physics and astronomy, Monash University\\
-3. Supervisor, Department of electrical and computer systems engineering, Monash University\\
-4. Original writer of AtomicPy for spin half systems\\
-5. Original writer of the spin one extension to AtomicPy\\
+1. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Primary author of the released packages.\\
+2. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Present address: Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
+	Author of first version of code.\\
+3. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
+	Optimization and extension to spin one of first version of code.\\
+4. School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
+	Original conception of first version of code.\\
+5. Department of Electrical and Computer Systems Engineering, Monash University, Victoria 3800, Australia.\\
+	Advice on numerical analysis.\\
+6. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Original conception of released version of algorithm.
 

### 2020-11-23 docs/source/conf.py

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.1.1'
+release = '0.1.3'
 
 
 # -- General configuration ---------------------------------------------------

### 2020-11-23 example.py

@@ -1,39 +1,96 @@
+# import spinsim
+# import numpy as np
+# import matplotlib.pyplot as plt
+
+# def get_source_larmor(time_sample, source_modifier, source_sample):
+#    source_sample[0] = 0            # Zero source in x direction
+#    source_sample[1] = 0            # Zero source in y direction
+#    source_sample[2] = 1000         # Split spin z eigenstates by 1kHz
+
+# simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
+
+# state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
+
+# state, time = simulator_larmor.get_state(0, 0e-3, 100e-3, 100e-9, 500e-9, state_init)
+# spin = simulator_larmor.get_spin(state)
+
+# plt.figure()
+# plt.plot(time, spin)
+# plt.legend(["x", "y", "z"])
+# plt.xlim(0e-3, 2e-3)
+# plt.xlabel("time (s)")
+# plt.ylabel("spin expectation (hbar)")
+# plt.title("Spin projection for Larmor precession")
+# plt.show()
+
 import spinsim
 import numpy as np
 import matplotlib.pyplot as plt
 import math
 
-def get_source(time_sample, source_modifier, source_sample):
-   source_sample[0] = 2000*math.exp(-((time_sample - 0.05)/0.01)**2)*math.cos(math.tau*700e3*time_sample)
-   source_sample[1] = 0
-   source_sample[2] = 700e3
+def get_source_rabi(time_sample, source_modifier, source_sample):
+   # Dress atoms from the x direction, Rabi flopping at 1kHz
+   source_sample[0] = 2000*math.cos(math.tau*20e3*source_modifier*time_sample)
+   source_sample[1] = 0                        # Zero source in y direction
+   source_sample[2] = 20e3*source_modifier     # Split spin z eigenstates by 700kHz
+   source_sample[3] = 0                        # Zero quadratic shift, found in spin one systems
 
-simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
+simulator_rabi = spinsim.Simulator(get_source_rabi, spinsim.SpinQuantumNumber.ONE)
 
-time_step_coarse = 500e-9
[…]

### 2020-11-23 spinsim/__init__.py

@@ -5,6 +5,7 @@
 from . import utilities
 
 from enum import Enum
+import numpy as np
 import numba as nb
 from numba import cuda
 import math
@@ -100,7 +101,7 @@ class ExponentiationMethod(Enum):
     # """
 
 class Simulator:
-    def __init__(self, get_source, spin_quantum_number, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF_4, exponentiation_method = ExponentiationMethod.LIE_TROTTER, trotter_cutoff = 28, max_registers = 63, threads_per_block = 64):
+    def __init__(self, get_source, spin_quantum_number, exponentiation_method = None, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF_4, trotter_cutoff = 28, max_registers = 63, threads_per_block = 64):
         """
         Parameters
         ----------
@@ -118,6 +119,7 @@ class Simulator:
         """
 
         self.threads_per_block = threads_per_block
+        self.spin_quantum_number = spin_quantum_number
 
         self.get_time_evolution_raw = None
         try:
@@ -134,7 +136,7 @@ class Simulator:
             print("\033[31mspinsim error: numba.cuda could not jit get_source function into a cuda device function.\033[0m\n")
             raise
 
-    def compile_time_evolver(self, get_source, spin_quantum_number, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF_4, exponentiation_method = ExponentiationMethod.LIE_TROTTER, trotter_cutoff = 28, max_registers = 63):
+    def compile_time_evolver(self, get_source, spin_quantum_number, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF_4, exponentiation_method = None, trotter_cutoff = 28, max_registers = 63):
         """
         Parameters
         ----------
@@ -153,6 +155,12 @@ class Simulator:
         dimension = spin_quantum_number.dimension
         lie_dimension = dimension + 1
         utility_set = spin_quantum_number.utility_set
+
+        if not exponentiation_method:
+            if spin_quantum_number == SpinQuantumNumber.ONE:
+                exponentiation_method = ExponentiationMethod.LIE_TROTTER
+            elif spin_quantum_number == SpinQuantumNumber.HALF:
+                exponentiation_method = ExponentiationMethod.ANALYTIC
 
         if integration_method == IntegrationMethod.MAGNUS_CF_4:
             sample_index_max = 3
@@ -382,25 +390,49 @@ class Simulator:
 
[…]

### 2020-11-24 docs/source/conf.py
Benchmark section added

@@ -57,6 +57,7 @@ extensions = [
 ]
 
 autoclass_content = 'both'
+numfig = True
 
 # Napoleon settings
 napoleon_google_docstring = False

### 2020-11-27 article/article.tex
readme started
readme
Potential uses and limitations

@@
 \section*{Title}
-Spinsim: a GPU optimised solver of spin one and half quantum systems
+spinsim: a GPU optimised solver of spin one and half quantum systems
 
@@
 
+1. Alex Tritt\\
+	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Primary author of the released packages.\\
+2. Joshua Morris\\
+	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Present address: Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
+	Author of first version of code.\\
+3. Joel Hockstetter\\
+	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
+	Optimization and extension to spin one of first version of code.\\
+4. Russell P. Anderson\\
+	School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
+	Original conception of first version of code.\\
+5. James Saunderson\\
+	Department of Electrical and Computer Systems Engineering, Monash University, Victoria 3800, Australia.\\
+	Advice on numerical analysis.\\
+6. Lincoln D. Turner\\
+	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
+	Original conception of released version of algorithm.
+
 \textcolor{blue}{Please list anyone who helped to create the software (who may also not be an author of this paper), including their roles and affiliations.}
+
+\section*{Software location:}
+
+{\bf Archive}
+
+\begin{description}[noitemsep,topsep=0pt]
+	\item[Name:] Monash Bridges
+	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
+	\item[Licence:] BSD 3 Clause
+	\item[Publisher:]  Alex Tritt
+	\item[Version published:] 1.0.0
+	\item[Date published:] \textcolor{blue}{dd/mm/yy}
+\end{description}
+
+{\bf Code repository}
+
+\begin{description}[noitemsep,topsep=0pt]
+	\item[Name:] GitHub
+	\item[Persistent identifier:] https://github.com/alexander-tritt-monash/spinsim
+	\item[Licence:] BSD 3 Clause
+	\item[Date published:] 18/11/20
+\end{description}
+
+\section*{Language}
+
+English.
 
@@
 
+The authors declare that they have no competing interests.
+
 \textcolor{blue}{If any of the authors have any competing interests then these must be declared.

### 2020-11-30 docs/source/conf.py
Correct dependencies in toml

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.1.3'
+release = '0.1.5'
 
 
 # -- General configuration ---------------------------------------------------

### 2020-11-30 example.py

@@ -1,27 +1,27 @@
-# import spinsim
-# import numpy as np
-# import matplotlib.pyplot as plt
+import spinsim
+import numpy as np
+import matplotlib.pyplot as plt
 
-# def get_source_larmor(time_sample, source_modifier, source_sample):
-#    source_sample[0] = 0            # Zero source in x direction
-#    source_sample[1] = 0            # Zero source in y direction
-#    source_sample[2] = 1000         # Split spin z eigenstates by 1kHz
+def get_source_larmor(time_sample, source_modifier, source_sample):
+   source_sample[0] = 0            # Zero source in x direction
+   source_sample[1] = 0            # Zero source in y direction
+   source_sample[2] = 1000         # Split spin z eigenstates by 1kHz
 
-# simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
+simulator_larmor = spinsim.Simulator(get_source_larmor, spinsim.SpinQuantumNumber.HALF)
 
-# state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
+state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
 
-# state, time = simulator_larmor.get_state(0, 0e-3, 100e-3, 100e-9, 500e-9, state_init)
-# spin = simulator_larmor.get_spin(state)
+state, time = simulator_larmor.get_state(0, 0e-3, 100e-3, 100e-9, 500e-9, state_init)
+spin = simulator_larmor.get_spin(state)
 
-# plt.figure()
-# plt.plot(time, spin)
-# plt.legend(["x", "y", "z"])
-# plt.xlim(0e-3, 2e-3)
-# plt.xlabel("time (s)")
-# plt.ylabel("spin expectation (hbar)")
-# plt.title("Spin projection for Larmor precession")
-# plt.show()
+plt.figure()
+plt.plot(time, spin)
+plt.legend(["x", "y", "z"])
+plt.xlim(0e-3, 2e-3)
+plt.xlabel("time (s)")
+plt.ylabel("spin expectation (hbar)")
+plt.title("Spin projection for Larmor precession")
+plt.show()
 
 import spinsim
 import numpy as np
@@ -62,203 +62,3 @@ plt.xlabel("time (s)")
 plt.ylabel("spin expectation (hbar)")
 plt.title("Spin projection for Rabi flopping")
 plt.show()
-
-
-
[…]

### 2020-12-02 example.py
Added CPU jitted option

@@ -1,3 +1,6 @@
+import colorama         # Colourful terminal
+colorama.init()
+
 import spinsim
 import numpy as np
 import matplotlib.pyplot as plt

### 2020-12-02 spinsim/__init__.py

@@ -2,7 +2,7 @@
 
 """
 
-from . import utilities
+# from . import utilities
 
 from enum import Enum
 import numpy as np
@@ -21,25 +21,22 @@ class SpinQuantumNumber(Enum):
     ----------
     value : `int`
         Dimension of the hilbert space the states belong to.
-    utility_set : `module`
-        The module for GPU device functions for that particular spin value.
     label : `string`
         What to write in the HDF5 archive file.
     """
 
-    def __init__(self, value, dimension, utility_set, label):
+    def __init__(self, value, dimension, label):
         super().__init__()
         self._value_ = value
         self.dimension = dimension
-        self.utility_set = utility_set
         self.label = label
 
-    HALF = (1/2, 2, utilities.spin_half, "half")
+    HALF = (1/2, 2, "half")
     """
     For two level systems.
     """
 
-    ONE = (1, 3, utilities.spin_one, "one")
+    ONE = (1, 3, "one")
     """
     For three level systems.
     """
@@ -100,8 +97,51 @@ class ExponentiationMethod(Enum):
     # Taylor expansion.
     # """
 
+class Device(Enum):
+    def __init__(self, value, index):
+        super().__init__()
+        self._value_ = value
+        self.index = index
+
+        if value == "cpu":
+            def jit_host(template, max_registers):
+                def jit_host(func):
+                    return nb.njit(template, parallel = True)(func)
+                return jit_host
+            self.jit_host = jit_host
+
+            def jit_device(func):
+                return nb.njit()(func)
+            self.jit_device = jit_device
+
+            def jit_device_template(template):
+                def jit_device_template(func):
+                    return nb.njit(template)(func)
+                return jit_device_template
+            self.jit_device_template = jit_device_template
+
+        elif value == "cuda":
+            def jit_host(template, max_registers):
+                def jit_host(func):
+                    return cuda.jit(template, debug = False,  max_registers = max_registers)(func)
+                return jit_host
+            self.jit_host = jit_host
+
+            def jit_device(func):
+                return cuda.jit(device = True, inline = True)(func)
+            self.jit_device = jit_device
+
+            def jit_device_template(template):
+                def jit_device_template(func):
+                    return cuda.jit(template, device = True, inline = True)(func)
+                return jit_device_template
[…]

### 2020-12-02 spinsim/utilities_old/__init__.py

@@ -11,7 +11,7 @@ from . import scalar
 from . import spin_half
 from . import spin_one
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def interpolate_source_linear(source, time_sample, time_step_source, source_sample):
     """
     Samples the source using linear interpolation.
@@ -38,7 +38,7 @@ def interpolate_source_linear(source, time_sample, time_step_source, source_samp
     for spacial_index in range(source.shape[1]):
         source_sample[spacial_index] = (time_sample*(source[time_index_source_next, spacial_index] - source[time_index_source, spacial_index]) + source[time_index_source, spacial_index])
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def interpolate_source_cubic(source, time_sample, time_step_source, source_sample):
     """
     Samples the source using cubic interpolation.

### 2020-12-02 spinsim/utilities_old/scalar.py

@@ -7,7 +7,7 @@ import numpy as np
 import numba as nb
 from numba import cuda
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def conj(z):
     """
     Conjugate of a complex number.
@@ -30,7 +30,7 @@ def conj(z):
     """
     return (z.real - 1j*z.imag)
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def complex_abs(z):
     """
     The absolute value of a complex number.

### 2020-12-02 spinsim/utilities_old/spin_half.py

@@ -15,7 +15,7 @@ sqrt3 = math.sqrt(3)
 machine_epsilon = np.finfo(np.float64).eps*1000  # When to decide that vectors are parallel
 # trotter_cutoff = 52
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def matrix_exponential_analytic(source_sample, result):
     """
     Calculates a :math:`su(2)` matrix exponential based on its analytic form.
@@ -90,7 +90,7 @@ def matrix_exponential_analytic(source_sample, result):
         result[0, 1] = 0
         result[1, 1] = 1
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def matrix_exponential_lie_trotter(source_sample, result, trotter_cutoff):
     """
     Calculates a matrix exponential based on the Lie Product Formula,
@@ -200,7 +200,7 @@ def matrix_exponential_lie_trotter(source_sample, result, trotter_cutoff):
         matrix_multiply(result, result, temporary)
         matrix_multiply(temporary, temporary, result)
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def matrix_exponential_trotter(exponent, result, trotter_cutoff):
     """
     Calculates a matrix exponential based on the Lie Product Formula,
@@ -314,7 +314,7 @@ def matrix_exponential_trotter(exponent, result, trotter_cutoff):
         matrix_multiply(result, result, exponent)
         matrix_multiply(exponent, exponent, result)
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def matrix_exponential_taylor(exponent, result, cutoff):
     """
     Calculate a matrix exponential using a Taylor series. The matrix being exponentiated is complex, and of any dimension.
@@ -361,7 +361,7 @@ def matrix_exponential_taylor(exponent, result, cutoff):
             for y_index in nb.prange(2):
                 result[y_index, x_index] += T[y_index, x_index]
 
-@cuda.jit(device = True, inline = True)
+#@cuda.jit(device = True, inline = True)
 def norm2(z):
     """
     The 2 norm of a complex vector.
@@ -380,7 +380,7 @@ def norm2(z):
     """
     return math.sqrt(z[0].real**2 + z[0].imag**2 + z[1].real**2 + z[1].imag**2)
 
[…]

### 2020-12-03 spinsim/__init__.py
Added multiprocessing single core, and python mode

@@ -8,6 +8,7 @@ from enum import Enum
 import numpy as np
 import numba as nb
 from numba import cuda
+from numba import roc
 import math
 
 sqrt2 = math.sqrt(2)
@@ -103,7 +104,41 @@ class Device(Enum):
         self._value_ = value
         self.index = index
 
-        if value == "cpu":
+        if value == "python":
+            def jit_host(template, max_registers):
+                def jit_host(func):
+                    return func
+                return jit_host
+            self.jit_host = jit_host
+
+            def jit_device(func):
+                return func
+            self.jit_device = jit_device
+
+            def jit_device_template(template):
+                def jit_device_template(func):
+                    return func
+                return jit_device_template
+            self.jit_device_template = jit_device_template
+
+        elif value == "cpu_single":
+            def jit_host(template, max_registers):
+                def jit_host(func):
+                    return nb.njit(template)(func)
+                return jit_host
+            self.jit_host = jit_host
+
+            def jit_device(func):
+                return nb.njit()(func)
+            self.jit_device = jit_device
+
+            def jit_device_template(template):
+                def jit_device_template(func):
+                    return nb.njit(template)(func)
+                return jit_device_template
+            self.jit_device_template = jit_device_template
+
+        elif value == "cpu":
             def jit_host(template, max_registers):
                 def jit_host(func):
                     return nb.njit(template, parallel = True)(func)
@@ -137,11 +172,31 @@ class Device(Enum):
                 return jit_device_template
             self.jit_device_template = jit_device_template
 
+        elif value == "roc":
+            def jit_host(template, max_registers):
+                def jit_host(func):
+                    return roc.jit(template)(func)
+                return jit_host
+            self.jit_host = jit_host
+
+            def jit_device(func):
+                return roc.jit(device = True)(func)
+            self.jit_device = jit_device
+
+            def jit_device_template(template):
+                def jit_device_template(func):
+                    return roc.jit(template, device = True)(func)
+                return jit_device_template
+            self.jit_device_template = jit_device_template
+
+    PYTHON = ("python", 0)
+    CPU_SINGLE = ("cpu_single", 0)
     CPU = ("cpu", 0)
[…]

### 2020-12-04 gaussian_example.py
Changed bounds, forgot to push earlier

@@ -16,7 +16,7 @@ def cumulative_gaussian(t):
 
 plt.figure()
 
-time = np.arange(-5.0, 5.0, 2.0)
+time = np.arange(-5.0, 5.1, 2.0)
 state_analytic = np.asarray([[math.cos(0.5*math.pi*cumulative_gaussian(t)), -1j*math.sin(0.5*math.pi*cumulative_gaussian(t))] for t in time], dtype = np.complex128)
 
 simulator = spinsim.Simulator(gaussian_pulse, spinsim.SpinQuantumNumber.HALF)
@@ -38,7 +38,7 @@ time_steps = np.asarray([0.01, 0.05, 0.1, 0.25, 0.5, 1.0, 2.0])
 number_of_steps = 10 / time_steps
 plot_start_index = 4
 for simulation_index, time_step in enumerate(time_steps):
-    state_simulated, time = simulator.get_state(0.0, -5.0, 5.0, time_step, 2.0, np.asarray([1, 0], np.complex128))
+    state_simulated, time = simulator.get_state(0.0, -5.0, 7.0, time_step, 2.0, np.asarray([1, 0], np.complex128))
     spin_simulated = simulator.get_spin(state_simulated)
 
     error += [np.sum(np.abs(state_simulated - state_analytic))/5]

### 2020-12-04 gaussian_example.py
spelling mistake

@@ -55,7 +55,7 @@ for simulation_index, time_step in enumerate(time_steps):
         ]
 
 plt.legend(legend, loc = "lower left")
-plt.xlabel("Time (standard devaitions)")
+plt.xlabel("Time (standard deviations)")
 plt.ylabel("Spin")
 plt.title("{}\nGaussian pulse at various numbers of steps".format(time_now_string))
 plt.savefig("gaussian_pulse.png")

### 2020-12-04 docs/source/conf.py
Update of documentation (Simulator and enums)

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.1.5'
+release = '0.1.6'
 
 
 # -- General configuration ---------------------------------------------------

### 2020-12-04 spinsim/__init__.py

@@ -16,14 +16,16 @@ sqrt3 = math.sqrt(3)
 
 class SpinQuantumNumber(Enum):
     """
-    The spin quantum number of the system being simulated. 
+    Options for the spin quantum number of a system.
 
     Parameters
     ----------
-    value : `int`
-        Dimension of the hilbert space the states belong to.
-    label : `string`
-        What to write in the HDF5 archive file.
+    value : :obj:`float`
+        The numerical value of the spin quantum number.
+    dimension : :obj:`int`
+        Dimension of the hilbert space the states with this spin belong to.
+    label : :obj:`str`
+        A text label that can be used for archiving.
     """
 
     def __init__(self, value, dimension, label):
@@ -48,23 +50,23 @@ class IntegrationMethod(Enum):
 
     Parameters
     ----------
-    value : `string`
-        The code name for this method.
+    value : :obj:`str`
+        A text label that can be used for archiving.
     """
 
     MAGNUS_CF_4 = "magnus_cf4"
     """
-    Commutator free fourth order Magnus based.
+    Commutator free, fourth order Magnus based integrator.
     """
 
     MIDPOINT_SAMPLE = "midpoint_sample"
     """
-    Naive integration method.
+    Euler integration method.
     """
 
     HALF_STEP = "half_step"
     """
-    Integration method from AtomicPy.
+    Integration method from AtomicPy. Makes two Euler integration steps, one sampling the field from the start of the time step, one sampling the field from the end of the time step. The equivalent of the trapezoidal method.
     """
 
 class ExponentiationMethod(Enum):
@@ -73,10 +75,10 @@ class ExponentiationMethod(Enum):
 
     Parameters
     ----------
-    value : `string`
-        The code name for this method.
-    index : `int`
-        A reference number, used in the integrator factory where higher level objects cannot be interpreted.
+    value : :obj:`str`
+        A text label that can be used for archiving.
+    index : :obj:`int`
+        A reference number, used when compiling the integrator, where higher level objects like enums cannot be interpreted.
     """
     def __init__(self, value, index):
         super().__init__()
@@ -85,7 +87,7 @@ class ExponentiationMethod(Enum):
 
     ANALYTIC = ("analytic", 0)
     """
-    Analytic expression for spin half systems only.
+    Analytic expression of the matrix exponential. For spin half :obj:`SpinQuantumNumber.HALF` systems only.
[…]

### 2021-04-15 article/article.tex
Updated article draft to latex

@@
 \documentclass{jors}
+\usepackage{amsmath, amssymb}
+\usepackage{cite}
+\usepackage{graphicx}
+\graphicspath{ {images/} }
 
@@
 
-To complete this template, please replace the blue text with your own. The paper has three main sections: (1) Overview; (2) Availability; (3) Reuse potential. \\
-
 Please submit the completed paper to: editor.jors@ubiquitypress.com
@@
 
-\textcolor{blue}{The title of the software paper should focus on the software, e.g.
-“Text mining software from the X project”.
-If the software is closely linked to a specific research paper, then “Software from Paper Title” is appropriate.
-The title should be factual, relating to the functionality of the software and the area it relates to rather than making claims about the software, e.g.
-“Easy-to-use”.}
-
 \section*{Paper Authors}
@@
 6. Turner, L. D.;\\
-
-\textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
-2. Last name, first name; etc.}
 
@@
 
-\textcolor{blue}{1. First author role and affiliation \\
-2. Second author role and affiliation etc.}
-
 \section*{Abstract}
-
-\textcolor{blue}{A short (ca.
-100 word) summary of the software being described: what problem the software addresses, how it was implemented and architected, where it is stored, and its reuse potential.}
+	\emph{spinsim} is a python package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
+It makes use of the \emph{numba.cuda} llvm compiler \cite{lam_numba_2015}, and other optimisations, to allow for fast and accurate evaluation on \emph{Nvidia Cuda} \cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
+\emph{spinsim} is available for install on \emph{PyPI}, and the source code is available on \emph{github}.
+The initial use case for the package will be to simulate quantum sensing based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but will be useful in simulating any range of spin one or half quantum systems with involved time dependent Hamiltonians in fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin one systems of nitrogen vacancy centres (NVCs) and BECs.
 
 \section*{Keywords}
-Time dependent Schrödinger equation; Spin one; Spin half; Integrator; GPU;\\
+Time dependent Schroedinger equation; Spin one; Spin half; Integrator; GPU; Solver; python; numba;\\
 
@@
 \subsection*{Motivation}
-Spinsim is a package for python designed to simulate the spin one dynamics of Bose Einstein Condensates, specifically for the Spinor BEC lab group at Monash University.
+	Ultracold atoms have proven their effectiveness in state of the art technologies in quantum metrology \cite{huang_quantum_2014}, the use of quantum mechanics to make precise measurements of small signals.
+Design of such measurement protocols requires many steps of verification, including simulation.
+This is especially important, since running real experiments can be expensive and time consuming, and thus it is more practical to debug such protocols quickly and cheaply on a computer.
+In general, any design of experiments using spin systems could benefit from a fast, accurate method of simulation.\\
 
-\subsection*{Motivation}
+	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, cython based script \emph{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, which this package is originally based off, and standard differential equation solvers (such as \emph{Mathematica}'s function \emph{NDSolve}) to solve the Schroedinger equation for these spin one systems, which are sometimes approximated to spin half for a faster execution time.
+However, these methods are not completely optimised for our use case, and therefore come with some issues.\\
 
-\textcolor{blue}{An overview of the software, how it was produced, and the research for which it has been used, including references to relevant research articles.
-A short comparison with software which implements similar functionality should be included in this section.
-}
+	First of all, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require thousands of simulations to be run), this time accumulates to the order of many hours.\\
+
+	Secondly, the Schroedinger equation has the geometric property of being norm persevering.
+In other words, the time evolution operator for a system between two points in time must be unitary.
+This is important, because all quantum states live on the boundary of a ball of length one in their Hilbert space.
+For many numerical methods like those in the Runge Kutta family, the approximations used might not be norm preserving, and the evaluated quantum state may well diverge to infinite norm, or converge to zero if run for too many iterations.\\
+
+	Thirdly, our system (and similar spin systems) can be very oscillatory.
+In standard conditions for our application, the expected spin projection of a system can rotate in space (alternatively viewed as a point rotating around an abstract object known as a Bloch sphere) at a rate of 700kHz.
+Standard integration methods require very small time steps in order to accurately depict these oscillations.
+We found that the integration method used by AtomicPy has an accuracy of only order \(10^{-2}\) when the time step is set to the small value of 10ns.
 
 \section*{Implementation and architecture}
+	\subsection*{Mathematical methods}
+		\subsubsection*{Parallelisation}
+			In general, \emph{spinsim} solves the Schroedinger equation,
 
-\textcolor{blue}{How the software was implemented, with details of the architecture where relevant.
-Use of relevant diagrams is appropriate.
-Please also describe any variants and associated implementation differences.}
+			\begin{align*}
+				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) &= -iH(t)\psi(t),
+			\end{align*}
+
+			with \(i^2 = -1\), the state, \(\psi(t)\) a time dependent, 3 (2) dimensional, unit complex vector, and \(H(t)\) a time dependent 3 by 3 (2 by 2) complex matrix for spin one (spin half) systems.
+However, in \emph{spinsim}, the Hamiltonian \(H(t)\) is instead defined by its vector representation in Lie Algebra.
+For example, when set to spin half mode, the \emph{spinsim} package solves time dependent Schroedinger Equations of the form
+
+			\begin{align*}
+				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
+			\end{align*}
+
+			where \(i^2 = -1\), \(\psi(t) \in \mathbb{C}^2\), and the spin half spin projection operators are given by
+
+			\begin{align*}
+				J_x &= \frac12\begin{pmatrix}
+					0 & 1 \\
+					1 & 0
+				\end{pmatrix},
+				&J_y &= \frac12\begin{pmatrix}
+					0 & -i \\
+					i &  0
+				\end{pmatrix},
+				&J_z &= \frac12\begin{pmatrix}
+					1 &  0 \\
+					0 & -1
+				\end{pmatrix}.
+			\end{align*}
+
+			The source of the system is the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with \(t\) in units of s and \(f\) in units of Hz that control the dynamics of the system.
+The user must define a function that returns a sample of these source functions when a sampling time is input.
+In physical terms, these functions would represent the \(x,y,z\) components of a magnetic field applied to an atom being simulated, for example.\\
+
+			Similarly, when \emph{spinsim} is set to spin one mode, it can solve Schroedinger equations of the form
+
+			\begin{align*}
+				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
+			\end{align*}
+
+			where now \(\psi(t) \in \mathbb{C}^3\), and the spin one operators are given by
+
+			\begin{align*}
+				J_x &= \frac{1}{\sqrt{2}}\begin{pmatrix}
+					0 & 1 & 0 \\
+					1 & 0 & 1 \\
+					0 & 1 & 0
+				\end{pmatrix},&
+				J_y &= \frac{1}{\sqrt{2}}\begin{pmatrix}
+					0 & -i &  0 \\
+					i &  0 & -i \\
+					0 &  i &  0
+				\end{pmatrix},\\
+				J_z &= \begin{pmatrix}
+					1 & 0 &  0 \\
+					0 & 0 &  0 \\
+					0 & 0 & -1
+				\end{pmatrix},&
+				Q &= \frac{1}{3}\begin{pmatrix}
+					1 &  0 & 0 \\
+					0 & -2 & 0 \\
+					0 &  0 & 1
+				\end{pmatrix}.
+			\end{align*}
+
+			\(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadratic operator, proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.\\
+
+			Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\).
+If the system is solved this way, using a geometric method, we can guarantee that \(\psi(t)\) will always be a unit vector, which is not true with solvers in general.
+
+			\begin{align*}
+				\psi(t) &= U(t, t_0)\psi(t_0)
+			\end{align*}
+
+			This means that a time series for the state of the system can be evaluated by evaluating the time evolution operator between each of the sample times.
+
+			\begin{align*}
+				\psi_k &= U_k\psi_{k-1}\textrm{, standing for}\\
+				\psi(t_{k}) &= U(t_{k}, t_{k-1})\psi(t_{k-1})\textrm{, where}\\
+				t_k &= t_0 + \mathrm{D}t\cdot k
+			\end{align*}
+
+			with \(\mathrm{D}t\) the time step of the time series.
+
+			Also importantly, while each of the \(\psi_k\) must be evaluated sequentially, the value of the \(U_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(U_{k_0}\).
+This means that the time evolution operators \(U_k\) can all be calculated in parallel, and it allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.\\
+
+			In summary, \emph{spinsim} splits the time evolution of the full simulation into time evolution \(U_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
+When all the \(U_k\) are calculated CPU then multiplies the \(U_k\) together (a comparatively less demanding job than calculating them) to determine the \(\psi_k\).
+
+		\subsubsection*{Rotating frame}
+			If the rotating frame option is selected, the \(U_k\) are first calculated within a local rotating frame as \(U^r_k\), which shrinks the size of the terms used in the calculation, increasing accuracy.
+The midpoint value \(f_r = f_z(t_k + \frac12\mathrm{D}t)\) is sampled to be removed from the source.
+This transforms the source functions as follows,
+
+			\begin{align*}
+				f^r_x(t) + if^r_y(t) &= e^{-i 2\pi f_r t}(f_x(t) + if_y(t)),\\
+				f^r_z(t) &= f_z(t) - f_r,\\
+				f^r_q(t) &= f_q(t), \textrm{ for spin one.}\\
+			\end{align*}
+
+			This, (assuming that a midpoint sample is representative of an average value over the time interval), decreases the magnitude of \(f_z(t)\), while leaving the other source components at an equivalent magnitude.
+The rotation is then applied to obtain the lab frame time evolution operator \(U_k\),
+
+			\begin{align*}
+				U_k &= \exp(-i 2 \pi f_r J_z \mathrm{D}t) U^r_k,\\
+				U_k &= \begin{pmatrix}
+					e^{-i 2\pi f_r \mathrm{D}t} & 0 & 0\\
+					0 & 1 & 0\\
+					0 & 0 & e^{i 2\pi f_r \mathrm{D}t}
+				\end{pmatrix} U^r_k, \textrm{ for spin one}\\
+				U_k &= \begin{pmatrix}
+					e^{-i \pi f_r \mathrm{D}t} & 0\\
+					0 & e^{i \pi f_r \mathrm{D}t}
+				\end{pmatrix} U^r_k, \textrm{ for spin half.}
+			\end{align*}
+
+		\subsubsection*{Magnus based integration method}
+			The integration method used in \emph{spinsim} is the CF4 method from Auer et al \cite{auer_magnus_2018}.
+Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller timestep,
+
+			\begin{align*}
+				U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+				U_k &= u^k_{L-1} \cdots u^k_0,
+			\end{align*}
+
+			with \(\mathrm{d}t\) being the integration level, (ie, fine) time step.
+
+			The CF4 method is used to calculate each individual \(u^k_l\).
+Let the fine sample time be given by \(t_f = l\mathrm{d}t + t_k\).
+Then as part of the CF4 method, the source functions are sampled at particular times based on the second order Gauss-Legendre quadrature,
+
+			\begin{align*}
+				f(t_1) &= (f_x(t_1), f_y(t_1), f_z(t_1), f_q(t_1)), \textrm{ with}\\
+				t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right),\\
+				f(t_2) &= (f_x(t_2), f_y(t_2), f_z(t_2), f_q(t_2)), \textrm{ with}\\
+				t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
+			\end{align*}
+
+			The fine time evolution operator can then be calculated using
+
+			\begin{align*}
+				g_1 =& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\\
+				g_2 =& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\\
+				u =& \exp(-i \left( g_{2,x} J_x + g_{2,y} J_y + g_{2,z} J_z + g_{2,q} Q\right))\\
+				&\cdot\exp(-i \left( g_{1,x} J_x + g_{1,y} J_y + g_{1,z} J_z + g_{1,q} Q\right)).
+			\end{align*}
+
+		\subsubsection*{Exponentiator}
+			For all exponentiation, the exponentiator takes exponent in the form of
+
+			\begin{align*}
+				E(g) &= \exp(-i (g_x J_x + g_y J_y + g_z J_z + g_q Q)), \textrm{ with}\\
+				g &= (g_x, g_y, g_z, g_q)
+			\end{align*}
+
+			For spin half, the default exponentiator is in an analytic form.
+For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used.
+Importantly, these two methods both use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.\\
+
+			This also means that the package cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8 dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the four dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
+Including the full algebra could be possible as a feature update if there is demand for it, though just including this subspace is sufficient for our application, and many others.
+
+	\subsection*{Software architecture}
+		\subsubsection*{Integrator architecture}
+			The integrator in the \emph{spinsim} package calls a \emph{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(U_k\).
+This returns when each of the \(U_k\) have been evaluated.\\
+
+			The thread starts by calculating \(t_k\) and, if the rotating frame is being used, \(f_r\).
+The latter is done by sampling a (\emph{numba.cuda.jit()}ed version of a) user provided python function \(f\) describing how to sample the source Hamiltonian.
+The code then loops over each fine time step \(\mathrm{d}t\) to calculate the fine time evolution operators \(u^k_l\).\\
+
+			Within the loop, the integrator enters a device function (ie a GPU subroutine, which is inline for speed) to sample \(f(t)\), as well as calculate \(e^{-i 2 \pi f_r t}\), at the sample times needed for the integration method.
+After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating \(g\) values, and finally taking the matrix exponentiation in a fourth device function.
+\(u^k_l\) is premultiplied to \(U^r_k\) (which is initialised to \(1\)), and the loop continues.\\
+
+			When the loop has finished, if the rotating frame is being used, \(U^r_k\) is transformed to \(U_k\) as above, and this is returned.
+Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \emph{numba.jit()}ed function from the \(U_k\) and an initial condition \(\psi_{\mathrm{init}}\).
+
+		\subsubsection*{Compilation of integrator}
+			The \emph{spinsim} integrator is constructed and compiled just in time, using \emph{numba.cuda.jit()}.
+The particular device functions used are not predetermined, but are instead chosen based off user input to decide a closure.
+This structure has multiple advantages.
+Firstly, the source function \(f\) is provided by the user as a plain python function (that must be \emph{numba.cuda.jit()} compatible).
+This allows users to define \(f\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
+Compiling the simulator also allows the user to set metaparameters, and choose the features they want to use, in a way that does not require experience with the \emph{numba.cuda} library.
+This was especially useful for running benchmarks comparing old integration methods to the new ones, like CF4.
+The default settings should be optimal for most users, although tuning the values of \emph{Cuda} metaparameters \emph{max\_registers} and \emph{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile GTX1070 mainly used in testing here.
+Finally, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.\\
+
+			This functionality is interfaced through an object of class \emph{spinsim.Simulator}.
+The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \emph{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection (that is, Bloch vector.
+Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object).
 
 \section*{Quality control}
+	\subsection*{Benchmarks}
+		\subsubsection*{Speed}
+			Benchmarks were performed using \emph{sense.sim.benchmark}, by comparing evaluation speed of typical spin one metrology experiments on different devices.
+This is shown in Figure \ref{fig:benchmark_device_aggregate}.
+The integration code was compiled by \emph{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different devices.
+These devices are,
+			\begin{itemize}
+				\item {} 
+				Intel Core i7-8750H, a 6 core laptop processor released in 2018. Run with 16GiB of RAM. Air cooled (laptop fan). Base clock speed of 2.2GHz.
 
-\textcolor{blue}{Detail the level of testing that has been carried out on the code (e.g.
-unit, functional, load etc.), and in which environments.
-If not already included in the software documentation, provide details of how a user could quickly understand if the software is working (e.g.
-providing examples of running the software with sample input and output data).
-}
+				\item {} 
+				AMD Ryzen 7 5800X, an 8 core desktop processor released in 2020. Run with 32GiB of RAM. Liquid cooled. Base clock speed of 3.8GHz.
+
+				\item {} 
+				AMD Ryzen 9 5900X, a 12 core desktop processor released in 2020. Run with 32GiB of RAM. Air cooled. Base clock speed of 3.7GHz.
+
+				\item {} 
+				Nvidia GeForce GTX 1070, a 2048 \emph{Cuda} core laptop graphics processor released in 2016. Run with 8GiB of VRAM. Air cooled (laptop fan).
+
+				\item {} 
+				Nvidia GeForce RTX 3070, a 5888 \emph{Cuda} core desktop graphics processor released in 2020. Run with 8GiB of VRAM. Air cooled.
+
+				\item {} 
+				Nvidia GeForce RTX 3080, an 8704 \emph{Cuda} core desktop graphics processor released in 2020. Run with 10GiB of VRAM. Air cooled.
+			\end{itemize}
+
+			\begin{figure}[h!]
+				\includegraphics[scale=0.9]{benchmark_device_aggregate_publication.pdf}
+				\caption{Evaluation speed of a typical spin one metrology experiment.
+Fine time step is 100ns, as determined to be ideal by the accuracy experiments.
+Experiments run for a duration of 100ms.
+Evaluation time is determined by an average of 100 similar experiments for each device.}
+				\label{fig:benchmark_device_aggregate}
+			\end{figure}
+
+			This benchmark shows the benefit to using parallelisation when solving this problem.
+Moving from a 6 core processor to a 12 core processor doubles the execution speed.
+Moving from a single core processor to a GPU increases performance by well over an order of magnitude.
+As an aside, liquid cooling allows the 8 core processor to increase its boost clock and outperform the 12 core processor.
+
+		\subsubsection*{Accuracy}
+			Benchmarks were performed using \emph{neural-sense.sim.benchmark} (where \emph{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for), by comparing state evaluations of many different typical metrology experiments and finding the mean error introduced when the fine (integration) time step is increased.\\
+
+			\begin{figure}[h!]
+				\includegraphics[scale=0.9]{benchmark_comparison_spin_one_publication.pdf}
+				\caption{Fine time step benchmark for spin one systems.
+CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \emph{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
+HS and MP results are drawn on top of each other due to their similarities.}
+				\label{fig:benchmark_comparison_spin_one}
+			\end{figure}
+
+			Figure \ref{fig:benchmark_comparison_spin_one} shows the performance of \emph{spinsim} when running in spin one mode.
+This shows that both using the Magnus based CF4 method and moving into a rotating frame give significant increases to accuracy.
+The HS (half step) method in the lab frame, with a time step of 10ns was the method used by \emph{AtomicPy}, the previous code used by the group for simulating spin systems.
+Compared to this, the best performing \emph{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.\\
+
+			\begin{figure}[h!]
+				\includegraphics[scale=0.9]{benchmark_comparison_spin_half_lt_publication.pdf}
+				\caption{Fine time step benchmark for spin half systems, using the Lie Trotter based exponentiator.
+CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \emph{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
+HS and MP results are drawn on top of each other due to their similarities.}
+				\label{fig:benchmark_comparison_spin_half_lt}
+			\end{figure}
+
+			From Figure \ref{fig:benchmark_comparison_spin_half_lt}, one gets essentially the same accuracy for each method when working in spin half mode compared to spin one, if all else is kept constant.\\
+
+			\begin{figure}[h!]
+				\includegraphics[scale=0.9]{benchmark_comparison_spin_half_a_publication.pdf}
+				\caption{Fine time step benchmark for spin half systems, using the analytic based exponentiator.
+CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \emph{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
+HS and MP results are drawn on top of each other due to their similarities.}
+				\label{fig:benchmark_comparison_spin_half_a}
+			\end{figure}
+
+			Figure \ref{fig:benchmark_comparison_spin_half_a} shows that the Lie Trotter based exponentiator does limit the maximum accuracy obtainable, and for spin half systems, one can increase accuracy further (and decrease execution time) by using an analytic based exponentiator.
+
+		\subsubsection*{Comparison to alternatives}
+			As mentioned before, compared to our previous code, \emph{AtomicPy}, the best performing \emph{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.
+We had planned to benchmark against some popular generic solvers.
+One such solver was \emph{qutip.sesolve()}, a solver in the popular quantum mechanics python library, \emph{QuTip} \cite{johansson_qutip_2013}.
+However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
+We also planned to benchmark accuracy against the generic solver \emph{scipy.integrate.ivp\_solve()} in the python library \emph{SciPy} \cite{virtanen_scipy_2020}.
+However, using the same \emph{get\_field} function as in the spin one benchmarks used for the \emph{spinsim}, simulating with a fine time step of 500ns (the largest used during the \emph{spinsim} benchmarks), we found that a single simulation ran in 153s, which is over three orders of magnitude slower than the most accurate \emph{spinsim} simulations.
+This means that a generous projection for the time it would take to run the same benchmarks that \emph{spinsim} runs in 11 minutes, using \emph{scipy} would be over six days; for an integration package not designed for this problem (and would therefore likely be less accurate).
+
+	\subsection*{Testing}
+		The simulator as a whole has been functionally tested against well known analytic approximations of the behaviour spin systems.
+This was done for every combination of integrator settings possible when compiling the integrator.
+The system was benchmarked in terms of accuracy vs fine time step, again, using every possible combination of integrator settings.
+This confirms that no integrator diverges away from the limiting solution when the time step is decreased in magnitude.
+The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.\\
+
+		These tests and benchmarks were run as part of the \emph{neural\_sense} package.
+The simulator has also been used as part of the measurement protocol being developed there, and it has been tested as part of those algorithms as well.\\
+
+		The kernel execution was profiled thoroughly, and changes were made to optimise VRAM and register usage and transfer.
+This was done specifically for the hardware of an Nvidia GTX1070, so one may get some performance increases by changing some GPU specific metaparameters when instantiating the \emph{spinsim.Simulator} object.\\
+
+		A good way to confirm that \emph{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
+Otherwise, one can run the benchmarks and simulation protocols in \emph{neural\_sense.sim.benchmark}.
 
@@
 \section*{Operating system}
-
-\textcolor{blue}{Please include minimum version compatibility.}
+Developed on Windows 10. Tested on MacOS Big Sur.
 
 \section*{Programming language}
-
-\textcolor{blue}{Please include minimum version compatibility.}
+Python (3.7 or greater)
 
 \section*{Additional system requirements}
-
-\textcolor{blue}{E.g. memory, disk space, processor, input devices, output devices.}
+To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \href{https://developer.nvidia.com/cuda-gpus}{\emph{Cuda} compatible \emph{Nvidia GPU}}.
+For \emph{Cuda} mode to function, one also needs to install the \href{https://developer.nvidia.com/cuda-toolkit}{\emph{Nvidia Cuda} toolkit}.
+If \emph{Cuda} is not available on the system, the simulator will automatically parallelise over multicore CPUs instead
 
 \section*{Dependencies}
-
-\textcolor{blue}{E.g. libraries, frameworks, incl. minimum version compatibility.}
+numba (0.50.1 or greater)\\
+numpy (1.19.3)\\
+matplotlib (for example code, 3.2)\\
+neuralsense (for benchmark code)
 
@@
 	Original conception of released version of algorithm.
-
-\textcolor{blue}{Please list anyone who helped to create the software (who may also not be an author of this paper), including their roles and affiliations.}
 
@@
 
+	\subsection*{Use potential and limitations}
+		\emph{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
+This is immediately relevant to developing new quantum sensing protocols with spin one and spin half systems.
+The package will be used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab, both within and outside the project it was conceived for.\\
+
+		This project is to be able to measure neural signals using BECs.
+The electrical pulses made by neurons are currently measured using electrical probes, which is intrusive and damages the cells.
+We instead propose to sense the small magnetic fields that these electrical currents produce.
+Rubidium BECs can potentially be made sensitive enough to these tiny magnetic fields that they can be measured by them.
+An array of BECs can theoretically be made to sample the frequency components of the magnetic signal, essentially making a Fourier transform of it, which can be transformed back.
+Assuming that pulses do not occur very often (the signal is sparse in the time domain), a smaller BEC array with fewer frequency samples can be used to create a compressed measurement, reconstructed with theory from the field of compressive sensing \cite{candes_introduction_2008}.
+\emph{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.\\
+
+		Another example of spin based magnetic field sensing is the use of Nitrogen Vacancy Centres (NVCs).
+These are spin one structures found in diamond doped with Nitrogen atoms.
+This leaves a vacancy in a position adjacent to the Nitrogen atom, which pairs of electrons occupy to obtain the spin one properties.
+Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
+A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs \cite{parashar_axon_2020}, which is something that \emph{spinsim} could be useful for.\\
+
+		\emph{spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
+This means that it would not be able to integrate large arrays of entangled states or interacting particles.
+As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
+In addition, \emph{spinsim} is currently designed to integrate the time evolution of pure states only.
+This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation \cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).\\
+
+		With these restrictions in mind, \emph{spinsim} could be used for some simplified simulations in various areas of NMR.
+There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14) \cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
+The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei \cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
+Another possible use case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
+MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
+While this package offers some advantages over state of the art simulators in the field \cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are likely its downfall here.
+
+	\subsection*{Support}
+		Documentation for \emph{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
+This documentation contains a thorough tutorial on how to use the package, and installation instructions.\\
+
+		For direct support with the \emph{spinsim} package, one can open an issue in the \emph{github} repository.
+One can also use this contact to suggest extensions to the package.
+\emph{spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
+
 \textcolor{blue}{Please describe in as much detail as possible the ways in which the software could be reused by other researchers both within and outside of your field.
@@
 
-\textcolor{blue}{Please add any relevant acknowledgements to anyone else who supported the project in which the software was created, but did not work directly on the software itself.}
+Thank you to Hamish Taylor and Travis Hartley from the Monash University School of Physics and Astronomy spinor BEC lab, who have started using \emph{spinsim} for their own projects and have given feedback of their user experience with the package.
 
@@
 “The authors declare that they have no competing interests.” }
+
+\bibliography{spinsim}{}
+\bibliographystyle{vancouver}
 

### 2021-04-29 article/article.tex
Updated article

@@
 \section*{Title}
-spinsim: a GPU optimised solver of spin one and half quantum systems
+spinsim: a GPU optimised solver of spin half and spin one quantum systems
 
@@
 \section*{Abstract}
-	\emph{spinsim} is a python package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
-It makes use of the \emph{numba.cuda} llvm compiler \cite{lam_numba_2015}, and other optimisations, to allow for fast and accurate evaluation on \emph{Nvidia Cuda} \cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
-\emph{spinsim} is available for install on \emph{PyPI}, and the source code is available on \emph{github}.
-The initial use case for the package will be to simulate quantum sensing based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but will be useful in simulating any range of spin one or half quantum systems with involved time dependent Hamiltonians in fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin one systems of nitrogen vacancy centres (NVCs) and BECs.
+	\texttt{spinsim} is a \emph{python} package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
+It makes use of \texttt{numba.cuda} \cite{lam_numba_2015}, which is an \emph{LLVM} (Low Level Virtual Machine) \cite{lattner_llvm_2004} compiler, and other optimisations, to allow for fast and accurate evaluation on \emph{Nvidia Cuda} \cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
+\texttt{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
+The initial use case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin half or spin one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
+These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin one systems of nitrogen vacancy centres (NVCs) and BECs.
 
 \section*{Keywords}
-Time dependent Schroedinger equation; Spin one; Spin half; Integrator; GPU; Solver; python; numba;\\
-
-\textcolor{blue}{keyword 1; keyword 2; etc. \\
-Keywords should make it easy to identify who and what the software will be useful for.}
+Time dependent Schroedinger equation; Spin one; Spin half; Integrator; GPU; Solver; python; numba;
 
@@
 \subsection*{Motivation}
-	Ultracold atoms have proven their effectiveness in state of the art technologies in quantum metrology \cite{huang_quantum_2014}, the use of quantum mechanics to make precise measurements of small signals.
-Design of such measurement protocols requires many steps of verification, including simulation.
+	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing \cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
+The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
+The simplest spin system, spin half (also referred to as a qubit), is quantised into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
+However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin one quantum system (also referred to as a quitrit), which is quantised into three quantum spin levels.
+
+	The design of sensing protocols requires many steps of verification, including simulation.
 This is especially important, since running real experiments can be expensive and time consuming, and thus it is more practical to debug such protocols quickly and cheaply on a computer.
-In general, any design of experiments using spin systems could benefit from a fast, accurate method of simulation.\\
+In general, any design of experiments using spin systems could benefit from a fast, accurate method of simulation.
 
-	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, cython based script \emph{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, which this package is originally based off, and standard differential equation solvers (such as \emph{Mathematica}'s function \emph{NDSolve}) to solve the Schroedinger equation for these spin one systems, which are sometimes approximated to spin half for a faster execution time.
-However, these methods are not completely optimised for our use case, and therefore come with some issues.\\
+	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schroedinger equation for quantum sensing spin systems.
+These spin one systems  are sometimes approximated to spin half for a faster execution time, at the cost of modelling all effects of the system.
+However, these methods are not completely optimised for our use case, and therefore come with some issues.
 
-	First of all, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require thousands of simulations to be run), this time accumulates to the order of many hours.\\
+	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours.
 
-	Secondly, the Schroedinger equation has the geometric property of being norm persevering.
+	Second, the Schroedinger equation has the geometric property of being norm persevering.
 In other words, the time evolution operator for a system between two points in time must be unitary.
-This is important, because all quantum states live on the boundary of a ball of length one in their Hilbert space.
-For many numerical methods like those in the Runge Kutta family, the approximations used might not be norm preserving, and the evaluated quantum state may well diverge to infinite norm, or converge to zero if run for too many iterations.\\
+As such, numerical solutions to the Schroedinger equation should also preserve this property.
+For many numerical methods like those in the Runge Kutta family, the approximations used might not be norm preserving, and the evaluated quantum state may diverge towards an infinite norm, or converge to zero if run for many iterations.
 
-	Thirdly, our system (and similar spin systems) can be very oscillatory.
-In standard conditions for our application, the expected spin projection of a system can rotate in space (alternatively viewed as a point rotating around an abstract object known as a Bloch sphere) at a rate of 700kHz.
+	Third, our system (and similar spin systems) can be very oscillatory.
+In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz.
 Standard integration methods require very small time steps in order to accurately depict these oscillations.
-We found that the integration method used by AtomicPy has an accuracy of only order \(10^{-2}\) when the time step is set to the small value of 10ns.
+For instance, we found that the integration method used by \emph{AtomicPy} has an accuracy of only order \(10^{-2}\) when the integration time step is set to the small value of 10ns.
 
@@
 	\subsection*{Mathematical methods}
-		\subsubsection*{Parallelisation}
-			In general, \emph{spinsim} solves the Schroedinger equation,
+		\subsubsection*{Background}
+			In general, \texttt{spinsim} solves the Schroedinger equation,
 
@@
 
-			with \(i^2 = -1\), the state, \(\psi(t)\) a time dependent, 3 (2) dimensional, unit complex vector, and \(H(t)\) a time dependent 3 by 3 (2 by 2) complex matrix for spin one (spin half) systems.
-However, in \emph{spinsim}, the Hamiltonian \(H(t)\) is instead defined by its vector representation in Lie Algebra.
-For example, when set to spin half mode, the \emph{spinsim} package solves time dependent Schroedinger Equations of the form
+			where \(i^2 = -1\), the state \(\psi(t) \in \mathbb{C}^N\) a time dependent, \(N\) dimensional, unit complex vector, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is a time dependent \(N \times N\) complex Hermitian matrix.
+Here \(N\) is the number spin levels in the quantum system, so spin half is the \(N = 2\) case, and spin one refers to the \(N = 3\) case.
+Rather than being represented by standard coodintaes in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
+For example, when set to spin half mode, the \texttt{spinsim} package solves the time dependent Schroedinger equations of the form
 
@@
 				\end{pmatrix},
-				&J_z &= \frac12\begin{pmatrix}
+				&\textrm{and }J_z &= \frac12\begin{pmatrix}
 					1 &  0 \\
@@
 
-			The source of the system is the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with \(t\) in units of s and \(f\) in units of Hz that control the dynamics of the system.
-The user must define a function that returns a sample of these source functions when a sampling time is input.
-In physical terms, these functions would represent the \(x,y,z\) components of a magnetic field applied to an atom being simulated, for example.\\
+			The energy source \(f\) that represents the time dependent Hamiltonian \(H(t)\), is the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with \(t\) in units of s and \(f\) in units of Hz that control the dynamics of the system.
+The user must define a method that returns a sample of these source functions when a sampling time is input.
+In physical terms, these functions could represent the \(x,y,z\) components of a magnetic field applied to a magnetically sensitive.
 
-			Similarly, when \emph{spinsim} is set to spin one mode, it can solve Schroedinger equations of the form
+			Similarly, when \texttt{spinsim} is set to spin one mode, it can solve Schroedinger equations of the form
 
@@
 
-			\(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadratic operator, proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.\\
+			\(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadratic operator, proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
 
+		\subsubsection*{Parallelisation}
 			Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\).
@@
 			Also importantly, while each of the \(\psi_k\) must be evaluated sequentially, the value of the \(U_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(U_{k_0}\).
-This means that the time evolution operators \(U_k\) can all be calculated in parallel, and it allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.\\
+This means that the time evolution operators \(U_k\) can all be calculated in parallel, and it allows \texttt{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
 
-			In summary, \emph{spinsim} splits the time evolution of the full simulation into time evolution \(U_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
+			In summary, \texttt{spinsim} splits the time evolution of the full simulation into time evolution \(U_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
 When all the \(U_k\) are calculated CPU then multiplies the \(U_k\) together (a comparatively less demanding job than calculating them) to determine the \(\psi_k\).
@@
 		\subsubsection*{Magnus based integration method}
-			The integration method used in \emph{spinsim} is the CF4 method from Auer et al \cite{auer_magnus_2018}.
+			The integration method used in \texttt{spinsim} is the CF4 method from Auer et al \cite{auer_magnus_2018}.
 Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller timestep,
@@
 For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used.
-Importantly, these two methods both use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.\\
+Importantly, these two methods both use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
 
@@
 		\subsubsection*{Integrator architecture}
-			The integrator in the \emph{spinsim} package calls a \emph{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(U_k\).
-This returns when each of the \(U_k\) have been evaluated.\\
+			The integrator in the \texttt{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(U_k\).
+This returns when each of the \(U_k\) have been evaluated.
 
 			The thread starts by calculating \(t_k\) and, if the rotating frame is being used, \(f_r\).
-The latter is done by sampling a (\emph{numba.cuda.jit()}ed version of a) user provided python function \(f\) describing how to sample the source Hamiltonian.
-The code then loops over each fine time step \(\mathrm{d}t\) to calculate the fine time evolution operators \(u^k_l\).\\
+The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(f\) describing how to sample the source Hamiltonian.
+The code then loops over each fine time step \(\mathrm{d}t\) to calculate the fine time evolution operators \(u^k_l\).
 
@@
 After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating \(g\) values, and finally taking the matrix exponentiation in a fourth device function.
-\(u^k_l\) is premultiplied to \(U^r_k\) (which is initialised to \(1\)), and the loop continues.\\
+\(u^k_l\) is premultiplied to \(U^r_k\) (which is initialised to \(1\)), and the loop continues.
 
 			When the loop has finished, if the rotating frame is being used, \(U^r_k\) is transformed to \(U_k\) as above, and this is returned.
-Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \emph{numba.jit()}ed function from the \(U_k\) and an initial condition \(\psi_{\mathrm{init}}\).
+Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \texttt{numba.jit()}ed function from the \(U_k\) and an initial condition \(\psi_{\mathrm{init}}\).
 
 		\subsubsection*{Compilation of integrator}
-			The \emph{spinsim} integrator is constructed and compiled just in time, using \emph{numba.cuda.jit()}.
+			The \texttt{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
 The particular device functions used are not predetermined, but are instead chosen based off user input to decide a closure.
 This structure has multiple advantages.
-Firstly, the source function \(f\) is provided by the user as a plain python function (that must be \emph{numba.cuda.jit()} compatible).
+Firstly, the source function \(f\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
 This allows users to define \(f\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
-Compiling the simulator also allows the user to set metaparameters, and choose the features they want to use, in a way that does not require experience with the \emph{numba.cuda} library.
+Compiling the simulator also allows the user to set metaparameters, and choose the features they want to use, in a way that does not require experience with the \texttt{numba.cuda} library.
 This was especially useful for running benchmarks comparing old integration methods to the new ones, like CF4.
-The default settings should be optimal for most users, although tuning the values of \emph{Cuda} metaparameters \emph{max\_registers} and \emph{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile GTX1070 mainly used in testing here.
-Finally, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.\\
+The default settings should be optimal for most users, although tuning the values of \emph{Cuda} metaparameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile GTX1070 mainly used in testing here.
+Finally, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.
 
-			This functionality is interfaced through an object of class \emph{spinsim.Simulator}.
-The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \emph{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection (that is, Bloch vector.
+			This functionality is interfaced through an object of class \texttt{spinsim.Simulator}.
+The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection (that is, Bloch vector.
 Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object).
@@
 		\subsubsection*{Speed}
-			Benchmarks were performed using \emph{sense.sim.benchmark}, by comparing evaluation speed of typical spin one metrology experiments on different devices.
+			Benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin one sensing experiments on different devices.
 This is shown in Figure \ref{fig:benchmark_device_aggregate}.
-The integration code was compiled by \emph{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different devices.
+The integration code was compiled by \texttt{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different devices.
 These devices are,
@@
 				\includegraphics[scale=0.9]{benchmark_device_aggregate_publication.pdf}
-				\caption{Evaluation speed of a typical spin one metrology experiment.
+				\caption{Evaluation speed of a typical spin one sensing experiment.
 Fine time step is 100ns, as determined to be ideal by the accuracy experiments.
@@
 		\subsubsection*{Accuracy}
-			Benchmarks were performed using \emph{neural-sense.sim.benchmark} (where \emph{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for), by comparing state evaluations of many different typical metrology experiments and finding the mean error introduced when the fine (integration) time step is increased.\\
+			Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for), by comparing state evaluations of many different typical sensing experiments and finding the mean error introduced when the fine (integration) time step is increased.
 
@@
 				\caption{Fine time step benchmark for spin one systems.
-CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \emph{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
+CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
 HS and MP results are drawn on top of each other due to their similarities.}
@@
 
-			Figure \ref{fig:benchmark_comparison_spin_one} shows the performance of \emph{spinsim} when running in spin one mode.
+			Figure \ref{fig:benchmark_comparison_spin_one} shows the performance of \texttt{spinsim} when running in spin one mode.
 This shows that both using the Magnus based CF4 method and moving into a rotating frame give significant increases to accuracy.
-The HS (half step) method in the lab frame, with a time step of 10ns was the method used by \emph{AtomicPy}, the previous code used by the group for simulating spin systems.
-Compared to this, the best performing \emph{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.\\
+The HS (half step) method in the lab frame, with a time step of 10ns was the method used by \texttt{AtomicPy}, the previous code used by the group for simulating spin systems.
+Compared to this, the best performing \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.
 
@@
 				\caption{Fine time step benchmark for spin half systems, using the Lie Trotter based exponentiator.
-CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \emph{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
+CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
 HS and MP results are drawn on top of each other due to their similarities.}
@@
 
-			From Figure \ref{fig:benchmark_comparison_spin_half_lt}, one gets essentially the same accuracy for each method when working in spin half mode compared to spin one, if all else is kept constant.\\
+			From Figure \ref{fig:benchmark_comparison_spin_half_lt}, one gets essentially the same accuracy for each method when working in spin half mode compared to spin one, if all else is kept constant.
 
@@
 				\caption{Fine time step benchmark for spin half systems, using the analytic based exponentiator.
-CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \emph{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
+CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
 HS and MP results are drawn on top of each other due to their similarities.}
@@
 		\subsubsection*{Comparison to alternatives}
-			As mentioned before, compared to our previous code, \emph{AtomicPy}, the best performing \emph{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.
-We had planned to benchmark against some popular generic solvers.
-One such solver was \emph{qutip.sesolve()}, a solver in the popular quantum mechanics python library, \emph{QuTip} \cite{johansson_qutip_2013}.
+			As mentioned before, compared to our previous code, \texttt{AtomicPy}, the best performing \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.
+
+			Another solver used by the lab group is \emph{Mathematica}'s \texttt{NDSolve}.
+
+			We had planned to benchmark against some other popular generic solvers.
+One such solver was \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
 However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
-We also planned to benchmark accuracy against the generic solver \emph{scipy.integrate.ivp\_solve()} in the python library \emph{SciPy} \cite{virtanen_scipy_2020}.
-However, using the same \emph{get\_field} function as in the spin one benchmarks used for the \emph{spinsim}, simulating with a fine time step of 500ns (the largest used during the \emph{spinsim} benchmarks), we found that a single simulation ran in 153s, which is over three orders of magnitude slower than the most accurate \emph{spinsim} simulations.
-This means that a generous projection for the time it would take to run the same benchmarks that \emph{spinsim} runs in 11 minutes, using \emph{scipy} would be over six days; for an integration package not designed for this problem (and would therefore likely be less accurate).
+We also planned to benchmark accuracy against the generic solver \texttt{scipy.integrate.ivp\_solve()} in the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}.
+However, using the same \texttt{get\_field} function as in the spin one benchmarks used for the \texttt{spinsim}, simulating with a fine time step of 500ns (the largest used during the \texttt{spinsim} benchmarks), we found that a single simulation ran in 153s, which is over three orders of magnitude slower than the most accurate \texttt{spinsim} simulations.
+This means that a generous projection for the time it would take to run the same benchmarks that \texttt{spinsim} runs in 11 minutes, using \texttt{scipy} would be over six days; for an integration package not designed for this problem (and would therefore likely be less accurate).
 
@@
 This confirms that no integrator diverges away from the limiting solution when the time step is decreased in magnitude.
-The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.\\
+The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.
 
-		These tests and benchmarks were run as part of the \emph{neural\_sense} package.
-The simulator has also been used as part of the measurement protocol being developed there, and it has been tested as part of those algorithms as well.\\
+		These tests and benchmarks were run as part of the \texttt{neural\_sense} package.
+The simulator has also been used as part of the measurement protocol being developed there, and it has been tested as part of those algorithms as well.
 
 		The kernel execution was profiled thoroughly, and changes were made to optimise VRAM and register usage and transfer.
-This was done specifically for the hardware of an Nvidia GTX1070, so one may get some performance increases by changing some GPU specific metaparameters when instantiating the \emph{spinsim.Simulator} object.\\
+This was done specifically for the hardware of an Nvidia GTX1070, so one may get some performance increases by changing some GPU specific metaparameters when instantiating the \texttt{spinsim.Simulator} object.
 
-		A good way to confirm that \emph{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
-Otherwise, one can run the benchmarks and simulation protocols in \emph{neural\_sense.sim.benchmark}.
+		A good way to confirm that \texttt{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
+Otherwise, one can run the benchmarks and simulation protocols in \texttt{neural\_sense.sim.benchmark}.
 
@@
 
-\section*{Software location:}
-
-{\bf Archive} \textcolor{blue}{(e.g.
-institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)}
-
-\begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \textcolor{blue}{The name of the archive.}
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
-	\item[Publisher:]  \textcolor{blue}{Name of the person who deposited the software.}
-	\item[Version published:] \textcolor{blue}{The version number of the software archived.}
-	\item[Date published:] \textcolor{blue}{dd/mm/yy}
-\end{description}
-
-{\bf Code repository} \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}
-
-\begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \textcolor{blue}{The name of the archive.}
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
-	\item[Date published:] \textcolor{blue}{dd/mm/yy}
-\end{description}
-
-{\bf Emulation environment} \textcolor{blue}{(if appropriate)}
-
-\begin{description}[noitemsep,topsep=0pt]
-	\item[Name:] \textcolor{blue}{The name of the archive.}
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
-	\item[Date published:] \textcolor{blue}{dd/mm/yy}
-\end{description}
-
-\section*{Language}
-
-\textcolor{blue}{Language of repository, software and supporting files.}
-
 \section*{(3) Reuse potential}
@@
 	\subsection*{Use potential and limitations}
-		\emph{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
-This is immediately relevant to developing new quantum sensing protocols with spin one and spin half systems.
-The package will be used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab, both within and outside the project it was conceived for.\\
+		\texttt{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
+This is immediately relevant to developing new quantum sensing protocols with spin half and spin one systems.
+The package will be used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab, both within and outside the project it was conceived for.
 
@@
 Assuming that pulses do not occur very often (the signal is sparse in the time domain), a smaller BEC array with fewer frequency samples can be used to create a compressed measurement, reconstructed with theory from the field of compressive sensing \cite{candes_introduction_2008}.
-\emph{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.\\
+\texttt{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
 
@@
 Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
-A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs \cite{parashar_axon_2020}, which is something that \emph{spinsim} could be useful for.\\
+A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs \cite{parashar_axon_2020}, which is something that \texttt{spinsim} could be useful for.
 
-		\emph{spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
+		\texttt{spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
 This means that it would not be able to integrate large arrays of entangled states or interacting particles.
 As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
-In addition, \emph{spinsim} is currently designed to integrate the time evolution of pure states only.
-This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation \cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).\\
+In addition, \texttt{spinsim} is currently designed to integrate the time evolution of pure states only.
+This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation \cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).
 
-		With these restrictions in mind, \emph{spinsim} could be used for some simplified simulations in various areas of NMR.
-There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14) \cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
-The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei \cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+		With these restrictions in mind, \texttt{spinsim} could be used for some simplified simulations in various areas of NMR.
+There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14) \cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \texttt{spinsim} could be used to simulate for spectroscopy experiments, for example.
+The inclusion of a quadrupole operator means that, with the same level of simplifications, \texttt{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei \cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
 This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
 Another possible use case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
-MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
+MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \texttt{spinsim} simulations of spins at different positions in space.
 While this package offers some advantages over state of the art simulators in the field \cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are likely its downfall here.
@@
 	\subsection*{Support}
-		Documentation for \emph{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
-This documentation contains a thorough tutorial on how to use the package, and installation instructions.\\
+		Documentation for \texttt{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
+This documentation contains a thorough tutorial on how to use the package, and installation instructions.
 
-		For direct support with the \emph{spinsim} package, one can open an issue in the \emph{github} repository.
+		For direct support with the \texttt{spinsim} package, one can open an issue in the \emph{github} repository.
 One can also use this contact to suggest extensions to the package.
-\emph{spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
-
-\textcolor{blue}{Please describe in as much detail as possible the ways in which the software could be reused by other researchers both within and outside of your field.
-This should include the use cases for the software, and also details of how the software might be modified or extended (including how contributors should contact you) if appropriate.
-Also you must include details of what support mechanisms are in place for this software (even if there is no support).}
+\texttt{spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
 
@@
 
-Thank you to Hamish Taylor and Travis Hartley from the Monash University School of Physics and Astronomy spinor BEC lab, who have started using \emph{spinsim} for their own projects and have given feedback of their user experience with the package.
+Thank you to Hamish Taylor and Travis Hartley from the Monash University School of Physics and Astronomy spinor BEC lab, who have started using \texttt{spinsim} for their own projects and have given feedback of their user experience with the package.
 
@@
 
-\textcolor{blue}{If any of the authors have any competing interests then these must be declared.
-The authors’ initials should be used to denote differing competing interests.
-For example: “BH has minority shares in [company name], which part funded the research grant for this project.
-All other authors have no competing interests." \\
-If there are no competing interests, please add the statement:
-“The authors declare that they have no competing interests.” }
-
 \bibliography{spinsim}{}
 \bibliographystyle{vancouver}
-
-\section*{References}
-
-\textcolor{blue}{Please enter references in the Harvard style and include a DOI where available, citing them in the text with a number in square brackets, e.g. \\ }
-
-\textcolor{blue}{[1] Piwowar, H A 2011 Who Shares?
-Who Doesn't?
-Factors Associated with Openly Archiving Raw Research Data.
-PLoS ONE 6(7): e18657.
-DOI: \\ http://dx.doi.org/10.1371/journal.pone.0018657.}
 

### 2021-04-29 article/article.tex
Updated article

@@
 
-			Similarly, when \texttt{spinsim} is set to spin one mode, it can solve Schroedinger equations of the form
+			Similarly, when \texttt{spinsim} is set to spin one mode, it can solve the Schroedinger equation of the form
 
@@
 				\end{pmatrix},&
-				Q &= \frac{1}{3}\begin{pmatrix}
+				\textrm{and }Q &= \frac{1}{3}\begin{pmatrix}
 					1 &  0 & 0 \\
@@
 
-			\(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadratic operator, proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
+			The matrices \(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadrupole operator.
+Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
 
@@
 			Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\).
-If the system is solved this way, using a geometric method, we can guarantee that \(\psi(t)\) will always be a unit vector, which is not true with solvers in general.
+In other words, for any \(t_0,t \in \mathbb{R}\), there is a unitary transformation \(U(t, t_0)\) such that
 
 			\begin{align*}
-				\psi(t) &= U(t, t_0)\psi(t_0)
+				\psi(t) &= U(t, t_0)\psi(t_0).
 			\end{align*}

### 2021-04-30 article/article.tex
Update to paper
Integrated James's advice on article

@@
 
-			\begin{align*}
+			\begin{align}
 				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) &= -iH(t)\psi(t),
-			\end{align*}
+			\end{align}
 
@@
 
-			\begin{align*}
+			\begin{align}
 				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
-			\end{align*}
+			\end{align}
 
@@
 
-			\begin{align*}
+			\begin{align}
 				J_x &= \frac12\begin{pmatrix}
@@
 				\end{pmatrix}.
-			\end{align*}
+			\end{align}
 
@@
 
-			\begin{align*}
+			\begin{align}
 				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
-			\end{align*}
+			\end{align}
 
@@
 
-			\begin{align*}
+			\begin{align}
 				J_x &= \frac{1}{\sqrt{2}}\begin{pmatrix}
@@
 
-			\begin{align*}
+			\begin{align}
 				\psi(t) &= U(t, t_0)\psi(t_0).
-			\end{align*}
+			\end{align}
 
-			This means that a time series for the state of the system can be evaluated by evaluating the time evolution operator between each of the sample times.
+			This means that a time series for the state of the system can be evaluated by evaluating the time evolution operator between each of the sample times. Consider quantising time with
+			\begin{align}
+				t_k &= t_0 + \mathrm{D}t\cdot k,
+			\end{align}
 
-			\begin{align*}
-				\psi_k &= U_k\psi_{k-1}\textrm{, standing for}\\
-				\psi(t_{k}) &= U(t_{k}, t_{k-1})\psi(t_{k-1})\textrm{, where}\\
-				t_k &= t_0 + \mathrm{D}t\cdot k
-			\end{align*}
+			where \(\mathrm{D}t\) is the time step of the time series (in contrast to \(\mathrm{d}t\), a smaller time step for integration). If we define
 
-			with \(\mathrm{D}t\) the time step of the time series.
+			\begin{align}
+				\psi_k = \psi(t_k)\textrm{ and}\\
+				U_k = U(t_{k}, t_{k-1}),
+			\end{align}
 
-			Also importantly, while each of the \(\psi_k\) must be evaluated sequentially, the value of the \(U_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(U_{k_0}\).
+			then the time series of states \(\psi_k\) and time evolution operators \(U_k\) satisfies
+
+			\begin{align}
+				\psi_k &= U_k\psi_{k-1}\label{eq:integration_compilation}
+			\end{align}
+
+			This presents an opportunity for parallelism.
+While each of the \(\psi_k\) must be evaluated sequentially, the value of the \(U_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(U_{k_0}\).
 This means that the time evolution operators \(U_k\) can all be calculated in parallel, and it allows \texttt{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
@@
 			In summary, \texttt{spinsim} splits the time evolution of the full simulation into time evolution \(U_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
-When all the \(U_k\) are calculated CPU then multiplies the \(U_k\) together (a comparatively less demanding job than calculating them) to determine the \(\psi_k\).
+When all the \(U_k\) are calculated, the CPU then multiplies the \(U_k\) together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the \(\psi_k\).
 
 		\subsubsection*{Rotating frame}
-			If the rotating frame option is selected, the \(U_k\) are first calculated within a local rotating frame as \(U^r_k\), which shrinks the size of the terms used in the calculation, increasing accuracy.
-The midpoint value \(f_r = f_z(t_k + \frac12\mathrm{D}t)\) is sampled to be removed from the source.
-This transforms the source functions as follows,
+			If the rotating frame option is selected, the \(U_k\) are first calculated within a rotating frame of reference as \(U^r_k\), which, in some situations, reduces the size of the source functions used in the calculation, increasing accuracy.
+The rotation speed of the rotating frame is calculated locally for each parallel time step \(U_k\), and only for rotations around the \(z\) axis.
+The rotating from source functions \(f^r_x, f^r_y, f^r_z,\) and \(f^r_q\) are related to the source function from the user input via
 
-			\begin{align*}
+			\begin{align}
 				f^r_x(t) + if^r_y(t) &= e^{-i 2\pi f_r t}(f_x(t) + if_y(t)),\\
-				f^r_z(t) &= f_z(t) - f_r,\\
-				f^r_q(t) &= f_q(t), \textrm{ for spin one.}\\
-			\end{align*}
+				f^r_z(t) &= f_z(t) - f_r\textrm{, and}\\
+				f^r_q(t) &= f_q(t), \textrm{ for spin one.}
+			\end{align}
 
-			This, (assuming that a midpoint sample is representative of an average value over the time interval), decreases the magnitude of \(f_z(t)\), while leaving the other source components at an equivalent magnitude.
-The rotation is then applied to obtain the lab frame time evolution operator \(U_k\),
+			Where \(f_r = f_z(t_k + \frac12\mathrm{D}t)\) is sampled the midpoint value of the source over the interval \([t_{k - 1}, t_k]\).
+This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of \(f_z(t)\), while leaving the other source components at an equivalent magnitude.
+The rotation is then applied to obtain the lab frame time evolution operator \(U_k\) via
 
-			\begin{align*}
-				U_k &= \exp(-i 2 \pi f_r J_z \mathrm{D}t) U^r_k,\\
+			\begin{align}
+				U_k &= \exp(-i 2 \pi f_r J_z \mathrm{D}t) U^r_k.
+			\end{align}
+
+			Specifically, this relationship is
+
+			\begin{align}
 				U_k &= \begin{pmatrix}
@@
 					0 & 0 & e^{i 2\pi f_r \mathrm{D}t}
-				\end{pmatrix} U^r_k, \textrm{ for spin one}\\
+				\end{pmatrix} U^r_k, \textrm{ for spin one, and}\\
 				U_k &= \begin{pmatrix}
@@
 				\end{pmatrix} U^r_k, \textrm{ for spin half.}
-			\end{align*}
+			\end{align}
+
+			It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures \cite{j_j_sakurai_jun_john_modern_1994}.
+Note that this is typically done in conjunction with the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of \(f^r_x, f^r_y, f^r_z,\) and \(f^r_q\) on an average of many cycles do not have a large contribution to time evolution of the solution and can be ignored.
+In some cases, this allows for analytic solutions to the approximate quantum system to be obtained.
+Note that the RWA is \emph{not} invoked in \texttt{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
 
@@
 			The integration method used in \texttt{spinsim} is the CF4 method from Auer et al \cite{auer_magnus_2018}.
-Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller timestep,
+Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller timestep, that is,
 
-			\begin{align*}
+			\begin{align}
 				U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
-				U_k &= u^k_{L-1} \cdots u^k_0,
-			\end{align*}
+				U_k &= u^k_{L-1} \cdots u^k_0,\textrm{, where}\\
+				u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+			\end{align}
 
-			with \(\mathrm{d}t\) being the integration level, (ie, fine) time step.
+			with \(\mathrm{d}t\) being the integration level, (ie, fine) time step. Note that the timesteps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
 
@@
 Let the fine sample time be given by \(t_f = l\mathrm{d}t + t_k\).
-Then as part of the CF4 method, the source functions are sampled at particular times based on the second order Gauss-Legendre quadrature,
+Then as part of the CF4 method, the source functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
 
-			\begin{align*}
-				f(t_1) &= (f_x(t_1), f_y(t_1), f_z(t_1), f_q(t_1)), \textrm{ with}\\
-				t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right),\\
-				f(t_2) &= (f_x(t_2), f_y(t_2), f_z(t_2), f_q(t_2)), \textrm{ with}\\
+			\begin{align}
+				t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
 				t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
-			\end{align*}
+			\end{align}
+
+			Now, let
+			\begin{align}
+				f(t_1) &= (f_x(t_1), f_y(t_1), f_z(t_1), f_q(t_1))\textrm{, and}
+				f(t_2) &= (f_x(t_2), f_y(t_2), f_z(t_2), f_q(t_2)).
+			\end{align}
 
@@
 
-			\begin{align*}
-				g_1 =& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\\
-				g_2 =& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\\
+			\begin{align}
+				g_1 =& (g_{1,x}, g_{1,y}, g_{1,z}, g_{1,q})\\
+				=& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, and}\\
+				g_2 =& (g_{2,x}, g_{2,y}, g_{2,z}, g_{2,q})\\
+				=& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, so}\\
 				u =& \exp(-i \left( g_{2,x} J_x + g_{2,y} J_y + g_{2,z} J_z + g_{2,q} Q\right))\\
 				&\cdot\exp(-i \left( g_{1,x} J_x + g_{1,y} J_y + g_{1,z} J_z + g_{1,q} Q\right)).
-			\end{align*}
+			\end{align}
 
 		\subsubsection*{Exponentiator}
-			For all exponentiation, the exponentiator takes exponent in the form of
+			For all exponentiation, the exponentiator computes the matrix exponential
 
-			\begin{align*}
-				E(g) &= \exp(-i (g_x J_x + g_y J_y + g_z J_z + g_q Q)), \textrm{ with}\\
-				g &= (g_x, g_y, g_z, g_q)
-			\end{align*}
+			\begin{align}
+				E(g) &= E(g_x, g_y, g_z, g_q)\\
+				&= \exp(-i (g_x J_x + g_y J_y + g_z J_z + g_q Q)), \textrm{ with}
+			\end{align}
 
@@
 For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used.
-Importantly, these two methods both use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
+Specifically, the exponential can be approximated as, for large \(\tau\),
 
-			This also means that the package cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8 dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the four dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
-Including the full algebra could be possible as a feature update if there is demand for it, though just including this subspace is sufficient for our application, and many others.
+            \begin{align*}
+                E(g) &= \exp(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q)\\
+                &= \exp(2^{-\tau}(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q))^{2^\tau}\\
+                &\approx (\exp(-i(2^{-\tau} g_x) J_x) \exp(-i(2^{-\tau} g_y) J_y) \exp(-i(2^{-\tau} g_z J_z + (2^{-\tau} g_q) Q)))^{2^\tau}\\
+                &= \begin{pmatrix}
+                    \frac{e^{-i\left(Z + \frac{Q}{3}\right)}(c_X + c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2Q}{3}} (-s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{Q}{3}\right)}(c_X - c_Y + i s_Xs_Y)}{2} \\
+                    \frac{e^{-i\left(Z + \frac{Q}{3}\right)} (-i s_X + c_X s_Y)}{\sqrt{2}} & e^{i\frac{2Q}{3}} c_X c_Y & \frac{e^{-i(Z - \frac{Q}{3})} (-i s_X - c_X s_Y)}{\sqrt{2}} \\
+                    \frac{e^{-i\left(Z + \frac{Q}{3}\right)}(c_X - c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2Q}{3}} (s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{Q}{3}\right)}(c_X + c_Y + i s_Xs_Y)}{2}
+                \end{pmatrix}^{2^\tau}\\
+                &= T^{2^\tau},
+            \end{align*}
+
+			with
+
+            \begin{align*}
+                X &= 2^{-\tau}g_x,\\
+                Y &= 2^{-\tau}g_y,\\
+                Z &= 2^{-\tau}g_z,\\
+                Q &= 2^{-\tau}g_q,\\
+                c_{\theta} &= \cos(\theta),\\
+                s_{\theta} &= \sin(\theta).
+            \end{align*}
+
+			Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(g)\).
+The approach used for spin one exponentiation means that the package cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8 dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the four dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
+Including the full algebra could be possible as a feature update if there is demand for it, though just including this subspace is sufficient for our application, and many others, and has the advantage of being able to use this faster, more specialised method of matrix exponentiation.
+
+			Note that, the methods for both spin half and spin one use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
+This guarantees that the results of \texttt{spinsim} maintain unitary.
 
@@
 
-			When the loop has finished, if the rotating frame is being used, \(U^r_k\) is transformed to \(U_k\) as above, and this is returned.
+			When the loop has finished, if the rotating frame is being used, \(U^r_k\) is transformed to \(U_k\) as in Equation \eqref{eq:integration_compilation}, and this is returned.
 Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \texttt{numba.jit()}ed function from the \(U_k\) and an initial condition \(\psi_{\mathrm{init}}\).
@@
 			The \texttt{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
-The particular device functions used are not predetermined, but are instead chosen based off user input to decide a closure.
+The particular device functions used are not predetermined, but are instead chosen based on user input to decide a closure.
 This structure has multiple advantages.
-Firstly, the source function \(f\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
+First, the source function \(f\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
 This allows users to define \(f\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
@@
 			This functionality is interfaced through an object of class \texttt{spinsim.Simulator}.
-The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection (that is, Bloch vector.
-Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object).
+The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection (that is, Bloch vector).
+Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object.
 
@@
 Rubidium BECs can potentially be made sensitive enough to these tiny magnetic fields that they can be measured by them.
-An array of BECs can theoretically be made to sample the frequency components of the magnetic signal, essentially making a Fourier transform of it, which can be transformed back.
-Assuming that pulses do not occur very often (the signal is sparse in the time domain), a smaller BEC array with fewer frequency samples can be used to create a compressed measurement, reconstructed with theory from the field of compressive sensing \cite{candes_introduction_2008}.
 \texttt{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
+The package is also now being used to simulate other BEC magnetometry experiments by the lab group.
 
@@
 MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \texttt{spinsim} simulations of spins at different positions in space.
-While this package offers some advantages over state of the art simulators in the field \cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are likely its downfall here.
+While this package offers some advantages over state of the art simulators in the field \cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
 

### 2021-04-30 article/article.tex
Started writing up comparison for article

@@
 					0 &  i &  0
-				\end{pmatrix},\\
+				\end{pmatrix},\nonumber\\
 				J_z &= \begin{pmatrix}
@@
 
-            \begin{align*}
+            \begin{align}
                 E(g) &= \exp(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q)\\
@@
                 &= \begin{pmatrix}
-                    \frac{e^{-i\left(Z + \frac{Q}{3}\right)}(c_X + c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2Q}{3}} (-s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{Q}{3}\right)}(c_X - c_Y + i s_Xs_Y)}{2} \\
-                    \frac{e^{-i\left(Z + \frac{Q}{3}\right)} (-i s_X + c_X s_Y)}{\sqrt{2}} & e^{i\frac{2Q}{3}} c_X c_Y & \frac{e^{-i(Z - \frac{Q}{3})} (-i s_X - c_X s_Y)}{\sqrt{2}} \\
-                    \frac{e^{-i\left(Z + \frac{Q}{3}\right)}(c_X - c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2Q}{3}} (s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{Q}{3}\right)}(c_X + c_Y + i s_Xs_Y)}{2}
-                \end{pmatrix}^{2^\tau}\\
-                &= T^{2^\tau},
-            \end{align*}
+                    \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X + c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (-s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X - c_Y + i s_Xs_Y)}{2} \\
+                    \frac{e^{-i\left(Z + \frac{P}{3}\right)} (-i s_X + c_X s_Y)}{\sqrt{2}} & e^{i\frac{2P}{3}} c_X c_Y & \frac{e^{-i(Z - \frac{P}{3})} (-i s_X - c_X s_Y)}{\sqrt{2}} \\
+                    \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X - c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X + c_Y + i s_Xs_Y)}{2}
+                \end{pmatrix}^{2^\tau}
+            \end{align}
 
@@
 
-            \begin{align*}
-                X &= 2^{-\tau}g_x,\\
-                Y &= 2^{-\tau}g_y,\\
-                Z &= 2^{-\tau}g_z,\\
-                Q &= 2^{-\tau}g_q,\\
-                c_{\theta} &= \cos(\theta),\\
+            \begin{align}
+                X &= 2^{-\tau}g_x,&
+                Y &= 2^{-\tau}g_y,\nonumber\\
+                Z &= 2^{-\tau}g_z,&
+                P &= 2^{-\tau}g_q,\nonumber\\
+                c_{\theta} &= \cos(\theta),&
                 s_{\theta} &= \sin(\theta).
-            \end{align*}
+            \end{align}
 
@@
 			\begin{itemize}
-				\item {} 
-				Intel Core i7-8750H, a 6 core laptop processor released in 2018. Run with 16GiB of RAM. Air cooled (laptop fan). Base clock speed of 2.2GHz.
+				\item{
+					Computer A\begin{itemize}
+						\item Intel Core i7-8750H, a 6 core laptop processor released in 2018. Run with 16GiB of RAM. Air cooled (laptop fan). Base clock speed of 2.2GHz.
+						\item Nvidia GeForce GTX 1070, a 2048 \emph{Cuda} core laptop graphics processor released in 2016. Run with 8GiB of VRAM. Air cooled (laptop fan).
+					\end{itemize}
+				}
 
-				\item {} 
-				AMD Ryzen 7 5800X, an 8 core desktop processor released in 2020. Run with 32GiB of RAM. Liquid cooled. Base clock speed of 3.8GHz.
+				\item{Computer B\begin{itemize}
+						\item AMD Ryzen 9 5900X, a 12 core desktop processor released in 2020. Run with 32GiB of RAM. Air cooled. Base clock speed of 3.7GHz.
+						\item Nvidia GeForce RTX 3070, a 5888 \emph{Cuda} core desktop graphics processor released in 2020. Run with 8GiB of VRAM. Air cooled.
+					\end{itemize}
+				}
 
-				\item {} 
-				AMD Ryzen 9 5900X, a 12 core desktop processor released in 2020. Run with 32GiB of RAM. Air cooled. Base clock speed of 3.7GHz.
-
-				\item {} 
-				Nvidia GeForce GTX 1070, a 2048 \emph{Cuda} core laptop graphics processor released in 2016. Run with 8GiB of VRAM. Air cooled (laptop fan).
-
-				\item {} 
-				Nvidia GeForce RTX 3070, a 5888 \emph{Cuda} core desktop graphics processor released in 2020. Run with 8GiB of VRAM. Air cooled.
-
-				\item {} 
-				Nvidia GeForce RTX 3080, an 8704 \emph{Cuda} core desktop graphics processor released in 2020. Run with 10GiB of VRAM. Air cooled.
+				\item{Computer C\begin{itemize}
+						\item AMD Ryzen 7 5800X, an 8 core desktop processor released in 2020. Run with 32GiB of RAM. Liquid cooled. Base clock speed of 3.8GHz.
+						\item Nvidia GeForce RTX 3080, an 8704 \emph{Cuda} core desktop graphics processor released in 2020. Run with 10GiB of VRAM. Air cooled.
+					\end{itemize}
+				}
 			\end{itemize}
@@
 		\subsubsection*{Comparison to alternatives}
-			As mentioned before, compared to our previous code, \texttt{AtomicPy}, the best performing \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.
+			We compared \texttt{spinsim} to other separate packages.
+These were all run on computer C, which from Figure \ref{fig:benchmark_device_aggregate} has the fastest CPU (liquid cooled AMD Ryzen 7 5800X) and GPU (Nvidia GeForce RTX 3080).
+The packages compared were:
+			\begin{itemize}
+				\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode.
+				\item \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, the previous custom written \emph{cython} based code developed by our lab group.
+				\item \texttt{NDSolve} from the \emph{Mathematica} \cite{wolfram_research_inc_mathematica_2020} software.
+This was chosen as it is popular with our lab group for simulating magnetometry experiments.
+				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}. This was chosen as a generic solver from within the python ecosystem.
+				\item We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
+However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
+			\end{itemize}
 
-			Another solver used by the lab group is \emph{Mathematica}'s \texttt{NDSolve}.
+			We 
+			% Compared to our previous code, \texttt{AtomicPy}, the best performing (default) spin one \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster on computer A.
+Another popular solver used by the lab group for magnetometry simulations is \emph{Mathematica}'s \cite{wolfram_research_inc_mathematica_2020} \texttt{NDSolve}.
+For a comparison between python packages, we also
 
-			We had planned to benchmark against some other popular generic solvers.
+			% We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
+However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
+
+			% We had planned to benchmark against some other popular generic solvers.
 One such solver was \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.

### 2021-05-11 article/article.tex
Updates to Lie Trotter exponentiator

@@
 
-			The fine time evolution operator can then be calculated using
+			The integration time evolution operator can then be calculated using
 
@@
 The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(f\) describing how to sample the source Hamiltonian.
-The code then loops over each fine time step \(\mathrm{d}t\) to calculate the fine time evolution operators \(u^k_l\).
+The code then loops over each integration time step \(\mathrm{d}t\) to calculate the integration time evolution operators \(u^k_l\).
 
@@
 This is shown in Figure \ref{fig:benchmark_device_aggregate}.
-The integration code was compiled by \texttt{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different devices.
-These devices are,
+The integration code was compiled by \texttt{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different models of each of them.
+These test devices are,
 			\begin{itemize}
@@
 
-		\subsubsection*{Accuracy}
-			Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for), by comparing state evaluations of many different typical sensing experiments and finding the mean error introduced when the fine (integration) time step is increased.
+		\subsubsection*{Evaluation of techniques}
+			Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for).
+We first wanted to test the accuracy of the different integration techniques for various integration time steps.
+This accuracy was calculated by taking state evaluations of a typical quantum sensing expeirment and finding the Root Mean Squared (RMS) to a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
 
-			\begin{figure}[h!]
-				\includegraphics[scale=0.9]{benchmark_comparison_spin_one_publication.pdf}
-				\caption{Fine time step benchmark for spin one systems.
+			\begin{align}
+                \epsilon_{\mathrm{d}t} &= \frac{1}{3\cdot K}\sqrt{\sum_{k = 0}^{K - 1}\sum_{m_s = -1}^1|\psi_{k, (m_s)}^{\mathrm{d}t} - \psi_{k, (m_s)}^{\textrm{baseline}}|^2}.
+            \end{align}
+
+			This baseline was computed in 3.8 hours, and was also used for comparisons to other software packages.
+For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, for any given integration time step the CF4 method is slower.
+In all of these comparisons, errors above \(10^-1\) were counted as a failed simulation (as the maximum possible error for a quantum state saturates at order \(10^0\)).
+
+			The integration techniques tested were
+			\begin{itemize}
+				\item The Magnus based method Commutator Free 4. Abbreviated CF4.
+				\item The Euler based half step method used in the previous version of our code, where two Euler steps are made in each iteration, one sampled from the left, and one from the right.
+Abbreviated HS.
+				\item The Euler based midpoint method, where a single sample is made from the midpoint of the interval being stepped over. Abbreviated MP.
+			\end{itemize}
+
+			We benchmarked these methods both while using the rotating frame option (abbreviated RF), and not (abbreviated LF, for Lab Frame).
+
+			% \begin{figure}[h!]
+			% 	\includegraphics[scale=0.9]{benchmark_comparison_spin_one_publication.pdf}
+			% 	\caption{Fine time step benchmark for spin one systems.
 CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
 HS and MP results are drawn on top of each other due to their similarities.}
-				\label{fig:benchmark_comparison_spin_one}
-			\end{figure}
+			% 	\label{fig:benchmark_comparison_spin_one}
+			% \end{figure}
 
-			Figure \ref{fig:benchmark_comparison_spin_one} shows the performance of \texttt{spinsim} when running in spin one mode.
+			% Figure \ref{fig:benchmark_comparison_spin_one} shows the performance of \texttt{spinsim} when running in spin one mode.
 This shows that both using the Magnus based CF4 method and moving into a rotating frame give significant increases to accuracy.
@@
 
-			\begin{figure}[h!]
-				\includegraphics[scale=0.9]{benchmark_comparison_spin_half_lt_publication.pdf}
-				\caption{Fine time step benchmark for spin half systems, using the Lie Trotter based exponentiator.
+			% \begin{figure}[h!]
+			% 	\includegraphics[scale=0.9]{benchmark_comparison_spin_half_lt_publication.pdf}
+			% 	\caption{Fine time step benchmark for spin half systems, using the Lie Trotter based exponentiator.
 CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
 HS and MP results are drawn on top of each other due to their similarities.}
-				\label{fig:benchmark_comparison_spin_half_lt}
-			\end{figure}
+			% 	\label{fig:benchmark_comparison_spin_half_lt}
+			% \end{figure}
 
-			From Figure \ref{fig:benchmark_comparison_spin_half_lt}, one gets essentially the same accuracy for each method when working in spin half mode compared to spin one, if all else is kept constant.
+			% From Figure \ref{fig:benchmark_comparison_spin_half_lt}, one gets essentially the same accuracy for each method when working in spin half mode compared to spin one, if all else is kept constant.
 
-			\begin{figure}[h!]
-				\includegraphics[scale=0.9]{benchmark_comparison_spin_half_a_publication.pdf}
-				\caption{Fine time step benchmark for spin half systems, using the analytic based exponentiator.
+			% \begin{figure}[h!]
+			% 	\includegraphics[scale=0.9]{benchmark_comparison_spin_half_a_publication.pdf}
+			% 	\caption{Fine time step benchmark for spin half systems, using the analytic based exponentiator.
 CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
 HS and MP results are drawn on top of each other due to their similarities.}
-				\label{fig:benchmark_comparison_spin_half_a}
-			\end{figure}
+			% 	\label{fig:benchmark_comparison_spin_half_a}
+			% \end{figure}
 
-			Figure \ref{fig:benchmark_comparison_spin_half_a} shows that the Lie Trotter based exponentiator does limit the maximum accuracy obtainable, and for spin half systems, one can increase accuracy further (and decrease execution time) by using an analytic based exponentiator.
+			% Figure \ref{fig:benchmark_comparison_spin_half_a} shows that the Lie Trotter based exponentiator does limit the maximum accuracy obtainable, and for spin half systems, one can increase accuracy further (and decrease execution time) by using an analytic based exponentiator.
 
@@
 We also planned to benchmark accuracy against the generic solver \texttt{scipy.integrate.ivp\_solve()} in the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}.
-However, using the same \texttt{get\_field} function as in the spin one benchmarks used for the \texttt{spinsim}, simulating with a fine time step of 500ns (the largest used during the \texttt{spinsim} benchmarks), we found that a single simulation ran in 153s, which is over three orders of magnitude slower than the most accurate \texttt{spinsim} simulations.
+However, using the same \texttt{get\_field} function as in the spin one benchmarks used for the \texttt{spinsim}, simulating with a integration time step of 500ns (the largest used during the \texttt{spinsim} benchmarks), we found that a single simulation ran in 153s, which is over three orders of magnitude slower than the most accurate \texttt{spinsim} simulations.
 This means that a generous projection for the time it would take to run the same benchmarks that \texttt{spinsim} runs in 11 minutes, using \texttt{scipy} would be over six days; for an integration package not designed for this problem (and would therefore likely be less accurate).
@@
 This was done for every combination of integrator settings possible when compiling the integrator.
-The system was benchmarked in terms of accuracy vs fine time step, again, using every possible combination of integrator settings.
+The system was benchmarked in terms of accuracy vs integration time step, again, using every possible combination of integrator settings.
 This confirms that no integrator diverges away from the limiting solution when the time step is decreased in magnitude.

### 2021-05-11 docs/source/conf.py

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.1.8'
+release = '0.1.14'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-05-11 spinsim/__init__.py

@@ -325,7 +325,7 @@ class Simulator:
         
         * **spin** (:obj:`numpy.ndarray` of :obj:`numpy.float64` (time_index, spatial_direction)) - The expected spin projection (Bloch vector) over time.
     """
-    def __init__(self, get_field, spin_quantum_number, device = None, exponentiation_method = None, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF4, trotter_cutoff = 28, threads_per_block = 64, max_registers = 63):
+    def __init__(self, get_field, spin_quantum_number, device = None, exponentiation_method = None, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF4, trotter_cutoff = 32, threads_per_block = 64, max_registers = 63):
         """
         .. _Achieved Occupancy: https://docs.nvidia.com/gameworks/content/developertools/desktop/analysis/report/cudaexperiments/kernellevel/achievedoccupancy.htm
 
@@ -822,7 +822,7 @@ class Simulator:
             An object containing the results of the simulation.
         """
         if math.fabs(time_step_output/time_step_integration - round(time_step_output/time_step_integration)) > 1e-6:
-            print(f"\033[31mspinsim warning: time_step_output not an integer multiple of time_step_integration. Resetting time_step_integration to {time_step_output/round(time_step_output/time_step_integration):e8.4}.\033[0m\n")
+            print(f"\033[33mspinsim warning: time_step_output not an integer multiple of time_step_integration. Resetting time_step_integration to {time_step_output/round(time_step_output/time_step_integration):8.4e}.\033[0m\n")
         time_step_integration = time_step_output/round(time_step_output/time_step_integration)
 
 
@@ -1328,22 +1328,25 @@ class Utilities:
                     hyper_cube_amount = 0
                 precision = 4**hyper_cube_amount
                 
-                x = field_sample[0]/(2*precision)
-                y = field_sample[1]/(2*precision)
-                z = field_sample[2]/(2*precision)
+                a = math.sqrt(field_sample[0]*field_sample[0] + field_sample[1]*field_sample[1])
+                ep = (field_sample[0] + 1j*field_sample[1])/a
+                a = a/precision
 
-                cx = math.cos(x)
[…]

### 2021-05-13 article/article.tex
Draft 2 of article

@@
-%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham Universtiy, UK.
+%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham University, UK.
 
@@
 \usepackage{cite}
-\usepackage{graphicx}
+\usepackage{graphicx, subcaption}
 \graphicspath{ {images/} }
@@
 \section*{Title}
-spinsim: a GPU optimised solver of spin half and spin one quantum systems
+spinsim: a GPU optimised simulator of spin half and spin one quantum systems
 
@@
 The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
-The simplest spin system, spin half (also referred to as a qubit), is quantised into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
-However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin one quantum system (also referred to as a quitrit), which is quantised into three quantum spin levels.
+The simplest spin system, spin half (ie spin quantum number of \(\frac12\), also referred to as a qubit), is quantised into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
+However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin one quantum system (ie spin quantum number of \(1\), also referred to as a quitrit), which is quantised into three quantum spin levels.
 
@@
 
-	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schroedinger equation for quantum sensing spin systems.
-These spin one systems  are sometimes approximated to spin half for a faster execution time, at the cost of modelling all effects of the system.
+	% \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}
+	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schroedinger equation for quantum sensing spin systems.
+Spin one systems are sometimes approximated to spin half for a faster execution time, at the cost of modelling all effects of the system.
 However, these methods are not completely optimised for our use case, and therefore come with some issues.
@@
 Standard integration methods require very small time steps in order to accurately depict these oscillations.
-For instance, we found that the integration method used by \emph{AtomicPy} has an accuracy of only order \(10^{-2}\) when the integration time step is set to the small value of 10ns.
 
@@
 
-			where \(i^2 = -1\), the state \(\psi(t) \in \mathbb{C}^N\) a time dependent, \(N\) dimensional, unit complex vector, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is a time dependent \(N \times N\) complex Hermitian matrix.
+			where \(i^2 = -1\), the quantum state \(\psi(t) \in \mathbb{C}^N\) a time dependent, \(N\) dimensional, unit complex vector, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is a time dependent \(N \times N\) complex Hermitian matrix.
 Here \(N\) is the number spin levels in the quantum system, so spin half is the \(N = 2\) case, and spin one refers to the \(N = 3\) case.
-Rather than being represented by standard coodintaes in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
+Rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
 For example, when set to spin half mode, the \texttt{spinsim} package solves the time dependent Schroedinger equations of the form
@@
 Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
+
+			Frequently when one calculates the times series of the quantum state \(\psi(t)\), they are also interested in its expected spin projection \(\left\langle J\right\rangle\)(t).
+It is given by the vector
+
+			\begin{align}
+				\left\langle J\right\rangle(t) &= \begin{pmatrix}
+					\psi(t)^\dagger J_x \psi(t)\\
+					\psi(t)^\dagger J_y \psi(t)\\
+					\psi(t)^\dagger J_z \psi(t)
+				\end{pmatrix},
+			\end{align}
+
+			where \(\cdot^\dagger\) is the adjoint operator (also referred to as Hermitian conjugate, and is implemented as complex conjugate transpose).
+The expected spin projection can be interpreted as the average direction that the spin system is oriented in space when many systems of the equivalent state are measured (due to the Heisenberg uncertainty principle, only one component of the exact orientation of a quantum state can be known at any point in time, which is why we need to deal with expected values rather than absolute values).
+However, it can also be used to model the overall orientation of an ensemble of many quantum systems, like a BEC, for instance.
+\texttt{spinsim} has the functionality to calculate the expected spin projection of a system from its state.
 
@@
 			The integration method used in \texttt{spinsim} is the CF4 method from Auer et al \cite{auer_magnus_2018}.
-Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller timestep, that is,
+Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
 
@@
 				U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
-				U_k &= u^k_{L-1} \cdots u^k_0,\textrm{, where}\\
+				U_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
 				u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
@@
 
-			with \(\mathrm{d}t\) being the integration level, (ie, fine) time step. Note that the timesteps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
+			with \(\mathrm{d}t\) being the integration level time step. Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
 
@@
 			For spin half, the default exponentiator is in an analytic form.
-For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used.
-Specifically, the exponential can be approximated as, for large \(\tau\),
+For spin one, a simple analytic form cannot be written, so instead an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used.
+Explicitly, this formula is
 
 			\begin{align}
-                E(g) &= \exp(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q)\\
-                &= \exp(2^{-\tau}(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q))^{2^\tau}\\
-                &\approx (\exp(-i(2^{-\tau} g_x) J_x) \exp(-i(2^{-\tau} g_y) J_y) \exp(-i(2^{-\tau} g_z J_z + (2^{-\tau} g_q) Q)))^{2^\tau}\\
-                &= \begin{pmatrix}
-                    \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X + c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (-s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X - c_Y + i s_Xs_Y)}{2} \\
-                    \frac{e^{-i\left(Z + \frac{P}{3}\right)} (-i s_X + c_X s_Y)}{\sqrt{2}} & e^{i\frac{2P}{3}} c_X c_Y & \frac{e^{-i(Z - \frac{P}{3})} (-i s_X - c_X s_Y)}{\sqrt{2}} \\
-                    \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X - c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X + c_Y + i s_Xs_Y)}{2}
-                \end{pmatrix}^{2^\tau}
+				\exp\left( A + B\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{A}{n}\right) \exp\left(\frac{B}{n}\right)\right)^n
 			\end{align}
 
-			with
+			Where \(A,B\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
+The equality holds for without the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
+This tells us that we can approximate a matrix exponential of a linear combination of spin operators by reducing the size of the coefficients of these operators, taking the analytically known exponentials of each of the operators separately, multiplying each individual result together, and then raising the combination \(T\) to the power of the original reduction.
+For our spin one case, the exponential \(E(g)\) can be approximated as, for large \(2^\tau\),
+
+            % \begin{align}
+            %     E(g) &= \exp(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q)\\
+            %     &= \exp(2^{-\tau}(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q))^{2^\tau}\\
+            %     &\approx (\exp(-i(2^{-\tau} g_x) J_x) \exp(-i(2^{-\tau} g_y) J_y) \exp(-i(2^{-\tau} g_z J_z + (2^{-\tau} g_q) Q)))^{2^\tau}\\
+            %     &= \begin{pmatrix}
+            %         \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X + c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (-s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X - c_Y + i s_Xs_Y)}{2} \\
+            %         \frac{e^{-i\left(Z + \frac{P}{3}\right)} (-i s_X + c_X s_Y)}{\sqrt{2}} & e^{i\frac{2P}{3}} c_X c_Y & \frac{e^{-i(Z - \frac{P}{3})} (-i s_X - c_X s_Y)}{\sqrt{2}} \\
+            %         \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X - c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X + c_Y + i s_Xs_Y)}{2}
+            %     \end{pmatrix}^{2^\tau}
+            % \end{align}
 
 			\begin{align}
-                X &= 2^{-\tau}g_x,&
-                Y &= 2^{-\tau}g_y,\nonumber\\
-                Z &= 2^{-\tau}g_z,&
-                P &= 2^{-\tau}g_q,\nonumber\\
-                c_{\theta} &= \cos(\theta),&
-                s_{\theta} &= \sin(\theta).
+                E(g) =& \exp\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\\
+                =& \exp\left(2^{-\tau}\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\right)^{2^\tau}\\
+                \approx& \biggl(\exp\left(-i\left(2^{-\tau} \frac12g_z J_z + \left(2^{-\tau}\frac12g_q\right) Q\right)\right)\nonumber\\
+				&\cdot\exp\left(-i\left(2^{-\tau} g_\phi J_\phi\right)\right)\nonumber\\
+				&\cdot\exp\left(-i\left(2^{-\tau} \frac12g_z J_z + \left(2^{-\tau} \frac12g_q\right) Q\right)\right)\biggr)^{2^\tau}\\
+                =& \begin{pmatrix}
+                    \left(\frac{\Gamma}{PZ}\right)^2 & \frac{SP}{Z\Phi} & -\left(\frac{\Sigma P}{\Phi}\right)^2 \\
+					\frac{SP\Phi}{Z} & CP^4 & \frac{SPZ}{\Phi} \\
+					-\left(\frac{\Sigma \Phi}{P}\right)^2 & \frac{SPZ\Phi}{1} & \left(\frac{\Gamma Z}{P}\right)^2
+                \end{pmatrix}^{2^\tau}\\
+				=& T^{2^\tau}.
+            \end{align}
+
+			where
+
+            \begin{align}
+				g_\phi &= \sqrt{g_x^2 + g_y^2}&&\nonumber\\
+				J_\phi &= \frac{g_x}{g_\phi}J_x + \frac{g_y}{g_\phi}J_y&&\nonumber\\
+				\Gamma &= \cos\left(2^{-\tau} \frac{g_\phi}{2}\right) & \Phi &= e^{i2^{-\tau}g_\phi}\nonumber\\
+				\Sigma &= \sin\left(2^{-\tau} \frac{g_\phi}{2}\right) & Z &= e^{i2^{-\tau}\frac{g_z}{2}}\nonumber\\
+				C &= \cos(2^{-\tau} g_\phi) & P &= e^{i2^{-\tau}\frac{g_q}{6}}\nonumber\\
+				S &= \frac{-i}{\sqrt2}\sin(2^{-\tau} g_\phi)&&
             \end{align}
@@
 This allows users to define \(f\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
-Compiling the simulator also allows the user to set metaparameters, and choose the features they want to use, in a way that does not require experience with the \texttt{numba.cuda} library.
+Compiling the simulator also allows the user to set meta parameters, and choose the features they want to use, in a way that does not require experience with the \texttt{numba.cuda} library.
 This was especially useful for running benchmarks comparing old integration methods to the new ones, like CF4.
-The default settings should be optimal for most users, although tuning the values of \emph{Cuda} metaparameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile GTX1070 mainly used in testing here.
+The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile GTX1070 mainly used in testing here.
 Finally, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.
@@
 		\subsubsection*{Speed}
+			\begin{figure}[htbp!]
+				\centering
+				\includegraphics[scale=0.7]{benchmark_device_aggregate.pdf}
+				\caption{Evaluation speed of a typical spin one sensing experiment.
+Fine time step is 100ns, as determined to be ideal by the accuracy experiments.
+Experiments run for a duration of 100ms.
+Evaluation time is determined by an average of 100 similar experiments for each device.}
+				\label{fig:benchmark_device_aggregate}
+			\end{figure}
+
 			Benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin one sensing experiments on different devices.
@@
 
-			\begin{figure}[h!]
-				\includegraphics[scale=0.9]{benchmark_device_aggregate_publication.pdf}
-				\caption{Evaluation speed of a typical spin one sensing experiment.
-Fine time step is 100ns, as determined to be ideal by the accuracy experiments.
-Experiments run for a duration of 100ms.
-Evaluation time is determined by an average of 100 similar experiments for each device.}
-				\label{fig:benchmark_device_aggregate}
-			\end{figure}
-
 			This benchmark shows the benefit to using parallelisation when solving this problem.
@@
 		\subsubsection*{Evaluation of techniques}
+		All subsequent benchmarks were run on computer C, which from Figure \ref{fig:benchmark_device_aggregate} has the fastest CPU (liquid cooled AMD Ryzen 7 5800X) and GPU (Nvidia GeForce RTX 3080).
 Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for).
 We first wanted to test the accuracy of the different integration techniques for various integration time steps.
-This accuracy was calculated by taking state evaluations of a typical quantum sensing expeirment and finding the Root Mean Squared (RMS) to a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
+This accuracy was calculated by taking state evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) to a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
 
 			\begin{align}
-                \epsilon_{\mathrm{d}t} &= \frac{1}{3\cdot K}\sqrt{\sum_{k = 0}^{K - 1}\sum_{m_s = -1}^1|\psi_{k, (m_s)}^{\mathrm{d}t} - \psi_{k, (m_s)}^{\textrm{baseline}}|^2}.
+                \epsilon &= \frac{1}{K}\sqrt{\sum_{k = 0}^{K - 1}\sum_{m_j = -j}^j|\psi_{k, (m_j)} - \psi_{k, (m_j)}^{\textrm{baseline}}|^2},\label{eq:error}
             \end{align}
 
+			where \(j \in \{\frac12, 1\}\) is the spin quantum number of the system.
+This quantum sensing experiment involves continuously driving transitions in the system, while exposing it to a short pulsed signal that the system should be able to sense.
+It runs over a duration of 1ms.
+
 			This baseline was computed in 3.8 hours, and was also used for comparisons to other software packages.
-For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, for any given integration time step the CF4 method is slower.
-In all of these comparisons, errors above \(10^-1\) were counted as a failed simulation (as the maximum possible error for a quantum state saturates at order \(10^0\)).
+These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, \ref{fig:benchmark_spin_half_step_error}, and \ref{fig:benchmark_spin_half_trotter_step_error}.
+For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, the CF4 method is slower for any fixed integration time step.
+These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, \ref{fig:benchmark_spin_half_execution_error}, and \ref{fig:benchmark_spin_half_trotter_execution_error}.
+In all of these comparisons, errors above \(10^{-3}\) were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
 
@@
 			\begin{itemize}
-				\item The Magnus based method Commutator Free 4. Abbreviated CF4.
+				\item The Magnus based method Commutator Free 4. Abbreviated as CF4.
 				\item The Euler based half step method used in the previous version of our code, where two Euler steps are made in each iteration, one sampled from the left, and one from the right.
-Abbreviated HS.
-				\item The Euler based midpoint method, where a single sample is made from the midpoint of the interval being stepped over. Abbreviated MP.
+Abbreviated as HS.
+				\item The Euler based midpoint method, where a single sample is made from the midpoint of the interval being stepped over. Abbreviated as MP.
 			\end{itemize}
 
-			We benchmarked these methods both while using the rotating frame option (abbreviated RF), and not (abbreviated LF, for Lab Frame).
+			We benchmarked these methods both while using the rotating frame option (abbreviated as RF), and not (abbreviated as LF, for lab frame).
+The spin half simulations were benchmarked using both the analytic based exponentiator,and the Lie Trotter based exponentiator.
+This was done separately for spin one and spin half systems, to ensure they all yield accurate results.
+
+			From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \texttt{spinsim} gives are accurate to those of \emph{SciPy}.
+Figures \ref{fig:benchmark_spin_one_step_error}, \ref{fig:benchmark_spin_half_step_error}, and \ref{fig:benchmark_spin_half_trotter_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
+Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
+From Figures \ref{fig:benchmark_spin_one_execution_error}, \ref{fig:benchmark_spin_half_execution_error}, and \ref{fig:benchmark_spin_half_trotter_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
+Thus, by default \texttt{spinsim} sets the integrator to CF4, and uses the rotating frame.
+These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
+
+			\begin{figure}[h!]
+				\begin{subfigure}[b]{0.45\textwidth}
+					\includegraphics[scale=0.45]{benchmark_spin_one_step_error.pdf}
+					\caption{Accuracy of the spin one options of \texttt{spinsim}.}
+					\label{fig:benchmark_spin_one_step_error}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{0.45\textwidth}
+					\includegraphics[scale=0.45]{benchmark_spin_one_execution_error.pdf}
+					\caption{Speed vs accuracy of the spin one options of \texttt{spinsim}.}
+					\label{fig:benchmark_spin_one_execution_error}
+				\end{subfigure}\
+				\caption{Speed and accuracy of the spin one options of \texttt{spinsim}.}
+				\label{fig:benchmark_spin_one}
+			\end{figure}
+
+			The that the accuracy of spin half simulations using the Lie Trotter based exponentiator in Figure \ref{fig:benchmark_spin_half_trotter_step_error} plateaus below \(10^{-8}\), whereas an accuracy below \(10^{-12}\) is able to be obtained when when the analytic exponentiator in Figure \ref{fig:benchmark_spin_half_step_error} is used.
+This also explains the plateau in accuracy from the spin one integrator, where the Lie Trotter based method is the only method implemented.
+Furthermore, the analytic exponentiator is much faster in Figure \ref{fig:benchmark_spin_half_execution_error}, as compared to the Lie Trotter based integrator in Figure \ref{fig:benchmark_spin_half_trotter_execution_error}.
+Hence, the analytic exponentiator is the default option for \texttt{spinsim} simulations when in spin half mode.
+
+			\begin{figure}[h!]
+				\begin{subfigure}[b]{0.45\textwidth}
+					\includegraphics[scale=0.45]{benchmark_spin_half_step_error.pdf}
+					\caption{Accuracy of the spin half options of \texttt{spinsim}, using the analytic exponentiator.}
+					\label{fig:benchmark_spin_half_step_error}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{0.45\textwidth}
+					\includegraphics[scale=0.45]{benchmark_spin_half_execution_error.pdf}
+					\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}, using the analytic exponentiator.}
+					\label{fig:benchmark_spin_half_execution_error}
+				\end{subfigure}\
+				\vfill
+				\begin{subfigure}[b]{0.45\textwidth}
+					\includegraphics[scale=0.45]{benchmark_spin_half_trotter_step_error.pdf}
+					\caption{Accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
+					\label{fig:benchmark_spin_half_trotter_step_error}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{0.45\textwidth}
+					\includegraphics[scale=0.45]{benchmark_spin_half_trotter_execution_error.pdf}
+					\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
+					\label{fig:benchmark_spin_half_trotter_execution_error}
+				\end{subfigure}\
+				\caption{Speed and accuracy of the spin half options of \texttt{spinsim}.}
+				\label{fig:benchmark_spin_half}
+			\end{figure}
 
@@
 		\subsubsection*{Comparison to alternatives}
-			We compared \texttt{spinsim} to other separate packages.
-These were all run on computer C, which from Figure \ref{fig:benchmark_device_aggregate} has the fastest CPU (liquid cooled AMD Ryzen 7 5800X) and GPU (Nvidia GeForce RTX 3080).
-The packages compared were:
+			We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \texttt{spinsim}'s performance to theirs. The packages compared were:
 			\begin{itemize}
-				\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode.
-				\item \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, the previous custom written \emph{cython} based code developed by our lab group.
+				\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode, which were the highest performing options when comparing \texttt{spinsim} integration methods.
+Abbreviated as ss.
+				% \item \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, the previous custom written \emph{cython} based code developed by our lab group.
 				\item \texttt{NDSolve} from the \emph{Mathematica} \cite{wolfram_research_inc_mathematica_2020} software.
 This was chosen as it is popular with our lab group for simulating magnetometry experiments.
-				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}. This was chosen as a generic solver from within the python ecosystem.
+Abbreviated as mm.
+				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}.
+This was chosen as a generic solver from within the python ecosystem.
+Abbreviated as sp.
 				\item We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
@@
 
-			We 
+			In each case, the step sizes of the alternative integrators were limited to a maximum value obtain simulation results of different accuracies.
+Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
+Similarly to with the internal \texttt{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
+Also like with the internal benchmarks, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as both \emph{Mathematica} and \texttt{spinsim} plateau in accuracy at small time steps.
+
+			Each benchmark was run one simulation at a time, however it might be possible to increase the average speed of many benchmarks from alternative packages using multithreading to run multiple benchmarks at a time.
+When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
+Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the benchmark only single threaded uses up a day of computational time.
+But to be fair, both \emph{Mathematica} and \emph{SciPy} benchmarks are plotted with an artificial reduction in execution time by a factor of 4 and 8, which is an upper bound for the speed increase that could be obtained by running them parallel on a 4 and 8 core processor, respectively.
+These are respectively shown in plots as disconnected \(+\) and \(\times\).
+
+			From Figure \ref{fig:benchmark_external}, if an error of \(10^{-8}\) is acceptable, \texttt{spinsim} is 3 orders of magnitude faster than \emph{Mathematica}, and 4 orders of magnitude faster than \emph{SciPy}.
+In practice, this means that an 8 minute \emph{SciPy} simulation is reduced to 50ms, and a full week long batch simulation of 1000 separate systems (a realistic situation for quantum sensing protocols) would take less than one minute.
+With that said, if a smaller error is needed, it also plateaus at a greater minimum error than its alternatives, with \emph{Mathematica} having a minimum error less than \(10^{-10}\), and \emph{SciPy} not plateauing during the benchmark.
+However, for the vast majority of use cases, an error of \(10^{-8}\) is acceptable, and \texttt{spinsim} has vastly better performance in terms of speed and accuracy.
+
+			\begin{figure}[h!]
+				\includegraphics[scale=0.9]{benchmark_external_execution_error.pdf}
+				\caption{Speed vs accuracy of various integration packages.}
+				\label{fig:benchmark_external}
+			\end{figure}
 			% Compared to our previous code, \texttt{AtomicPy}, the best performing (default) spin one \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster on computer A.
@@
 	\subsection*{Testing}
-		The simulator as a whole has been functionally tested against well known analytic approximations of the behaviour spin systems.
-This was done for every combination of integrator settings possible when compiling the integrator.
-The system was benchmarked in terms of accuracy vs integration time step, again, using every possible combination of integrator settings.
-This confirms that no integrator diverges away from the limiting solution when the time step is decreased in magnitude.
+		During the accuracy tests, it was confirmed that all possible modes of \texttt{spinsim} agree with a standard \emph{SciPy} simulation up to a small error.
 The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.
-
 These tests and benchmarks were run as part of the \texttt{neural\_sense} package.
@@
 		The kernel execution was profiled thoroughly, and changes were made to optimise VRAM and register usage and transfer.
-This was done specifically for the hardware of an Nvidia GTX1070, so one may get some performance increases by changing some GPU specific metaparameters when instantiating the \texttt{spinsim.Simulator} object.
+This was done specifically for the development hardware of computer A with an \emph{Nvidia} GTX1070, so one may get some performance increases by changing some GPU specific meta parameters when instantiating the \texttt{spinsim.Simulator} object.
 
 		A good way to confirm that \texttt{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
-Otherwise, one can run the benchmarks and simulation protocols in \texttt{neural\_sense.sim.benchmark}.
+Otherwise, one can reproduce the benchmarks shown here using \texttt{neural\_sense.sim.benchmark}.
 
@@
 \section*{Operating system}
-Developed on Windows 10. Tested on MacOS Big Sur.
+Developed and tested on Windows 10.
+CPU functionality tested on MacOS Big Sur (note that modern Mac computers are not compatible with \emph{Cuda} software).
+All packages referenced in \texttt{spinsim} are compatible with Linux, but functionality has not been tested.
 
@@
 \section*{Additional system requirements}
-To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \href{https://developer.nvidia.com/cuda-gpus}{\emph{Cuda} compatible \emph{Nvidia GPU}}.
-For \emph{Cuda} mode to function, one also needs to install the \href{https://developer.nvidia.com/cuda-toolkit}{\emph{Nvidia Cuda} toolkit}.
-If \emph{Cuda} is not available on the system, the simulator will automatically parallelise over multicore CPUs instead
+To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU \cite{noauthor_cuda_2012}.
+For \emph{Cuda} mode to function, one also needs to install the \emph{Nvidia Cuda} toolkit \cite{noauthor_cuda_2013}.
+If \emph{Cuda} is not available on the system, the simulator will automatically parallelise over multicore CPUs instead.
 
@@
 	\item[Name:] Monash Bridges
-	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
-	\item[Licence:] BSD 3 Clause
+	\item[Persistent identifier:] 10.26180/13285460
+	\item[Licence:] Apache 2.0
 	\item[Publisher:]  Alex Tritt
@@
 This is immediately relevant to developing new quantum sensing protocols with spin half and spin one systems.
-The package will be used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab, both within and outside the project it was conceived for.
+This package is being used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab.
 
@@
 
-Thank you to Hamish Taylor and Travis Hartley from the Monash University School of Physics and Astronomy spinor BEC lab, who have started using \texttt{spinsim} for their own projects and have given feedback of their user experience with the package.
+Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group, particularly Hamish Taylor and Travis Hartley, who have started using \texttt{spinsim} for their own projects and have given useful feedback of their user experience with the package.
 

### 2021-05-26 article/article.tex
Article draft 3 and version 0.2.1

@@
 
-	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours.
+	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
 
@@
 		\subsubsection*{Magnus based integration method}
-			The integration method used in \texttt{spinsim} is the CF4 method from Auer et al \cite{auer_magnus_2018}.
+			The integration method used in \texttt{spinsim} is the commutator free 4 (CF4) method from Auer et al \cite{auer_magnus_2018}, which based on the Magnus expansion.
 Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
@@
 			For spin half, the default exponentiator is in an analytic form.
-For spin one, a simple analytic form cannot be written, so instead an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used.
+For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used instead.
 Explicitly, this formula is
@@
 The integration code was compiled by \texttt{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different models of each of them.
-These test devices are,
-			\begin{itemize}
-				\item{
-					Computer A\begin{itemize}
-						\item Intel Core i7-8750H, a 6 core laptop processor released in 2018. Run with 16GiB of RAM. Air cooled (laptop fan). Base clock speed of 2.2GHz.
-						\item Nvidia GeForce GTX 1070, a 2048 \emph{Cuda} core laptop graphics processor released in 2016. Run with 8GiB of VRAM. Air cooled (laptop fan).
-					\end{itemize}
-				}
+These test devices are given in Table \ref{tab:devices}.
 
-				\item{Computer B\begin{itemize}
-						\item AMD Ryzen 9 5900X, a 12 core desktop processor released in 2020. Run with 32GiB of RAM. Air cooled. Base clock speed of 3.7GHz.
-						\item Nvidia GeForce RTX 3070, a 5888 \emph{Cuda} core desktop graphics processor released in 2020. Run with 8GiB of VRAM. Air cooled.
-					\end{itemize}
-				}
+			\begin{table}[h!]
+				\caption{Devices used in the parallelisation speed test.}
+				\label{tab:devices}
+				\begin{tabular}{l|l|l|l|l}
+					\textbf{Device}	&\textbf{Type}	&\textbf{RAM (GiB)}	&\textbf{Cores}	&\textbf{Cooling}\\
+					\hline
+					Core i7-6700	&Intel CPU		&16					&4				&Air\\
+					Quadro K620		&Nvidia GPU		&2					&384			&Air\\
+					\hline
+					Core i7-8750H	&Intel CPU		&16					&6				&Air\\
+					GeForce GTX 1070&Nvidia GPU		&8					&2048			&Air\\
+					\hline
+					Ryzen 9 5900X	&AMD CPU		&32					&12				&Air\\
+					GeForce RTX 3070&Nvidia GPU		&8					&5888			&Air\\
+					\hline
+					Ryzen 7 5800X	&AMD CPU		&32					&8				&Liquid\\
+					GeForce RTX 3080&Nvidia GPU		&10					&8704			&Air\\
+				\end{tabular}
+			\end{table}
+			% \begin{itemize}
+			% 	\item{
+			% 		Computer A\begin{itemize}
+			% 			\item Intel Core i7-8750H, a 6 core laptop processor. Run with 16GiB of RAM. Air cooled (laptop fan). Base clock speed of 2.2GHz.
+			% 			\item Nvidia GeForce GTX 1070, a 2048 \emph{Cuda} core laptop graphics processor released in 2016. Run with 8GiB of VRAM. Air cooled (laptop fan).
+			% 		\end{itemize}
+			% 	}
 
-				\item{Computer C\begin{itemize}
-						\item AMD Ryzen 7 5800X, an 8 core desktop processor released in 2020. Run with 32GiB of RAM. Liquid cooled. Base clock speed of 3.8GHz.
-						\item Nvidia GeForce RTX 3080, an 8704 \emph{Cuda} core desktop graphics processor released in 2020. Run with 10GiB of VRAM. Air cooled.
-					\end{itemize}
-				}
-			\end{itemize}
+			% 	\item{Computer B\begin{itemize}
+			% 			\item AMD Ryzen 9 5900X, a 12 core desktop processor. Run with 32GiB of RAM. Air cooled. Base clock speed of 3.7GHz.
+			% 			\item Nvidia GeForce RTX 3070, a 5888 \emph{Cuda} core desktop graphics processor. Run with 8GiB of VRAM. Air cooled.
+			% 		\end{itemize}
+			% 	}
+
+			% 	\item{Computer C\begin{itemize}
+			% 			\item AMD Ryzen 7 5800X, an 8 core desktop processor. Run with 32GiB of RAM. Liquid cooled. Base clock speed of 3.8GHz.
+			% 			\item Nvidia GeForce RTX 3080, an 8704 \emph{Cuda} core desktop graphics processor. Run with 10GiB of VRAM. Air cooled.
+			% 		\end{itemize}
+			% 	}
+
+			% 	\item{Computer D\begin{itemize}
+			% 		\item Intel Core i7-6700, a 4 core desktop processor. Run with 16GiB of RAM. Air cooled. Base clock speed of 3.4GHz.
+			% 		\item Nvidia Quadro K620, a 384 \emph{Cuda} core desktop graphics processor. Run with 2GiB of VRAM. Air cooled.
+			% 	\end{itemize}
+			% 	}
+			% \end{itemize}
 
@@
 Moving from a 6 core processor to a 12 core processor doubles the execution speed.
-Moving from a single core processor to a GPU increases performance by well over an order of magnitude.
+Moving from a single core processor to a high end GPU increases performance by well over an order of magnitude.
+Even the low end Quadro K620 was an improvement over the i7-6700 used by that computer.
 As an aside, liquid cooling allows the 8 core processor to increase its boost clock and outperform the 12 core processor.
@@
 		\subsubsection*{Evaluation of techniques}
-		All subsequent benchmarks were run on computer C, which from Figure \ref{fig:benchmark_device_aggregate} has the fastest CPU (liquid cooled AMD Ryzen 7 5800X) and GPU (Nvidia GeForce RTX 3080).
+		All subsequent benchmarks were run on the desktop computer with the Ryzen 7 5800X and GeForce RTX 3080, which from Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
 Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for).
 We first wanted to test the accuracy of the different integration techniques for various integration time steps.
-This accuracy was calculated by taking state evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) to a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
+Here we wanted to test the advantages, if any of using a Magnus based integration method.
+Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) to a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
 
@@
 			where \(j \in \{\frac12, 1\}\) is the spin quantum number of the system.
-This quantum sensing experiment involves continuously driving transitions in the system, while exposing it to a short pulsed signal that the system should be able to sense.
+This simulation of the quantum sensing experiment involves continuously driving transitions in the system, while exposing it to a short pulsed signal that the system should be able to sense.
 It runs over a duration of 1ms.
@@
 			This baseline was computed in 3.8 hours, and was also used for comparisons to other software packages.
-These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, \ref{fig:benchmark_spin_half_step_error}, and \ref{fig:benchmark_spin_half_trotter_step_error}.
+These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
 For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, the CF4 method is slower for any fixed integration time step.
-These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, \ref{fig:benchmark_spin_half_execution_error}, and \ref{fig:benchmark_spin_half_trotter_execution_error}.
+These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
 In all of these comparisons, errors above \(10^{-3}\) were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
+Additionally, errors bellow \(10^{-11}\) were excluded, as this was the order of magnitude of the errors in the reference simulation.
 
-			The integration techniques tested were
-			\begin{itemize}
-				\item The Magnus based method Commutator Free 4. Abbreviated as CF4.
-				\item The Euler based half step method used in the previous version of our code, where two Euler steps are made in each iteration, one sampled from the left, and one from the right.
-Abbreviated as HS.
-				\item The Euler based midpoint method, where a single sample is made from the midpoint of the interval being stepped over. Abbreviated as MP.
-			\end{itemize}
+			% The integration techniques tested were
+			% \begin{itemize}
+			% 	\item The Magnus based method, Commutator Free 4.
+			% 	\item The Heun (trapezoidal) Euler method.
+			% 	\item The midpoint Euler method.
+			% \end{itemize}
 
-			We benchmarked these methods both while using the rotating frame option (abbreviated as RF), and not (abbreviated as LF, for lab frame).
-The spin half simulations were benchmarked using both the analytic based exponentiator,and the Lie Trotter based exponentiator.
-This was done separately for spin one and spin half systems, to ensure they all yield accurate results.
+			The integration techniques tested were the Magnus based CF4, as well as two Euler based sampling methods.
+A midpoint Euler method was chosen as the simplest (and fastest for a given integration time step)  possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code, which also used it.
+We benchmarked these methods both while using and not using the rotating frame option.
+This was done separately for spin one and spin half systems, to ensure they both yield accurate results.
 
 			From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \texttt{spinsim} gives are accurate to those of \emph{SciPy}.
-Figures \ref{fig:benchmark_spin_one_step_error}, \ref{fig:benchmark_spin_half_step_error}, and \ref{fig:benchmark_spin_half_trotter_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
+Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
 Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
-From Figures \ref{fig:benchmark_spin_one_execution_error}, \ref{fig:benchmark_spin_half_execution_error}, and \ref{fig:benchmark_spin_half_trotter_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
+From Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
 Thus, by default \texttt{spinsim} sets the integrator to CF4, and uses the rotating frame.
@@
 			\begin{figure}[h!]
-				\begin{subfigure}[b]{0.45\textwidth}
-					\includegraphics[scale=0.45]{benchmark_spin_one_step_error.pdf}
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_one_step_error.pdf}
 					\caption{Accuracy of the spin one options of \texttt{spinsim}.}
@@
 				\hfill
-				\begin{subfigure}[b]{0.45\textwidth}
-					\includegraphics[scale=0.45]{benchmark_spin_one_execution_error.pdf}
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.pdf}
 					\caption{Speed vs accuracy of the spin one options of \texttt{spinsim}.}
@@
 
-			The that the accuracy of spin half simulations using the Lie Trotter based exponentiator in Figure \ref{fig:benchmark_spin_half_trotter_step_error} plateaus below \(10^{-8}\), whereas an accuracy below \(10^{-12}\) is able to be obtained when when the analytic exponentiator in Figure \ref{fig:benchmark_spin_half_step_error} is used.
+			% The that the accuracy of spin half simulations using the Lie Trotter based exponentiator in Figure \ref{fig:benchmark_spin_half_trotter_step_error} plateaus below \(10^{-8}\), whereas an accuracy below \(10^{-12}\) is able to be obtained when when the analytic exponentiator in Figure \ref{fig:benchmark_spin_half_step_error} is used.
 This also explains the plateau in accuracy from the spin one integrator, where the Lie Trotter based method is the only method implemented.
@@
 			\begin{figure}[h!]
-				\begin{subfigure}[b]{0.45\textwidth}
-					\includegraphics[scale=0.45]{benchmark_spin_half_step_error.pdf}
-					\caption{Accuracy of the spin half options of \texttt{spinsim}, using the analytic exponentiator.}
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_half_step_error.pdf}
+					\caption{Accuracy of the spin half options of \texttt{spinsim}.}
 					\label{fig:benchmark_spin_half_step_error}
@@
 				\hfill
-				\begin{subfigure}[b]{0.45\textwidth}
-					\includegraphics[scale=0.45]{benchmark_spin_half_execution_error.pdf}
-					\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}, using the analytic exponentiator.}
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.pdf}
+					\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}.}
 					\label{fig:benchmark_spin_half_execution_error}
-				\end{subfigure}\
-				\vfill
-				\begin{subfigure}[b]{0.45\textwidth}
-					\includegraphics[scale=0.45]{benchmark_spin_half_trotter_step_error.pdf}
-					\caption{Accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
-					\label{fig:benchmark_spin_half_trotter_step_error}
 				\end{subfigure}
-				\hfill
-				\begin{subfigure}[b]{0.45\textwidth}
-					\includegraphics[scale=0.45]{benchmark_spin_half_trotter_execution_error.pdf}
-					\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
-					\label{fig:benchmark_spin_half_trotter_execution_error}
-				\end{subfigure}\
+				% \vfill
+				% \begin{subfigure}[b]{0.45\textwidth}
+				% 	\includegraphics[scale=0.45]{benchmark_spin_half_trotter_step_error.pdf}
+				% 	\caption{Accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
+				% 	\label{fig:benchmark_spin_half_trotter_step_error}
+				% \end{subfigure}
+				% \hfill
+				% \begin{subfigure}[b]{0.45\textwidth}
+				% 	\includegraphics[scale=0.45]{benchmark_spin_half_trotter_execution_error.pdf}
+				% 	\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
+				% 	\label{fig:benchmark_spin_half_trotter_execution_error}
+				% \end{subfigure}\
 				\caption{Speed and accuracy of the spin half options of \texttt{spinsim}.}
@@
 				\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode, which were the highest performing options when comparing \texttt{spinsim} integration methods.
-Abbreviated as ss.
 				% \item \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, the previous custom written \emph{cython} based code developed by our lab group.
@@
 This was chosen as it is popular with our lab group for simulating magnetometry experiments.
-Abbreviated as mm.
-				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}.
-This was chosen as a generic solver from within the python ecosystem.
-Abbreviated as sp.
+				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}. This was chosen as a generic solver from within the python ecosystem.
 				\item We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
@@
 Similarly to with the internal \texttt{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
-Also like with the internal benchmarks, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as both \emph{Mathematica} and \texttt{spinsim} plateau in accuracy at small time steps.
+Also like with the internal benchmarks, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
 
-			Each benchmark was run one simulation at a time, however it might be possible to increase the average speed of many benchmarks from alternative packages using multithreading to run multiple benchmarks at a time.
+			Each benchmark was run one simulation at a time.
+However, it might be possible to increase the average speed of many benchmarks from alternative packages using multithreading to run multiple benchmarks at a time.
 When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
-Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the benchmark only single threaded uses up a day of computational time.
+Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step consumes a day of computational time.
 But to be fair, both \emph{Mathematica} and \emph{SciPy} benchmarks are plotted with an artificial reduction in execution time by a factor of 4 and 8, which is an upper bound for the speed increase that could be obtained by running them parallel on a 4 and 8 core processor, respectively.
-These are respectively shown in plots as disconnected \(+\) and \(\times\).
+These are respectively shown in plots as both faded and dotted lines.
 
-			From Figure \ref{fig:benchmark_external}, if an error of \(10^{-8}\) is acceptable, \texttt{spinsim} is 3 orders of magnitude faster than \emph{Mathematica}, and 4 orders of magnitude faster than \emph{SciPy}.
-In practice, this means that an 8 minute \emph{SciPy} simulation is reduced to 50ms, and a full week long batch simulation of 1000 separate systems (a realistic situation for quantum sensing protocols) would take less than one minute.
-With that said, if a smaller error is needed, it also plateaus at a greater minimum error than its alternatives, with \emph{Mathematica} having a minimum error less than \(10^{-10}\), and \emph{SciPy} not plateauing during the benchmark.
-However, for the vast majority of use cases, an error of \(10^{-8}\) is acceptable, and \texttt{spinsim} has vastly better performance in terms of speed and accuracy.
+			From Figure \ref{fig:benchmark_external}, for any given error tolerance, \texttt{spinsim} is over 3 orders of magnitude faster than \emph{Mathematica}, and 4 orders of magnitude more accurate than \emph{SciPy}.
+In practice, this means that an 8 minute \emph{SciPy} simulation is reduced to 50ms, and a full week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic situation for testing quantum sensing protocols) would take less than one minute in \texttt{spinsim}.
 
@@
 	\subsection*{Testing}
-		During the accuracy tests, it was confirmed that all possible modes of \texttt{spinsim} agree with a standard \emph{SciPy} simulation up to a small error.
+		During the accuracy tests, it was confirmed that all possible modes of \texttt{spinsim} agree with a standard \emph{SciPy} simulation up to an arbitrarily small error.
 The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.
@@
 		The kernel execution was profiled thoroughly, and changes were made to optimise VRAM and register usage and transfer.
-This was done specifically for the development hardware of computer A with an \emph{Nvidia} GTX1070, so one may get some performance increases by changing some GPU specific meta parameters when instantiating the \texttt{spinsim.Simulator} object.
+This was done specifically for the development hardware of an \emph{Nvidia} GTX1070, so one may get some performance increases by changing some GPU specific meta parameters when instantiating the \texttt{spinsim.Simulator} object.
 

### 2021-05-26 docs/source/conf.py

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.1.14'
+release = '0.2.1'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-05-26 example.py

@@ -7,7 +7,7 @@ def get_field_larmor(time_sample, field_modifier, field_sample):
    field_sample[1] = 0            # Zero field in y direction
    field_sample[2] = 1000         # Split spin z eigenstates by 1kHz
 
-simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF)
+simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF, exponentiation_method = spinsim.ExponentiationMethod.LIE_TROTTER)
 
 state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
 

### 2021-05-26 spinsim/__init__.py

@@ -383,7 +383,7 @@ class Simulator:
             print("\033[31mspinsim error: numba could not jit get_field function into a device function.\033[0m\n")
             raise
 
-    def compile_time_evolver(self, get_field, spin_quantum_number, device, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF4, exponentiation_method = None, trotter_cutoff = 28, threads_per_block = 64, max_registers = 63):
+    def compile_time_evolver(self, get_field, spin_quantum_number, device, use_rotating_frame = True, integration_method = IntegrationMethod.MAGNUS_CF4, exponentiation_method = None, trotter_cutoff:int = 28, threads_per_block = 64, max_registers = 63):
         """
         Compiles the integrator and spin calculation functions of the simulator.
 
@@ -1288,6 +1288,14 @@ class Utilities:
                 result[1, 1] = left[1, 0]*right[0, 1] + left[1, 1]*right[1, 1]
 
             @jit_device
+            def matrix_square_residual(operator, result):
+                result[0, 0] = (2 + operator[0, 0])*operator[0, 0] + operator[0, 1]*operator[1, 0]
+                result[1, 0] = operator[1, 0]*operator[0, 0] + (2 + operator[1, 1])*operator[1, 0]
+
+                result[0, 1] = (2 + operator[0, 0])*operator[0, 1] + operator[0, 1]*operator[1, 1]
+                result[1, 1] = operator[1, 0]*operator[0, 1] + (2 + operator[1, 1])*operator[1, 1]
+
+            @jit_device
             def adjoint(operator, result):
                 result[0, 0] = conj(operator[0, 0])
                 result[1, 0] = conj(operator[0, 1])
@@ -1329,7 +1337,10 @@ class Utilities:
                 precision = 4**hyper_cube_amount
                 
                 a = math.sqrt(field_sample[0]*field_sample[0] + field_sample[1]*field_sample[1])
-                ep = (field_sample[0] + 1j*field_sample[1])/a
+                if a > 0:
+                    ep = (field_sample[0] + 1j*field_sample[1])/a
+                else:
+                    ep = 1
                 a = a/precision
 
                 Ca = math.cos(a/2)
@@ -1339,14 +1350,14 @@ class Utilities:
                 ez = field_sample[2]/(2*precision)
                 ez = math.cos(ez) + 1j*math.sin(ez)
 
[…]

### 2021-05-31 article/article.tex
Article draft 4

@@
 
-\section*{(1) Overview}
+\section{(1) Overview}
 
@@
 
-\section*{Title}
+\section{Title}
 spinsim: a GPU optimised simulator of spin half and spin one quantum systems
 
-\section*{Paper Authors}
+\section{Paper Authors}
 1. Tritt, Alex;\\
@@
 
-\section*{Paper Author Roles and Affiliations}
+\section{Paper Author Roles and Affiliations}
 1. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
@@
 
-\section*{Abstract}
+\section{Abstract}
 	\texttt{spinsim} is a \emph{python} package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
@@
 
-\section*{Keywords}
+\section{Keywords}
 Time dependent Schroedinger equation; Spin one; Spin half; Integrator; GPU; Solver; python; numba;
 
-\section*{Introduction}
-\subsection*{Motivation}
+\section{Introduction}
+\subsection{Motivation}
 	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing \cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
@@
 
-\section*{Implementation and architecture}
-	\subsection*{Mathematical methods}
-		\subsubsection*{Background}
+\section{Implementation and architecture}
+	\subsection{Mathematical methods}
+		\subsubsection{Quantum mechanics background}
 			In general, \texttt{spinsim} solves the Schroedinger equation,
@@
 			\begin{align}
-				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) &= -iH(t)\psi(t),
+				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) &= -i2\pi H(t)\psi(t),\label{eq:schroedinger}
 			\end{align}
@@
 Here \(N\) is the number spin levels in the quantum system, so spin half is the \(N = 2\) case, and spin one refers to the \(N = 3\) case.
-Rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
-For example, when set to spin half mode, the \texttt{spinsim} package solves the time dependent Schroedinger equations of the form
+Furthermore, we have chosen for the Hamiltonian \(H(t)\) to have the physical dimension of frequency, rather than the more typical dimension of energy.
+To elaborate, we represent energies \(E\) of the system as their equivalent frequencies \(f\) from the Planck relation
+
+			\begin{align}
+				E &= \hbar \omega\\
+				&= 2\pi\hbar f,
+			\end{align}
+
+			where \(\hbar\) is (reduced) Planck's constant (or equivalently, setting 
+			\(\hbar = 1\)).
+In addition, rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
+For example, when set to spin half mode, the \texttt{spinsim} package solves the time dependent Schroedinger equation of the form
 
@@
 					0 & -1
-				\end{pmatrix}.
+				\end{pmatrix}.\label{eq:spin_half_operators}
 			\end{align}
 
-			The energy source \(f\) that represents the time dependent Hamiltonian \(H(t)\), is the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with \(t\) in units of s and \(f\) in units of Hz that control the dynamics of the system.
-The user must define a method that returns a sample of these source functions when a sampling time is input.
-In physical terms, these functions could represent the \(x,y,z\) components of a magnetic field applied to a magnetically sensitive.
+			The fields \(f\) that represents the time dependent Hamiltonian \(H(t)\), are the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with time \(t\) and \(f\) with physical dimension of frequency that control the dynamics of the system.
+The user must define a method that returns a sample of these field functions when a sampling time is input.
+In physical terms, these functions could represent the \(x,y,z\) components of a magnetic field applied to a magnetically spin one BEC or NVC.
 
@@
 					0 &  0 & 1
-				\end{pmatrix}.
+				\end{pmatrix}.\label{eq:spin_one_operators}
 			\end{align}
@@
 
-		\subsubsection*{Parallelisation}
+		\subsubsection{Unitary time evolution and the Magnus expansion}
 			Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\).
@@
 
-			This means that a time series for the state of the system can be evaluated by evaluating the time evolution operator between each of the sample times. Consider quantising time with
+			From Equation \eqref{eq:schroedinger}, \(U(t, t_0)\) also follows the Schroedinger equation via
+
+			\begin{align}
+				\frac{\mathrm{d}}{\mathrm{d}t}U(t, t_0)\psi(t_0) &= -i2\pi H(t)U(t, t_0)\psi(t_0)\textrm{ for any }\psi(t_0)\in\mathbb{C}^N,\textrm{ so}\\
+				\frac{\mathrm{d}}{\mathrm{d}t}U(t, t_0) &= -i2\pi H(t)U(t, t_0).\label{eq:unitary_schroedinger}
+			\end{align}
+
+			Thus, to solve Equation \eqref{eq:schroedinger} for \(\psi(t)\) given a particular \(\psi(t_0)\), one only needs to solve Equation \eqref{eq:unitary_schroedinger} for \(U(t, t_0)\).
+Note that because \(U(t, t_0)\) is unitary, the calculated value of \(\psi(t)\) using this method will not change in magnitude, conserving probability.
+
+			Also since \(U(t, t_0)\) is unitary (and continuous in time \(t\)), it can be written as a matrix exponential of a skew Hermitian matrix.
+For example, if the Hamiltonian \(H(t)\) is constant in time (and a real linear combination of Hermitian matrices defined by Equations \eqref{eq:spin_half_operators} or \eqref{eq:spin_one_operators}), then the solution would be
+
+			\begin{align}
+				U(t, t_0) &= \exp(-i2\pi H(t - t_0)).
+			\end{align}
+
+			The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series \cite{blanes_magnus_2009}, where
+
+			\begin{align}
+				U(t, t_0) &= \exp(-i2\pi G(t - t_0))\\
+				&= \exp(-i2\pi \sum_{m = 1}^\infty G_m(t - t_0)),
+			\end{align}
+
+			where \(G(t)\) is a series of \(G_m(t)\), each of which are a function of \(H\) and its commutators.
+\(G_1(t)\), for example, is just \(G_1(t) = H_\mathrm{av}t\), where \(H_\mathrm{av}\) is the average value of \(H\) over the interval being integrated over, which is the solution for when \(H\) is constant in time.
+The terms \(G_m(t)\) for \(m > 1\) are corrections to this approximation.
+One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for \(U(t, t_0)\).
+Importantly, any truncation of the Magnus expansion is unitary, meaning that probability will be conserved when used.
+
+			Something else to note about unitary time evolution operators, is that they can be broken into a product of multiple other time evolution operators via
+
+			\begin{align}
+				U(t, t_0) &= U(t, t_1)U(t_1, t_0).
+			\end{align}
+
+			Each of these parts can be approximated as a Magnus expansion.
+So, if the Magnus expansion of time evolution operator is inaccurate, it can be broken down into a product of many time evolution operators which each make a much smaller step between times.
+These components will each have a much more accurate Magnus expansion.
+
+			In fact, many unitary time stepping techniques have been developed based on the Magnus expansion \cite{auer_magnus_2018}.
+Some of these techniques use Gauss-Legendre quadrature sampling to avoid the integration of commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping.
+In particular, we used the commutator free 4 (CF4) from \cite{auer_magnus_2018} as our integration method.
+Suppose we wish to evaluate a short time step of \(U(t_f + \mathrm{d}t, t_f)\) by taking a short step \(\mathrm{d}t\) from a fine sample time \(t_f\).
+Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
+
+			\begin{align}
+				t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
+				t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
+			\end{align}
+
+			Then given the matrices
+
+			\begin{align}
+				\overline{G}_1 &= 2\pi\mathrm{d}t\left(\frac{3 + 2\sqrt{3}}{12}H(t_1) + \frac{3 - 2\sqrt{3}}{12}H(t_2)\right)\textrm{, and}\label{eq:cf4_sample_1}\\
+				\overline{G}_2 &= 2\pi\mathrm{d}t\left(\frac{3 - 2\sqrt{3}}{12}H(t_1) + \frac{3 + 2\sqrt{3}}{12}H(t_2)\right),\label{eq:cf4_sample_2}
+			\end{align}
+
+			the unitary time step can be calculated using
+
+			\begin{align}
+				U(t_f + \mathrm{d}t, t_f) = \exp(-i\overline{G}_2)\exp(-i\overline{G}_1).\label{eq:cf4_implementation}
+			\end{align}
+
+		\subsubsection{Exponentiator}
+			From Equation \eqref{eq:cf4_implementation}, evaluating matrix exponentials is a core part of the integration algorithm.
+However, the \texttt{spinsim} package uses the user provided field functions \(f(t)\) as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
+This allows for implementation of matrix exponentiation that takes advantage of this representation.
+For all implementations of exponentiation, the \texttt{spinsim} computes the matrix exponential
+
+			\begin{align}
+				E(g) &= E(g_x, g_y, g_z, g_q)\\
+				&= \exp(-i (g_x J_x + g_y J_y + g_z J_z + g_q Q)).
+			\end{align}
+
+			In practice, \(g\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{G_1}\) or \(\overline{G_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
+For spin half, the default exponentiator is in an analytic form.
+For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used instead.
+Explicitly, this formula is
+
+			\begin{align}
+				\exp\left( A + B\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{A}{n}\right) \exp\left(\frac{B}{n}\right)\right)^n
+			\end{align}
+
+			Where \(A,B\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
+The equality holds for without the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
+This tells us that we can approximate a matrix exponential of a linear combination of spin operators by reducing the size of the coefficients of these operators, taking the analytically simple exponentials of each of the operators \(-iJ_x, -iJ_y, -iJ_z\) and \(-iQ\) separately, multiplying each individual result together, and then raising the combination \(T\) to the power of the original reduction.
+
+			For our spin one case, the exponential \(E(g)\) can be approximated as, for large \(2^\tau\),
+
+			\begin{align}
+                E(g) =& \exp\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\\
+                =& \exp\left(2^{-\tau}\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\right)^{2^\tau}\\
+                \approx& \biggl(\exp\left(-i\frac12\left(2^{-\tau} g_z J_z + 2^{-\tau}g_q Q\right)\right)\nonumber\\
+				&\cdot\exp\left(-i\left(2^{-\tau} g_\phi J_\phi\right)\right)\nonumber\\
+				&\cdot\exp\left(-i\frac12\left(2^{-\tau} g_z J_z + 2^{-\tau} g_q Q\right)\right)\biggr)^{2^\tau}\\
+                =& \begin{pmatrix}
+                    \left(\frac{\Gamma}{PZ}\right)^2 & \frac{SP}{Z\Phi} & -\left(\frac{\Sigma P}{\Phi}\right)^2 \\
+					\frac{SP\Phi}{Z} & CP^4 & \frac{SPZ}{\Phi} \\
+					-\left(\frac{\Sigma \Phi}{P}\right)^2 & \frac{SPZ\Phi}{1} & \left(\frac{\Gamma Z}{P}\right)^2
+                \end{pmatrix}^{2^\tau}\\
+				=& T^{2^\tau}.
+            \end{align}
+
+			where
+
+            \begin{align}
+				g_\phi &= \sqrt{g_x^2 + g_y^2}&&\nonumber\\
+				J_\phi &= \frac{g_x}{g_\phi}J_x + \frac{g_y}{g_\phi}J_y&&\nonumber\\
+				\Gamma &= \cos\left(2^{-\tau} \frac{g_\phi}{2}\right) & \Phi &= \exp\left(i2^{-\tau}g_\phi\right)\nonumber\\
+				\Sigma &= \sin\left(2^{-\tau} \frac{g_\phi}{2}\right) & Z &= \exp\left(i2^{-\tau}\frac{g_z}{2}\right)\nonumber\\
+				C &= \cos\left(2^{-\tau} g_\phi\right) & P &= \exp\left(i2^{-\tau}\frac{g_q}{6}\right)\nonumber\\
+				S &= \frac{-i}{\sqrt2}\sin\left(2^{-\tau} g_\phi\right)&&
+            \end{align}
+
+			Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(g)\).
+The approach used for spin one exponentiation means that the package cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8 dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the four dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
+Including the full algebra could be possible as a feature update if there is demand for it, though just including this subspace is sufficient for our application, and many others, and has the advantage of being able to use this faster, more specialised method of matrix exponentiation.
+
+			Note that, the methods for both spin half and spin one use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
+This guarantees that the results of \texttt{spinsim} maintain unitary and conserve probability as required.
+
+		\subsubsection{Descretisation and parallelisation}
+			Consider quantising time with
 			\begin{align}
@@
 
-		\subsubsection*{Rotating frame}
-			If the rotating frame option is selected, the \(U_k\) are first calculated within a rotating frame of reference as \(U^r_k\), which, in some situations, reduces the size of the source functions used in the calculation, increasing accuracy.
+			Beyond discretisation for parallelisation, we discretise our time evolution operator into individual integration time steps.
+So, each of the \(U_k\) are split into products of time evolution operators between times separated by the integration time step via
+
+			\begin{align}
+				U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+				U_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
+				u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+			\end{align}
+
+			with \(\mathrm{d}t\) being the integration level time step. Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
+
+		\subsubsection{Rotating frame}
+			If the rotating frame option is selected, the \(U_k\) are first calculated within a rotating frame of reference as \(U^r_k\), which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
 The rotation speed of the rotating frame is calculated locally for each parallel time step \(U_k\), and only for rotations around the \(z\) axis.
-The rotating from source functions \(f^r_x, f^r_y, f^r_z,\) and \(f^r_q\) are related to the source function from the user input via
+The rotating from field functions \(f^r_x, f^r_y, f^r_z,\) and \(f^r_q\) are related to the field function from the user input via
 
@@
 
-			Where \(f_r = f_z(t_k + \frac12\mathrm{D}t)\) is sampled the midpoint value of the source over the interval \([t_{k - 1}, t_k]\).
-This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of \(f_z(t)\), while leaving the other source components at an equivalent magnitude.
+			Where \(f_r = f_z(t_k + \frac12\mathrm{D}t)\) is sampled the midpoint value of the fields over the interval \([t_{k - 1}, t_k]\).
+This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of \(f_z(t)\), while leaving the other field components at an equivalent magnitude.
 The rotation is then applied to obtain the lab frame time evolution operator \(U_k\) via
@@
 
-		\subsubsection*{Magnus based integration method}
-			The integration method used in \texttt{spinsim} is the commutator free 4 (CF4) method from Auer et al \cite{auer_magnus_2018}, which based on the Magnus expansion.
+		% \subsubsection{Magnus based integration method}
+		% 	The integration method used in \texttt{spinsim} is the commutator free 4 (CF4) method from Auer et al \cite{auer_magnus_2018}, which based on the Magnus expansion.
 Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
 
-			\begin{align}
-				U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
-				U_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
-				u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
-			\end{align}
+		% 	\begin{align}
+		% 		U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+		% 		U_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
+		% 		u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+		% 	\end{align}
 
-			with \(\mathrm{d}t\) being the integration level time step. Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
+		% 	with \(\mathrm{d}t\) being the integration level time step. Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
 
-			The CF4 method is used to calculate each individual \(u^k_l\).
+			% The CF4 method is used to calculate each individual \(u^k_l\).
 Let the fine sample time be given by \(t_f = l\mathrm{d}t + t_k\).
-Then as part of the CF4 method, the source functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
-
-			\begin{align}
-				t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
-				t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
-			\end{align}
-
-			Now, let
-			\begin{align}
-				f(t_1) &= (f_x(t_1), f_y(t_1), f_z(t_1), f_q(t_1))\textrm{, and}
-				f(t_2) &= (f_x(t_2), f_y(t_2), f_z(t_2), f_q(t_2)).
-			\end{align}
-
-			The integration time evolution operator can then be calculated using
-
-			\begin{align}
-				g_1 =& (g_{1,x}, g_{1,y}, g_{1,z}, g_{1,q})\\
-				=& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, and}\\
-				g_2 =& (g_{2,x}, g_{2,y}, g_{2,z}, g_{2,q})\\
-				=& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, so}\\
-				u =& \exp(-i \left( g_{2,x} J_x + g_{2,y} J_y + g_{2,z} J_z + g_{2,q} Q\right))\\
-				&\cdot\exp(-i \left( g_{1,x} J_x + g_{1,y} J_y + g_{1,z} J_z + g_{1,q} Q\right)).
-			\end{align}
-
-		\subsubsection*{Exponentiator}
-			For all exponentiation, the exponentiator computes the matrix exponential
-
-			\begin{align}
-				E(g) &= E(g_x, g_y, g_z, g_q)\\
-				&= \exp(-i (g_x J_x + g_y J_y + g_z J_z + g_q Q)), \textrm{ with}
-			\end{align}
-
-			For spin half, the default exponentiator is in an analytic form.
-For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used instead.
-Explicitly, this formula is
-
-			\begin{align}
-				\exp\left( A + B\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{A}{n}\right) \exp\left(\frac{B}{n}\right)\right)^n
-			\end{align}
-
-			Where \(A,B\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
-The equality holds for without the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
-This tells us that we can approximate a matrix exponential of a linear combination of spin operators by reducing the size of the coefficients of these operators, taking the analytically known exponentials of each of the operators separately, multiplying each individual result together, and then raising the combination \(T\) to the power of the original reduction.
-For our spin one case, the exponential \(E(g)\) can be approximated as, for large \(2^\tau\),
+Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
 
 			% \begin{align}
-            %     E(g) &= \exp(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q)\\
-            %     &= \exp(2^{-\tau}(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q))^{2^\tau}\\
-            %     &\approx (\exp(-i(2^{-\tau} g_x) J_x) \exp(-i(2^{-\tau} g_y) J_y) \exp(-i(2^{-\tau} g_z J_z + (2^{-\tau} g_q) Q)))^{2^\tau}\\
-            %     &= \begin{pmatrix}
-            %         \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X + c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (-s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X - c_Y + i s_Xs_Y)}{2} \\
-            %         \frac{e^{-i\left(Z + \frac{P}{3}\right)} (-i s_X + c_X s_Y)}{\sqrt{2}} & e^{i\frac{2P}{3}} c_X c_Y & \frac{e^{-i(Z - \frac{P}{3})} (-i s_X - c_X s_Y)}{\sqrt{2}} \\
-            %         \frac{e^{-i\left(Z + \frac{P}{3}\right)}(c_X - c_Y - i s_Xs_Y)}{2} & \frac{e^{i\frac{2P}{3}} (s_Y -i c_Y s_X)}{\sqrt{2}} & \frac{e^{-i\left(-Z + \frac{P}{3}\right)}(c_X + c_Y + i s_Xs_Y)}{2}
-            %     \end{pmatrix}^{2^\tau}
+			% 	t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
+			% 	t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
 			% \end{align}
 
-			\begin{align}
-                E(g) =& \exp\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\\
-                =& \exp\left(2^{-\tau}\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\right)^{2^\tau}\\
-                \approx& \biggl(\exp\left(-i\left(2^{-\tau} \frac12g_z J_z + \left(2^{-\tau}\frac12g_q\right) Q\right)\right)\nonumber\\
-				&\cdot\exp\left(-i\left(2^{-\tau} g_\phi J_\phi\right)\right)\nonumber\\
-				&\cdot\exp\left(-i\left(2^{-\tau} \frac12g_z J_z + \left(2^{-\tau} \frac12g_q\right) Q\right)\right)\biggr)^{2^\tau}\\
-                =& \begin{pmatrix}
-                    \left(\frac{\Gamma}{PZ}\right)^2 & \frac{SP}{Z\Phi} & -\left(\frac{\Sigma P}{\Phi}\right)^2 \\
-					\frac{SP\Phi}{Z} & CP^4 & \frac{SPZ}{\Phi} \\
-					-\left(\frac{\Sigma \Phi}{P}\right)^2 & \frac{SPZ\Phi}{1} & \left(\frac{\Gamma Z}{P}\right)^2
-                \end{pmatrix}^{2^\tau}\\
-				=& T^{2^\tau}.
-            \end{align}
+			% Now, let
+			% \begin{align}
+			% 	f(t_1) &= (f_x(t_1), f_y(t_1), f_z(t_1), f_q(t_1))\textrm{, and}
+			% 	f(t_2) &= (f_x(t_2), f_y(t_2), f_z(t_2), f_q(t_2)).
+			% \end{align}
 
-			where
+			% The integration time evolution operator can then be calculated using
 
-            \begin{align}
-				g_\phi &= \sqrt{g_x^2 + g_y^2}&&\nonumber\\
-				J_\phi &= \frac{g_x}{g_\phi}J_x + \frac{g_y}{g_\phi}J_y&&\nonumber\\
-				\Gamma &= \cos\left(2^{-\tau} \frac{g_\phi}{2}\right) & \Phi &= e^{i2^{-\tau}g_\phi}\nonumber\\
-				\Sigma &= \sin\left(2^{-\tau} \frac{g_\phi}{2}\right) & Z &= e^{i2^{-\tau}\frac{g_z}{2}}\nonumber\\
-				C &= \cos(2^{-\tau} g_\phi) & P &= e^{i2^{-\tau}\frac{g_q}{6}}\nonumber\\
-				S &= \frac{-i}{\sqrt2}\sin(2^{-\tau} g_\phi)&&
-            \end{align}
+			% \begin{align}
+			% 	g_1 =& (g_{1,x}, g_{1,y}, g_{1,z}, g_{1,q})\\
+			% 	=& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, and}\\
+			% 	g_2 =& (g_{2,x}, g_{2,y}, g_{2,z}, g_{2,q})\\
+			% 	=& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, so}\\
+			% 	u =& \exp(-i \left( g_{2,x} J_x + g_{2,y} J_y + g_{2,z} J_z + g_{2,q} Q\right))\\
+			% 	&\cdot\exp(-i \left( g_{1,x} J_x + g_{1,y} J_y + g_{1,z} J_z + g_{1,q} Q\right)).
+			% \end{align}
 
-			Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(g)\).
-The approach used for spin one exponentiation means that the package cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8 dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the four dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
-Including the full algebra could be possible as a feature update if there is demand for it, though just including this subspace is sufficient for our application, and many others, and has the advantage of being able to use this faster, more specialised method of matrix exponentiation.
-
-			Note that, the methods for both spin half and spin one use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
-This guarantees that the results of \texttt{spinsim} maintain unitary.
-
-	\subsection*{Software architecture}
-		\subsubsection*{Integrator architecture}
+	\subsection{Software architecture}
+		\subsubsection{Integrator architecture}
 			The integrator in the \texttt{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(U_k\).
@@
 			The thread starts by calculating \(t_k\) and, if the rotating frame is being used, \(f_r\).
-The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(f\) describing how to sample the source Hamiltonian.
+The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(f\) describing how to sample the Hamiltonian.
 The code then loops over each integration time step \(\mathrm{d}t\) to calculate the integration time evolution operators \(u^k_l\).
@@
 
-		\subsubsection*{Compilation of integrator}
+		\subsubsection{Compilation of integrator}
 			The \texttt{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
@@
 This structure has multiple advantages.
-First, the source function \(f\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
+First, the field function \(f\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
 This allows users to define \(f\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
@@
 This was especially useful for running benchmarks comparing old integration methods to the new ones, like CF4.
-The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile GTX1070 mainly used in testing here.
+The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile \emph{GeForce GTX 1070} mainly used in testing here.
 Finally, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.
@@
 
-\section*{Quality control}
-	\subsection*{Benchmarks}
-		\subsubsection*{Speed}
-			\begin{figure}[htbp!]
-				\centering
-				\includegraphics[scale=0.7]{benchmark_device_aggregate.pdf}
-				\caption{Evaluation speed of a typical spin one sensing experiment.
-Fine time step is 100ns, as determined to be ideal by the accuracy experiments.
-Experiments run for a duration of 100ms.
-Evaluation time is determined by an average of 100 similar experiments for each device.}
-				\label{fig:benchmark_device_aggregate}
+			\texttt{spinsim} is designed so that a single simulator compilation can be used to execute many simulations, sweeping through a particular parameter, while not needing to be recompiled.
+This is done through the \texttt{sweep\_parameter} argument to the user provided field function \(f\).
+The user uses \texttt{sweep\_parameter} to determine a variable parameter for the Hamiltonian.
+After compiling the \texttt{spinsim.Simulator} object, the user can set the value for \texttt{sweep\_parameter} for a particular simulation as the first argument when calling the function \texttt{spinsim.Simulator.evaluate()}.
+For a use case example, one might want to simulate many spin systems at different locations in a magnetic field gradient in an MRI experiment.
+To do this they could choose to set \(f_z =\texttt{sweep\_parameter}\), which would vary the magnetic field bias in the \(z\) direction for each experiment.
+This feature is demonstrated with examples in the documentation.
+
+\section{Quality control}
+	\subsection{Benchmarks}
+		\subsubsection{Evaluation of accuracy}
+		All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from the tests in Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
+Note that these benchmarks do not take into account the amount of time required to JIT compile simulation code for the first time (order of seconds), as we want to look at this in the limit of running many simulations while sweeping through a parameter that differs in each one.
+
+		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for).
+This simulation involves continuously driving transitions in the system for 100ms, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
+We first wanted to test the accuracy of the different integration techniques for various integration time steps.
+Here we wanted to test the advantages, if any of using a Magnus based integration method.
+Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) error from a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
+
+			\begin{align}
+                \epsilon &= \frac{1}{K}\sqrt{\sum_{k = 0}^{K - 1}\sum_{m_j = -j}^j|\psi_{k, (m_j)} - \psi_{k, (m_j)}^{\textrm{baseline}}|^2},\label{eq:error}
+            \end{align}
+
+			where \(j \in \{\frac12, 1\}\) is the spin quantum number of the system.
+
+			This baseline was computed in 3.8 hours (in comparison to order of 10ths of a second these \texttt{spinsim} tests were executed in), and was also used for comparisons to other software packages.
+These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
+For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, the CF4 method is slower for any fixed integration time step.
+These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
+In all of these comparisons, errors above \(10^{-3}\) were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
+Additionally, errors bellow \(10^{-11}\) were excluded, as this was the order of magnitude of the errors in the reference simulation.
+
+			The integration techniques tested were the Magnus based CF4, as well as two Euler based sampling methods.
+A midpoint Euler method was chosen as the simplest (and fastest for a given integration time step)  possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code, which also used it.
+We benchmarked these methods both while using and not using the rotating frame option.
+This was done separately for spin one and spin half systems, to ensure they both yield accurate results.
+
+			From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \texttt{spinsim} gives are accurate to those of \emph{SciPy}.
+Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
+Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
+From Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
+Thus, by default \texttt{spinsim} sets the integrator to CF4, and uses the rotating frame.
+These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
+
+			\begin{figure}[h!]
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_one_step_error.pdf}
+					% \caption{Accuracy of the spin one options of \texttt{spinsim}.}
+					\caption{}
+					\label{fig:benchmark_spin_one_step_error}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.pdf}
+					% \caption{Speed vs accuracy of the spin one options of \texttt{spinsim}.}
+					\caption{}
+					\label{fig:benchmark_spin_one_execution_error}
+				\end{subfigure}\
+				\caption{Speed and accuracy of the spin one options of \texttt{spinsim}.
+A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
+In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+Each technique was tested while both using and not using a transformation into a rotating frame.
+Both execution time and error were recorded for each of the simulations.
+Error is RMS error compared to a long running \emph{SciPy} baseline.}
+				\label{fig:benchmark_spin_one}
 			\end{figure}
 
-			Benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin one sensing experiments on different devices.
+			\begin{figure}[h!]
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_half_step_error.pdf}
+					% \caption{Accuracy of the spin half options of \texttt{spinsim}.}
+					\caption{}
+					\label{fig:benchmark_spin_half_step_error}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{0.475\textwidth}
+					\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.pdf}
+					% \caption{Speed vs accuracy of the spin half options of \texttt{spinsim}.}
+					\caption{}
+					\label{fig:benchmark_spin_half_execution_error}
+				\end{subfigure}
+				\caption{Speed and accuracy of the spin half options of \texttt{spinsim}.
+A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
+In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+Each technique was tested while both using and not using a transformation into a rotating frame.
+Both execution time and error were recorded for each of the simulations.
+Error is RMS error compared to a long running \emph{SciPy} baseline.}
+				\label{fig:benchmark_spin_half}
+			\end{figure}
+
+		\subsubsection{Comparison to alternatives}
+			We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \texttt{spinsim}'s performance to theirs. The packages compared were:
+			\begin{itemize}
+				\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode, which were the highest performing options when comparing \texttt{spinsim} integration methods.
+				\item \texttt{NDSolve} from the \emph{Mathematica} \cite{wolfram_research_inc_mathematica_2020} software.
+This was chosen as it is popular with our lab group for simulating magnetometry experiments.
+				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}. This was chosen as a generic solver from within the python ecosystem.
+				\item We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
+However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
+			\end{itemize}
+
+			In each case, the step sizes of the alternative integrators were limited to a maximum value obtain simulation results of different accuracies.
+Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
+Similarly to with the internal \texttt{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
+Also like with the internal benchmarks, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
+
+			Each benchmark was run one simulation at a time.
+However, it might be possible to increase the average speed of many benchmarks from alternative packages using multithreading to run multiple benchmarks at a time.
+When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
+Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step consumes a day of computational time.
+But to be fair, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 4 and 8, which is an upper bound for the speed increase that could be obtained by running them parallel on a 4 and 8 core processor, respectively.
+These are respectively shown in plots as both faded and dotted lines.
+
+			From Figure \ref{fig:benchmark_external}, for any given error tolerance, \texttt{spinsim} is over 3 orders of magnitude faster than \emph{Mathematica}, and 4 orders of magnitude more accurate than \emph{SciPy}.
+In practice, this means that an 8 minute \emph{SciPy} simulation is reduced to 50ms, and a full week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic situation for testing quantum sensing protocols) would take less than one minute in \texttt{spinsim}.
+
+			\begin{figure}[h!]
+				\includegraphics[scale=0.9]{benchmark_external_execution_error.pdf}
+				\caption{Speed vs accuracy of two alternative integration packages.
+A simulation of a typical neural sensing experiment was run for every integration time step, for each of alternative packages (\texttt{NDSolve} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
+In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+Both execution time and error were recorded for each of the simulations.
+Error is RMS error compared to a long running \emph{SciPy} baseline.
+The \emph{Mathematica} and \emph{SciPy} results are also shown with a speed up by a factor of 4 and 8 to represent the upper bound of hypothetical parallelisation across a 4 and 8 core CPU respectively.}
+				\label{fig:benchmark_external}
+			\end{figure}
+
+		\subsubsection{Parallelisation performance}
+			Once the algorithm behind \texttt{spinsim} was developed, we wanted to check its execution speed while running on various devices.
+Part of this test was also to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), compared highly procedural devices (being CPUs).
+Speed benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin one sensing experiments on different devices.
 This is shown in Figure \ref{fig:benchmark_device_aggregate}.
-The integration code was compiled by \texttt{numba} for single core CPUs, multicore CPUs, and \emph{Nvidia Cuda}, and run on different models of each of them.
+The integration code was compiled by \texttt{numba} for multicore CPUs, CPUs running single threaded, and \emph{Nvidia Cuda} compatible GPUs, and run on different models of each of them.
 These test devices are given in Table \ref{tab:devices}.
@@
 			\begin{table}[h!]
-				\caption{Devices used in the parallelisation speed test.}
+				\caption{Devices used in the parallelisation speed test. These devices are part of individual computers, which are separated here by horizontal lines.}
 				\label{tab:devices}
@@
 			\end{table}
-			% \begin{itemize}
-			% 	\item{
-			% 		Computer A\begin{itemize}
-			% 			\item Intel Core i7-8750H, a 6 core laptop processor. Run with 16GiB of RAM. Air cooled (laptop fan). Base clock speed of 2.2GHz.
-			% 			\item Nvidia GeForce GTX 1070, a 2048 \emph{Cuda} core laptop graphics processor released in 2016. Run with 8GiB of VRAM. Air cooled (laptop fan).
-			% 		\end{itemize}
-			% 	}
 
-			% 	\item{Computer B\begin{itemize}
-			% 			\item AMD Ryzen 9 5900X, a 12 core desktop processor. Run with 32GiB of RAM. Air cooled. Base clock speed of 3.7GHz.
-			% 			\item Nvidia GeForce RTX 3070, a 5888 \emph{Cuda} core desktop graphics processor. Run with 8GiB of VRAM. Air cooled.
-			% 		\end{itemize}
-			% 	}
-
-			% 	\item{Computer C\begin{itemize}
-			% 			\item AMD Ryzen 7 5800X, an 8 core desktop processor. Run with 32GiB of RAM. Liquid cooled. Base clock speed of 3.8GHz.
-			% 			\item Nvidia GeForce RTX 3080, an 8704 \emph{Cuda} core desktop graphics processor. Run with 10GiB of VRAM. Air cooled.
-			% 		\end{itemize}
-			% 	}
-
-			% 	\item{Computer D\begin{itemize}
-			% 		\item Intel Core i7-6700, a 4 core desktop processor. Run with 16GiB of RAM. Air cooled. Base clock speed of 3.4GHz.
-			% 		\item Nvidia Quadro K620, a 384 \emph{Cuda} core desktop graphics processor. Run with 2GiB of VRAM. Air cooled.
-			% 	\end{itemize}
-			% 	}
-			% \end{itemize}
-
-			This benchmark shows the benefit to using parallelisation when solving this problem.
-Moving from a 6 core processor to a 12 core processor doubles the execution speed.
-Moving from a single core processor to a high end GPU increases performance by well over an order of magnitude.
-Even the low end Quadro K620 was an improvement over the i7-6700 used by that computer.
-As an aside, liquid cooling allows the 8 core processor to increase its boost clock and outperform the 12 core processor.
-
-		\subsubsection*{Evaluation of techniques}
-		All subsequent benchmarks were run on the desktop computer with the Ryzen 7 5800X and GeForce RTX 3080, which from Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
-Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for).
-We first wanted to test the accuracy of the different integration techniques for various integration time steps.
-Here we wanted to test the advantages, if any of using a Magnus based integration method.
-Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) to a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
-
-			\begin{align}
-                \epsilon &= \frac{1}{K}\sqrt{\sum_{k = 0}^{K - 1}\sum_{m_j = -j}^j|\psi_{k, (m_j)} - \psi_{k, (m_j)}^{\textrm{baseline}}|^2},\label{eq:error}
-            \end{align}
-
-			where \(j \in \{\frac12, 1\}\) is the spin quantum number of the system.
-This simulation of the quantum sensing experiment involves continuously driving transitions in the system, while exposing it to a short pulsed signal that the system should be able to sense.
-It runs over a duration of 1ms.
-
-			This baseline was computed in 3.8 hours, and was also used for comparisons to other software packages.
-These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
-For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, the CF4 method is slower for any fixed integration time step.
-These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
-In all of these comparisons, errors above \(10^{-3}\) were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
-Additionally, errors bellow \(10^{-11}\) were excluded, as this was the order of magnitude of the errors in the reference simulation.
-
-			% The integration techniques tested were
-			% \begin{itemize}
-			% 	\item The Magnus based method, Commutator Free 4.
-			% 	\item The Heun (trapezoidal) Euler method.
-			% 	\item The midpoint Euler method.
-			% \end{itemize}
-
-			The integration techniques tested were the Magnus based CF4, as well as two Euler based sampling methods.
-A midpoint Euler method was chosen as the simplest (and fastest for a given integration time step)  possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code, which also used it.
-We benchmarked these methods both while using and not using the rotating frame option.
-This was done separately for spin one and spin half systems, to ensure they both yield accurate results.
-
-			From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \texttt{spinsim} gives are accurate to those of \emph{SciPy}.
-Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
-Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
-From Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
-Thus, by default \texttt{spinsim} sets the integrator to CF4, and uses the rotating frame.
-These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
-
-			\begin{figure}[h!]
-				\begin{subfigure}[b]{0.475\textwidth}
-					\includegraphics[scale=0.475]{benchmark_spin_one_step_error.pdf}
-					\caption{Accuracy of the spin one options of \texttt{spinsim}.}
-					\label{fig:benchmark_spin_one_step_error}
-				\end{subfigure}
-				\hfill
-				\begin{subfigure}[b]{0.475\textwidth}
-					\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.pdf}
-					\caption{Speed vs accuracy of the spin one options of \texttt{spinsim}.}
-					\label{fig:benchmark_spin_one_execution_error}
-				\end{subfigure}\
-				\caption{Speed and accuracy of the spin one options of \texttt{spinsim}.}
-				\label{fig:benchmark_spin_one}
+			\begin{figure}[htbp!]
+				\centering
+				\includegraphics[scale=0.7]{benchmark_device_aggregate.pdf}
+				\caption{Evaluation speed of a simulation of a typical spin one sensing experiment on both CPUs and GPUs.
+Integration time step is set to 100ns.
+Transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+Evaluation time is determined by an average of 100 similar simulations for each device, where each individual simulation varies in dressing amplitude (transition frequency).}
+				\label{fig:benchmark_device_aggregate}
 			\end{figure}
 
-			% The that the accuracy of spin half simulations using the Lie Trotter based exponentiator in Figure \ref{fig:benchmark_spin_half_trotter_step_error} plateaus below \(10^{-8}\), whereas an accuracy below \(10^{-12}\) is able to be obtained when when the analytic exponentiator in Figure \ref{fig:benchmark_spin_half_step_error} is used.
-This also explains the plateau in accuracy from the spin one integrator, where the Lie Trotter based method is the only method implemented.
-Furthermore, the analytic exponentiator is much faster in Figure \ref{fig:benchmark_spin_half_execution_error}, as compared to the Lie Trotter based integrator in Figure \ref{fig:benchmark_spin_half_trotter_execution_error}.
-Hence, the analytic exponentiator is the default option for \texttt{spinsim} simulations when in spin half mode.
+			The results shown in Figure \ref{fig:benchmark_device_aggregate} show the benefit to using parallelisation when solving a spin system problem.
+Moving from the 6 core \emph{Core i7-8750H} CPU to the 12 core \emph{Ryzen 9 5900X} CPU doubles the execution speed, as expected.
+Moving from a single core processor to a high end GPU increases performance by well over an order of magnitude on three of the four computers tested on.
+Even the low end \emph{Quadro K620} was an improvement over the \emph{Core i7-6700} used by the same computer.
+Execution speed vs number of cuda cores starts to plateau as the number of cores increases.
+This happens as the time it takes to transfer memory from RAM to VRAM (dedicated graphics memory), which is independent on the number of cores of the GPU, becomes a comparable to the execution time of the simulator logic.
+However, there is still a large improvement from using the high end \emph{GeForce RTX 3070} to the \emph{GeForce RTX 3080}, with the latter simulating the experiment in almost half the time of the simulated experiment duration.
 
-			\begin{figure}[h!]
-				\begin{subfigure}[b]{0.475\textwidth}
-					\includegraphics[scale=0.475]{benchmark_spin_half_step_error.pdf}
-					\caption{Accuracy of the spin half options of \texttt{spinsim}.}
-					\label{fig:benchmark_spin_half_step_error}
-				\end{subfigure}
-				\hfill
-				\begin{subfigure}[b]{0.475\textwidth}
-					\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.pdf}
-					\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}.}
-					\label{fig:benchmark_spin_half_execution_error}
-				\end{subfigure}
-				% \vfill
-				% \begin{subfigure}[b]{0.45\textwidth}
-				% 	\includegraphics[scale=0.45]{benchmark_spin_half_trotter_step_error.pdf}
-				% 	\caption{Accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
-				% 	\label{fig:benchmark_spin_half_trotter_step_error}
-				% \end{subfigure}
-				% \hfill
-				% \begin{subfigure}[b]{0.45\textwidth}
-				% 	\includegraphics[scale=0.45]{benchmark_spin_half_trotter_execution_error.pdf}
-				% 	\caption{Speed vs accuracy of the spin half options of \texttt{spinsim}, using the Lie Trotter exponentiator.}
-				% 	\label{fig:benchmark_spin_half_trotter_execution_error}
-				% \end{subfigure}\
-				\caption{Speed and accuracy of the spin half options of \texttt{spinsim}.}
-				\label{fig:benchmark_spin_half}
-			\end{figure}
+			Surprisingly, we found that the \emph{Ryzen 7 5800X} 8 core CPU was able to execute the benchmark faster than the \emph{Ryzen 9 5900X} 12 core CPU.
+This can be explained by the fact that the \emph{Ryzen 7 5800X} was liquid cooled, rather than being air cooled, meaning it was likely able to boost to a higher core clock, and resist thermal throttling.
 
-			% \begin{figure}[h!]
-			% 	\includegraphics[scale=0.9]{benchmark_comparison_spin_one_publication.pdf}
-			% 	\caption{Fine time step benchmark for spin one systems.
-CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
-HS and MP results are drawn on top of each other due to their similarities.}
-			% 	\label{fig:benchmark_comparison_spin_one}
-			% \end{figure}
+			Figure \ref{fig:benchmark_device_aggregate} can be used by potential \texttt{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
+We would recommend Another factor not shown in the plot is the fact that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
+In contrast, this does not happen when running a GPU based program, as it requires very little CPU utilisation to function.
+This can be convenient when running simulations on a personal laptop or desktop, as other work on the computer does not have to halt while simulations are being run.
 
-			% Figure \ref{fig:benchmark_comparison_spin_one} shows the performance of \texttt{spinsim} when running in spin one mode.
-This shows that both using the Magnus based CF4 method and moving into a rotating frame give significant increases to accuracy.
-The HS (half step) method in the lab frame, with a time step of 10ns was the method used by \texttt{AtomicPy}, the previous code used by the group for simulating spin systems.
-Compared to this, the best performing \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster.
-
-			% \begin{figure}[h!]
-			% 	\includegraphics[scale=0.9]{benchmark_comparison_spin_half_lt_publication.pdf}
-			% 	\caption{Fine time step benchmark for spin half systems, using the Lie Trotter based exponentiator.
-CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
-HS and MP results are drawn on top of each other due to their similarities.}
-			% 	\label{fig:benchmark_comparison_spin_half_lt}
-			% \end{figure}
-
-			% From Figure \ref{fig:benchmark_comparison_spin_half_lt}, one gets essentially the same accuracy for each method when working in spin half mode compared to spin one, if all else is kept constant.
-
-			% \begin{figure}[h!]
-			% 	\includegraphics[scale=0.9]{benchmark_comparison_spin_half_a_publication.pdf}
-			% 	\caption{Fine time step benchmark for spin half systems, using the analytic based exponentiator.
-CF4 is the Magnus commutator free integrator, HS is the two sample exponential integrator used in \texttt{AtomicPy}, MP is a single sample exponential integrator, RF is use of the rotating frame, and LF is lab frame (no use of the rotating frame).
-HS and MP results are drawn on top of each other due to their similarities.}
-			% 	\label{fig:benchmark_comparison_spin_half_a}
-			% \end{figure}
-
-			% Figure \ref{fig:benchmark_comparison_spin_half_a} shows that the Lie Trotter based exponentiator does limit the maximum accuracy obtainable, and for spin half systems, one can increase accuracy further (and decrease execution time) by using an analytic based exponentiator.
-
-		\subsubsection*{Comparison to alternatives}
-			We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \texttt{spinsim}'s performance to theirs. The packages compared were:
-			\begin{itemize}
-				\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode, which were the highest performing options when comparing \texttt{spinsim} integration methods.
-				% \item \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}, the previous custom written \emph{cython} based code developed by our lab group.
-				\item \texttt{NDSolve} from the \emph{Mathematica} \cite{wolfram_research_inc_mathematica_2020} software.
-This was chosen as it is popular with our lab group for simulating magnetometry experiments.
-				\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}. This was chosen as a generic solver from within the python ecosystem.
-				\item We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
-However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
-			\end{itemize}
-
-			In each case, the step sizes of the alternative integrators were limited to a maximum value obtain simulation results of different accuracies.
-Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
-Similarly to with the internal \texttt{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
-Also like with the internal benchmarks, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
-
-			Each benchmark was run one simulation at a time.
-However, it might be possible to increase the average speed of many benchmarks from alternative packages using multithreading to run multiple benchmarks at a time.
-When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
-Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step consumes a day of computational time.
-But to be fair, both \emph{Mathematica} and \emph{SciPy} benchmarks are plotted with an artificial reduction in execution time by a factor of 4 and 8, which is an upper bound for the speed increase that could be obtained by running them parallel on a 4 and 8 core processor, respectively.
-These are respectively shown in plots as both faded and dotted lines.
-
-			From Figure \ref{fig:benchmark_external}, for any given error tolerance, \texttt{spinsim} is over 3 orders of magnitude faster than \emph{Mathematica}, and 4 orders of magnitude more accurate than \emph{SciPy}.
-In practice, this means that an 8 minute \emph{SciPy} simulation is reduced to 50ms, and a full week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic situation for testing quantum sensing protocols) would take less than one minute in \texttt{spinsim}.
-
-			\begin{figure}[h!]
-				\includegraphics[scale=0.9]{benchmark_external_execution_error.pdf}
-				\caption{Speed vs accuracy of various integration packages.}
-				\label{fig:benchmark_external}
-			\end{figure}
-			% Compared to our previous code, \texttt{AtomicPy}, the best performing (default) spin one \texttt{spinsim} method is 5 orders of magnitude more accurate, while executing in a time 2 orders of magnitude faster on computer A.
-Another popular solver used by the lab group for magnetometry simulations is \emph{Mathematica}'s \cite{wolfram_research_inc_mathematica_2020} \texttt{NDSolve}.
-For a comparison between python packages, we also
-
-			% We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
-However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
-
-			% We had planned to benchmark against some other popular generic solvers.
-One such solver was \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
-However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
-We also planned to benchmark accuracy against the generic solver \texttt{scipy.integrate.ivp\_solve()} in the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}.
-However, using the same \texttt{get\_field} function as in the spin one benchmarks used for the \texttt{spinsim}, simulating with a integration time step of 500ns (the largest used during the \texttt{spinsim} benchmarks), we found that a single simulation ran in 153s, which is over three orders of magnitude slower than the most accurate \texttt{spinsim} simulations.
-This means that a generous projection for the time it would take to run the same benchmarks that \texttt{spinsim} runs in 11 minutes, using \texttt{scipy} would be over six days; for an integration package not designed for this problem (and would therefore likely be less accurate).
-
-	\subsection*{Testing}
+	\subsection{Testing}
 		During the accuracy tests, it was confirmed that all possible modes of \texttt{spinsim} agree with a standard \emph{SciPy} simulation up to an arbitrarily small error.
@@
 		The kernel execution was profiled thoroughly, and changes were made to optimise VRAM and register usage and transfer.
-This was done specifically for the development hardware of an \emph{Nvidia} GTX1070, so one may get some performance increases by changing some GPU specific meta parameters when instantiating the \texttt{spinsim.Simulator} object.
+This was done specifically for the development hardware of the \emph{GeForce GTX 1070}, so one may get some performance increases by changing some GPU specific meta parameters when instantiating the \texttt{spinsim.Simulator} object.
 
@@
 
-\section*{(2) Availability}
+\section{(2) Availability}
 \vspace{0.5cm}
-\section*{Operating system}
+\section{Operating system}
 Developed and tested on Windows 10.
@@
 
-\section*{Programming language}
+\section{Programming language}
 Python (3.7 or greater)
 
-\section*{Additional system requirements}
+\section{Additional system requirements}
 To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU \cite{noauthor_cuda_2012}.
@@
 
-\section*{Dependencies}
+\section{Dependencies}
 numba (0.50.1 or greater)\\
@@
 
-\section*{List of contributors}
+\section{List of contributors}
 
@@
 
-\section*{Software location:}
+\section{Software location:}
 
@@
 
-\section*{Language}
+\section{Language}
 
@@
 
-\section*{(3) Reuse potential}
+\section{(3) Reuse potential}
 
-	\subsection*{Use potential and limitations}
+	\subsection{Use potential and limitations}
 		\texttt{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
@@
 
-	\subsection*{Support}
+	\subsection{Support}
 		Documentation for \texttt{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
@@
 
-\section*{Acknowledgements}
+\section{Acknowledgements}
 
@@
 
-\section*{Funding statement}
+\section{Funding statement}
 
@@
 
-\section*{Competing interests}
+\section{Competing interests}
 

### 2021-06-07 article/article.tex
Version 0.3.4, cos_exp_m1 implementation

@@
 \section{Implementation and architecture}
-	\subsection{Mathematical methods}
-		\subsubsection{Quantum mechanics background}
-			In general, \texttt{spinsim} solves the Schroedinger equation,
+	% \subsection{Mathematical methods}
+	\subsection{Quantum mechanics background}
+		\texttt{spinsim} solves the time-dependent Schr\"{o}dinger equation
 
 		\begin{align}
-				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) &= -i2\pi H(t)\psi(t),\label{eq:schroedinger}
+			i\hbar\frac{\mathrm{d}\psi(t)}{\mathrm{d}t} &= H(t)\psi(t),\label{eq:schroedinger}
 		\end{align}
 
-			where \(i^2 = -1\), the quantum state \(\psi(t) \in \mathbb{C}^N\) a time dependent, \(N\) dimensional, unit complex vector, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is a time dependent \(N \times N\) complex Hermitian matrix.
-Here \(N\) is the number spin levels in the quantum system, so spin half is the \(N = 2\) case, and spin one refers to the \(N = 3\) case.
-Furthermore, we have chosen for the Hamiltonian \(H(t)\) to have the physical dimension of frequency, rather than the more typical dimension of energy.
+		where the quantum state \(\psi(t) \in \mathbb{C}^N\) is assumed normalised, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is Hermitian.
+Here \(N\) is the number of levels in the quantum system.
+Often we are considering systems with spin \(S\).
+Here spin-half is the \(N = 2\) case, and spin-one is \(N = 3\).
+We set \(\hbar = 1\), so that the Hamiltonian has units
+
+		% Furthermore, we have chosen for the Hamiltonian \(H(t)\) to have the physical dimension of frequency, rather than the more typical dimension of energy.
 To elaborate, we represent energies \(E\) of the system as their equivalent frequencies \(f\) from the Planck relation
@@
 
-			where \(\hbar\) is (reduced) Planck's constant (or equivalently, setting 
-			\(\hbar = 1\)).
+		% where \(\hbar\) is (reduced) Planck's constant (or equivalently, setting 
+		% \(\hbar = 1\)).
 In addition, rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
 For example, when set to spin half mode, the \texttt{spinsim} package solves the time dependent Schroedinger equation of the form
+		Rather than ... parametrizing the problem ... we consider time varying real coefficients in a linear combination of fixed operators,
 
 		\begin{align}
-				\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
+			H(t) &= \sum_{j = 1}^{N^2 - 1} a_j(t) A_j.
 		\end{align}
+
+		It is well known that ... spin in magnetic field has ... . We exclude the identity ... energy zero point.
+
+		In the spin one case there is no standard basis ... . Choices include Gell Mann, quadrupole basis, ... . In general ... Lie algebra ... mathfrak ... admits a basis ... .
+		% \begin{align}
+		% 	\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
+		% \end{align}
 
@@
 
+		DONT WRITE OUT, sigma
 		\begin{align}
@@
 
-			The fields \(f\) that represents the time dependent Hamiltonian \(H(t)\), are the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with time \(t\) and \(f\) with physical dimension of frequency that control the dynamics of the system.
+		Call omega, no implementation detail
+		% The fields \(f\) that represents the time dependent Hamiltonian \(H(t)\), are the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with time \(t\) and \(f\) with physical dimension of frequency that control the dynamics of the system.
 The user must define a method that returns a sample of these field functions when a sampling time is input.
@@
 Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
+		INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
 
+		% Too far out of scope
+		% Alternative: integrate Bloch equations 3 coupled real equations
+		% fast and parallel function from wavefunctions
 		Frequently when one calculates the times series of the quantum state \(\psi(t)\), they are also interested in its expected spin projection \(\left\langle J\right\rangle\)(t).
@@
 
+		% Inline
 		\begin{align}
@@
 
-		\subsubsection{Unitary time evolution and the Magnus expansion}
+	\subsection{Unitary time evolution and the Magnus expansion}
 		Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\).
@@
 
-		\subsubsection{Exponentiator}
+	\subsection{Exponentiator}
 		From Equation \eqref{eq:cf4_implementation}, evaluating matrix exponentials is a core part of the integration algorithm.
@@
 
-		\subsubsection{Descretisation and parallelisation}
+	\subsection{Discretisation and parallelisation}
 		Consider quantising time with
@@
 
-		\subsubsection{Rotating frame}
+	\subsection{Rotating frame}
 		If the rotating frame option is selected, the \(U_k\) are first calculated within a rotating frame of reference as \(U^r_k\), which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
@@
 
-	\subsection{Software architecture}
-		\subsubsection{Integrator architecture}
+% \subsection{Software architecture}
+	\subsection{Integrator architecture}
 		The integrator in the \texttt{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(U_k\).
@@
 
-		\subsubsection{Compilation of integrator}
+	\subsection{Compilation of integrator}
 		The \texttt{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
@@
 \section{Quality control}
-	\subsection{Benchmarks}
-		\subsubsection{Evaluation of accuracy}
+	% \subsection{Benchmarks}
+	\subsection{Evaluation of accuracy}
 	All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from the tests in Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
@@
 
-		\subsubsection{Comparison to alternatives}
+	\subsection{Comparison to alternatives}
 		We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \texttt{spinsim}'s performance to theirs. The packages compared were:
@@
 
-		\subsubsection{Parallelisation performance}
+	\subsection{Parallelisation performance}
 		Once the algorithm behind \texttt{spinsim} was developed, we wanted to check its execution speed while running on various devices.

### 2021-06-07 docs/source/conf.py

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.2.1'
+release = '0.3.4'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-06-07 example.py

@@ -1,13 +1,14 @@
 import spinsim
 import numpy as np
 import matplotlib.pyplot as plt
+import math
 
 def get_field_larmor(time_sample, field_modifier, field_sample):
    field_sample[0] = 0            # Zero field in x direction
    field_sample[1] = 0            # Zero field in y direction
-   field_sample[2] = 1000         # Split spin z eigenstates by 1kHz
+   field_sample[2] = math.tau*1000         # Split spin z eigenstates by 1kHz
 
-simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF, exponentiation_method = spinsim.ExponentiationMethod.LIE_TROTTER)
+simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF)
 
 state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
 
@@ -29,9 +30,9 @@ import math
 
 def get_field_rabi(time_sample, field_modifier, field_sample):
    # Dress atoms from the x direction, Rabi flopping at 1kHz
-   field_sample[0] = 2000*math.cos(math.tau*20e3*field_modifier*time_sample)
+   field_sample[0] = math.tau*2000*math.cos(math.tau*20e3*field_modifier*time_sample)
    field_sample[1] = 0                        # Zero field in y direction
-   field_sample[2] = 20e3*field_modifier     # Split spin z eigenstates by 700kHz
+   field_sample[2] = math.tau*20e3*field_modifier     # Split spin z eigenstates by 700kHz
    field_sample[3] = 0                        # Zero quadratic shift, found in spin one systems
 
 simulator_rabi = spinsim.Simulator(get_field_rabi, spinsim.SpinQuantumNumber.ONE)

### 2021-06-07 spinsim/__init__.py

@@ -10,6 +10,7 @@ import numba as nb
 from numba import cuda
 from numba import roc
 import math
+import cmath
 
 sqrt2 = math.sqrt(2)
 sqrt3 = math.sqrt(3)
@@ -432,6 +433,7 @@ class Simulator:
         set_to_one = utilities.set_to_one
         set_to_zero = utilities.set_to_zero
         matrix_multiply = utilities.matrix_multiply
+        matrix_multiply_m1 = utilities.matrix_multiply_m1
         adjoint = utilities.adjoint
         matrix_exponential_analytic = utilities.matrix_exponential_analytic
         matrix_exponential_lie_trotter = utilities.matrix_exponential_lie_trotter
@@ -484,7 +486,7 @@ class Simulator:
 
             # Premultiply to the exitsing time evolution operator
             set_to(time_evolution_coarse, time_evolution_old)
-            matrix_multiply(time_evolution_fine, time_evolution_old, time_evolution_coarse)
+            matrix_multiply_m1(time_evolution_fine, time_evolution_old, time_evolution_coarse)
 
         if use_rotating_frame:
             if dimension == 3:
@@ -515,12 +517,12 @@ class Simulator:
             @jit_device_template("(float64, float64, float64, float64, float64[:, :], float64, complex128[:])")
             def get_field_integration_magnus_cf4(sweep_parameter, time_fine, time_coarse, time_step_integration, field_sample, rotating_wave, rotating_wave_winding):
                 time_sample = ((time_fine + 0.5*time_step_integration*(1 - 1/sqrt3)) - time_coarse)
-                rotating_wave_winding[0] = math.cos(math.tau*rotating_wave*time_sample) + 1j*math.sin(math.tau*rotating_wave*time_sample)
+                rotating_wave_winding[0] = cmath.exp(1j*rotating_wave*time_sample)
                 time_sample += time_coarse
                 get_field_jit(time_sample, sweep_parameter, field_sample[0, :])
 
                 time_sample = ((time_fine + 0.5*time_step_integration*(1 + 1/sqrt3)) - time_coarse)
-                rotating_wave_winding[1] = math.cos(math.tau*rotating_wave*time_sample) + 1j*math.sin(math.tau*rotating_wave*time_sample)
+                rotating_wave_winding[1] = cmath.exp(1j*rotating_wave*time_sample)
                 time_sample += time_coarse
                 get_field_jit(time_sample, sweep_parameter, field_sample[1, :])
 
[…]

### 2021-06-22 article/article.tex
v0.4.0. Sweep parameter now array, initital states

@@
 \section{Abstract}
-	\texttt{spinsim} is a \emph{python} package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
+	\emph{spinsim} is a \emph{python} package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
 	It makes use of \texttt{numba.cuda} \cite{lam_numba_2015}, which is an \emph{LLVM} (Low Level Virtual Machine) \cite{lattner_llvm_2004} compiler, and other optimisations, to allow for fast and accurate evaluation on \emph{Nvidia Cuda} \cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
-\texttt{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
+	\emph{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
 	The initial use case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin half or spin one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
@@
 	\subsection{Quantum mechanics background}
-		\texttt{spinsim} solves the time-dependent Schr\"{o}dinger equation
-
+		\emph{spinsim} solves the time-dependent Schr\"{o}dinger equation
 		\begin{align}
@@
 		\end{align}
-
 		where the quantum state \(\psi(t) \in \mathbb{C}^N\) is assumed normalised, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is Hermitian.
 		Here \(N\) is the number of levels in the quantum system.
-Often we are considering systems with spin \(S\).
+		Often we are considering systems with spin \(J\) of half or one.
 		Here spin-half is the \(N = 2\) case, and spin-one is \(N = 3\).
-We set \(\hbar = 1\), so that the Hamiltonian has units
-
+		We set \(\hbar = 1\), so that the Hamiltonian has physical dimension of inverse frequency.
 		% Furthermore, we have chosen for the Hamiltonian \(H(t)\) to have the physical dimension of frequency, rather than the more typical dimension of energy.
@@
 
-		\begin{align}
-			E &= \hbar \omega\\
-			&= 2\pi\hbar f,
-		\end{align}
+		% \begin{align}
+		% 	E &= \hbar \omega\\
+		% 	&= 2\pi\hbar f,
+		% \end{align}
 
@@
 		% \(\hbar = 1\)).
-In addition, rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \texttt{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
-For example, when set to spin half mode, the \texttt{spinsim} package solves the time dependent Schroedinger equation of the form
-		Rather than ... parametrizing the problem ... we consider time varying real coefficients in a linear combination of fixed operators,
+In addition, rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \emph{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
+For example, when set to spin half mode, the \emph{spinsim} package solves the time dependent Schroedinger equation of the form
 
+		Rather than parametrizing the problem in terms of the matrix elements of \(H(t)\), we consider time varying real coefficients in a linear combination of fixed operators,
 		\begin{align}
-			H(t) &= \sum_{j = 1}^{N^2 - 1} a_j(t) A_j.
+			H(t) &= \sum_{j = 1}^{N^2 - 1} \omega_j(t) O_j.
+		\end{align}
+		It is well known that a charged spin half system with magnetic moment \(\overrightarrow{\mu}\), and gyromagnetic ratio \(\gamma\), in a magnetic field \(\overrightarrow{B}(t)\), has Hamiltonian
+		\begin{align}
+			H(t) &= -\overrightarrow{B}(t)\cdot \overrightarrow{\mu}\\
+			&= -\gamma \overrightarrow{B}(t)\cdot \overrightarrow{J}\\
+			&= -\gamma \left(B_x(t) J_x + B_y(t) J_y + B_z(t) J_z\right)\\
+			&= \left(-\gamma B_x(t) J_x\right) + \left(-\gamma B_y(t) J_y\right) + \left(-\gamma B_z(t) J_z\right)\\
+			&= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z.
 		\end{align}
 
-		It is well known that ... spin in magnetic field has ... . We exclude the identity ... energy zero point.
+		Here \(J_x, J_y\) and \(J_z\) are spin operators, equal to the Pauli matrices scaled down by \(\frac12\).
+		We exclude the identity so that the Hamiltonian is traceless, which we can do because it corresponds to choosing an energy zero point, which is physically meaningless.
 
-		In the spin one case there is no standard basis ... . Choices include Gell Mann, quadrupole basis, ... . In general ... Lie algebra ... mathfrak ... admits a basis ... .
+		In the spin one case there is no standard basis of operators \(A_j\).
+		Choices include the Gell Mann matrices, and multiple dipole-quadrupole bases \cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
+		In general, we can choose any basis from the 8-dimensional Lie algebra \(\mathfrak{su}(3)\), which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group \(SU(3)\)) in the spin one system.
+		With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of \(\mathfrak{su}(3)\), consisting of the spin matrices \(J_x, J_y\) and \(J_z\), and a single quadrupole operator \(Q = \frac13\mathrm{diag}(1, -2, 1)\),
+		\begin{align}
+			H(t) &= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q.
+		\end{align}
+
+		Note that \(Q\) is proportional to \(Q_{zz}\) \cite{hamley_spin-nematic_2012} and \(Q_0\) \cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
+		These are the only operators necessary to simulate many spin one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula.
+		\emph{spinsim} can also be configured to solve a general spin one system by setting the Hamiltonian to an arbitrary point in \(\mathfrak{su}(3)\), using the full quadrupole basis, which extends the possible Hamiltonian to
+		\begin{align}
+			H(t) &= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q\nonumber\\
+			&+ \omega_{ux}(t) U_1 + \omega_{uy}(t) U_2 + \omega_{vx}(t) V_1 + \omega_{vy}(t) V_2.
+		\end{align}
+		Here the added operators are those defined in \cite{di_dipolequadrupole_2010}.
+Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the \(U_1, U_2, V_1\) and \(V_2\) operators.
+		% In general ... Lie algebra ... mathfrak ... admits a basis ... .
 		% \begin{align}
@@
 
-		where \(i^2 = -1\), \(\psi(t) \in \mathbb{C}^2\), and the spin half spin projection operators are given by
+		% where \(i^2 = -1\), \(\psi(t) \in \mathbb{C}^2\), and the spin half spin projection operators are given by
 
-		DONT WRITE OUT, sigma
-		\begin{align}
-			J_x &= \frac12\begin{pmatrix}
-				0 & 1 \\
-				1 & 0
-			\end{pmatrix},
-			&J_y &= \frac12\begin{pmatrix}
-				0 & -i \\
-				i &  0
-			\end{pmatrix},
-			&\textrm{and }J_z &= \frac12\begin{pmatrix}
-				1 &  0 \\
-				0 & -1
-			\end{pmatrix}.\label{eq:spin_half_operators}
-		\end{align}
+		% DONT WRITE OUT, sigma
+		% \begin{align}
+		% 	J_x &= \frac12\begin{pmatrix}
+		% 		0 & 1 \\
+		% 		1 & 0
+		% 	\end{pmatrix},
+		% 	&J_y &= \frac12\begin{pmatrix}
+		% 		0 & -i \\
+		% 		i &  0
+		% 	\end{pmatrix},
+		% 	&\textrm{and }J_z &= \frac12\begin{pmatrix}
+		% 		1 &  0 \\
+		% 		0 & -1
+		% 	\end{pmatrix}.\label{eq:spin_half_operators}
+		% \end{align}
 
-		Call omega, no implementation detail
+		% Call omega, no implementation detail
 		% The fields \(f\) that represents the time dependent Hamiltonian \(H(t)\), are the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with time \(t\) and \(f\) with physical dimension of frequency that control the dynamics of the system.
@@
 
-		Similarly, when \texttt{spinsim} is set to spin one mode, it can solve the Schroedinger equation of the form
+		% Similarly, when \emph{spinsim} is set to spin one mode, it can solve the Schroedinger equation of the form
 
-		\begin{align}
-			\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
-		\end{align}
+		% \begin{align}
+		% 	\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
+		% \end{align}
 
-		where now \(\psi(t) \in \mathbb{C}^3\), and the spin one operators are given by
+		% where now \(\psi(t) \in \mathbb{C}^3\), and the spin one operators are given by
 
-		\begin{align}
-			J_x &= \frac{1}{\sqrt{2}}\begin{pmatrix}
-				0 & 1 & 0 \\
-				1 & 0 & 1 \\
-				0 & 1 & 0
-			\end{pmatrix},&
-			J_y &= \frac{1}{\sqrt{2}}\begin{pmatrix}
-				0 & -i &  0 \\
-				i &  0 & -i \\
-				0 &  i &  0
-			\end{pmatrix},\nonumber\\
-			J_z &= \begin{pmatrix}
-				1 & 0 &  0 \\
-				0 & 0 &  0 \\
-				0 & 0 & -1
-			\end{pmatrix},&
-			\textrm{and }Q &= \frac{1}{3}\begin{pmatrix}
-				1 &  0 & 0 \\
-				0 & -2 & 0 \\
-				0 &  0 & 1
-			\end{pmatrix}.\label{eq:spin_one_operators}
-		\end{align}
+		% \begin{align}
+		% 	J_x &= \frac{1}{\sqrt{2}}\begin{pmatrix}
+		% 		0 & 1 & 0 \\
+		% 		1 & 0 & 1 \\
+		% 		0 & 1 & 0
+		% 	\end{pmatrix},&
+		% 	J_y &= \frac{1}{\sqrt{2}}\begin{pmatrix}
+		% 		0 & -i &  0 \\
+		% 		i &  0 & -i \\
+		% 		0 &  i &  0
+		% 	\end{pmatrix},\nonumber\\
+		% 	J_z &= \begin{pmatrix}
+		% 		1 & 0 &  0 \\
+		% 		0 & 0 &  0 \\
+		% 		0 & 0 & -1
+		% 	\end{pmatrix},&
+		% 	\textrm{and }Q &= \frac{1}{3}\begin{pmatrix}
+		% 		1 &  0 & 0 \\
+		% 		0 & -2 & 0 \\
+		% 		0 &  0 & 1
+		% 	\end{pmatrix}.\label{eq:spin_one_operators}
+		% \end{align}
 
-		The matrices \(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadrupole operator.
+		% The matrices \(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadrupole operator.
 Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
-		INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
+		% INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
 
@@
 		% fast and parallel function from wavefunctions
-		Frequently when one calculates the times series of the quantum state \(\psi(t)\), they are also interested in its expected spin projection \(\left\langle J\right\rangle\)(t).
-It is given by the vector
+		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection \(\left\langle \overrightarrow{J}\right\rangle\)(t) of a system from its state.
+		In an experimental setting, one cannot measure the value of the state itself, and must instead measure observables such as spin projection.
+		If this is done for an ensemble of systems, the average spin projection over all systems will converge to the expected value as calculated here.
 
-		% Inline
+		% Frequently when one calculates the times series of the quantum state \(\psi(t)\), they are also interested in its expected spin projection. It is given by the vector
+
+		% % Inline
+		% \begin{align}
+		% 	\left\langle J\right\rangle(t) &= \begin{pmatrix}
+		% 		\psi(t)^\dagger J_x \psi(t)\\
+		% 		\psi(t)^\dagger J_y \psi(t)\\
+		% 		\psi(t)^\dagger J_z \psi(t)
+		% 	\end{pmatrix},
+		% \end{align}
+
+		% where \(\cdot^\dagger\) is the adjoint operator.
+The expected spin projection can be interpreted as the average direction that the spin system is oriented in space when many systems of the equivalent state are measured (due to the Heisenberg uncertainty principle, only one component of the exact orientation of a quantum state can be known at any point in time, which is why we need to deal with expected values rather than absolute values).
+However, it can also be used to model the overall orientation of an ensemble of many quantum systems, like a BEC, for instance.
+\emph{spinsim} has the functionality to calculate the expected spin projection of a system from its state.
+
+	\subsection{Unitary time evolution and the Magnus expansion}
+		It is possible to write \(\psi(t)\) in terms of a unitary transformation \(\mathcal{U}(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\), that is, \(\psi(t) = \mathcal{U}(t, t_0)\psi(t_0)\).
+		It then follows from Equation \eqref{eq:schroedinger} that \(\mathcal{U}(t, t_0)\) also follows a Schr\"{o}dinger equation,
 		\begin{align}
-			\left\langle J\right\rangle(t) &= \begin{pmatrix}
-				\psi(t)^\dagger J_x \psi(t)\\
-				\psi(t)^\dagger J_y \psi(t)\\
-				\psi(t)^\dagger J_z \psi(t)
-			\end{pmatrix},
+			i\hbar\frac{\mathrm{d}\mathcal{U}(t, t_0)}{\mathrm{d}t} &= H(t)\mathcal{U}(t, t_0).\label{eq:unitary_schroedinger}
 		\end{align}
 
-		where \(\cdot^\dagger\) is the adjoint operator (also referred to as Hermitian conjugate, and is implemented as complex conjugate transpose).
-The expected spin projection can be interpreted as the average direction that the spin system is oriented in space when many systems of the equivalent state are measured (due to the Heisenberg uncertainty principle, only one component of the exact orientation of a quantum state can be known at any point in time, which is why we need to deal with expected values rather than absolute values).
-However, it can also be used to model the overall orientation of an ensemble of many quantum systems, like a BEC, for instance.
-\texttt{spinsim} has the functionality to calculate the expected spin projection of a system from its state.
+		Thus, to solve Equation \eqref{eq:schroedinger} for \(\psi(t)\) given a particular \(\psi(t_0)\), one only needs to solve Equation \eqref{eq:unitary_schroedinger} for \(\mathcal{U}(t, t_0)\).
+		% Note that because \(\mathcal{U}(t, t_0)\) is unitary, the calculated value of \(\psi(t)\) using this method will not change in magnitude, conserving probability.
+		Also since \(\mathcal{U}(t, t_0)\) is unitary, it can be written as a matrix exponential of a skew-Hermitian (also termed anti-Hermitian) matrix.
+		If the Hamiltonian is constant, then this exponential is % Check if continuity requirement on unitary
+		\begin{align}
+			\mathcal{U}(t, t_0) &= \exp(-i H\cdot(t - t_0)).\label{eq:exp_sol_of_constant}
+		\end{align}
+		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series \cite{blanes_magnus_2009}, where
+		For a time varying Hamiltonian, the general solution for \(\mathcal{U}(t, t_0)\) is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
+		The Dyson series gives an explicit expression for \(\mathcal{U}(t, t_0)\) in terms of multiple time integrals over nested time commutators of \(H(t')\). % Cite 2? recent papers
+		While the Dyson series has been used numerically, it has only been so recently, in particular because once truncated, it is in general no longer unitary.
 
-	\subsection{Unitary time evolution and the Magnus expansion}
-		Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\).
-In other words, for any \(t_0,t \in \mathbb{R}\), there is a unitary transformation \(U(t, t_0)\) such that
+		The Magnus series
+		\begin{align}
+			\mathcal{U}(t, t_0) &= \exp\left(\Omega(t, t_0)\right) = \exp\left(\sum_{m = 1}^\infty \Omega_m(t, t_0)\right)
+		\end{align}
+		explicitly preserves unitarity when truncated\cite{magnus_exponential_1954}.
+		The first terms in the Magnus series are\cite{blanes_magnus_2009}
+		\begin{align}
+			\Omega_1(t, t_0) &= \int_0^t\mathrm{d}t_1A(t_1)\\
+			\Omega_2(t, t_0) &= \frac12\int_{t_0}^t\mathrm{d}t_1\int_{t_0}^{t_1}\mathrm{d}t_2[A(t_1), A(t_2)]\\
+			\Omega_3(t, t_0) &= \frac16\int_{t_0}^t\mathrm{d}t_1\int_{t_0}^{t_1}\mathrm{d}t_2\int_{t_0}^{t_2}\mathrm{d}t_3\left([A(t_1), [A(t_2), A(t_3)]] + [A(t_3), [A(t_2), A(t_1)]]\right),
+		\end{align}
+		where\([X, Y] = XY - YX\) is the commutator, and, in the case of quantum mechanics, \(A(t') = -iH(t')\).
+Note that, when truncated to first order, the magnus expansion \(\mathcal{U}(t, t_0) = \exp\left(\int_0^t\mathrm{d}t_1\left(-iH(t_1)\right)\right)\) reduces to Equation \eqref{eq:exp_sol_of_constant}, with \(H\) approximated to be constant with its average value.
 
+		% Insert first few omegas here
+		% Throw back to constant
+		% Here each \(\Omega_m(t)\) are integrals over time commutators of \(H(t')\).
+		% \(\Omega_1(t)\), for example, is \(\Omega_1(t) = H_\mathrm{av}t\), where \(H_\mathrm{av}\) is the average value of \(H\) over the interval being integrated over, which is the solution for when \(H\) is constant in time.
+		% The terms \(\Omega_m(t)\) for \(m > 1\) are corrections to this approximation.
+One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for \(\mathcal{U}(t, t_0)\).
+		% Importantly, any truncation of the Magnus expansion is unitary, meaning that probability will be conserved when used.
+
+		A Magnus series over a time step \(T\) will be guaranteed to converge only if the spectral norm of \(H\) is sufficiently small, \(\int_{t_0}^{t_0 + T}\mathrm{d}t_1\|H(t_1)\| < \pi\)\cite{blanes_magnus_2009}.
+Furthermore, each subsequent term in the expansion increases in complexity rapidly.
+For these reasons, the Magnus expansion can be used as a time stepping method rather than a single step to solve the complete system.
+Time stepping can be made from the fact that time evolution operators can be split into a product via
 		\begin{align}
-			\psi(t) &= U(t, t_0)\psi(t_0).
+			\mathcal{U}(t, t_0) &= \mathcal{U}(t, t_{n - 1})\mathcal{U}(t_{n - 1}, t_{n - 2})\cdots\mathcal{U}(t_2, t_1)\mathcal{U}(t_1, t_0).\label{eq:product_of_time_evolution}
 		\end{align}
+		Each of the time evolution operators can be approximated by a Magnus expansion.
 
-		From Equation \eqref{eq:schroedinger}, \(U(t, t_0)\) also follows the Schroedinger equation via
-
-		\begin{align}
-			\frac{\mathrm{d}}{\mathrm{d}t}U(t, t_0)\psi(t_0) &= -i2\pi H(t)U(t, t_0)\psi(t_0)\textrm{ for any }\psi(t_0)\in\mathbb{C}^N,\textrm{ so}\\
-			\frac{\mathrm{d}}{\mathrm{d}t}U(t, t_0) &= -i2\pi H(t)U(t, t_0).\label{eq:unitary_schroedinger}
-		\end{align}
-
-		Thus, to solve Equation \eqref{eq:schroedinger} for \(\psi(t)\) given a particular \(\psi(t_0)\), one only needs to solve Equation \eqref{eq:unitary_schroedinger} for \(U(t, t_0)\).
-Note that because \(U(t, t_0)\) is unitary, the calculated value of \(\psi(t)\) using this method will not change in magnitude, conserving probability.
-
-		Also since \(U(t, t_0)\) is unitary (and continuous in time \(t\)), it can be written as a matrix exponential of a skew Hermitian matrix.
-For example, if the Hamiltonian \(H(t)\) is constant in time (and a real linear combination of Hermitian matrices defined by Equations \eqref{eq:spin_half_operators} or \eqref{eq:spin_one_operators}), then the solution would be
-
-		\begin{align}
-			U(t, t_0) &= \exp(-i2\pi H(t - t_0)).
-		\end{align}
-
-		The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series \cite{blanes_magnus_2009}, where
-
-		\begin{align}
-			U(t, t_0) &= \exp(-i2\pi G(t - t_0))\\
-			&= \exp(-i2\pi \sum_{m = 1}^\infty G_m(t - t_0)),
-		\end{align}
-
-		where \(G(t)\) is a series of \(G_m(t)\), each of which are a function of \(H\) and its commutators.
-\(G_1(t)\), for example, is just \(G_1(t) = H_\mathrm{av}t\), where \(H_\mathrm{av}\) is the average value of \(H\) over the interval being integrated over, which is the solution for when \(H\) is constant in time.
-The terms \(G_m(t)\) for \(m > 1\) are corrections to this approximation.
-One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for \(U(t, t_0)\).
-Importantly, any truncation of the Magnus expansion is unitary, meaning that probability will be conserved when used.
-
-		Something else to note about unitary time evolution operators, is that they can be broken into a product of multiple other time evolution operators via
-
-		\begin{align}
-			U(t, t_0) &= U(t, t_1)U(t_1, t_0).
-		\end{align}
-
-		Each of these parts can be approximated as a Magnus expansion.
+		% Each of these parts can be approximated as a Magnus expansion.
 So, if the Magnus expansion of time evolution operator is inaccurate, it can be broken down into a product of many time evolution operators which each make a much smaller step between times.
 These components will each have a much more accurate Magnus expansion.
+% convergence of Magnus series, not simple.
+Also Dyson.
+Standard bounds.
+		% Numerical solver takes only a few terms of the expansion. However, any long operator can be broken into a product. Cite Magnus papers. Designing a Magnus based integrator is a trade off.
 
-		In fact, many unitary time stepping techniques have been developed based on the Magnus expansion \cite{auer_magnus_2018}.
+		Many unitary time stepping techniques have been developed based on the Magnus expansion \cite{auer_magnus_2018}.
 		Some of these techniques use Gauss-Legendre quadrature sampling to avoid the integration of commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping.
 		In particular, we used the commutator free 4 (CF4) from \cite{auer_magnus_2018} as our integration method.
-Suppose we wish to evaluate a short time step of \(U(t_f + \mathrm{d}t, t_f)\) by taking a short step \(\mathrm{d}t\) from a fine sample time \(t_f\).
+		Suppose we wish to evaluate a short time step of \(\mathcal{U}(t_f + \mathrm{d}t, t_f)\) by taking a short step \(\mathrm{d}t\) from a fine sample time \(t_f\).
 		Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
@@
 		\begin{align}
-			\overline{G}_1 &= 2\pi\mathrm{d}t\left(\frac{3 + 2\sqrt{3}}{12}H(t_1) + \frac{3 - 2\sqrt{3}}{12}H(t_2)\right)\textrm{, and}\label{eq:cf4_sample_1}\\
-			\overline{G}_2 &= 2\pi\mathrm{d}t\left(\frac{3 - 2\sqrt{3}}{12}H(t_1) + \frac{3 + 2\sqrt{3}}{12}H(t_2)\right),\label{eq:cf4_sample_2}
+			\overline{H}_1 &= \mathrm{d}t\left(\frac{3 + 2\sqrt{3}}{12}H(t_1) + \frac{3 - 2\sqrt{3}}{12}H(t_2)\right)\textrm{, and}\label{eq:cf4_sample_1}\\
+			\overline{H}_2 &= \mathrm{d}t\left(\frac{3 - 2\sqrt{3}}{12}H(t_1) + \frac{3 + 2\sqrt{3}}{12}H(t_2)\right),\label{eq:cf4_sample_2}
 		\end{align}
@@
 		\begin{align}
-			U(t_f + \mathrm{d}t, t_f) = \exp(-i\overline{G}_2)\exp(-i\overline{G}_1).\label{eq:cf4_implementation}
+			\mathcal{U}(t_f + \mathrm{d}t, t_f) = \exp(-i\overline{H}_2)\exp(-i\overline{H}_1).\label{eq:cf4_implementation}
 		\end{align}
@@
 		From Equation \eqref{eq:cf4_implementation}, evaluating matrix exponentials is a core part of the integration algorithm.
-However, the \texttt{spinsim} package uses the user provided field functions \(f(t)\) as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
+		However, the \emph{spinsim} package uses the user provided field functions \(\omega(t)\) as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
 		This allows for implementation of matrix exponentiation that takes advantage of this representation.
-For all implementations of exponentiation, the \texttt{spinsim} computes the matrix exponential
+		For all implementations of exponentiation, the \emph{spinsim} computes the matrix exponential
 
 		\begin{align}
-			E(g) &= E(g_x, g_y, g_z, g_q)\\
-			&= \exp(-i (g_x J_x + g_y J_y + g_z J_z + g_q Q)).
+			E(\omega) &= E(\omega_x, \omega_y, \omega_z, \omega_q)\\
+			&= \exp(-i (\omega_x J_x + \omega_y J_y + \omega_z J_z + \omega_q Q)).
 		\end{align}
 
-		In practice, \(g\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{G_1}\) or \(\overline{G_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
+		In practice, \(\omega\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{H_1}\) or \(\overline{H_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
 		For spin half, the default exponentiator is in an analytic form.
@@
 		\begin{align}
-			\exp\left( A + B\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{A}{n}\right) \exp\left(\frac{B}{n}\right)\right)^n
+			\exp\left( X + Y\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{X}{n}\right) \exp\left(\frac{Y}{n}\right)\right)^n
 		\end{align}
 
-		Where \(A,B\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
+		Where \(X,Y\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
 		The equality holds for without the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
@@
 
-		For our spin one case, the exponential \(E(g)\) can be approximated as, for large \(2^\tau\),
-
+		For our spin one case, the exponential \(E(\omega)\) can be approximated as, for large \(2^\tau\),
 		\begin{align}
-			E(g) =& \exp\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\\
-			=& \exp\left(2^{-\tau}\left(-ig_x J_x - ig_y J_y - ig_z J_z - ig_q Q\right)\right)^{2^\tau}\\
-			\approx& \biggl(\exp\left(-i\frac12\left(2^{-\tau} g_z J_z + 2^{-\tau}g_q Q\right)\right)\nonumber\\
-			&\cdot\exp\left(-i\left(2^{-\tau} g_\phi J_\phi\right)\right)\nonumber\\
-			&\cdot\exp\left(-i\frac12\left(2^{-\tau} g_z J_z + 2^{-\tau} g_q Q\right)\right)\biggr)^{2^\tau}\\
+			E(\omega) =& \exp\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\right)\\
+			=& \exp\left(2^{-\tau}\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\right)\right)^{2^\tau}\\
+			\approx& \biggl(\exp\left(-i\frac12\left(2^{-\tau} \omega_z J_z + 2^{-\tau}\omega_q Q\right)\right)\nonumber\\
+			&\cdot\exp\left(-i\left(2^{-\tau} \omega_\phi J_\phi\right)\right)\nonumber\\
+			&\cdot\exp\left(-i\frac12\left(2^{-\tau} \omega_z J_z + 2^{-\tau} \omega_q Q\right)\right)\biggr)^{2^\tau}\\
 			=& \begin{pmatrix}
-				\left(\frac{\Gamma}{PZ}\right)^2 & \frac{SP}{Z\Phi} & -\left(\frac{\Sigma P}{\Phi}\right)^2 \\
-				\frac{SP\Phi}{Z} & CP^4 & \frac{SPZ}{\Phi} \\
-				-\left(\frac{\Sigma \Phi}{P}\right)^2 & \frac{SPZ\Phi}{1} & \left(\frac{\Gamma Z}{P}\right)^2
+				\left(\cos\left(\frac{\Phi}{2}\right) e^{-iz}e^{-iq}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{-iz}e^{-i\phi} & -\left(\sin\left(\frac{\Phi}{2}\right)e^{iq}e^{-i\phi}\right)^2\\
+				\frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{-iz}e^{i\phi} & \cos(\Phi)e^{i4q} & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{iz}e^{-i\phi}\\
+				-\left(\sin\left(\frac{\Phi}{2}\right)e^{-iq}e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{iz}e^{i\phi} & \left(\cos\left(\frac{\Phi}{2}\right) e^{iz}e^{-iq}\right)^2
+		% 		\left(\frac{\Gamma}{PZ}\right)^2 & \frac{SP}{Z\Phi} & -\left(\frac{\Sigma P}{\Phi}\right)^2 \\
+		% 		\frac{SP\Phi}{Z} & CP^4 & \frac{SPZ}{\Phi} \\
+		% 		-\left(\frac{\Sigma \Phi}{P}\right)^2 & \frac{SPZ\Phi}{1} & \left(\frac{\Gamma Z}{P}\right)^2
 			\end{pmatrix}^{2^\tau}\\
@@
 
-		where
-
-		\begin{align}
-			g_\phi &= \sqrt{g_x^2 + g_y^2}&&\nonumber\\
-			J_\phi &= \frac{g_x}{g_\phi}J_x + \frac{g_y}{g_\phi}J_y&&\nonumber\\
-			\Gamma &= \cos\left(2^{-\tau} \frac{g_\phi}{2}\right) & \Phi &= \exp\left(i2^{-\tau}g_\phi\right)\nonumber\\
-			\Sigma &= \sin\left(2^{-\tau} \frac{g_\phi}{2}\right) & Z &= \exp\left(i2^{-\tau}\frac{g_z}{2}\right)\nonumber\\
-			C &= \cos\left(2^{-\tau} g_\phi\right) & P &= \exp\left(i2^{-\tau}\frac{g_q}{6}\right)\nonumber\\
-			S &= \frac{-i}{\sqrt2}\sin\left(2^{-\tau} g_\phi\right)&&
-		\end{align}
-
-		Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(g)\).
-The approach used for spin one exponentiation means that the package cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8 dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the four dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
-Including the full algebra could be possible as a feature update if there is demand for it, though just including this subspace is sufficient for our application, and many others, and has the advantage of being able to use this faster, more specialised method of matrix exponentiation.
+		Here \(z = 2^{-\tau}\frac{\omega_z}{2}\), \(z = 2^{-\tau}\frac{\omega_q}{6}\), \(\phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2}\), and \(\phi = \mathrm{atan}2(\omega_y, \omega_x)\).
+		Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(\omega)\).
+		In practice the calculations here are done by finding the differences from the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
+		The approach used for spin one exponentiation means that this particular exponentiator cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the 4-dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
+		An exponentiator which can exponentiate an element of the full algebra is included in the package for completeness, though this was not rigorously tested as our lab does not deal with physical systems that would require this functionality to work.
 
 		Note that, the methods for both spin half and spin one use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
-This guarantees that the results of \texttt{spinsim} maintain unitary and conserve probability as required.
+		This guarantees that the results of \emph{spinsim} maintain unitary and conserve probability as required.
 
@@
 
-		where \(\mathrm{D}t\) is the time step of the time series (in contrast to \(\mathrm{d}t\), a smaller time step for integration). If we define
+		where \(\mathrm{D}t\) is the time step of the time series (in contrast to \(\mathrm{d}t\), a smaller time step for integration).
+		If we define
 
@@
 			\psi_k = \psi(t_k)\textrm{ and}\\
-			U_k = U(t_{k}, t_{k-1}),
+			\mathcal{U}_k = \mathcal{U}(t_{k}, t_{k-1}),
 		\end{align}
 
-		then the time series of states \(\psi_k\) and time evolution operators \(U_k\) satisfies
+		then the time series of states \(\psi_k\) and time evolution operators \(\mathcal{U}_k\) satisfies
 
 		\begin{align}
-			\psi_k &= U_k\psi_{k-1}\label{eq:integration_compilation}
+			\psi_k &= \mathcal{U}_k\psi_{k-1}\label{eq:integration_compilation}
 		\end{align}
@@
 		This presents an opportunity for parallelism.
-While each of the \(\psi_k\) must be evaluated sequentially, the value of the \(U_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(U_{k_0}\).
-This means that the time evolution operators \(U_k\) can all be calculated in parallel, and it allows \texttt{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
+		While each of the \(\psi_k\) must be evaluated sequentially, the value of the \(\mathcal{U}_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(\mathcal{U}_{k_0}\).
+		This means that the time evolution operators \(\mathcal{U}_k\) can all be calculated in parallel, and it allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
 
-		In summary, \texttt{spinsim} splits the time evolution of the full simulation into time evolution \(U_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
-When all the \(U_k\) are calculated, the CPU then multiplies the \(U_k\) together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the \(\psi_k\).
+		In summary, \emph{spinsim} splits the time evolution of the full simulation into time evolution \(\mathcal{U}_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
+		When all the \(\mathcal{U}_k\) are calculated, the CPU then multiplies the \(\mathcal{U}_k\) together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the \(\psi_k\).
 
 		Beyond discretisation for parallelisation, we discretise our time evolution operator into individual integration time steps.
-So, each of the \(U_k\) are split into products of time evolution operators between times separated by the integration time step via
+		So, each of the \(\mathcal{U}_k\) are split into products of time evolution operators between times separated by the integration time step via
 
 		\begin{align}
-			U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
-			U_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
-			u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+			\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \mathrm{d}t) \cdots \mathcal{U}(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) \mathcal{U}(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+			\mathcal{U}_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
+			u^k_{L-1} &= \mathcal{U}(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
 		\end{align}
 
-		with \(\mathrm{d}t\) being the integration level time step. Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
+		with \(\mathrm{d}t\) being the integration level time step.
+		Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
 
 	\subsection{Rotating frame}
-		If the rotating frame option is selected, the \(U_k\) are first calculated within a rotating frame of reference as \(U^r_k\), which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
-The rotation speed of the rotating frame is calculated locally for each parallel time step \(U_k\), and only for rotations around the \(z\) axis.
-The rotating from field functions \(f^r_x, f^r_y, f^r_z,\) and \(f^r_q\) are related to the field function from the user input via
+		If the rotating frame option is selected, the \(\mathcal{U}_k\) are first calculated within a rotating frame of reference as \(\mathcal{U}^r_k\), which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
+		The rotation speed of the rotating frame is calculated locally for each parallel time step \(\mathcal{U}_k\), and only for rotations around the \(z\) axis.
+		The rotating from field functions \(\omega^r_x, \omega^r_y, \omega^r_z,\) and \(\omega^r_q\) are related to the field function \(\omega\) from the user input via
 
 		\begin{align}
-			f^r_x(t) + if^r_y(t) &= e^{-i 2\pi f_r t}(f_x(t) + if_y(t)),\\
-			f^r_z(t) &= f_z(t) - f_r\textrm{, and}\\
-			f^r_q(t) &= f_q(t), \textrm{ for spin one.}
+			\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(f_x(t) + i\omega_y(t)),\\
+			\omega^r_z(t) &= \omega_z(t) - \omega_r\textrm{, and}\\
+			\omega^r_q(t) &= \omega_q(t), \textrm{ for spin one.}
 		\end{align}
 
-		Where \(f_r = f_z(t_k + \frac12\mathrm{D}t)\) is sampled the midpoint value of the fields over the interval \([t_{k - 1}, t_k]\).
-This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of \(f_z(t)\), while leaving the other field components at an equivalent magnitude.
-The rotation is then applied to obtain the lab frame time evolution operator \(U_k\) via
+		Where \(\omega_r = \omega_z(t_k + \frac12\mathrm{D}t)\) is sampled the midpoint value of the fields over the interval \([t_{k - 1}, t_k]\).
+		This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of \(\omega_z(t)\), while leaving the other field components at an equivalent magnitude.
+		The rotation is then applied to obtain the lab frame time evolution operator \(\mathcal{U}_k\) via
 
 		\begin{align}
-			U_k &= \exp(-i 2 \pi f_r J_z \mathrm{D}t) U^r_k.
+			\mathcal{U}_k &= \exp(-i \omega_r J_z \mathrm{D}t) \mathcal{U}^r_k.
 		\end{align}
 
-		Specifically, this relationship is
+		Specifically, this relationship is \(\mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right)\) for spin half, and \(\mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t))\) for spin one.
 
-		\begin{align}
-			U_k &= \begin{pmatrix}
-				e^{-i 2\pi f_r \mathrm{D}t} & 0 & 0\\
-				0 & 1 & 0\\
-				0 & 0 & e^{i 2\pi f_r \mathrm{D}t}
-			\end{pmatrix} U^r_k, \textrm{ for spin one, and}\\
-			U_k &= \begin{pmatrix}
-				e^{-i \pi f_r \mathrm{D}t} & 0\\
-				0 & e^{i \pi f_r \mathrm{D}t}
-			\end{pmatrix} U^r_k, \textrm{ for spin half.}
-		\end{align}
+		% \begin{align}
+		% 	\mathcal{U}_k &= \begin{pmatrix}
+		% 		e^{-i \omega_r \mathrm{D}t} & 0 & 0\\
+		% 		0 & 1 & 0\\
+		% 		0 & 0 & e^{i 2\pi f_r \mathrm{D}t}
+		% 	\end{pmatrix} \mathcal{U}^r_k, \textrm{ for spin one, and}\\
+		% 	\mathcal{U}_k &= \begin{pmatrix}
+		% 		e^{-i \pi f_r \mathrm{D}t} & 0\\
+		% 		0 & e^{i \pi f_r \mathrm{D}t}
+		% 	\end{pmatrix} \mathcal{U}^r_k, \textrm{ for spin half.}
+		% \end{align}
 
 		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures \cite{j_j_sakurai_jun_john_modern_1994}.
-Note that this is typically done in conjunction with the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of \(f^r_x, f^r_y, f^r_z,\) and \(f^r_q\) on an average of many cycles do not have a large contribution to time evolution of the solution and can be ignored.
+		Note that this is typically done in conjunction with the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of \(\omega^r_x, \omega^r_y, \omega^r_z,\) and \(\omega^r_q\) on an average of many cycles do not have a large contribution to time evolution of the solution and can be ignored.
 		In some cases, this allows for analytic solutions to the approximate quantum system to be obtained.
-Note that the RWA is \emph{not} invoked in \texttt{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
+		Note that the RWA is \emph{not} invoked in \emph{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
 
 	% \subsubsection{Magnus based integration method}
-	% 	The integration method used in \texttt{spinsim} is the commutator free 4 (CF4) method from Auer et al \cite{auer_magnus_2018}, which based on the Magnus expansion.
-Each of the \(U_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
+	% 	The integration method used in \emph{spinsim} is the commutator free 4 (CF4) method from Auer et al \cite{auer_magnus_2018}, which based on the Magnus expansion.
+Each of the \(\mathcal{U}_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
 
 	% 	\begin{align}
-	% 		U(t_k, t_{k-1}) &= U(t_k, t_k - \mathrm{d}t) \cdots U(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) U(t_{k-1} + \mathrm{d}t, t_{k-1})\\
-	% 		U_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
-	% 		u^k_{L-1} &= U(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+	% 		\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \mathrm{d}t) \cdots \mathcal{U}(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) \mathcal{U}(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+	% 		\mathcal{U}_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
+	% 		u^k_{L-1} &= \mathcal{U}(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
 	% 	\end{align}
@@
 		% \begin{align}
-		% 	g_1 =& (g_{1,x}, g_{1,y}, g_{1,z}, g_{1,q})\\
+		% 	\omega_1 =& (\omega_{1,x}, \omega_{1,y}, \omega_{1,z}, \omega_{1,q})\\
 		% 	=& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, and}\\
-		% 	g_2 =& (g_{2,x}, g_{2,y}, g_{2,z}, g_{2,q})\\
+		% 	\omega_2 =& (\omega_{2,x}, \omega_{2,y}, \omega_{2,z}, \omega_{2,q})\\
 		% 	=& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, so}\\
-		% 	u =& \exp(-i \left( g_{2,x} J_x + g_{2,y} J_y + g_{2,z} J_z + g_{2,q} Q\right))\\
-		% 	&\cdot\exp(-i \left( g_{1,x} J_x + g_{1,y} J_y + g_{1,z} J_z + g_{1,q} Q\right)).
+		% 	u =& \exp(-i \left( \omega_{2,x} J_x + \omega_{2,y} J_y + \omega_{2,z} J_z + \omega_{2,q} Q\right))\\
+		% 	&\cdot\exp(-i \left( \omega_{1,x} J_x + \omega_{1,y} J_y + \omega_{1,z} J_z + \omega_{1,q} Q\right)).
 		% \end{align}
@@
 	\subsection{Integrator architecture}
-		The integrator in the \texttt{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(U_k\).
-This returns when each of the \(U_k\) have been evaluated.
+		The integrator in the \emph{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(\mathcal{U}_k\).
+		This returns when each of the \(\mathcal{U}_k\) have been evaluated.
 
-		The thread starts by calculating \(t_k\) and, if the rotating frame is being used, \(f_r\).
-The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(f\) describing how to sample the Hamiltonian.
+		The thread starts by calculating \(t_k\) and, if the rotating frame is being used, \(\omega_r\).
+		The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(\omega\) describing how to sample the Hamiltonian.
 		The code then loops over each integration time step \(\mathrm{d}t\) to calculate the integration time evolution operators \(u^k_l\).
 
-		Within the loop, the integrator enters a device function (ie a GPU subroutine, which is inline for speed) to sample \(f(t)\), as well as calculate \(e^{-i 2 \pi f_r t}\), at the sample times needed for the integration method.
-After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating \(g\) values, and finally taking the matrix exponentiation in a fourth device function.
-\(u^k_l\) is premultiplied to \(U^r_k\) (which is initialised to \(1\)), and the loop continues.
+		Within the loop, the integrator enters a device function (ie a GPU subroutine, which is inline for speed) to sample \(\omega(t)\), as well as calculate \(e^{-i \omega_r t}\), at the sample times needed for the integration method.
+		After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating \(\overline{H}_1\) and \(\overline{H}_2\) values, and finally taking the matrix exponentiation in a fourth device function.
+		\(u^k_l\) is premultiplied to \(\mathcal{U}^r_k\) (which is initialised to \(1\)), and the loop continues.
 
-		When the loop has finished, if the rotating frame is being used, \(U^r_k\) is transformed to \(U_k\) as in Equation \eqref{eq:integration_compilation}, and this is returned.
-Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \texttt{numba.jit()}ed function from the \(U_k\) and an initial condition \(\psi_{\mathrm{init}}\).
+		When the loop has finished, if the rotating frame is being used, \(\mathcal{U}^r_k\) is transformed to \(\mathcal{U}_k\) as in Equation \eqref{eq:integration_compilation}, and this is returned.
+		Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \texttt{numba.jit()}ed function from the \(\mathcal{U}_k\) and an initial condition \(\psi_{\mathrm{init}}\).
 
 	\subsection{Compilation of integrator}
-		The \texttt{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
+		The \emph{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
 		The particular device functions used are not predetermined, but are instead chosen based on user input to decide a closure.
 		This structure has multiple advantages.
-First, the field function \(f\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
-This allows users to define \(f\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
+		First, the field function \(\omega\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
+		This allows users to define \(\omega\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
 		Compiling the simulator also allows the user to set meta parameters, and choose the features they want to use, in a way that does not require experience with the \texttt{numba.cuda} library.
 		This was especially useful for running benchmarks comparing old integration methods to the new ones, like CF4.
-The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for GPUs with a differing number of registers and \emph{Cuda} cores to the mobile \emph{GeForce GTX 1070} mainly used in testing here.
-Finally, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.
+		The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for different GPUs.
+		Third, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.
 
 		This functionality is interfaced through an object of class \texttt{spinsim.Simulator}.
-The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection (that is, Bloch vector).
+		The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection.
 		Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object.
 
-		\texttt{spinsim} is designed so that a single simulator compilation can be used to execute many simulations, sweeping through a particular parameter, while not needing to be recompiled.
-This is done through the \texttt{sweep\_parameter} argument to the user provided field function \(f\).
+		\emph{spinsim} is designed so that a single simulator compilation can be used to execute many simulations, sweeping through a particular parameter, while not needing to be recompiled.
+		This is done through the \texttt{sweep\_parameter} argument to the user provided field function \(\omega\).
 		The user uses \texttt{sweep\_parameter} to determine a variable parameter for the Hamiltonian.
@@
 		For a use case example, one might want to simulate many spin systems at different locations in a magnetic field gradient in an MRI experiment.
-To do this they could choose to set \(f_z =\texttt{sweep\_parameter}\), which would vary the magnetic field bias in the \(z\) direction for each experiment.
+		To do this they could choose to set \(\omega_z =\texttt{sweep\_parameter}\), which would vary the magnetic field bias in the \(\omega\) direction for each experiment.
 		This feature is demonstrated with examples in the documentation.
@@
 
-	Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \texttt{spinsim} was written for).
+	Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for).
 	This simulation involves continuously driving transitions in the system for 100ms, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
@@
 
-		This baseline was computed in 3.8 hours (in comparison to order of 10ths of a second these \texttt{spinsim} tests were executed in), and was also used for comparisons to other software packages.
+		This baseline was computed in 2.4 hours (in comparison to order of 10ths of a second these \emph{spinsim} tests were executed in), and was also used for comparisons to other software packages.
 		These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
@@
 		The integration techniques tested were the Magnus based CF4, as well as two Euler based sampling methods.
-A midpoint Euler method was chosen as the simplest (and fastest for a given integration time step)  possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code, which also used it.
+		A midpoint Euler method was chosen as the simplest (and fastest for a given integration time step)  possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code.
 		We benchmarked these methods both while using and not using the rotating frame option.
@@
 
-		From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \texttt{spinsim} gives are accurate to those of \emph{SciPy}.
+		From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \emph{spinsim} gives are accurate to those of \emph{SciPy}.
 		Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
@@
 		From Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
-Thus, by default \texttt{spinsim} sets the integrator to CF4, and uses the rotating frame.
+		Thus, by default \emph{spinsim} sets the integrator to CF4, and uses the rotating frame.
 		These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
@@
 				\includegraphics[scale=0.475]{benchmark_spin_one_step_error.pdf}
-				% \caption{Accuracy of the spin one options of \texttt{spinsim}.}
+				% \caption{Accuracy of the spin one options of \emph{spinsim}.}
 				\caption{}
@@
 				\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.pdf}
-				% \caption{Speed vs accuracy of the spin one options of \texttt{spinsim}.}
+				% \caption{Speed vs accuracy of the spin one options of \emph{spinsim}.}
 				\caption{}
@@
 			\end{subfigure}\
-			\caption{Speed and accuracy of the spin one options of \texttt{spinsim}.
+			\caption{Speed and accuracy of the spin one options of \emph{spinsim}.
 			A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
@@
 				\includegraphics[scale=0.475]{benchmark_spin_half_step_error.pdf}
-				% \caption{Accuracy of the spin half options of \texttt{spinsim}.}
+				% \caption{Accuracy of the spin half options of \emph{spinsim}.}
 				\caption{}
@@
 				\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.pdf}
-				% \caption{Speed vs accuracy of the spin half options of \texttt{spinsim}.}
+				% \caption{Speed vs accuracy of the spin half options of \emph{spinsim}.}
 				\caption{}
@@
 			\end{subfigure}
-			\caption{Speed and accuracy of the spin half options of \texttt{spinsim}.
+			\caption{Speed and accuracy of the spin half options of \emph{spinsim}.
 			A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
@@
 	\subsection{Comparison to alternatives}
-		We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \texttt{spinsim}'s performance to theirs. The packages compared were:
-		\begin{itemize}
-			\item \texttt{spinsim} running on the \emph{Cuda} device, using the CF4 integrator and the rotating frame mode, which were the highest performing options when comparing \texttt{spinsim} integration methods.
-			\item \texttt{NDSolve} from the \emph{Mathematica} \cite{wolfram_research_inc_mathematica_2020} software.
-This was chosen as it is popular with our lab group for simulating magnetometry experiments.
-			\item \texttt{scipy.integrate.ivp\_solve()} from the \emph{python} library \texttt{SciPy} \cite{virtanen_scipy_2020}. This was chosen as a generic solver from within the python ecosystem.
-			\item We had also planned to benchmark against \texttt{qutip.sesolve()}, a solver in the popular quantum mechanics \emph{python} library, \texttt{QuTip} \cite{johansson_qutip_2013}.
-However, due to a known bug with the library’s dependencies, this was not installable on Windows 10, the operating system being used for testing, and so benchmarks for it could not be run.
-		\end{itemize}
+		We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \emph{spinsim}'s performance to theirs.
+		The packages compared were are listed in Table \ref{tab:external}.
+		\begin{table}[h!]
+			\caption{The software packages used for and verification of \emph{spinsim}.}
+			\label{tab:external}
+			\begin{tabular}{l|l|p{6.5cm}}
+				\textbf{Software package}									&\textbf{Function}					&\textbf{Details}\\
+				\hline
+				spinsim														&\texttt{Simulator()}				&The best performing \emph{spinsim} configuration, using the CF4 integrator and the rotating frame mode. This was run both on CPU and GPU.
+				\\
+				\hline
+				QuTip \cite{johansson_qutip_2013}							&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
+				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
+				Like \emph{spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\
+				\hline
+				Mathematica \cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
+				This was chosen as it is popular with our lab group for simulating magnetometry experiments.\\
+				\hline
+				SciPy \cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
+				This was chosen as a comparison to a generic solver from within the python ecosystem.
+			\end{tabular}
+		\end{table}
 
-		In each case, the step sizes of the alternative integrators were limited to a maximum value obtain simulation results of different accuracies.
+		In each case, the step sizes of the alternative integrators were limited to a maximum value to obtain simulation results of different accuracies, and the maximum number of steps were modified in some cases to allow more steps to take place.
 		Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
-Similarly to with the internal \texttt{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
-Also like with the internal benchmarks, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
+
+		Similarly to with the internal \emph{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
+		Again, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
+		Functions used for sampling were compiled in both \emph{spinsim} and \emph{QuTip}, and the time taken to complete a simulation was measured in both cases for a second simulation using the already compiled functions.
 
 		Each benchmark was run one simulation at a time.
-However, it might be possible to increase the average speed of many benchmarks from alternative packages using multithreading to run multiple benchmarks at a time.
+		However, it might be possible to increase the average speed of many benchmarks from \emph{Mathematica} and \emph{SciPy} packages using multithreading to run multiple benchmarks at a time.
 		When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
 		Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step consumes a day of computational time.
-But to be fair, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 4 and 8, which is an upper bound for the speed increase that could be obtained by running them parallel on a 4 and 8 core processor, respectively.
-These are respectively shown in plots as both faded and dotted lines.
+		But to be fair, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8, which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor, which appears as dotted lines.
+		Results from \emph{spinsim} and \emph{QuTip} automatically run multithreaded, so this handicap is not plotted for these packages.
 
-		From Figure \ref{fig:benchmark_external}, for any given error tolerance, \texttt{spinsim} is over 3 orders of magnitude faster than \emph{Mathematica}, and 4 orders of magnitude more accurate than \emph{SciPy}.
-In practice, this means that an 8 minute \emph{SciPy} simulation is reduced to 50ms, and a full week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic situation for testing quantum sensing protocols) would take less than one minute in \texttt{spinsim}.
+		From Figure \ref{fig:benchmark_external}, for any given error tolerance, \emph{spinsim} is over 3 orders of magnitude faster than \emph{Mathematica} and \emph{QuTip}, and 4 orders of magnitude more accurate than \emph{SciPy}.
+		In practice, this means that a 25 minute \emph{SciPy} simulation is reduced to 50ms, and a three week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic requirement for testing quantum sensing protocols) would take less than one minute in \emph{spinsim}.
 
@@
 			\caption{Speed vs accuracy of two alternative integration packages.
-A simulation of a typical neural sensing experiment was run for every integration time step, for each of alternative packages (\texttt{NDSolve} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
+			A simulation of a typical neural sensing experiment was run for every integration time step, for each of alternative packages (\texttt{qutip.sesolve()} from \emph{QuTip}, \texttt{NDSolve()} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
 			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
@@
 			Error is RMS error compared to a long running \emph{SciPy} baseline.
-The \emph{Mathematica} and \emph{SciPy} results are also shown with a speed up by a factor of 4 and 8 to represent the upper bound of hypothetical parallelisation across a 4 and 8 core CPU respectively.}
+			The \emph{Mathematica} and \emph{SciPy} results are also shown with a speed up by a factor of 8 to represent the upper bound of hypothetical parallelisation across an 8 core CPU.}
 			\label{fig:benchmark_external}
@@
 	\subsection{Parallelisation performance}
-		Once the algorithm behind \texttt{spinsim} was developed, we wanted to check its execution speed while running on various devices.
-Part of this test was also to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), compared highly procedural devices (being CPUs).
+		Once the algorithm behind \emph{spinsim} was developed, we wanted to check its execution speed while running on various devices.
+		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), compared highly procedural devices (being CPUs).
 		Speed benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin one sensing experiments on different devices.
@@
 		\begin{table}[h!]
-			\caption{Devices used in the parallelisation speed test. These devices are part of individual computers, which are separated here by horizontal lines.}
+			\caption{Devices used in the parallelisation speed test.
+			These devices are part of individual computers, which are separated here by horizontal lines.}
 			\label{tab:devices}
@@
 				GeForce GTX 1070&Nvidia GPU		&8					&2048			&Air\\
+				\hline
+				Core i7-10850H	&Intel CPU		&32					&6				&Air\\
+				Quadro T1000	&Nvidia GPU		&4					&768			&Air\\
 				\hline
@@
 
-		The results shown in Figure \ref{fig:benchmark_device_aggregate} show the benefit to using parallelisation when solving a spin system problem.
-Moving from the 6 core \emph{Core i7-8750H} CPU to the 12 core \emph{Ryzen 9 5900X} CPU doubles the execution speed, as expected.
+		The results in Figure \ref{fig:benchmark_device_aggregate} show the benefit to using parallelisation when solving a spin system problem.
+		Moving from the 6 core \emph{Core i7-8750H} CPU to the 12 core \emph{Ryzen 9 5900X} CPU doubles the execution speed, as does moving from the 384 core \emph{Quadro K620} GPU to the 768 core \emph{Quadro T1000} GPU.
+		So, in these cases, performance scales in proportion to thread count.
 		Moving from a single core processor to a high end GPU increases performance by well over an order of magnitude on three of the four computers tested on.
@@
 		Execution speed vs number of cuda cores starts to plateau as the number of cores increases.
-This happens as the time it takes to transfer memory from RAM to VRAM (dedicated graphics memory), which is independent on the number of cores of the GPU, becomes a comparable to the execution time of the simulator logic.
-However, there is still a large improvement from using the high end \emph{GeForce RTX 3070} to the \emph{GeForce RTX 3080}, with the latter simulating the experiment in almost half the time of the simulated experiment duration.
+		This happens because the time it takes to transfer memory from RAM to VRAM (dedicated graphics memory), which is independent on the number of cores of the GPU, becomes a comparable to the execution time of the simulator logic.
+		However, there is still a large improvement from using the high end \emph{GeForce RTX 3070} to the \emph{GeForce RTX 3080}, with the latter simulating the experiment almost twice as fast as it would take to run the simulated experiment in the real world.
 
@@
 
-		Figure \ref{fig:benchmark_device_aggregate} can be used by potential \texttt{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
+		Figure \ref{fig:benchmark_device_aggregate} can be used by potential \emph{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
 		We would recommend Another factor not shown in the plot is the fact that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
@@
 	\subsection{Testing}
-		During the accuracy tests, it was confirmed that all possible modes of \texttt{spinsim} agree with a standard \emph{SciPy} simulation up to an arbitrarily small error.
+		During the accuracy tests, it was confirmed that all possible modes of \emph{spinsim} agree with a standard \emph{SciPy} simulation up to an arbitrarily small error.
 		The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.
@@
 
-		A good way to confirm that \texttt{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
+		A good way to confirm that \emph{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
 		Otherwise, one can reproduce the benchmarks shown here using \texttt{neural\_sense.sim.benchmark}.
@@
 CPU functionality tested on MacOS Big Sur (note that modern Mac computers are not compatible with \emph{Cuda} software).
-All packages referenced in \texttt{spinsim} are compatible with Linux, but functionality has not been tested.
+All packages referenced in \emph{spinsim} are compatible with Linux, but functionality has not been tested.
 
@@
 	\subsection{Use potential and limitations}
-		\texttt{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
+		\emph{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
 		This is immediately relevant to developing new quantum sensing protocols with spin half and spin one systems.
@@
 		Rubidium BECs can potentially be made sensitive enough to these tiny magnetic fields that they can be measured by them.
-\texttt{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
+		\emph{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
 		The package is also now being used to simulate other BEC magnetometry experiments by the lab group.
@@
 		Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
-A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs \cite{parashar_axon_2020}, which is something that \texttt{spinsim} could be useful for.
+		A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs \cite{parashar_axon_2020}, which is something that \emph{spinsim} could be useful for.
 
-		\texttt{spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
+		\emph{spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
 		This means that it would not be able to integrate large arrays of entangled states or interacting particles.
 		As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
-In addition, \texttt{spinsim} is currently designed to integrate the time evolution of pure states only.
+		In addition, \emph{spinsim} is currently designed to integrate the time evolution of pure states only.
 		This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation \cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).
 
-		With these restrictions in mind, \texttt{spinsim} could be used for some simplified simulations in various areas of NMR.
-There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14) \cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \texttt{spinsim} could be used to simulate for spectroscopy experiments, for example.
-The inclusion of a quadrupole operator means that, with the same level of simplifications, \texttt{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei \cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+		With these restrictions in mind, \emph{spinsim} could be used for some simplified simulations in various areas of NMR.
+		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14) \cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
+		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei \cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
 		This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
 		Another possible use case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
-MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \texttt{spinsim} simulations of spins at different positions in space.
+		MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
 		While this package offers some advantages over state of the art simulators in the field \cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
@@
 	\subsection{Support}
-		Documentation for \texttt{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
+		Documentation for \emph{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
 		This documentation contains a thorough tutorial on how to use the package, and installation instructions.
 
-		For direct support with the \texttt{spinsim} package, one can open an issue in the \emph{github} repository.
+		For direct support with the \emph{spinsim} package, one can open an issue in the \emph{github} repository.
 		One can also use this contact to suggest extensions to the package.
-\texttt{spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
+		\emph{spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
 
@@
 
-Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group, particularly Hamish Taylor and Travis Hartley, who have started using \texttt{spinsim} for their own projects and have given useful feedback of their user experience with the package.
+Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group, particularly Hamish Taylor and Travis Hartley, who have started using \emph{spinsim} for their own projects and have given useful feedback of their user experience with the package.
 

### 2021-06-22 docs/source/conf.py

@@ -39,7 +39,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.3.4'
+release = '0.4.0'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-06-22 example.py

@@ -3,16 +3,14 @@ import numpy as np
 import matplotlib.pyplot as plt
 import math
 
-def get_field_larmor(time_sample, field_modifier, field_sample):
-   field_sample[0] = 0            # Zero field in x direction
-   field_sample[1] = 0            # Zero field in y direction
-   field_sample[2] = math.tau*1000         # Split spin z eigenstates by 1kHz
+def get_field_larmor(time_sample, sweep_parameters, field_sample):
+   field_sample[0] = 0              # Zero field in x direction
+   field_sample[1] = 0              # Zero field in y direction
+   field_sample[2] = math.tau*1000  # Split spin z eigenstates by 1kHz
 
 simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF)
 
-state_init = np.asarray([1/np.sqrt(2), 1/np.sqrt(2)], np.cdouble)
-
-results_larmor = simulator_larmor.evaluate(0, 0e-3, 100e-3, 100e-9, 500e-9, state_init)
+results_larmor = simulator_larmor.evaluate(0e-3, 100e-3, 100e-9, 500e-9, spinsim.SpinQuantumNumber.HALF.plus_x)
 
 plt.figure()
 plt.plot(results_larmor.time, results_larmor.spin)
@@ -28,29 +26,28 @@ import numpy as np
 import matplotlib.pyplot as plt
 import math
 
-def get_field_rabi(time_sample, field_modifier, field_sample):
+def get_field_rabi(time_sample, sweep_parameters, field_sample):
    # Dress atoms from the x direction, Rabi flopping at 1kHz
-   field_sample[0] = math.tau*2000*math.cos(math.tau*20e3*field_modifier*time_sample)
-   field_sample[1] = 0                        # Zero field in y direction
-   field_sample[2] = math.tau*20e3*field_modifier     # Split spin z eigenstates by 700kHz
-   field_sample[3] = 0                        # Zero quadratic shift, found in spin one systems
+   field_sample[0] = math.tau*2000*math.cos(sweep_parameters[0]*time_sample)
+   field_sample[1] = 0                    # Zero field in y direction
[…]

### 2021-06-22 full_algebra_example.py

@@ -1,0 +1,29 @@
+import spinsim
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+
+def get_field_rabi(time_sample, sweep_parameters, field_sample):
+    # Dress atoms from the x direction, Rabi flopping at 1kHz
+    field_sample[0] = math.tau*2000*math.cos(sweep_parameters[0]*time_sample)
+    field_sample[1] = 0
+    field_sample[2] = sweep_parameters[0]   # Split spin z eigenstates by 700kHz
+    field_sample[3] = math.tau*100                        # Zero quadratic shift, found in spin one systems
+    field_sample[4] = math.tau*100
+    field_sample[5] = math.tau*100
+    field_sample[6] = math.tau*100
+    field_sample[7] = math.tau*100
+
+simulator_rabi = spinsim.Simulator(get_field_rabi, spinsim.SpinQuantumNumber.ONE, exponentiation_method = spinsim.ExponentiationMethod.LIE_TROTTER_8)
+
+result = simulator_rabi.evaluate(0e-3, 100e-3, 100e-9, 500e-9, spinsim.SpinQuantumNumber.ONE.plus_z, [math.tau*20e3])
+
+plt.figure()
+plt.plot(result.time, result.spin)
+plt.legend(["x", "y", "z"])
+plt.xlim(0e-3, 2e-3)
+plt.ylim(-1, 1)
+plt.xlabel("time (s)")
+plt.ylabel("spin expectation (hbar)")
+plt.title("Spin projection for Rabi flopping")
+plt.show()

### 2021-06-22 gaussian_example.py

@@ -6,8 +6,8 @@ import datetime as dtm
 
 time_now_string = dtm.datetime.now().strftime("%Y%m%dT%H%M%S")
 
-def gaussian_pulse(time, modifier, pulse):
-    pulse[0] = (math.pi/math.sqrt(math.tau))*math.exp(-0.5*(time**2))/math.tau
+def gaussian_pulse(time, sweep_parameters, pulse):
+    pulse[0] = (math.pi/math.sqrt(math.tau))*math.exp(-0.5*(time**2))
     pulse[1] = 0.0
     pulse[2] = 0.0
 
@@ -69,7 +69,7 @@ state_analytic = np.asarray([[math.cos(0.5*math.pi*cumulative_gaussian(t)), -1j*
 
 simulator = spinsim.Simulator(gaussian_pulse, spinsim.SpinQuantumNumber.HALF)
 
-result_compare = simulator.evaluate(0.0, -5.0, 7.0, 1e-6, 2.0, np.asarray([1, 0], np.complex128))
+result_compare = simulator.evaluate(-5.0, 7.0, 1e-6, 2.0, spinsim.SpinQuantumNumber.HALF.plus_z)
 
 legend = []
 
@@ -79,7 +79,7 @@ time_steps = np.asarray([0.001, 0.005, 0.01, 0.05, 0.1, 0.25, 0.5, 1.0, 2.0])
 number_of_steps = 10 / time_steps
 plot_start_index = 4
 for simulation_index, time_step in enumerate(time_steps):
-    result_simulated = simulator.evaluate(0.0, -5.0, 7.0, time_step, 2.0, np.asarray([1, 0], np.complex128))
+    result_simulated = simulator.evaluate(-5.0, 7.0, time_step, 2.0, np.asarray([1, 0], np.complex128))
 
     error += [np.sum(np.abs(result_simulated.state - result_compare.state))/5]
 
@@ -98,8 +98,6 @@ plt.legend(legend, loc = "lower left")
 plt.xlabel("Time (standard deviations)")
 plt.ylabel("Spin")
 plt.title("{}\nGaussian pulse at various numbers of steps".format(time_now_string))
-plt.savefig("gaussian_pulse.png")
-plt.savefig("gaussian_pulse.pdf")
 plt.show()
 
 plt.figure()
@@ -108,6 +106,4 @@ plt.xlabel("Number of steps")
 plt.ylabel("Error")
[…]

### 2021-06-22 spinsim/__init__.py

@@ -34,6 +34,27 @@ class SpinQuantumNumber(Enum):
         self._value_ = value
         self.dimension = dimension
         self.label = label
+        if self.label == "half":
+            self.plus_x = np.array([1, 1], np.complex128)/math.sqrt(2)
+            self.minus_x = np.array([-1, 1], np.complex128)/math.sqrt(2)
+
+            self.plus_y = np.array([1, 1j], np.complex128)/math.sqrt(2)
+            self.minus_y = np.array([1, -1j], np.complex128)/math.sqrt(2)
+
+            self.plus_z = np.array([1, 0], np.complex128)
+            self.minus_z = np.array([0, 1], np.complex128)
+        else:
+            self.plus_x = np.array([1, math.sqrt(2), 1], np.complex128)/2
+            self.zero_x = np.array([-1, 0, 1], np.complex128)/math.sqrt(2)
+            self.minus_x = np.array([1, -math.sqrt(2), 1], np.complex128)/2
+
+            self.plus_y = np.array([-1, -1j*math.sqrt(2), 1], np.complex128)/2
+            self.zero_y = np.array([1, 0, 1], np.complex128)/math.sqrt(2)
+            self.minus_y = np.array([1, -1j*math.sqrt(2), 1], np.complex128)/2
+
+            self.plus_z = np.array([1, 0, 0], np.complex128)
+            self.zero_z = np.array([0, 1, 0], np.complex128)
+            self.minus_z = np.array([0, 0, 1], np.complex128)
 
     HALF = (1/2, 2, "half")
     """
@@ -93,7 +114,12 @@ class ExponentiationMethod(Enum):
 
     LIE_TROTTER = ("lie_trotter", 1)
     """
-    Approximation using the Lie Trotter theorem.
+    Approximation using the Lie Trotter theorem, using the Pauli matrices and a single quadratic operator.
+    """
+
+    LIE_TROTTER_8 = ("lie_trotter_8", 2)
+    """
+    Approximation using the Lie Trotter theorem, using all basis elements of su(3).
     """
 
 class Device(Enum):
@@ -309,7 +335,7 @@ class Simulator:
 
         Parameters:
 
-        * **sweep_parameter** (:obj:`float`) - The input to the `get_field` function supplied by the user. Modifies the field function so the integrator can be used for many experiments, without the need for slow recompilation. For example, if the `sweep_parameter` is used to define the bias field strength in `get_field`, then one can run many simulations, sweeping through bias values, by calling this method multiple times, each time varying `sweep_parameter`.   
[…]

### 2021-06-24 article/article.tex
Article and documentation updates

@@
 \section{Abstract}
-	\emph{spinsim} is a \emph{python} package that simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
-	It makes use of \texttt{numba.cuda} \cite{lam_numba_2015}, which is an \emph{LLVM} (Low Level Virtual Machine) \cite{lattner_llvm_2004} compiler, and other optimisations, to allow for fast and accurate evaluation on \emph{Nvidia Cuda} \cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
+	The \emph{spinsim} \emph{python} package simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
+	It makes use of \texttt{numba.cuda}\cite{lam_numba_2015}, which is an \emph{LLVM} (Low Level Virtual Machine)\cite{lattner_llvm_2004} compiler for \emph{Nvidia Cuda}\cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
+	Along with other optimisations, this allows for speed improvements of up to four orders of magnitude while keeping staying just as accurate.
 	\emph{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
@@
 \section{Keywords}
-Time dependent Schroedinger equation; Spin one; Spin half; Integrator; GPU; Solver; python; numba;
+Time dependent Schr\"odinger equation; Quantum; Physics; Spin one; Spin half; Integrator; Exponentiator; GPU; Parallel computing; Solver; python; numba;
 
@@
 \subsection{Motivation}
-	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing \cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
+	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing\cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
 	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
@@
 
-	% \texttt{AtomicPy} \cite{morris_qcmonkatomicpy_2018}
+	% \texttt{AtomicPy}\cite{morris_qcmonkatomicpy_2018}
 	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schroedinger equation for quantum sensing spin systems.
@@
 	Standard integration methods require very small time steps in order to accurately depict these oscillations.
+
+	Given the recent boom in machine learning, many research computers are now equipped with advanced graphics processing units (GPUs).
+	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
+	Examples include calculating colours for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
+	By finding ways to parallelise the problem of solving quantum spin systems, we can use the many cores of a GPU to our advantage in this context as well.
 
@@
 		In the spin one case there is no standard basis of operators \(A_j\).
-		Choices include the Gell Mann matrices, and multiple dipole-quadrupole bases \cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
+		Choices include the Gell Mann matrices, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
 		In general, we can choose any basis from the 8-dimensional Lie algebra \(\mathfrak{su}(3)\), which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group \(SU(3)\)) in the spin one system.
@@
 
-		Note that \(Q\) is proportional to \(Q_{zz}\) \cite{hamley_spin-nematic_2012} and \(Q_0\) \cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
-		These are the only operators necessary to simulate many spin one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula.
-		\emph{spinsim} can also be configured to solve a general spin one system by setting the Hamiltonian to an arbitrary point in \(\mathfrak{su}(3)\), using the full quadrupole basis, which extends the possible Hamiltonian to
+		Note that \(Q\) is proportional to \(Q_{zz}\)\cite{hamley_spin-nematic_2012} and \(Q_0\)\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
+		These are the only operators necessary to simulate many spin one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
+		The \emph{spinsim} simulator can also be configured to solve a general spin one system by setting the Hamiltonian to an arbitrary point in \(\mathfrak{su}(3)\), using the full quadrupole basis, which extends the possible Hamiltonian to
 		\begin{align}
 			H(t) &= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q\nonumber\\
-			&+ \omega_{ux}(t) U_1 + \omega_{uy}(t) U_2 + \omega_{vx}(t) V_1 + \omega_{vy}(t) V_2.
+			&+ \omega_{u1}(t) U_1 + \omega_{u2}(t) U_2 + \omega_{v1}(t) V_1 + \omega_{v2}(t) V_2.
 		\end{align}
-		Here the added operators are those defined in \cite{di_dipolequadrupole_2010}.
+		Here the added operators are those defined in\cite{di_dipolequadrupole_2010}.
 Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the \(U_1, U_2, V_1\) and \(V_2\) operators.
@@
 		% The matrices \(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadrupole operator.
-Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.
+Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al\cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al\cite{di_dipolequadrupole_2010}.
 		% INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
@@
 		% Note that because \(\mathcal{U}(t, t_0)\) is unitary, the calculated value of \(\psi(t)\) using this method will not change in magnitude, conserving probability.
-		Also since \(\mathcal{U}(t, t_0)\) is unitary, it can be written as a matrix exponential of a skew-Hermitian (also termed anti-Hermitian) matrix.
+		Since \(\mathcal{U}(t, t_0)\) is unitary, it can be written as a matrix exponential of a skew-Hermitian (also termed anti-Hermitian) matrix.
 		If the Hamiltonian is constant, then this exponential is % Check if continuity requirement on unitary
@@
 		\end{align}
-		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series \cite{blanes_magnus_2009}, where
+		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series\cite{blanes_magnus_2009}, where
 		For a time varying Hamiltonian, the general solution for \(\mathcal{U}(t, t_0)\) is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
-		The Dyson series gives an explicit expression for \(\mathcal{U}(t, t_0)\) in terms of multiple time integrals over nested time commutators of \(H(t')\). % Cite 2? recent papers
-		While the Dyson series has been used numerically, it has only been so recently, in particular because once truncated, it is in general no longer unitary.
+		The Dyson series\cite{kalev_integral-free_2020} gives an explicit expression for \(\mathcal{U}(t, t_0)\) in terms of multiple time integrals over nested time commutators of \(H(t')\).
+		While the Dyson series has been used numerically\cite{kalev_integral-free_2020}, it has only been so recently, in particular because once truncated, it is in general no longer unitary.
 
@@
 
-		A Magnus series over a time step \(T\) will be guaranteed to converge only if the spectral norm of \(H\) is sufficiently small, \(\int_{t_0}^{t_0 + T}\mathrm{d}t_1\|H(t_1)\| < \pi\)\cite{blanes_magnus_2009}.
+		A Magnus series over a time step \(T\) will be guaranteed to converge only if \(\int_{t_0}^{t_0 + T}\mathrm{d}t_1\|H(t_1)\| < \pi\)\cite{blanes_magnus_2009}.
 Furthermore, each subsequent term in the expansion increases in complexity rapidly.
-For these reasons, the Magnus expansion can be used as a time stepping method rather than a single step to solve the complete system.
+For these reasons, the Magnus expansion is used as a time stepping method rather than a single step to solve the complete system.
 Time stepping can be made from the fact that time evolution operators can be split into a product via
@@
 
-		Many unitary time stepping techniques have been developed based on the Magnus expansion \cite{auer_magnus_2018}.
-		Some of these techniques use Gauss-Legendre quadrature sampling to avoid the integration of commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping.
-		In particular, we used the commutator free 4 (CF4) from \cite{auer_magnus_2018} as our integration method.
-		Suppose we wish to evaluate a short time step of \(\mathcal{U}(t_f + \mathrm{d}t, t_f)\) by taking a short step \(\mathrm{d}t\) from a fine sample time \(t_f\).
-		Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
-
+		Many unitary time stepping techniques have been developed based on the Magnus expansion\cite{auer_magnus_2018}.
+		Some of these techniques use Gauss-Legendre quadrature sampling to avoid the integration of commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping\cite{auer_magnus_2018}.
+% Suggest not obvious
+		In particular, we use the commutator free, fourth order method (CF4) from Reference~\cite{auer_magnus_2018}.
+		Suppose we wish to evaluate a time step of \(\mathcal{U}(t + \mathrm{d}t, t)\) using the CF4 method.
+		The Hamiltonians are sampled at times
 		\begin{align}
-			t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
-			t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
+			t_1 &= t + \frac12 \left(1 - \frac{1}{\sqrt{3}}\right)\mathrm{d}t\quad\text{and}\\
+			t_2 &= t + \frac12 \left(1 + \frac{1}{\sqrt{3}}\right)\mathrm{d}t,
+		\end{align} % maybe not rm d
+		based on the second order Gauss-Legendre quadrature
+		\begin{align}
+			\overline{H}_1 &= \frac{3 + 2\sqrt{3}}{12}H(t_1) + \frac{3 - 2\sqrt{3}}{12}H(t_2)\quad\text{and}\label{eq:cf4_sample_1}\\
+			\overline{H}_2 &= \frac{3 - 2\sqrt{3}}{12}H(t_1) + \frac{3 + 2\sqrt{3}}{12}H(t_2).\label{eq:cf4_sample_2}
 		\end{align}
-
-		Then given the matrices
-
+		% \, \quad \qquad
+		The time evolution operator is then approximated by
 		\begin{align}
-			\overline{H}_1 &= \mathrm{d}t\left(\frac{3 + 2\sqrt{3}}{12}H(t_1) + \frac{3 - 2\sqrt{3}}{12}H(t_2)\right)\textrm{, and}\label{eq:cf4_sample_1}\\
-			\overline{H}_2 &= \mathrm{d}t\left(\frac{3 - 2\sqrt{3}}{12}H(t_1) + \frac{3 + 2\sqrt{3}}{12}H(t_2)\right),\label{eq:cf4_sample_2}
-		\end{align}
-
-		the unitary time step can be calculated using
-
-		\begin{align}
-			\mathcal{U}(t_f + \mathrm{d}t, t_f) = \exp(-i\overline{H}_2)\exp(-i\overline{H}_1).\label{eq:cf4_implementation}
-		\end{align}
+			\mathcal{U}(t + \mathrm{d}t, t) = \exp(-i\overline{H}_2\mathrm{d}t)\exp(-i\overline{H}_1\mathrm{d}t).\label{eq:cf4_implementation}
+		\end{align}% \approx? Unitary? End with sentence
 
@@
 		For all implementations of exponentiation, the \emph{spinsim} computes the matrix exponential
-
 		\begin{align}
@@
 		\end{align}
+		In practice, \(\omega\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{H_1}\) or \(\overline{H_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
 
-		In practice, \(\omega\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{H_1}\) or \(\overline{H_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
 		For spin half, the default exponentiator is in an analytic form.
-		For spin one, an exponentiator based on the Lie Trotter product formula \cite{moler_nineteen_2003} is used instead.
+		For spin one, an exponentiator based on the Lie Trotter product formula\cite{moler_nineteen_2003} is used instead.
 		Explicitly, this formula is
-
 		\begin{align}
@@
 		\end{align}
-
 		Where \(X,Y\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
@@
 				-\left(\sin\left(\frac{\Phi}{2}\right)e^{-iq}e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{iz}e^{i\phi} & \left(\cos\left(\frac{\Phi}{2}\right) e^{iz}e^{-iq}\right)^2
-		% 		\left(\frac{\Gamma}{PZ}\right)^2 & \frac{SP}{Z\Phi} & -\left(\frac{\Sigma P}{\Phi}\right)^2 \\
-		% 		\frac{SP\Phi}{Z} & CP^4 & \frac{SPZ}{\Phi} \\
-		% 		-\left(\frac{\Sigma \Phi}{P}\right)^2 & \frac{SPZ\Phi}{1} & \left(\frac{\Gamma Z}{P}\right)^2
 			\end{pmatrix}^{2^\tau}\\
@@
 		\end{align}
-
+		% \begin{align}
+		% 	E(\omega) =& \exp\biggl(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\\
+		% 	&- i\omega_{u1} U_1 - i\omega_{u2} U_2 - i\omega_{v1} V_1 - i\omega_{v2} V_2\biggr)\\
+		% 	& \exp\biggl(2^{-\tau}\biggl(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\\
+		% 	&- i\omega_{u1} U_1 - i\omega_{u2} U_2 - i\omega_{v1} V_1 - i\omega_{v2} V_2\biggr)\biggr)^{2^\tau}\\
+		% 	\approx& \biggl(\exp\left(-i2^{-\tau} \omega_\phi J_\phi\right)\exp\left(-i2^{-\tau} \omega_{u\phi} U_{u\phi}\right)\\
+		% 	&\cdot\exp\left(-i2^{-\tau} \omega_{v\phi} V_{v\phi}\right)\exp\left(-i2^{-\tau} \omega_z J_z -i2^{-\tau} \omega_q Q \right)\biggr)^{2^\tau}\\
+		% 	=& \biggl(\begin{pmatrix}
+		% 		\cos^2\left(\frac{\Phi}{2}\right) & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{-i\phi} & -\left(\sin\left(\frac{\Phi}{2}\right)e^{-i\phi}\right)^2\\
+		% 		\frac{-i}{\sqrt{2}} \sin(\Phi)e^{i\phi} & \cos\left(\Phi\right) & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{-i\phi}\\
+		% 		-\left(\sin\left(\frac{\Phi}{2}\right)e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{i\phi} & \cos^2\left(\frac{\Phi}{2}\right)
+		% 	\end{pmatrix}\\
+		% 	&\cdot \begin{pmatrix}
+		% 		\cos\left(\Phi_u\right) & 0 & -i \sin\left(\Phi_u\right)e^{-i\phi_u}\\
+		% 		0 & 1 & 0\\
+		% 		-i \sin\left(\Phi_u\right)e^{i\phi_u} & 0 & \cos\left(\Phi_u\right)
+		% 	\end{pmatrix}\\
+		% 	&\cdot \begin{pmatrix}
+		% 		\cos^2\left(\frac{\Phi_v}{2}\right) & \frac{-i}{\sqrt{2}} \sin(\Phi_v)e^{-i\phi_v} & \left(\sin\left(\frac{\Phi_v}{2}\right)e^{-i\phi_v}\right)^2\\
+		% 		\frac{-i}{\sqrt{2}} \sin(\Phi_v)e^{i\phi_v} & \cos\left(\Phi_v\right) & \frac{i}{\sqrt{2}} \sin(\Phi_v)e^{-i\phi_v}\\
+		% 		\left(\sin\left(\frac{\Phi_v}{2}\right)e^{i\phi_v}\right)^2 & \frac{i}{\sqrt{2}} \sin(\Phi_v)e^{i\phi_v} & \cos^2\left(\frac{\Phi_v}{2}\right)
+		% 	\end{pmatrix}\\
+		% 	&\cdot \begin{pmatrix}
+		% 		e^{-iz - iq} & 0 & 0\\
+		% 		0 & e^{i2q} & 0\\
+		% 		0 & 0 & e^{iz - iq}
+		% 	\end{pmatrix}\biggr)^{2^\tau}\\
+		% 	=& T^{2^\tau}
+		% \end{align}
 		Here \(z = 2^{-\tau}\frac{\omega_z}{2}\), \(z = 2^{-\tau}\frac{\omega_q}{6}\), \(\phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2}\), and \(\phi = \mathrm{atan}2(\omega_y, \omega_x)\).
@@
 		In practice the calculations here are done by finding the differences from the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
+
 		The approach used for spin one exponentiation means that this particular exponentiator cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the 4-dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
@@
 		\end{align}
-
 		where \(\mathrm{D}t\) is the time step of the time series (in contrast to \(\mathrm{d}t\), a smaller time step for integration).
 		If we define
-
 		\begin{align}
@@
 		\end{align}
-
 		then the time series of states \(\psi_k\) and time evolution operators \(\mathcal{U}_k\) satisfies
-
 		\begin{align}
@@
 		So, each of the \(\mathcal{U}_k\) are split into products of time evolution operators between times separated by the integration time step via
-
 		\begin{align}
@@
 		The rotating from field functions \(\omega^r_x, \omega^r_y, \omega^r_z,\) and \(\omega^r_q\) are related to the field function \(\omega\) from the user input via
-
 		\begin{align}
-			\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(f_x(t) + i\omega_y(t)),\\
+			\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(\omega_x(t) + i\omega_y(t)),\\
 			\omega^r_z(t) &= \omega_z(t) - \omega_r\textrm{, and}\\
@@
 		The rotation is then applied to obtain the lab frame time evolution operator \(\mathcal{U}_k\) via
-
 		\begin{align}
@@
 		\end{align}
-
 		Specifically, this relationship is \(\mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right)\) for spin half, and \(\mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t))\) for spin one.
 
-		% \begin{align}
-		% 	\mathcal{U}_k &= \begin{pmatrix}
-		% 		e^{-i \omega_r \mathrm{D}t} & 0 & 0\\
-		% 		0 & 1 & 0\\
-		% 		0 & 0 & e^{i 2\pi f_r \mathrm{D}t}
-		% 	\end{pmatrix} \mathcal{U}^r_k, \textrm{ for spin one, and}\\
-		% 	\mathcal{U}_k &= \begin{pmatrix}
-		% 		e^{-i \pi f_r \mathrm{D}t} & 0\\
-		% 		0 & e^{i \pi f_r \mathrm{D}t}
-		% 	\end{pmatrix} \mathcal{U}^r_k, \textrm{ for spin half.}
-		% \end{align}
-
-		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures \cite{j_j_sakurai_jun_john_modern_1994}.
+		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
 		Note that this is typically done in conjunction with the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of \(\omega^r_x, \omega^r_y, \omega^r_z,\) and \(\omega^r_q\) on an average of many cycles do not have a large contribution to time evolution of the solution and can be ignored.
@@
 	% \subsubsection{Magnus based integration method}
-	% 	The integration method used in \emph{spinsim} is the commutator free 4 (CF4) method from Auer et al \cite{auer_magnus_2018}, which based on the Magnus expansion.
+	% 	The integration method used in \emph{spinsim} is the commutator free 4 (CF4) method from Auer et al\cite{auer_magnus_2018}, which based on the Magnus expansion.
 Each of the \(\mathcal{U}_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
@@
 		% The CF4 method is used to calculate each individual \(u^k_l\).
-Let the fine sample time be given by \(t_f = l\mathrm{d}t + t_k\).
+Let the fine sample time be given by \(t_I = l\mathrm{d}t + t_k\).
 Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
@@
 		% \begin{align}
-		% 	t_1 &= t_f + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
-		% 	t_2 &= t_f + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
+		% 	t_1 &= t_I + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
+		% 	t_2 &= t_I + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
 		% \end{align}
@@
 \section{Quality control}
-	% \subsection{Benchmarks}
 	\subsection{Evaluation of accuracy}
@@
 
-	Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense} \cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for).
+		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for).
 		This simulation involves continuously driving transitions in the system for 100ms, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
@@
 		Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) error from a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
-
 		\begin{align}
@@
 		These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
-
 		\begin{figure}[h!]
@@
 		\end{figure}
-
 		\begin{figure}[h!]
@@
 				\hline
-				QuTip \cite{johansson_qutip_2013}							&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
+				QuTip\cite{johansson_qutip_2013}							&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
 				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
@@
 				\hline
-				Mathematica \cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
+				Mathematica\cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
 				This was chosen as it is popular with our lab group for simulating magnetometry experiments.\\
 				\hline
-				SciPy \cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
+				SciPy\cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
 				This was chosen as a comparison to a generic solver from within the python ecosystem.
@@
 		In practice, this means that a 25 minute \emph{SciPy} simulation is reduced to 50ms, and a three week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic requirement for testing quantum sensing protocols) would take less than one minute in \emph{spinsim}.
-
 		\begin{figure}[h!]
@@
 		\end{table}
-
 		\begin{figure}[htbp!]
@@
 \section{Additional system requirements}
-To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU \cite{noauthor_cuda_2012}.
-For \emph{Cuda} mode to function, one also needs to install the \emph{Nvidia Cuda} toolkit \cite{noauthor_cuda_2013}.
+To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU\cite{noauthor_cuda_2012}.
+For \emph{Cuda} mode to function, one also needs to install the \emph{Nvidia Cuda} toolkit\cite{noauthor_cuda_2013}.
 If \emph{Cuda} is not available on the system, the simulator will automatically parallelise over multicore CPUs instead.
@@
 		Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
-		A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs \cite{parashar_axon_2020}, which is something that \emph{spinsim} could be useful for.
+		A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs\cite{parashar_axon_2020}, which is something that \emph{spinsim} could be useful for.
 
@@
 		In addition, \emph{spinsim} is currently designed to integrate the time evolution of pure states only.
-		This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation \cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).
+		This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation\cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).
 
 		With these restrictions in mind, \emph{spinsim} could be used for some simplified simulations in various areas of NMR.
-		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14) \cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
-		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei \cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14)\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
+		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
 		This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
 		Another possible use case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
-		MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence \cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
-		While this package offers some advantages over state of the art simulators in the field \cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
+		MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
+		While this package offers some advantages over state of the art simulators in the field\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
 

### 2021-06-24 spinsim/__init__.py

@@ -27,6 +27,8 @@ class SpinQuantumNumber(Enum):
         Dimension of the hilbert space the states with this spin belong to.
     label : :obj:`str`
         A text label that can be used for archiving.
+    plus_x, plus_y, plus_z, zero_x, zero_y, zero_z, minus_x, minus_y, minus_z : :obj:`numpy.ndarray` of :obj:`numpy.complex128`
+        Eigenstates of the spin operators for quick reference.
     """
 
     def __init__(self, value, dimension, label):
@@ -340,7 +342,7 @@ class Simulator:
         * **time_end_points** (:obj:`numpy.ndarray` of :obj:`numpy.float64` (start/end)) - The time offset that the experiment is to start at, and the time that the experiment is to finish at. Measured in s.
         * **time_step_integration** (:obj:`float`) - The integration time step. Measured in s.
         * **time_step_output** (:obj:`float`) - The sample resolution of the output timeseries for the state. Must be a whole number multiple of `time_step_integration`. Measured in s.
-        * **time_evolution_coarse** (:obj:`numpy.ndarray` of :obj:`numpy.float128` (time_index, y_index, x_index)) - The evaluated time evolution operator between each time step. See :ref:`architecture` for some information.
+        * **time_evolution_output** (:obj:`numpy.ndarray` of :obj:`numpy.float128` (time_index, y_index, x_index)) - The evaluated time evolution operator between each time step. See :ref:`architecture` for some information.
     spin_calculator : :obj:`callable`
         Calculates the expected spin projection (Bloch vector) over time for a given time series of a quantum state. This :obj:`callable` is passed to the :obj:`Results` object returned from :func:`Simulator.evaluate()`, and is executed there just in time if the `spin` property is needed. Compiled for chosen device on object constrution.
 
@@ -417,38 +419,56 @@ class Simulator:
         Parameters
         ----------
         get_field : :obj:`callable`
-            A python function that describes the field that the spin system is being put under. It must have three arguments:
+            A python function that describes the field that the spin system is being put under.
+            It must have three arguments:
             
             * **time_sample** (:obj:`float`) - the time to sample the field at, in units of s.
-            * **simulation_index** (:obj:`int`) - a parameter that can be swept over when multiple simulations need to be run. For example, it is used to sweep over dressing frequencies during the simulations that `spinsim` was designed for.
[…]

### 2021-06-28 article/article.tex
Article changes

@@
 	\subsection{Exponentiator}
-		From Equation \eqref{eq:cf4_implementation}, evaluating matrix exponentials is a core part of the integration algorithm.
-		However, the \emph{spinsim} package uses the user provided field functions \(\omega(t)\) as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
-		This allows for implementation of matrix exponentiation that takes advantage of this representation.
-		For all implementations of exponentiation, the \emph{spinsim} computes the matrix exponential
+		Evaluating matrix exponentials is a core part of the integration algorithm.
+		Rather than exponentiating the Hamiltonian directly as in Equation \eqref{eq:cf4_implementation}, \emph{spinsim} works with the field functions \(\omega_i(t)\).
+		% as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
+		% This allows for matrix exponentiators that take advantage of this representation.
+		% For all implementations of exponentiation, the \emph{spinsim} computes the matrix exponential
+		% % \begin{align}
+		% % 	\exp(-iHt) &= E(\omega_x, \omega_y, \omega_z, \omega_q)\\
+		% % 	&= \exp(-i (\omega_x J_x + \omega_y J_y + \omega_z J_z + \omega_q Q)).
+		% % \end{align}
+		% \begin{align}
+		% 	\exp(-iHt) &= E(\omega_x, \omega_y, \omega_z, \omega_q)\\
+		% 	&= \exp(-i (\omega_x J_x + \omega_y J_y + \omega_z J_z + \omega_q Q)).
+		% \end{align}
+		% In practice, \(\omega\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{H_1}\) or \(\overline{H_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
+
+		For spin-half, the default exponentiator is in an analytic form in \(\omega_x\).% ... yz, which follows directly from eqref
+		For spin-one, an exponentiator based on the Lie-Trotter product formula\cite{moler_nineteen_2003}
+		% Explicitly, this formula is
 		\begin{align}
-			E(\omega) &= E(\omega_x, \omega_y, \omega_z, \omega_q)\\
-			&= \exp(-i (\omega_x J_x + \omega_y J_y + \omega_z J_z + \omega_q Q)).
+			\exp\left( X + Y\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{X}{n}\right) \exp\left(\frac{Y}{n}\right)\right)^n,\label{eq:lie_trotter}
 		\end{align}
-		In practice, \(\omega\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{H_1}\) or \(\overline{H_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
+		is used.
+		Here \(X,Y\in\mathbb{C}^{N\times N}\).
+		An advantage of the Lie-Trotter approach is that \(\exp(-iA_k/n)\) has known analytic forms for the Lie algebra basis elements \(A_k\).
+		Hence the unitary time evolution operator is approximated by \( U = \exp(iHt) \approx T^n \) where \( T= \exp(i \omega_x J_x / n) \exp(i \omega_y J_y / n) \dots \).
+		In fact, commutation relations between the Lie basis operators and Lie half step splitting allow us to write \(T = \exp(-iD_{z,q}/2n)\exp(-i\Phi J_\phi/n)\exp(-iD_{z,q}/2n)\) % Splitting methods
+		% The equality holds for the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
+		% This tells us that we can approximate a matrix exponential of a linear combination of Hermitian operators by scaling down these operators, taking the analytically simple exponentials of each of the operators \(-iJ_x, -iJ_y, -iJ_z\) and \(-iQ\) separately, multiplying each individual result together, and then raising the combination \(T\) to the power of the original reduction.
+		% 2^{-\tau} -> n
+		% where X=Jx+iJy and Y=Qz+JZ
+		% Dz=Jz+Qzz
 
-		For spin half, the default exponentiator is in an analytic form.
-		For spin one, an exponentiator based on the Lie Trotter product formula\cite{moler_nineteen_2003} is used instead.
-		Explicitly, this formula is
-		\begin{align}
-			\exp\left( X + Y\right) &= \lim_{n\to\infty} \left(\exp\left(\frac{X}{n}\right) \exp\left(\frac{Y}{n}\right)\right)^n
-		\end{align}
-		Where \(X,Y\in\mathbb{C}^{N\times N}\) are matrix operators, and \(n\in\mathbb{N}\).
-		The equality holds for without the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
-		This tells us that we can approximate a matrix exponential of a linear combination of spin operators by reducing the size of the coefficients of these operators, taking the analytically simple exponentials of each of the operators \(-iJ_x, -iJ_y, -iJ_z\) and \(-iQ\) separately, multiplying each individual result together, and then raising the combination \(T\) to the power of the original reduction.
-
-		For our spin one case, the exponential \(E(\omega)\) can be approximated as, for large \(2^\tau\),
+		The exponential \(E(\omega)\) can be approximated as, for large \(2^\tau\),
 		\begin{align}
@@
 		\end{align}
+		% % Trotter half
+		% \begin{align}
+		% 	E(\omega) =& \exp\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z\right)\\
+		% 	=& \exp\left(2^{-\tau}\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z\right)\right)^{2^\tau}\\
+		% 	\approx& \biggl(\exp\left(-i\frac12 2^{-\tau} \omega_z J_z\right)\exp\left(-i\left(2^{-\tau} \omega_\phi J_\phi\right)\right)\exp\left(-i\frac12 2^{-\tau} \omega_z J_z\right)\biggr)^{2^\tau}\\
+		% 	=& \begin{pmatrix}
+		% 		\cos\left(\frac{\Phi}{2}\right)e^{-iz} & -i\sin\left(\frac{\Phi}{2}\right) e^{i\phi}\\
+		% 		-i\sin\left(\frac{\Phi}{2}\right) e^{-i\phi} & \cos\left(\frac{\Phi}{2}\right)e^{iz}
+		% 	\end{pmatrix}^{2^\tau}\\
+		% 	=& T^{2^\tau}.
+		% \end{align}
+		% % Trotter 8
 		% \begin{align}
@@
 		% \end{align}
-		Here \(z = 2^{-\tau}\frac{\omega_z}{2}\), \(z = 2^{-\tau}\frac{\omega_q}{6}\), \(\phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2}\), and \(\phi = \mathrm{atan}2(\omega_y, \omega_x)\).
+
+		Consequently matrix exponentiation ... raising T to appropriately large n.
+		Choice of n. n is large number, integer, power of 2. Efficiently by recursive squaring.
+		Here \(z = 2^{-\tau}\frac{\omega_z}{2}\), \(q = 2^{-\tau}\frac{\omega_q}{6}\), \(\phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2}\), and \(\phi = \mathrm{atan}2(\omega_y, \omega_x)\).
 		Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(\omega)\).

### 2021-06-28 docs/source/conf.py

@@ -18,6 +18,7 @@ sphinx-apidoc -o source/ ../
 
 To build html from rst:
 make html
+(must run from cmd, not powershell)
 """
 
 import os
@@ -39,7 +40,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.0'
+release = '0.4.1'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-06-28 spinsim/__init__.py

@@ -354,7 +354,7 @@ class Simulator:
         
         * **spin** (:obj:`numpy.ndarray` of :obj:`numpy.float64` (time_index, spatial_direction)) - The expected spin projection (Bloch vector) over time.
     """
-    def __init__(self, get_field:callable, spin_quantum_number:SpinQuantumNumber, device:Device = None, exponentiation_method:ExponentiationMethod = None, use_rotating_frame:bool = True, integration_method:IntegrationMethod = IntegrationMethod.MAGNUS_CF4, trotter_cutoff:int = 32, threads_per_block:int = 64, max_registers:int = 63):
+    def __init__(self, get_field:callable, spin_quantum_number:SpinQuantumNumber, device:Device = None, exponentiation_method:ExponentiationMethod = None, use_rotating_frame:bool = True, integration_method:IntegrationMethod = IntegrationMethod.MAGNUS_CF4, number_of_squares:int = 28, threads_per_block:int = 64, max_registers:int = None):
         """
         .. _Achieved Occupancy: https://docs.nvidia.com/gameworks/content/developertools/desktop/analysis/report/cudaexperiments/kernellevel/achievedoccupancy.htm
 
@@ -385,15 +385,17 @@ class Simulator:
 
         integration_method : :obj:`IntegrationMethod`
             Which integration method to use in the integration. Defaults to :obj:`IntegrationMethod.MAGNUS_CF4`. See :obj:`IntegrationMethod` for more details.
-        trotter_cutoff : :obj:`int`
+        number_of_squares : :obj:`int`
             The number of squares made by the matrix exponentiator, if :obj:`ExponentiationMethod.LIE_TROTTER` is chosen.
         threads_per_block : :obj:`int`
             The size of each thread block (workgroup), in terms of the number of threads (workitems) they each contain, when running on the GPU target devices :obj:`Device.CUDA` (:obj:`Device.ROC`). Defaults to 64. Modifying might be able to increase execution time for different GPU models.
         max_registers : :obj:`int`
[…]

### 2021-06-28 article/article.tex
Article edits (parallelisation)

@@
 		Consequently matrix exponentiation ... raising T to appropriately large n.
-		Choice of n. n is large number, integer, power of 2. Efficiently by recursive squaring.
+		Choice of n. n is large number, integer, power of 2. Efficiently by iterated squaring. Reference. % Revisit!!!
 		Here \(z = 2^{-\tau}\frac{\omega_z}{2}\), \(q = 2^{-\tau}\frac{\omega_q}{6}\), \(\phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2}\), and \(\phi = \mathrm{atan}2(\omega_y, \omega_x)\).
 		Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(\omega)\).
-		In practice the calculations here are done by finding the differences from the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
+		In practice the calculations here are done by finding the differences of the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
+		% Three sentences rather than one
+		% Errors:
+		%	Trotter
+		% 	Evaluating T
+		% 	Iterated squaring
 
-		The approach used for spin one exponentiation means that this particular exponentiator cannot solve arbitrary spin one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the 4-dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z\}\), and the single quadratic operator \(Q\).
-		An exponentiator which can exponentiate an element of the full algebra is included in the package for completeness, though this was not rigorously tested as our lab does not deal with physical systems that would require this functionality to work.
+		% This spin-one exponentiator cannot solve arbitrary spin-one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the 4-dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z, Q\}\), and the single quadratic operator \(Q\).
+		This spin-one exponentiator evolves Hamiltonians spanned by \(J_x, J_y, J_z\) and \(Q\) which is sufficient for three level systems in arbitrary bias fields, but with single-photon coupling.
+		An exponentiator capable of evolving an arbitrary spin-one Hamiltonian, for example with different coupling between the lower and upper pairs of states, or with two-photon coupling, is included in the package.
+		When assessing accuracy for spin-one problems, we have used the single-photon exponentiator.
+		% though this was not rigorously tested as our lab does not deal with physical systems that would require this functionality to work.
 
-		Note that, the methods for both spin half and spin one use analytic forms of exponentials to construct the result, meaning that all calculated time evolution operators are unitary.
-		This guarantees that the results of \emph{spinsim} maintain unitary and conserve probability as required.
+		Note that, the methods for both spin-half and spin-one use analytic forms of matrix exponentials so that \(T\) is unitary by construction; \(\mathcal{U}=T^n\) is then also unitary.
+		Simulations in \emph{spinsim} thus maintain unitarity and so conserve probability even over very large numbers of time steps.
 
 	\subsection{Discretisation and parallelisation}
-		Consider quantising time with
+		Frequently we wish to sample the state at times \(t_k\) spaced more coarsely than the integration time step.
+		Consider discrete times \(t_k = t_0 + \mathrm{D}t\cdot k\) where \(\mathrm{D}t\) is the time step of the time-series, in contrast to \(\mathrm{d}t\), the time step of the integration.
+		% The unitary operator \(\mathcal{U}_k\) 
+		Denoting \(\psi_k = \psi(t_k)\) and \(\mathcal{U}_k = \mathcal{U}(t_{k}, t_{k-1})\), the time-series of states \( \psi_k\) and time-evolution operators \(\mathcal{U}_k\) satisfy
 		\begin{align}
-			t_k &= t_0 + \mathrm{D}t\cdot k,
+			\psi_k &= \mathcal{U}_k\psi_{k-1}.\label{eq:integration_compilation}
 		\end{align}
-		where \(\mathrm{D}t\) is the time step of the time series (in contrast to \(\mathrm{d}t\), a smaller time step for integration).
-		If we define
-		\begin{align}
-			\psi_k = \psi(t_k)\textrm{ and}\\
-			\mathcal{U}_k = \mathcal{U}(t_{k}, t_{k-1}),
-		\end{align}
-		then the time series of states \(\psi_k\) and time evolution operators \(\mathcal{U}_k\) satisfies
-		\begin{align}
-			\psi_k &= \mathcal{U}_k\psi_{k-1}\label{eq:integration_compilation}
-		\end{align}
+		This presents an opportunity for parallelism.
+		While \(\psi_k\) depends on \(\psi_{k-1}\), the operators \(\mathcal{U}_k\) depend only on the field functions, and not on previous states \(\psi_{k'}\) or previous operators \(\mathcal{U}_{k'}\).
+		Hence, the time-evolution operators \(\mathcal{U}_k\) can be calculated in parallel.
+		% It allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
 
-		This presents an opportunity for parallelism.
-		While each of the \(\psi_k\) must be evaluated sequentially, the value of the \(\mathcal{U}_k\) is independent of the value of any \(\psi_{k_0}\), or any other \(\mathcal{U}_{k_0}\).
-		This means that the time evolution operators \(\mathcal{U}_k\) can all be calculated in parallel, and it allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
-
-		In summary, \emph{spinsim} splits the time evolution of the full simulation into time evolution \(\mathcal{U}_k\) within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
+		\emph{spinsim} splits the full simulation into small time intervals \([t_{k - 1}, t_{k}]\), and calculates time-evolution operators \(\mathcal{U}_k\) massively in parallel on a GPU.
+		% within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
 		When all the \(\mathcal{U}_k\) are calculated, the CPU then multiplies the \(\mathcal{U}_k\) together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the \(\psi_k\).
 
+		Within each parallel discretisation, we ...
 		Beyond discretisation for parallelisation, we discretise our time evolution operator into individual integration time steps.

### 2021-06-29 docs/source/conf.py
Changed number of squares to 24 based off new test

@@ -40,7 +40,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.1'
+release = '0.4.2'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-06-29 spinsim/__init__.py

@@ -354,7 +354,7 @@ class Simulator:
         
         * **spin** (:obj:`numpy.ndarray` of :obj:`numpy.float64` (time_index, spatial_direction)) - The expected spin projection (Bloch vector) over time.
     """
-    def __init__(self, get_field:callable, spin_quantum_number:SpinQuantumNumber, device:Device = None, exponentiation_method:ExponentiationMethod = None, use_rotating_frame:bool = True, integration_method:IntegrationMethod = IntegrationMethod.MAGNUS_CF4, number_of_squares:int = 28, threads_per_block:int = 64, max_registers:int = None):
+    def __init__(self, get_field:callable, spin_quantum_number:SpinQuantumNumber, device:Device = None, exponentiation_method:ExponentiationMethod = None, use_rotating_frame:bool = True, integration_method:IntegrationMethod = IntegrationMethod.MAGNUS_CF4, number_of_squares:int = 24, threads_per_block:int = 64, max_registers:int = None):
         """
         .. _Achieved Occupancy: https://docs.nvidia.com/gameworks/content/developertools/desktop/analysis/report/cudaexperiments/kernellevel/achievedoccupancy.htm
 
@@ -414,7 +414,7 @@ class Simulator:
             print("\033[31mspinsim error!!!\nnumba could not jit get_field function into a device function.\033[0m\n")
             raise
 
-    def compile_time_evolver(self, get_field:callable, spin_quantum_number:SpinQuantumNumber, device:Device, use_rotating_frame:bool = True, integration_method:IntegrationMethod = IntegrationMethod.MAGNUS_CF4, exponentiation_method:ExponentiationMethod = None, number_of_squares:int = 28, threads_per_block:int = 64, max_registers:int = None):
+    def compile_time_evolver(self, get_field:callable, spin_quantum_number:SpinQuantumNumber, device:Device, use_rotating_frame:bool = True, integration_method:IntegrationMethod = IntegrationMethod.MAGNUS_CF4, exponentiation_method:ExponentiationMethod = None, number_of_squares:int = 24, threads_per_block:int = 64, max_registers:int = None):
         """
         Compiles the integrator and spin calculation functions of the simulator.
 

### 2021-06-29 article/article.tex
Paper torture (rotating frame)

@@
 \section{Title}
-spinsim: a GPU optimised simulator of spin half and spin one quantum systems
+spinsim: a GPU optimised simulator of spin-half and spin-one quantum systems
 
@@
 	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
-	Optimization and extension to spin one of first version of code.\\
+	Optimization and extension to spin-one of first version of code.\\
 4. School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
@@
 \section{Abstract}
-	The \emph{spinsim} \emph{python} package simulates spin half and spin one quantum mechanical systems following a time dependent Shroedinger equation.
+	The \emph{spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
 	It makes use of \texttt{numba.cuda}\cite{lam_numba_2015}, which is an \emph{LLVM} (Low Level Virtual Machine)\cite{lattner_llvm_2004} compiler for \emph{Nvidia Cuda}\cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
@@
 	\emph{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
-	The initial use case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin half or spin one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
-	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin one systems of nitrogen vacancy centres (NVCs) and BECs.
+	The initial use case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
+	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin-one systems of nitrogen vacancy centres (NVCs) and BECs.
 
@@
 	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
-	The simplest spin system, spin half (ie spin quantum number of \(\frac12\), also referred to as a qubit), is quantised into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
-	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin one quantum system (ie spin quantum number of \(1\), also referred to as a quitrit), which is quantised into three quantum spin levels.
+	The simplest spin system, spin-half (ie spin quantum number of $ \frac12 $, also referred to as a qubit), is quantised into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
+	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (ie spin quantum number of $ 1 $, also referred to as a quitrit), which is quantised into three quantum spin levels.
 
@@
 	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schroedinger equation for quantum sensing spin systems.
-	Spin one systems are sometimes approximated to spin half for a faster execution time, at the cost of modelling all effects of the system.
+	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of modelling all effects of the system.
 	However, these methods are not completely optimised for our use case, and therefore come with some issues.
@@
 	Second, the Schroedinger equation has the geometric property of being norm persevering.
-	In other words, the time evolution operator for a system between two points in time must be unitary.
+	In other words, the time-evolution operator for a system between two points in time must be unitary.
 	As such, numerical solutions to the Schroedinger equation should also preserve this property.
@@
 		\end{align}
-		where the quantum state \(\psi(t) \in \mathbb{C}^N\) is assumed normalised, and the Hamiltonian \(H(t) \in \mathbb{C}^{N \times N}\) is Hermitian.
-		Here \(N\) is the number of levels in the quantum system.
-		Often we are considering systems with spin \(J\) of half or one.
-		Here spin-half is the \(N = 2\) case, and spin-one is \(N = 3\).
-		We set \(\hbar = 1\), so that the Hamiltonian has physical dimension of inverse frequency.
-		% Furthermore, we have chosen for the Hamiltonian \(H(t)\) to have the physical dimension of frequency, rather than the more typical dimension of energy.
-To elaborate, we represent energies \(E\) of the system as their equivalent frequencies \(f\) from the Planck relation
+		where the quantum state $ \psi(t) \in \mathbb{C}^N $ is assumed normalised, and the Hamiltonian $ H(t) \in \mathbb{C}^{N \times N} $ is Hermitian.
+		Here $ N $ is the number of levels in the quantum system.
+		Often we are considering systems with spin $ J $ of half or one.
+		Here spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
+		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of inverse frequency.
+		% Furthermore, we have chosen for the Hamiltonian $ H(t) $ to have the physical dimension of frequency, rather than the more typical dimension of energy.
+To elaborate, we represent energies $ E $ of the system as their equivalent frequencies $ f $ from the Planck relation
 
@@
 
-		% where \(\hbar\) is (reduced) Planck's constant (or equivalently, setting 
-		% \(\hbar = 1\)).
-In addition, rather than being represented by standard coordinates in \(\mathbb{C}^{N \times N}\), in \emph{spinsim} the Hamiltonian \(H(t)\) is instead represented with respect to a choice of basis for the corresponding Lie Algebra, \(\mathfrak{su}(N)\).
-For example, when set to spin half mode, the \emph{spinsim} package solves the time dependent Schroedinger equation of the form
+		% where $ \hbar $ is (reduced) Planck's constant (or equivalently, setting 
+		% $ \hbar = 1 $).
+In addition, rather than being represented by standard coordinates in $ \mathbb{C}^{N \times N} $, in \emph{spinsim} the Hamiltonian $ H(t) $ is instead represented with respect to a choice of basis for the corresponding Lie Algebra, $ \mathfrak{su}(N) $.
+For example, when set to spin-half mode, the \emph{spinsim} package solves the time dependent Schroedinger equation of the form
 
-		Rather than parametrizing the problem in terms of the matrix elements of \(H(t)\), we consider time varying real coefficients in a linear combination of fixed operators,
+		Rather than parametrizing the problem in terms of the matrix elements of $ H(t) $, we consider time varying real coefficients in a linear combination of fixed operators,
 		\begin{align}
@@
 		\end{align}
-		It is well known that a charged spin half system with magnetic moment \(\overrightarrow{\mu}\), and gyromagnetic ratio \(\gamma\), in a magnetic field \(\overrightarrow{B}(t)\), has Hamiltonian
+		It is well known that a charged spin-half system with magnetic moment $ \overrightarrow{\mu} $, and gyromagnetic ratio $ \gamma $, in a magnetic field $ \overrightarrow{B}(t) $, has Hamiltonian
 		\begin{align}
@@
 
-		Here \(J_x, J_y\) and \(J_z\) are spin operators, equal to the Pauli matrices scaled down by \(\frac12\).
+		Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices scaled down by $ \frac12 $.
 		We exclude the identity so that the Hamiltonian is traceless, which we can do because it corresponds to choosing an energy zero point, which is physically meaningless.
 
-		In the spin one case there is no standard basis of operators \(A_j\).
+		In the spin-one case there is no standard basis of operators $ A_j $.
 		Choices include the Gell Mann matrices, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
-		In general, we can choose any basis from the 8-dimensional Lie algebra \(\mathfrak{su}(3)\), which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group \(SU(3)\)) in the spin one system.
-		With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of \(\mathfrak{su}(3)\), consisting of the spin matrices \(J_x, J_y\) and \(J_z\), and a single quadrupole operator \(Q = \frac13\mathrm{diag}(1, -2, 1)\),
+		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
+		With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \frac13\mathrm{diag}(1, -2, 1) $,
 		\begin{align}
@@
 
-		Note that \(Q\) is proportional to \(Q_{zz}\)\cite{hamley_spin-nematic_2012} and \(Q_0\)\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
-		These are the only operators necessary to simulate many spin one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
-		The \emph{spinsim} simulator can also be configured to solve a general spin one system by setting the Hamiltonian to an arbitrary point in \(\mathfrak{su}(3)\), using the full quadrupole basis, which extends the possible Hamiltonian to
+		Note that $ Q $ is proportional to $ Q_{zz} $\cite{hamley_spin-nematic_2012} and $ Q_0 $\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
+		These are the only operators necessary to simulate many spin-one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
+		The \emph{spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $, using the full quadrupole basis, which extends the possible Hamiltonian to
 		\begin{align}
@@
 		Here the added operators are those defined in\cite{di_dipolequadrupole_2010}.
-Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the \(U_1, U_2, V_1\) and \(V_2\) operators.
+Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the $ U_1, U_2, V_1 $ and $ V_2 $ operators.
 		% In general ... Lie algebra ... mathfrak ... admits a basis ... .
@@
 
-		% where \(i^2 = -1\), \(\psi(t) \in \mathbb{C}^2\), and the spin half spin projection operators are given by
+		% where $ i^2 = -1 $, $ \psi(t) \in \mathbb{C}^2 $, and the spin-half spin projection operators are given by
 
@@
 		% Call omega, no implementation detail
-		% The fields \(f\) that represents the time dependent Hamiltonian \(H(t)\), are the collection of energy functions \(f_x(t), f_y(t), f_z(t)\), with time \(t\) and \(f\) with physical dimension of frequency that control the dynamics of the system.
+		% The fields $ f $ that represents the time dependent Hamiltonian $ H(t) $, are the collection of energy functions $ f_x(t), f_y(t), f_z(t) $, with time $ t $ and $ f $ with physical dimension of frequency that control the dynamics of the system.
 The user must define a method that returns a sample of these field functions when a sampling time is input.
-In physical terms, these functions could represent the \(x,y,z\) components of a magnetic field applied to a magnetically spin one BEC or NVC.
+In physical terms, these functions could represent the $ x,y,z $ components of a magnetic field applied to a magnetically spin-one BEC or NVC.
 
-		% Similarly, when \emph{spinsim} is set to spin one mode, it can solve the Schroedinger equation of the form
+		% Similarly, when \emph{spinsim} is set to spin-one mode, it can solve the Schroedinger equation of the form
 
@@
 
-		% where now \(\psi(t) \in \mathbb{C}^3\), and the spin one operators are given by
+		% where now $ \psi(t) \in \mathbb{C}^3 $, and the spin-one operators are given by
 
@@
 
-		% The matrices \(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadrupole operator.
-Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al\cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al\cite{di_dipolequadrupole_2010}.
-		% INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
+		% The matrices $ J_x, J_y, J_z $ are regular spin operators, and $ Q $ is a quadrupole operator.
+Note that $ Q $ is proportional to $ Q_{zz} $ as defined by Hamley et al\cite{hamley_spin-nematic_2012}, and $ Q_0 $ as defined by Di et al\cite{di_dipolequadrupole_2010}.
+		% INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin-one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
 
@@
 		% fast and parallel function from wavefunctions
-		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection \(\left\langle \overrightarrow{J}\right\rangle\)(t) of a system from its state.
+		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection $ \left\langle \overrightarrow{J}\right\rangle $(t) of a system from its state.
 		In an experimental setting, one cannot measure the value of the state itself, and must instead measure observables such as spin projection.
@@
 
-		% Frequently when one calculates the times series of the quantum state \(\psi(t)\), they are also interested in its expected spin projection. It is given by the vector
+		% Frequently when one calculates the times series of the quantum state $ \psi(t) $, they are also interested in its expected spin projection. It is given by the vector
 
@@
 
-		% where \(\cdot^\dagger\) is the adjoint operator.
+		% where $ \cdot^\dagger $ is the adjoint operator.
 The expected spin projection can be interpreted as the average direction that the spin system is oriented in space when many systems of the equivalent state are measured (due to the Heisenberg uncertainty principle, only one component of the exact orientation of a quantum state can be known at any point in time, which is why we need to deal with expected values rather than absolute values).
@@
 	\subsection{Unitary time evolution and the Magnus expansion}
-		It is possible to write \(\psi(t)\) in terms of a unitary transformation \(\mathcal{U}(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\), that is, \(\psi(t) = \mathcal{U}(t, t_0)\psi(t_0)\).
-		It then follows from Equation \eqref{eq:schroedinger} that \(\mathcal{U}(t, t_0)\) also follows a Schr\"{o}dinger equation,
+		It is possible to write $ \psi(t) $ in terms of a unitary transformation $ \mathcal{U}(t, t_0) $ of the state $ \psi(t_0) $, for any time $ t_0 $, that is, $ \psi(t) = \mathcal{U}(t, t_0)\psi(t_0) $.
+		It then follows from Equation \eqref{eq:schroedinger} that $ \mathcal{U}(t, t_0) $ also follows a Schr\"{o}dinger equation,
 		\begin{align}
@@
 
-		Thus, to solve Equation \eqref{eq:schroedinger} for \(\psi(t)\) given a particular \(\psi(t_0)\), one only needs to solve Equation \eqref{eq:unitary_schroedinger} for \(\mathcal{U}(t, t_0)\).
-		% Note that because \(\mathcal{U}(t, t_0)\) is unitary, the calculated value of \(\psi(t)\) using this method will not change in magnitude, conserving probability.
-		Since \(\mathcal{U}(t, t_0)\) is unitary, it can be written as a matrix exponential of a skew-Hermitian (also termed anti-Hermitian) matrix.
+		Thus, to solve Equation \eqref{eq:schroedinger} for $ \psi(t) $ given a particular $ \psi(t_0) $, one only needs to solve Equation \eqref{eq:unitary_schroedinger} for $ \mathcal{U}(t, t_0) $.
+		% Note that because $ \mathcal{U}(t, t_0) $ is unitary, the calculated value of $ \psi(t) $ using this method will not change in magnitude, conserving probability.
+		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a skew-Hermitian (also termed anti-Hermitian) matrix.
 		If the Hamiltonian is constant, then this exponential is % Check if continuity requirement on unitary
@@
 		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series\cite{blanes_magnus_2009}, where
-		For a time varying Hamiltonian, the general solution for \(\mathcal{U}(t, t_0)\) is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
-		The Dyson series\cite{kalev_integral-free_2020} gives an explicit expression for \(\mathcal{U}(t, t_0)\) in terms of multiple time integrals over nested time commutators of \(H(t')\).
+		For a time varying Hamiltonian, the general solution for $ \mathcal{U}(t, t_0) $ is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
+		The Dyson series\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
 		While the Dyson series has been used numerically\cite{kalev_integral-free_2020}, it has only been so recently, in particular because once truncated, it is in general no longer unitary.
@@
 		\end{align}
-		where\([X, Y] = XY - YX\) is the commutator, and, in the case of quantum mechanics, \(A(t') = -iH(t')\).
-Note that, when truncated to first order, the magnus expansion \(\mathcal{U}(t, t_0) = \exp\left(\int_0^t\mathrm{d}t_1\left(-iH(t_1)\right)\right)\) reduces to Equation \eqref{eq:exp_sol_of_constant}, with \(H\) approximated to be constant with its average value.
+		where$ [X, Y] = XY - YX $ is the commutator, and, in the case of quantum mechanics, $ A(t') = -iH(t') $.
+Note that, when truncated to first order, the magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_0^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation \eqref{eq:exp_sol_of_constant}, with $ H $ approximated to be constant with its average value.
 
@@
 		% Throw back to constant
-		% Here each \(\Omega_m(t)\) are integrals over time commutators of \(H(t')\).
-		% \(\Omega_1(t)\), for example, is \(\Omega_1(t) = H_\mathrm{av}t\), where \(H_\mathrm{av}\) is the average value of \(H\) over the interval being integrated over, which is the solution for when \(H\) is constant in time.
-		% The terms \(\Omega_m(t)\) for \(m > 1\) are corrections to this approximation.
-One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for \(\mathcal{U}(t, t_0)\).
+		% Here each $ \Omega_m(t) $ are integrals over time commutators of $ H(t') $.
+		% $ \Omega_1(t) $, for example, is $ \Omega_1(t) = H_\mathrm{av}t $, where $ H_\mathrm{av} $ is the average value of $ H $ over the interval being integrated over, which is the solution for when $ H $ is constant in time.
+		% The terms $ \Omega_m(t) $ for $ m > 1 $ are corrections to this approximation.
+One can truncate the Magnus series before infinity to make a Mangus expansion, which can given an approximation for $ \mathcal{U}(t, t_0) $.
 		% Importantly, any truncation of the Magnus expansion is unitary, meaning that probability will be conserved when used.
 
-		A Magnus series over a time step \(T\) will be guaranteed to converge only if \(\int_{t_0}^{t_0 + T}\mathrm{d}t_1\|H(t_1)\| < \pi\)\cite{blanes_magnus_2009}.
+		A Magnus series over a time step $ T $ will be guaranteed to converge only if $ \int_{t_0}^{t_0 + T}\mathrm{d}t_1\|H(t_1)\| < \pi $\cite{blanes_magnus_2009}.
 Furthermore, each subsequent term in the expansion increases in complexity rapidly.
@@
 		\end{align}
-		Each of the time evolution operators can be approximated by a Magnus expansion.
+		Each of the time-evolution operators can be approximated by a Magnus expansion.
 
@@
 		Many unitary time stepping techniques have been developed based on the Magnus expansion\cite{auer_magnus_2018}.
-		Some of these techniques use Gauss-Legendre quadrature sampling to avoid the integration of commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping\cite{auer_magnus_2018}.
-% Suggest not obvious
+		Some of these techniques use Gauss-Legendre quadrature sampling and Baker–Campbell–Hausdorff formula to respectively avoid the integration and commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping\cite{blanes_fourth-_2006}.
+		% These take advantage of the Baker–Campbell–Hausdorff formula
+
 		In particular, we use the commutator free, fourth order method (CF4) from Reference~\cite{auer_magnus_2018}.
-		Suppose we wish to evaluate a time step of \(\mathcal{U}(t + \mathrm{d}t, t)\) using the CF4 method.
+		Suppose we wish to evaluate a time step of $ \mathcal{U}(t + \mathrm{d}t, t) $ using the CF4 method.
 		The Hamiltonians are sampled at times
@@
 		% \, \quad \qquad
-		The time evolution operator is then approximated by
+		% The time-evolution operator is then approximated by
+		Then
 		\begin{align}
-			\mathcal{U}(t + \mathrm{d}t, t) = \exp(-i\overline{H}_2\mathrm{d}t)\exp(-i\overline{H}_1\mathrm{d}t).\label{eq:cf4_implementation}
+			\mathcal{U}(t + \mathrm{d}t, t) \approx \exp(-i\overline{H}_2\mathrm{d}t)\exp(-i\overline{H}_1\mathrm{d}t)\label{eq:cf4_implementation}
 		\end{align}% \approx? Unitary? End with sentence
+		is used to approximate the time-evolution operator.
 
@@
 		Evaluating matrix exponentials is a core part of the integration algorithm.
-		Rather than exponentiating the Hamiltonian directly as in Equation \eqref{eq:cf4_implementation}, \emph{spinsim} works with the field functions \(\omega_i(t)\).
+		Rather than exponentiating the Hamiltonian directly as in Equation \eqref{eq:cf4_implementation}, \emph{spinsim} works with the field functions $ \omega_i(t) $.
 		% as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
@@
 		% \end{align}
-		% In practice, \(\omega\) is the Lie algebra (spin and quadrature) basis representation of \(\overline{H_1}\) or \(\overline{H_2}\) defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
+		% In practice, $ \omega $ is the Lie algebra (spin and quadrature) basis representation of $ \overline{H_1} $ or $ \overline{H_2} $ defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
 
-		For spin-half, the default exponentiator is in an analytic form in \(\omega_x\).% ... yz, which follows directly from eqref
+		For spin-half, the exponentiator is in an analytic form in $ \omega_x, \omega_y $ and $ \omega_z $.% ... yz, which follows directly from eqref
 		For spin-one, an exponentiator based on the Lie-Trotter product formula\cite{moler_nineteen_2003}
@@
 		is used.
-		Here \(X,Y\in\mathbb{C}^{N\times N}\).
-		An advantage of the Lie-Trotter approach is that \(\exp(-iA_k/n)\) has known analytic forms for the Lie algebra basis elements \(A_k\).
-		Hence the unitary time evolution operator is approximated by \( U = \exp(iHt) \approx T^n \) where \( T= \exp(i \omega_x J_x / n) \exp(i \omega_y J_y / n) \dots \).
-		In fact, commutation relations between the Lie basis operators and Lie half step splitting allow us to write \(T = \exp(-iD_{z,q}/2n)\exp(-i\Phi J_\phi/n)\exp(-iD_{z,q}/2n)\) % Splitting methods
-		% The equality holds for the limit for all \(n\) if the operators commute, like it does for real and complex numbers.
-		% This tells us that we can approximate a matrix exponential of a linear combination of Hermitian operators by scaling down these operators, taking the analytically simple exponentials of each of the operators \(-iJ_x, -iJ_y, -iJ_z\) and \(-iQ\) separately, multiplying each individual result together, and then raising the combination \(T\) to the power of the original reduction.
+		% Here $ X,Y\in\mathbb{C}^{N\times N} $.
+		An advantage of the Lie-Trotter approach is that $ \exp(-iA_k/n) $ has known analytic forms for the Lie algebra basis elements $ A_k $.
+		Hence the unitary time-evolution operator is approximated by $ U = \exp(-iHt) \approx T^n $ where
+		\begin{align}
+			T &= \exp\left(\frac{-i \omega_x J_x}{n}\right) \exp\left(\frac{-i \omega_y J_y}{n}\right) \exp\left(\frac{-i \omega_z J_z}{n}\right) \exp\left(\frac{-i \omega_q Q}{n}\right).
+		\end{align}
+		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method \cite{barthel_optimized_2020} allow us to write 
+		\begin{align}
+			T &= \exp\left(-i\frac12D_{z,q}\right)\exp(-i\Phi J_\phi)\exp\left(-i\frac12D_{z,q}\right).
+		\end{align}
+		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \mathrm{atan}2(\omega_y, \omega_x) $, $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
+		The element-wise analytic form of this is
+		\begin{align}
+			T &= \begin{pmatrix}
+				\left(\cos\left(\frac{\Phi}{2}\right) e^{-iz/2}e^{-iq/6}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{-iz/2}e^{-i\phi} & -\left(\sin\left(\frac{\Phi}{2}\right)e^{iq/6}e^{-i\phi}\right)^2\\
+				\frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{-iz/2}e^{i\phi} & \cos(\Phi)e^{i4q} & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{iz/2}e^{-i\phi}\\
+				-\left(\sin\left(\frac{\Phi}{2}\right)e^{-iq/6}e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{iz/2}e^{i\phi} & \left(\cos\left(\frac{\Phi}{2}\right) e^{iz/2}e^{-iq/6}\right)^2
+			\end{pmatrix}.
+		\end{align}
+		% The equality holds for the limit for all $ n $ if the operators commute, like it does for real and complex numbers.
+		% This tells us that we can approximate a matrix exponential of a linear combination of Hermitian operators by scaling down these operators, taking the analytically simple exponentials of each of the operators $ -iJ_x, -iJ_y, -iJ_z $ and $ -iQ $ separately, multiplying each individual result together, and then raising the combination $ T $ to the power of the original reduction.
 		% 2^{-\tau} -> n
@@
 
-		The exponential \(E(\omega)\) can be approximated as, for large \(2^\tau\),
-		\begin{align}
-			E(\omega) =& \exp\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\right)\\
-			=& \exp\left(2^{-\tau}\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\right)\right)^{2^\tau}\\
-			\approx& \biggl(\exp\left(-i\frac12\left(2^{-\tau} \omega_z J_z + 2^{-\tau}\omega_q Q\right)\right)\nonumber\\
-			&\cdot\exp\left(-i\left(2^{-\tau} \omega_\phi J_\phi\right)\right)\nonumber\\
-			&\cdot\exp\left(-i\frac12\left(2^{-\tau} \omega_z J_z + 2^{-\tau} \omega_q Q\right)\right)\biggr)^{2^\tau}\\
-			=& \begin{pmatrix}
-				\left(\cos\left(\frac{\Phi}{2}\right) e^{-iz}e^{-iq}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{-iz}e^{-i\phi} & -\left(\sin\left(\frac{\Phi}{2}\right)e^{iq}e^{-i\phi}\right)^2\\
-				\frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{-iz}e^{i\phi} & \cos(\Phi)e^{i4q} & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{iz}e^{-i\phi}\\
-				-\left(\sin\left(\frac{\Phi}{2}\right)e^{-iq}e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq}e^{iz}e^{i\phi} & \left(\cos\left(\frac{\Phi}{2}\right) e^{iz}e^{-iq}\right)^2
-			\end{pmatrix}^{2^\tau}\\
-			=& T^{2^\tau}.
-		\end{align}
+		% The exponential $ E(\omega) $ can be approximated as, for large $ 2^\tau $,
+		% \begin{align}
+		% 	E(\omega) =& \exp\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\right)\\
+		% 	=& \exp\left(2^{-\tau}\left(-i\omega_x J_x - i\omega_y J_y - i\omega_z J_z - i\omega_q Q\right)\right)^{2^\tau}\\
+		% 	\approx& \biggl(\exp\left(-i\frac12\left(2^{-\tau} \omega_z J_z + 2^{-\tau}\omega_q Q\right)\right)\nonumber\\
+		% 	&\cdot\exp\left(-i\left(2^{-\tau} \omega_\phi J_\phi\right)\right)\nonumber\\
+		% 	&\cdot\exp\left(-i\frac12\left(2^{-\tau} \omega_z J_z + 2^{-\tau} \omega_q Q\right)\right)\biggr)^{2^\tau}\\
+		% 	=& \begin{pmatrix}
+		% 		\left(\cos\left(\frac{\Phi}{2}\right) e^{-iz/2}e^{-iq/6}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{-iz/2}e^{-i\phi} & -\left(\sin\left(\frac{\Phi}{2}\right)e^{iq/6}e^{-i\phi}\right)^2\\
+		% 		\frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{-iz/2}e^{i\phi} & \cos(\Phi)e^{i4q} & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{iz/2}e^{-i\phi}\\
+		% 		-\left(\sin\left(\frac{\Phi}{2}\right)e^{-iq/6}e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{iz/2}e^{i\phi} & \left(\cos\left(\frac{\Phi}{2}\right) e^{iz/2}e^{-iq/6}\right)^2
+		% 	\end{pmatrix}^{2^\tau}\\
+		% 	=& T^{2^\tau}.
+		% \end{align}
 		% % Trotter half
@@
 
-		Consequently matrix exponentiation ... raising T to appropriately large n.
-		Choice of n. n is large number, integer, power of 2. Efficiently by iterated squaring. Reference. % Revisit!!!
-		Here \(z = 2^{-\tau}\frac{\omega_z}{2}\), \(q = 2^{-\tau}\frac{\omega_q}{6}\), \(\phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2}\), and \(\phi = \mathrm{atan}2(\omega_y, \omega_x)\).
-		Once \(T\) is calculated, it is then recursively squared \(\tau\) times to obtain \(E(\omega)\).
-		In practice the calculations here are done by finding the differences of the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
+		Matrix exponentiation is completed by raising $ T $ to an integer $ n $.
+		To approximate the limit in Equation \eqref{eq:lie_trotter}, $ n $ must be a large number.
+		We choose $ n $ to be of the form $ n = 2^\tau $, as powers of two are particularly effient large numbers to raise matrices to.This can be done just by iterative squaring, which requires a small number of operations.
+		While there are some loose lower bounds for the number of squares $ \tau $ \cite{suzuki_generalized_1976}, using these to choose a value can cause floating point errors from over-squaring.
+		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}.
+		We found that the error minimised after a number of squares of $ \tau = 24 $.
+		Thus, by default, $ n = 2^{24} $.
+
+		% % Choice of n. n is large number, integer, power of 2. Efficiently by iterated squaring. Reference. % Revisit!!!
+		% Here $ z = 2^{-\tau}\frac{\omega_z}{2} $, $ q = 2^{-\tau}\frac{\omega_q}{6} $, $ \phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2} $, and $ \phi = \mathrm{atan}2(\omega_y, \omega_x) $.
+		% Once $ T $ is calculated, it is then recursively squared $ \tau $ times to obtain $ E(\omega) $.
+		% In practice the calculations here are done by finding the differences of the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
 		% Three sentences rather than one
@@
 
-		% This spin-one exponentiator cannot solve arbitrary spin-one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of \(\mathfrak{su}(3)\), rather than just the 4-dimensional subspace spanned by the subalgebra \(\mathfrak{su}(2)\) spanned by \(\{J_x, J_y, J_z, Q\}\), and the single quadratic operator \(Q\).
-		This spin-one exponentiator evolves Hamiltonians spanned by \(J_x, J_y, J_z\) and \(Q\) which is sufficient for three level systems in arbitrary bias fields, but with single-photon coupling.
+		% This spin-one exponentiator cannot solve arbitrary spin-one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of $ \mathfrak{su}(3) $, rather than just the 4-dimensional subspace spanned by the subalgebra $ \mathfrak{su}(2) $ spanned by $ \{J_x, J_y, J_z, Q\} $, and the single quadratic operator $ Q $.
+		This spin-one exponentiator evolves Hamiltonians spanned by $ J_x, J_y, J_z $ and $ Q $ which is sufficient for three level systems in arbitrary bias fields, but with single-photon coupling.
 		An exponentiator capable of evolving an arbitrary spin-one Hamiltonian, for example with different coupling between the lower and upper pairs of states, or with two-photon coupling, is included in the package.
@@
 
-		Note that, the methods for both spin-half and spin-one use analytic forms of matrix exponentials so that \(T\) is unitary by construction; \(\mathcal{U}=T^n\) is then also unitary.
+		Note that, the methods for both spin-half and spin-one use analytic forms of matrix exponentials so that $ T $ is unitary by construction; $ \mathcal{U}=T^n $ is then also unitary.
 		Simulations in \emph{spinsim} thus maintain unitarity and so conserve probability even over very large numbers of time steps.
@@
 	\subsection{Discretisation and parallelisation}
-		Frequently we wish to sample the state at times \(t_k\) spaced more coarsely than the integration time step.
-		Consider discrete times \(t_k = t_0 + \mathrm{D}t\cdot k\) where \(\mathrm{D}t\) is the time step of the time-series, in contrast to \(\mathrm{d}t\), the time step of the integration.
-		% The unitary operator \(\mathcal{U}_k\) 
-		Denoting \(\psi_k = \psi(t_k)\) and \(\mathcal{U}_k = \mathcal{U}(t_{k}, t_{k-1})\), the time-series of states \( \psi_k\) and time-evolution operators \(\mathcal{U}_k\) satisfy
+		Frequently we wish to sample the state at times $ t_k $ spaced more coarsely than the integration time step.
+		Consider discrete times $ t_k = t_0 + \mathrm{D}t\cdot k $ where $ \mathrm{D}t $ is the time step of the time-series, in contrast to $ \mathrm{d}t $, the time step of the integration.
+		% The unitary operator $ \mathcal{U}_k $ 
+		Denoting $ \psi_k = \psi(t_k) $ and $ \mathcal{U}_k = \mathcal{U}(t_{k}, t_{k-1}) $, the time-series of states $  \psi_k $ and time-evolution operators $ \mathcal{U}_k $ satisfy
 		\begin{align}
@@
 		This presents an opportunity for parallelism.
-		While \(\psi_k\) depends on \(\psi_{k-1}\), the operators \(\mathcal{U}_k\) depend only on the field functions, and not on previous states \(\psi_{k'}\) or previous operators \(\mathcal{U}_{k'}\).
-		Hence, the time-evolution operators \(\mathcal{U}_k\) can be calculated in parallel.
+		While $ \psi_k $ depends on $ \psi_{k-1} $, the operators $ \mathcal{U}_k $ depend only on the field functions, and not on previous states $ \psi_{k'} $ or previous operators $ \mathcal{U}_{k'} $.
+		Hence, the time-evolution operators $ \mathcal{U}_k $ can be calculated in parallel.
 		% It allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
 
-		\emph{spinsim} splits the full simulation into small time intervals \([t_{k - 1}, t_{k}]\), and calculates time-evolution operators \(\mathcal{U}_k\) massively in parallel on a GPU.
-		% within small time intervals \([t_{k - 1}, t_{k}]\), which are each calculated massively in parallel on a GPU.
-		When all the \(\mathcal{U}_k\) are calculated, the CPU then multiplies the \(\mathcal{U}_k\) together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the \(\psi_k\).
+		\emph{spinsim} splits the full simulation into small time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals in massive parallel on a GPU.
+% check phrase "massive"
+		% within small time intervals $ [t_{k - 1}, t_{k}] $, which are each calculated massively in parallel on a GPU.
+		When all the $ \mathcal{U}_k $ are calculated, the CPU then multiplies them together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the output samples $ \psi_k $ of the evolving state.
 
-		Within each parallel discretisation, we ...
-		Beyond discretisation for parallelisation, we discretise our time evolution operator into individual integration time steps.
-		So, each of the \(\mathcal{U}_k\) are split into products of time evolution operators between times separated by the integration time step via
+		% Within each parallel discretisation, we ...
+		Beyond discretisation for parallelisation, we discretise our time-evolution operator into individual integration time steps.
+		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time step $ \mathrm{d}t = \mathrm{D}t/L $.
+		% Comment on number of samples for cores or whatever physics is being done
+		% Introduce K if it turns out I use it later
+
+		% \begin{align}
+		% 	\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \mathrm{d}t) \cdots \mathcal{U}(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) \mathcal{U}(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+		% 	\mathcal{U}_k &= u^k_{L-1} \cdots u^k_0,\quad\text{where}\\
+		% 	u^k_{l} &= \mathcal{U}(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+		% \end{align} % Just use middle product
+		% with $ \mathrm{d}t $ being the integration level time step.
+		% Note that the sampling time steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $.
+
+	\subsection{Dynamically rotating frame}
+		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantisation axis $ z $.
+		By transforming into a frame rotating around this axis, a new Hamiltonian $ H^r $ with reduced norm is formed, making the time evolution operators more accurate.
+		In numerical analysis, this is known as preconditioning [\emph{Is this right James?}]; in quantum mechanics, as transforming to the interaction picture.
+		% condition number?
+		% Use rotation matrix
+		If the rotating frame option is selected, the time-evolution operators $ \mathcal{U}_k $ are first calculated within a rotating frame of reference as $ \mathcal{U}^r_k $, which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
+		The rotation speed of the rotating frame is calculated locally for each parallel time step $ \mathcal{U}_k $, and only for rotations around the $ z $ axis.
+		The rotating from field functions $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ are related to the field function $ \omega $ from the user input via
 		\begin{align}
-			\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \mathrm{d}t) \cdots \mathcal{U}(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) \mathcal{U}(t_{k-1} + \mathrm{d}t, t_{k-1})\\
-			\mathcal{U}_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
-			u^k_{L-1} &= \mathcal{U}(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+			\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(\omega_x(t) + i\omega_y(t)),\\
+			\omega^r_z(t) &= \omega_z(t) - \omega_r\quad\text{and}\\
+			\omega^r_q(t) &= \omega_q(t),\quad\text{for spin-one.}
 		\end{align}
 
-		with \(\mathrm{d}t\) being the integration level time step.
-		Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
-
-	\subsection{Rotating frame}
-		If the rotating frame option is selected, the \(\mathcal{U}_k\) are first calculated within a rotating frame of reference as \(\mathcal{U}^r_k\), which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
-		The rotation speed of the rotating frame is calculated locally for each parallel time step \(\mathcal{U}_k\), and only for rotations around the \(z\) axis.
-		The rotating from field functions \(\omega^r_x, \omega^r_y, \omega^r_z,\) and \(\omega^r_q\) are related to the field function \(\omega\) from the user input via
-		\begin{align}
-			\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(\omega_x(t) + i\omega_y(t)),\\
-			\omega^r_z(t) &= \omega_z(t) - \omega_r\textrm{, and}\\
-			\omega^r_q(t) &= \omega_q(t), \textrm{ for spin one.}
-		\end{align}
-
-		Where \(\omega_r = \omega_z(t_k + \frac12\mathrm{D}t)\) is sampled the midpoint value of the fields over the interval \([t_{k - 1}, t_k]\).
-		This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of \(\omega_z(t)\), while leaving the other field components at an equivalent magnitude.
-		The rotation is then applied to obtain the lab frame time evolution operator \(\mathcal{U}_k\) via
+		Where $ \omega_r = \omega_z(t_k + \frac12\mathrm{D}t) $ is sampled the midpoint value of the fields over the interval $ [t_{k - 1}, t_k] $.
+		This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of $ \omega_z(t) $, while leaving the other field components at an equivalent magnitude.
+		The rotation is then applied to obtain the lab frame time-evolution operator $ \mathcal{U}_k $ via
 		\begin{align}
@@
 		\end{align}
-		Specifically, this relationship is \(\mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right)\) for spin half, and \(\mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t))\) for spin one.
+		Specifically, this relationship is $ \mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right) $ for spin-half, and $ \mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t)) $ for spin-one.
 
+		% Put up the top
 		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
-		Note that this is typically done in conjunction with the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of \(\omega^r_x, \omega^r_y, \omega^r_z,\) and \(\omega^r_q\) on an average of many cycles do not have a large contribution to time evolution of the solution and can be ignored.
+		This is typically done in to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ on an average make minor contributions to time evolution, and can be ignored.
 		In some cases, this allows for analytic solutions to the approximate quantum system to be obtained.
 		Note that the RWA is \emph{not} invoked in \emph{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
+		% Can still benefit from the rotating frame ...
+		% Can still key in RWA Hamiltonians
 
@@
 	% 	The integration method used in \emph{spinsim} is the commutator free 4 (CF4) method from Auer et al\cite{auer_magnus_2018}, which based on the Magnus expansion.
-Each of the \(\mathcal{U}_k\) are split into products of time evolution operators between times separated by a smaller time step, that is,
+Each of the $ \mathcal{U}_k $ are split into products of time evolution operators between times separated by a smaller time step, that is,
 
@@
 
-	% 	with \(\mathrm{d}t\) being the integration level time step. Note that the time steps are related to each other by \(\mathrm{D}t = L\mathrm{d}t\), where \(L\in\mathbb{N}\).
+	% 	with $ \mathrm{d}t $ being the integration level time step. Note that the time steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $, where $ L\in\mathbb{N} $.
 
-		% The CF4 method is used to calculate each individual \(u^k_l\).
-Let the fine sample time be given by \(t_I = l\mathrm{d}t + t_k\).
+		% The CF4 method is used to calculate each individual $ u^k_l $.
+Let the fine sample time be given by $ t_I = l\mathrm{d}t + t_k $.
 Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
@@
 	\subsection{Integrator architecture}
-		The integrator in the \emph{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the \(\mathcal{U}_k\).
-		This returns when each of the \(\mathcal{U}_k\) have been evaluated.
+		The integrator in the \emph{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the $ \mathcal{U}_k $.
+		This returns when each of the $ \mathcal{U}_k $ have been evaluated.
 
-		The thread starts by calculating \(t_k\) and, if the rotating frame is being used, \(\omega_r\).
-		The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function \(\omega\) describing how to sample the Hamiltonian.
-		The code then loops over each integration time step \(\mathrm{d}t\) to calculate the integration time evolution operators \(u^k_l\).
+		The thread starts by calculating $ t_k $ and, if the rotating frame is being used, $ \omega_r $.
+		The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function $ \omega $ describing how to sample the Hamiltonian.
+		The code then loops over each integration time step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
 
-		Within the loop, the integrator enters a device function (ie a GPU subroutine, which is inline for speed) to sample \(\omega(t)\), as well as calculate \(e^{-i \omega_r t}\), at the sample times needed for the integration method.
-		After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating \(\overline{H}_1\) and \(\overline{H}_2\) values, and finally taking the matrix exponentiation in a fourth device function.
-		\(u^k_l\) is premultiplied to \(\mathcal{U}^r_k\) (which is initialised to \(1\)), and the loop continues.
+		Within the loop, the integrator enters a device function (ie a GPU subroutine, which is inline for speed) to sample $ \omega(t) $, as well as calculate $ e^{-i \omega_r t} $, at the sample times needed for the integration method.
+		After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating $ \overline{H}_1 $ and $ \overline{H}_2 $ values, and finally taking the matrix exponentiation in a fourth device function.
+		$ u^k_l $ is premultiplied to $ \mathcal{U}^r_k $ (which is initialised to $ 1 $), and the loop continues.
 
-		When the loop has finished, if the rotating frame is being used, \(\mathcal{U}^r_k\) is transformed to \(\mathcal{U}_k\) as in Equation \eqref{eq:integration_compilation}, and this is returned.
-		Once all threads have executed, the state \(\psi_k\) is calculated in a (CPU) \texttt{numba.jit()}ed function from the \(\mathcal{U}_k\) and an initial condition \(\psi_{\mathrm{init}}\).
+		When the loop has finished, if the rotating frame is being used, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation \eqref{eq:integration_compilation}, and this is returned.
+		Once all threads have executed, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} $.
 
@@
 		This structure has multiple advantages.
-		First, the field function \(\omega\) is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
-		This allows users to define \(\omega\) in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
+		First, the field function $ \omega $ is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
+		This allows users to define $ \omega $ in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
 		Compiling the simulator also allows the user to set meta parameters, and choose the features they want to use, in a way that does not require experience with the \texttt{numba.cuda} library.
@@
 		This functionality is interfaced through an object of class \texttt{spinsim.Simulator}.
-		The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time evolution operator, and expected spin projection.
+		The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time-evolution operator, and expected spin projection.
 		Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object.
@@
 		\emph{spinsim} is designed so that a single simulator compilation can be used to execute many simulations, sweeping through a particular parameter, while not needing to be recompiled.
-		This is done through the \texttt{sweep\_parameter} argument to the user provided field function \(\omega\).
+		This is done through the \texttt{sweep\_parameter} argument to the user provided field function $ \omega $.
 		The user uses \texttt{sweep\_parameter} to determine a variable parameter for the Hamiltonian.
@@
 		For a use case example, one might want to simulate many spin systems at different locations in a magnetic field gradient in an MRI experiment.
-		To do this they could choose to set \(\omega_z =\texttt{sweep\_parameter}\), which would vary the magnetic field bias in the \(\omega\) direction for each experiment.
+		To do this they could choose to set $ \omega_z =\texttt{sweep\_parameter} $, which would vary the magnetic field bias in the $ \omega $ direction for each experiment.
 		This feature is demonstrated with examples in the documentation.
@@
 
-		where \(j \in \{\frac12, 1\}\) is the spin quantum number of the system.
+		where $ j \in \{\frac12, 1\} $ is the spin quantum number of the system.
 
@@
 		These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
-		In all of these comparisons, errors above \(10^{-3}\) were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
-		Additionally, errors bellow \(10^{-11}\) were excluded, as this was the order of magnitude of the errors in the reference simulation.
+		In all of these comparisons, errors above $ 10^{-3} $ were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
+		Additionally, errors bellow $ 10^{-11} $ were excluded, as this was the order of magnitude of the errors in the reference simulation.
 
@@
 		We benchmarked these methods both while using and not using the rotating frame option.
-		This was done separately for spin one and spin half systems, to ensure they both yield accurate results.
+		This was done separately for spin-one and spin-half systems, to ensure they both yield accurate results.
 
@@
 				\includegraphics[scale=0.475]{benchmark_spin_one_step_error.pdf}
-				% \caption{Accuracy of the spin one options of \emph{spinsim}.}
+				% \caption{Accuracy of the spin-one options of \emph{spinsim}.}
 				\caption{}
@@
 				\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.pdf}
-				% \caption{Speed vs accuracy of the spin one options of \emph{spinsim}.}
+				% \caption{Speed vs accuracy of the spin-one options of \emph{spinsim}.}
 				\caption{}
@@
 			\end{subfigure}\
-			\caption{Speed and accuracy of the spin one options of \emph{spinsim}.
+			\caption{Speed and accuracy of the spin-one options of \emph{spinsim}.
 			A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
@@
 				\includegraphics[scale=0.475]{benchmark_spin_half_step_error.pdf}
-				% \caption{Accuracy of the spin half options of \emph{spinsim}.}
+				% \caption{Accuracy of the spin-half options of \emph{spinsim}.}
 				\caption{}
@@
 				\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.pdf}
-				% \caption{Speed vs accuracy of the spin half options of \emph{spinsim}.}
+				% \caption{Speed vs accuracy of the spin-half options of \emph{spinsim}.}
 				\caption{}
@@
 			\end{subfigure}
-			\caption{Speed and accuracy of the spin half options of \emph{spinsim}.
+			\caption{Speed and accuracy of the spin-half options of \emph{spinsim}.
 			A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
@@
 		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), compared highly procedural devices (being CPUs).
-		Speed benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin one sensing experiments on different devices.
+		Speed benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin-one sensing experiments on different devices.
 		This is shown in Figure \ref{fig:benchmark_device_aggregate}.
@@
 			\includegraphics[scale=0.7]{benchmark_device_aggregate.pdf}
-			\caption{Evaluation speed of a simulation of a typical spin one sensing experiment on both CPUs and GPUs.
+			\caption{Evaluation speed of a simulation of a typical spin-one sensing experiment on both CPUs and GPUs.
 			Integration time step is set to 100ns.
@@
 	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
-	Optimization and extension to spin one of first version of code.\\
+	Optimization and extension to spin-one of first version of code.\\
 4. Russell P. Anderson\\
@@
 	\subsection{Use potential and limitations}
-		\emph{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin half or spin one systems.
-		This is immediately relevant to developing new quantum sensing protocols with spin half and spin one systems.
+		\emph{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin-half or spin-one systems.
+		This is immediately relevant to developing new quantum sensing protocols with spin-half and spin-one systems.
 		This package is being used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab.
@@
 		Rubidium BECs can potentially be made sensitive enough to these tiny magnetic fields that they can be measured by them.
-		\emph{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
+		\emph{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin-one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
 		The package is also now being used to simulate other BEC magnetometry experiments by the lab group.
@@
 		Another example of spin based magnetic field sensing is the use of Nitrogen Vacancy Centres (NVCs).
-		These are spin one structures found in diamond doped with Nitrogen atoms.
-		This leaves a vacancy in a position adjacent to the Nitrogen atom, which pairs of electrons occupy to obtain the spin one properties.
+		These are spin-one structures found in diamond doped with Nitrogen atoms.
+		This leaves a vacancy in a position adjacent to the Nitrogen atom, which pairs of electrons occupy to obtain the spin-one properties.
 		Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
@@
 		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14)\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
-		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin one nuclei\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin-one nuclei\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
 		This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
 		Another possible use case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
-		MRI uses measures the response of spins of an array of spin half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
+		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
 		While this package offers some advantages over state of the art simulators in the field\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.

### 2021-06-30 article/article.tex
Paper torture (Architecture)

@@
 		% fast and parallel function from wavefunctions
-		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection $ \left\langle \overrightarrow{J}\right\rangle $(t) of a system from its state.
+		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection $ \left\langle \overrightarrow{J}\right\rangle (t) $ of a system from its state.
 		In an experimental setting, one cannot measure the value of the state itself, and must instead measure observables such as spin projection.
@@
 		\end{align}
-		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \mathrm{atan}2(\omega_y, \omega_x) $, $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
+		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \mathrm{arctan}2(\omega_y, \omega_x) $ (where $ \mathrm{arctan}2(y, x) $ is the two argument arctangent\cite{organick_fortran_1966}), $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
 		The element-wise analytic form of this is
@@
 				-\left(\sin\left(\frac{\Phi}{2}\right)e^{-iq/6}e^{i\phi}\right)^2 & \frac{-i}{\sqrt{2}} \sin(\Phi)e^{iq/6}e^{iz/2}e^{i\phi} & \left(\cos\left(\frac{\Phi}{2}\right) e^{iz/2}e^{-iq/6}\right)^2
-			\end{pmatrix}.
+			\end{pmatrix}.\label{eq:lie_trotter_4}
 		\end{align}
@@
 
+		In addition to those introduced by the Lie-Trotter approximation, we find errors when manipulating matrices close to the identity.
+		This is a consequence of the diagonals of the matrices being close to 1, with the limited precision of floating point numbers being unable to represent these differences accurately.
+		Errors appear in two forms.
+		One is that iterative squaring of matrices close to the identity produces floating point cancellation errors.
+		This can be fixed by only working with the difference of the matrices from the identity when squaring.
+		That is, if $ A = I + a $, then instead of calculating the square $ S = I + s = A^2 $, we find $ s = (a + 2I)a $.
+		The other is that if we use this method, we must calculate $ T - I $ accurately, rather than $ T $, which cannot be done by simply subtracting the identity from Equation \eqref{eq:lie_trotter_4}.
+		This can be fixed by replacing the exponentials and trigonometric functions along the diagonal with specialised functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose\cite{hewlett-packard_hp_1994}.
+		The identity is added to the result of the iterative residual squaring and the full exponential is returned.
+
 		% % Choice of n. n is large number, integer, power of 2. Efficiently by iterated squaring. Reference. % Revisit!!!
@@
 		% 	Iterated squaring
-
 		% This spin-one exponentiator cannot solve arbitrary spin-one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of $ \mathfrak{su}(3) $, rather than just the 4-dimensional subspace spanned by the subalgebra $ \mathfrak{su}(2) $ spanned by $ \{J_x, J_y, J_z, Q\} $, and the single quadratic operator $ Q $.
@@
 		When assessing accuracy for spin-one problems, we have used the single-photon exponentiator.
-		% though this was not rigorously tested as our lab does not deal with physical systems that would require this functionality to work.
 
@@
 		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time step $ \mathrm{d}t = \mathrm{D}t/L $.
+
+		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error} .
+		To choose an appropriate value of $ \mathrm{D}t $, users must consider two factors.
+		For the most benefit out of GPU parallelisation, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{spinsim}.
+		Users should also make sure $ \mathrm{D}t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \left\langle \overrightarrow{J}\right\rangle_k $ to be used in their further analysis.
 		% Comment on number of samples for cores or whatever physics is being done
@@
 		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantisation axis $ z $.
-		By transforming into a frame rotating around this axis, a new Hamiltonian $ H^r $ with reduced norm is formed, making the time evolution operators more accurate.
-		In numerical analysis, this is known as preconditioning [\emph{Is this right James?}]; in quantum mechanics, as transforming to the interaction picture.
-		% condition number?
-		% Use rotation matrix
-		If the rotating frame option is selected, the time-evolution operators $ \mathcal{U}_k $ are first calculated within a rotating frame of reference as $ \mathcal{U}^r_k $, which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
-		The rotation speed of the rotating frame is calculated locally for each parallel time step $ \mathcal{U}_k $, and only for rotations around the $ z $ axis.
-		The rotating from field functions $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ are related to the field function $ \omega $ from the user input via
+		Transforming from the lab (standard) frame of reference into one rotating around this axis by rotation operator $ R_{\omega_r}(t) = \exp(i\omega_r J_z t) $, the resulting system follows a new Hamiltonian
 		\begin{align}
-			\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(\omega_x(t) + i\omega_y(t)),\\
-			\omega^r_z(t) &= \omega_z(t) - \omega_r\quad\text{and}\\
-			\omega^r_q(t) &= \omega_q(t),\quad\text{for spin-one.}
+			H_r(t) &= R_{\omega_r}(t) (\omega_x(t) J_x + \omega_y(t) J_y) R_{\omega_r}(-t) + (\omega_z(t) - \omega_r)J_z +\omega_q(t) Q
 		\end{align}
+		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
+		This almost always done to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ H_r(t) $ on average make minor contributions to time evolution, and can be ignored.
+		In some cases, this allows one to obtain analytic, but approximate, solutions to the quantum system.
+		Note that the RWA is never invoked by \emph{spinsim}, as doing this would reduce the accuracy of simulation results; although a problem already expressed in a rotating frame can of course be input by the user if desired.
+		In fact, because of the speed increase of \emph{spinsim} compared to alternatives, users who would have previously simulated their systems using the RWA due to speed concerns may now wish to use \emph{spinsim} to simulate beyond RWA effects that would previously have been missed.
 
-		Where $ \omega_r = \omega_z(t_k + \frac12\mathrm{D}t) $ is sampled the midpoint value of the fields over the interval $ [t_{k - 1}, t_k] $.
-		This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of $ \omega_z(t) $, while leaving the other field components at an equivalent magnitude.
-		The rotation is then applied to obtain the lab frame time-evolution operator $ \mathcal{U}_k $ via
+		Instead we take advantage of rotating frames to increase numerical accuracy.
+		By our assumption that $ |\omega_r| \approx |\omega_z(t)| \ge |\omega_x(t)|, |\omega_y(t)|, |\omega_q(t)| $ for the duration we have entered the frame, then the rotating frame Hamiltonian will have a smaller norm than the lab frame Hamiltonian.
+		This will yield a more accurate results when making discrete time steps by the integrator, as the distances stepped are smaller.
+
+		A different rotating frame is entered by \emph{spinsim} for each time interval $ [t_{k - 1}, t_k] $.
+		This dynamic application allows for the rotating frame to be used even during sweeps of the dominant term $ \omega_z(t) $ where it is only approximately constant locally.
+		Here we choose $ \omega_r = \omega_z(t_{k - 1} + \mathrm{D}t/2) $ as an approximate average value of $ \omega_z(t) $ over the duration.
+		The calculated time-evolution operator $ \mathcal{U}_k^r $ is then transformed back to the lab frame as
 		\begin{align}
-			\mathcal{U}_k &= \exp(-i \omega_r J_z \mathrm{D}t) \mathcal{U}^r_k.
+			\mathcal{U}_k &= R_{\omega_r}(-\mathrm{D}t)\mathcal{U}_k^r.\label{eq:exit_rotating_frame}
 		\end{align}
-		Specifically, this relationship is $ \mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right) $ for spin-half, and $ \mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t)) $ for spin-one.
+		This functionality can be disabled for systems that do not fit these criteria.
 
-		% Put up the top
-		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
-		This is typically done in to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ on an average make minor contributions to time evolution, and can be ignored.
-		In some cases, this allows for analytic solutions to the approximate quantum system to be obtained.
-		Note that the RWA is \emph{not} invoked in \emph{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
-		% Can still benefit from the rotating frame ...
-		% Can still key in RWA Hamiltonians
+		% % By transforming into a frame rotating around this axis, a new Hamiltonian $ H^r $ with reduced norm is formed, making the time evolution operators more accurate.
+		% % In numerical analysis, this is known as preconditioning [\emph{Is this right James?}]; in quantum mechanics, as transforming to the interaction picture.
+		% % condition number?
+		% % Use rotation matrix
+		% If the rotating frame option is selected, the time-evolution operators $ \mathcal{U}_k $ are first calculated within a rotating frame of reference as $ \mathcal{U}^r_k $, which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
+		% The rotation speed of the rotating frame is calculated locally for each parallel time step $ \mathcal{U}_k $, and only for rotations around the $ z $ axis.
+		% The rotating from field functions $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ are related to the field function $ \omega $ from the user input via
+		% \begin{align}
+		% 	\omega^r_x(t) + i\omega^r_y(t) &= e^{-i \omega_r t}(\omega_x(t) + i\omega_y(t)),\\
+		% 	\omega^r_z(t) &= \omega_z(t) - \omega_r\quad\text{and}\\
+		% 	\omega^r_q(t) &= \omega_q(t),\quad\text{for spin-one.}
+		% \end{align}
+
+		% Where $ \omega_r = \omega_z(t_k + \frac12\mathrm{D}t) $ is sampled the midpoint value of the fields over the interval $ [t_{k - 1}, t_k] $.
+		% This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of $ \omega_z(t) $, while leaving the other field components at an equivalent magnitude.
+		% The rotation is then applied to obtain the lab frame time-evolution operator $ \mathcal{U}_k $ via
+		% \begin{align}
+		% 	\mathcal{U}_k &= \exp(-i \omega_r J_z \mathrm{D}t) \mathcal{U}^r_k.
+		% \end{align}
+		% Specifically, this relationship is $ \mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right) $ for spin-half, and $ \mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t)) $ for spin-one.
+
+		% % Put up the top
+		% It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
+		% This is typically done in to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ on an average make minor contributions to time evolution, and can be ignored.
+		% In some cases, this allows for analytic solutions to the approximate quantum system to be obtained.
+		% Note that the RWA is \emph{not} invoked in \emph{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
+		% % Can still benefit from the rotating frame ...
+		% % Can still key in RWA Hamiltonians
 
@@
 	\subsection{Integrator architecture}
+		\begin{figure}[h!]
+			\centering
+			\includegraphics[scale=0.475]{architecture.pdf}
+			\caption{The architecture of \emph{spinsim}}
+			\label{fig:architecture}
+		\end{figure}
+		A visual summary of the architecture of \emph{spinsim} is shown in Figure \ref{fig:architecture}.
 		The integrator in the \emph{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the $ \mathcal{U}_k $.
-		This returns when each of the $ \mathcal{U}_k $ have been evaluated.
+		Alternatively, the kernel can be run in parallel on a multicore CPU if a compatible GPU is not available.
+		The kernel returns when each of the $ \mathcal{U}_k $ have been evaluated.
 
-		The thread starts by calculating $ t_k $ and, if the rotating frame is being used, $ \omega_r $.
-		The latter is done by sampling a (\texttt{numba.cuda.jit()}ed version of a) user provided \emph{python} function $ \omega $ describing how to sample the Hamiltonian.
-		The code then loops over each integration time step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
+		Each thread begins with initialisation of variables, which includes moving into the rotating frame.
+		It then starts a loop to find each of the time-stepping operators $ u^k_l $.
+		% The code then loops over each integration time step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
+		Within the loop, the integrator enters a device function (ie a GPU subroutine. All device functions are inline for speed) to sample the user-provided field functions $ \omega_i(t) $.
+		After this, it makes applies the rotating frame transformation $R_{\omega_r}(t)$, before calculating the Gauss-Legendre weightings $ \overline{H}_1 $ and $ \overline{H}_2 $ in this frame.
+Next, the matrix exponentials are taken within another device function.
+		Finally, $ u^k_l $ is premultiplied to $ \mathcal{U}^r_k $ (which is initialised to the identity), and the loop continues.
 
-		Within the loop, the integrator enters a device function (ie a GPU subroutine, which is inline for speed) to sample $ \omega(t) $, as well as calculate $ e^{-i \omega_r t} $, at the sample times needed for the integration method.
-		After this, it enters a second device function, which makes a rotating wave transformation as needed in a third device function, before calculating $ \overline{H}_1 $ and $ \overline{H}_2 $ values, and finally taking the matrix exponentiation in a fourth device function.
-		$ u^k_l $ is premultiplied to $ \mathcal{U}^r_k $ (which is initialised to $ 1 $), and the loop continues.
-
-		When the loop has finished, if the rotating frame is being used, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation \eqref{eq:integration_compilation}, and this is returned.
-		Once all threads have executed, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} $.
+		When the loop has finished, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation \eqref{eq:exit_rotating_frame}, and this is returned.
+		Once all threads have executed, using Equation \eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} $.
 
@@
 		\emph{spinsim} is designed so that a single simulator compilation can be used to execute many simulations, sweeping through a particular parameter, while not needing to be recompiled.
-		This is done through the \texttt{sweep\_parameter} argument to the user provided field function $ \omega $.
+		This is done through the \texttt{sweep\_parameter} argument to the user-provided field function $ \omega $.
 		The user uses \texttt{sweep\_parameter} to determine a variable parameter for the Hamiltonian.

### 2021-07-01 article/article.tex
Completed first round of paper torture

@@
 	The \emph{spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
-	It makes use of \texttt{numba.cuda}\cite{lam_numba_2015}, which is an \emph{LLVM} (Low Level Virtual Machine)\cite{lattner_llvm_2004} compiler for \emph{Nvidia Cuda}\cite{nickolls_scalable_2008} compatible systems using GPU parallelisation.
+	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelisation. 
 	Along with other optimisations, this allows for speed improvements of up to four orders of magnitude while keeping staying just as accurate.
 	\emph{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
-	The initial use case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
+	The initial use-case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
 	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin-one systems of nitrogen vacancy centres (NVCs) and BECs.
@@
 	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of modelling all effects of the system.
-	However, these methods are not completely optimised for our use case, and therefore come with some issues.
+	However, these methods are not completely optimised for our use-case, and therefore come with some issues.
 
@@
 	\subsection{Quantum mechanics background}
-		\emph{spinsim} solves the time-dependent Schr\"{o}dinger equation
+		The \emph{spinsim} package solves the time-dependent Schr\"{o}dinger equation
 		\begin{align}
@@
 		Often we are considering systems with spin $ J $ of half or one.
-		Here spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
-		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of inverse frequency.
+		Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
+		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of angular frequency.
 		% Furthermore, we have chosen for the Hamiltonian $ H(t) $ to have the physical dimension of frequency, rather than the more typical dimension of energy.
@@
 		\begin{align}
-			H(t) &= \sum_{j = 1}^{N^2 - 1} \omega_j(t) O_j.
+			H(t) &= \sum_{j = 1}^{N^2 - 1} \omega_j(t) \mathcal{A}_j.
 		\end{align}
@@
 			H(t) &= -\overrightarrow{B}(t)\cdot \overrightarrow{\mu}\\
-			&= -\gamma \overrightarrow{B}(t)\cdot \overrightarrow{J}\\
+			% &= -\gamma \overrightarrow{B}(t)\cdot \overrightarrow{J}\\
 			&= -\gamma \left(B_x(t) J_x + B_y(t) J_y + B_z(t) J_z\right)\\
-			&= \left(-\gamma B_x(t) J_x\right) + \left(-\gamma B_y(t) J_y\right) + \left(-\gamma B_z(t) J_z\right)\\
+			% &= \left(-\gamma B_x(t) J_x\right) + \left(-\gamma B_y(t) J_y\right) + \left(-\gamma B_z(t) J_z\right)\\
 			&= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z.
@@
 
-		Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices scaled down by $ \frac12 $.
-		We exclude the identity so that the Hamiltonian is traceless, which we can do because it corresponds to choosing an energy zero point, which is physically meaningless.
+		Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices halved.
+		We exclude the identity so that the Hamiltonian is traceless, which we can do because it corresponds to choosing a physically meaningless energy zero point.
 
-		In the spin-one case there is no standard basis of operators $ A_j $.
-		Choices include the Gell Mann matrices, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
+		In the spin-one case there is no standard basis of operators $ \mathcal{A}_j $.
+		Choices include the Gell-Mann matrices\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
 		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
-		With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \frac13\mathrm{diag}(1, -2, 1) $,
+		With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,
 		\begin{align}
@@
 		These are the only operators necessary to simulate many spin-one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
-		The \emph{spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $, using the full quadrupole basis, which extends the possible Hamiltonian to
+		The \emph{spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
 		\begin{align}
-			H(t) &= \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q\nonumber\\
+			H(t) =& \omega_x(t) J_x + \omega_y(t) J_y + \omega_z(t) J_z + \omega_q(t) Q\nonumber\\
 			&+ \omega_{u1}(t) U_1 + \omega_{u2}(t) U_2 + \omega_{v1}(t) V_1 + \omega_{v2}(t) V_2.
 		\end{align}
-		Here the added operators are those defined in\cite{di_dipolequadrupole_2010}.
+		Here the additional operators are those defined in\cite{di_dipolequadrupole_2010}.
 Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the $ U_1, U_2, V_1 $ and $ V_2 $ operators.
@@
 		% fast and parallel function from wavefunctions
-		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection $ \left\langle \overrightarrow{J}\right\rangle (t) $ of a system from its state.
+		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection $ \langle \overrightarrow{J}\rangle (t) $ of a system from its state.
 		In an experimental setting, one cannot measure the value of the state itself, and must instead measure observables such as spin projection.
 		If this is done for an ensemble of systems, the average spin projection over all systems will converge to the expected value as calculated here.
+		As an alternative to solving the Schr\"odinger equation, if one is only interested in the dynamics of the expected spin projection, one can instead solve for $ \langle \overrightarrow{J}\rangle (t) $ directly using the Bloch equations\cite{bloch_nuclear_1946}.
+		These are three coupled real equations as compared to three coupled complex equations for the spin-one Schr\"odinger equation.
+		However, the Bloch equations cannot be used to compute $ \psi(t) $, and can only fully model spin-half systems (and spin-one systems approximated to spin-half).
+		Thus, with \emph{spinsim} we choose to solve the full Schr\"odinger equation instead.
 
@@
 		Furthermore, each subsequent term in the expansion increases in complexity rapidly.
-For these reasons, the Magnus expansion is used as a time stepping method rather than a single step to solve the complete system.
+		For these reasons, the Magnus expansion is generally used as a time stepping method rather than a single step to solve the complete system.
+		Designing a Magnus based solver is a trade-off between the number of terms used in each expansion, and the number of time steps used.
 		Time stepping can be made from the fact that time evolution operators can be split into a product via
@@
 
-	\subsection{Exponentiator}
+	\subsection{Lie-Trotter based Exponentiator}
 		Evaluating matrix exponentials is a core part of the integration algorithm.
-		Rather than exponentiating the Hamiltonian directly as in Equation \eqref{eq:cf4_implementation}, \emph{spinsim} works with the field functions $ \omega_i(t) $.
+		Rather than exponentiating the Hamiltonian directly as in Equation \eqref{eq:cf4_implementation}, \emph{spinsim} works with the field functions $ \omega_j(t) $.
 		% as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
@@
 
-		For spin-half, the exponentiator is in an analytic form in $ \omega_x, \omega_y $ and $ \omega_z $.% ... yz, which follows directly from eqref
+		For spin-half, the exponentiator is in an analytic form in $ \omega_x, \omega_y $ and $ \omega_z $. % ... yz, which follows directly from eqref
 		For spin-one, an exponentiator based on the Lie-Trotter product formula\cite{moler_nineteen_2003}
@@
 		To approximate the limit in Equation \eqref{eq:lie_trotter}, $ n $ must be a large number.
-		We choose $ n $ to be of the form $ n = 2^\tau $, as powers of two are particularly effient large numbers to raise matrices to.This can be done just by iterative squaring, which requires a small number of operations.
+		We choose $ n $ to be of the form $ n = 2^\tau $, as powers of two are particularly effient large numbers to raise matrices to.
+		This can be done just by iterative squaring, which requires a small number of operations.
 		While there are some loose lower bounds for the number of squares $ \tau $ \cite{suzuki_generalized_1976}, using these to choose a value can cause floating point errors from over-squaring.
-		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}.
+		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}\cite{virtanen_scipy_2020}.
 		We found that the error minimised after a number of squares of $ \tau = 24 $.
@@
 
-		\emph{spinsim} splits the full simulation into small time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals in massive parallel on a GPU.
+		\emph{spinsim} splits the full simulation into small time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals massively in parallel on a GPU.
 % check phrase "massive"
@@
 
-		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error} .
-		To choose an appropriate value of $ \mathrm{D}t $, users must consider two factors.
+		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error}.
+		To choose an appropriate value of $ \mathrm{D}t $, users must consider three factors.
 		For the most benefit out of GPU parallelisation, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{spinsim}.
-		Users should also make sure $ \mathrm{D}t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \left\langle \overrightarrow{J}\right\rangle_k $ to be used in their further analysis.
+		Users should also make sure that $ \mathrm{D}t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \langle \overrightarrow{J}\rangle_k $ to be used in their further analysis.
+		Finally, if $ K $ is too large, then the GPU will run out of memory on compilation, which will raise an exception.
+% (which we found to be $ K = 3\cdot 10^8 $ sample points for the 10GiB \emph{GeForce RTX 3080}).
+		We found that a the 10GiB \emph{GeForce RTX 3080} could run at full memory capacity with 300 million sample points for spin-one mode and 600 million sample points for spin-half.
 		% Comment on number of samples for cores or whatever physics is being done
@@
 		By our assumption that $ |\omega_r| \approx |\omega_z(t)| \ge |\omega_x(t)|, |\omega_y(t)|, |\omega_q(t)| $ for the duration we have entered the frame, then the rotating frame Hamiltonian will have a smaller norm than the lab frame Hamiltonian.
-		This will yield a more accurate results when making discrete time steps by the integrator, as the distances stepped are smaller.
+		This will yield more accurate results when making discrete time steps by the integrator, as the distances stepped are smaller.
 
@@
 			\includegraphics[scale=0.475]{architecture.pdf}
-			\caption{The architecture of \emph{spinsim}}
+			\caption{The structure of \emph{spinsim}}
 			\label{fig:architecture}
 		\end{figure}
-		A visual summary of the architecture of \emph{spinsim} is shown in Figure \ref{fig:architecture}.
-		The integrator in the \emph{spinsim} package calls a \texttt{numba.cuda.jit()}ed kernel to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the $ \mathcal{U}_k $.
+		A visual summary of the structure of \emph{spinsim} is shown in Figure \ref{fig:architecture}.
+		The integrator in the \emph{spinsim} package calls a kernel (multithreaded function) to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the $ \mathcal{U}_k $.
 		Alternatively, the kernel can be run in parallel on a multicore CPU if a compatible GPU is not available.
@@
 		% The code then loops over each integration time step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
-		Within the loop, the integrator enters a device function (ie a GPU subroutine. All device functions are inline for speed) to sample the user-provided field functions $ \omega_i(t) $.
-		After this, it makes applies the rotating frame transformation $R_{\omega_r}(t)$, before calculating the Gauss-Legendre weightings $ \overline{H}_1 $ and $ \overline{H}_2 $ in this frame.
+		Within the loop, the integrator enters a device function to sample the user-provided field functions $ \omega_j(t) $ (device functions are GPU subroutines, and in practice all device functions here are compiled inline for speed).
+		After this, it applies the rotating frame transformation $R_{\omega_r}(t)$, before calculating the Gauss-Legendre weightings $ \overline{H}_1 $ and $ \overline{H}_2 $.
 Next, the matrix exponentials are taken within another device function.
@@
 		When the loop has finished, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation \eqref{eq:exit_rotating_frame}, and this is returned.
-		Once all threads have executed, using Equation \eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} $.
+		Once all threads have executed, using Equation \eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} = \psi(t_0) $.
 
 	\subsection{Compilation of integrator}
-		The \emph{spinsim} integrator is constructed and compiled just in time, using \texttt{numba.cuda.jit()}.
-		The particular device functions used are not predetermined, but are instead chosen based on user input to decide a closure.
-		This structure has multiple advantages.
-		First, the field function $ \omega $ is provided by the user as a plain python function (that must be \texttt{numba.cuda.jit()} compatible).
-		This allows users to define $ \omega $ in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
-		Compiling the simulator also allows the user to set meta parameters, and choose the features they want to use, in a way that does not require experience with the \texttt{numba.cuda} library.
-		This was especially useful for running benchmarks comparing old integration methods to the new ones, like CF4.
-		The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for different GPUs.
-		Third, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU, if the user so chooses.
+		The \emph{spinsim} integrator is constructed and compiled just in time, using the \emph{Numba}\cite{lam_numba_2015} python package.
+		This is achieved via the \texttt{numba.cuda.jit()} decorator, which compiles python functions into \emph{Nvidia Cuda}\cite{nickolls_scalable_2008} kernels using an LLVM\cite{lattner_llvm_2004} (Low Level Virtual Machine) compiler.
+		The particular device functions used are not predetermined, but are instead chosen based on user input to decide on a closure.
+		This technique has multiple advantages.
+		First, the field functions $ \omega_j(t) $ are provided by the user as a plain python method.
+		Note that this method must be \texttt{numba.cuda.jit()} compatible.
+		This allows users to define $ \omega_j(t) $ in a way that compiles and executes fast, does not put many restrictions on the form of the function, and returns the accurate results of analytic functions (compared to the errors seen in interpolation).
+		Compiling the simulator also allows the user to set meta-parameters, and choose the features they want to use in a way that does not require experience with the \texttt{numba.cuda} library.
+		This was especially useful for running benchmarks comparing integration methods from previous versions of the software to the current one, CF4.
+		The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta-parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for different GPUs.
+		Third, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU.
+		In particular, this allows for compatibility with products running \emph{Apple}'s \emph{MacOS}, which are incompatible with \emph{Cuda} devices.
 
 		This functionality is interfaced through an object of class \texttt{spinsim.Simulator}.
-		The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}, which returns a results object including the time, state, time-evolution operator, and expected spin projection.
+		The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}.
+		Users are returned an instance of \texttt{spinsim.Results} including the time, state, time-evolution operator, and expected spin projection.
 		Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object.
 
-		\emph{spinsim} is designed so that a single simulator compilation can be used to execute many simulations, sweeping through a particular parameter, while not needing to be recompiled.
-		This is done through the \texttt{sweep\_parameter} argument to the user-provided field function $ \omega $.
-		The user uses \texttt{sweep\_parameter} to determine a variable parameter for the Hamiltonian.
-		After compiling the \texttt{spinsim.Simulator} object, the user can set the value for \texttt{sweep\_parameter} for a particular simulation as the first argument when calling the function \texttt{spinsim.Simulator.evaluate()}.
-		For a use case example, one might want to simulate many spin systems at different locations in a magnetic field gradient in an MRI experiment.
-		To do this they could choose to set $ \omega_z =\texttt{sweep\_parameter} $, which would vary the magnetic field bias in the $ \omega $ direction for each experiment.
+		The \emph{spinsim} package is designed so that a single simulator instance can be used to execute many simulations, sweeping through parameters while not needing to be recompiled.
+		This is done through the \texttt{sweep\_parameters[]} argument to the user-provided field functions $ \omega_j(t) $.
+		% The user can set \texttt{sweep\_parameters[]} to determine parameter for the Hamiltonian.
+		First the user must instantiate a \texttt{spinsim.Simulator} object.
+		They can then set the value for \texttt{sweep\_parameters[]} for a particular simulation each time \texttt{spinsim.Simulator.evaluate()} is called.
+		As \texttt{sweep\_parameters[]} is a \texttt{numpy.ndarray}\cite{harris_array_2020}, one can use this functionality to sweep many parameters using the same simulator object.
+		For a use-case example, an MRI experimenter might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
+		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.
 		This feature is demonstrated with examples in the documentation.
@@
 	\subsection{Evaluation of accuracy}
-		All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from the tests in Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
+		All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
 		Note that these benchmarks do not take into account the amount of time required to JIT compile simulation code for the first time (order of seconds), as we want to look at this in the limit of running many simulations while sweeping through a parameter that differs in each one.
@@
 		We first wanted to test the accuracy of the different integration techniques for various integration time steps.
-		Here we wanted to test the advantages, if any of using a Magnus based integration method.
-		Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the Root Mean Squared (RMS) error from a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
+		Here we wanted to test the advantages of using a Magnus based integration method.
+		Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the root mean squared (RMS) error from a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
 		\begin{align}
@@
 		\end{align}
+		where $ j \in \{\frac12, 1\} $ is the spin quantum number of the system.
+		This baseline was computed in 2.4 hours (in comparison to order of 10ths of a second these \emph{spinsim} tests were executed in), and was also used for comparisons to other software packages.
 
-		where $ j \in \{\frac12, 1\} $ is the spin quantum number of the system.
-
-		This baseline was computed in 2.4 hours (in comparison to order of 10ths of a second these \emph{spinsim} tests were executed in), and was also used for comparisons to other software packages.
-		These are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
-		For each of these simulations we measured the time of execution, as although it is more accurate compared to Euler integration, the CF4 method is slower for any fixed integration time step.
-		These are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
+		Error vs time step plots are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
+		In order to find how long a simulation method takes to complete for a given accuracy, we also measured the execution time for each of the simulations.
+		These plots are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
+		The former sets of plots will be of interest to users choosing an appropriate time step for simulations, and the latter for estimating the execution time of such simulations.
 		In all of these comparisons, errors above $ 10^{-3} $ were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
-		Additionally, errors bellow $ 10^{-11} $ were excluded, as this was the order of magnitude of the errors in the reference simulation.
+		Errors bellow $ 10^{-11} $ were also excluded, as this was the order of magnitude of the errors in the reference simulation.
 
@@
 		Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
-		From Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, although the Magnus based method is slower than the midpoint Euler based method, it makes up for this in terms of its accuracy.
-		Thus, by default \emph{spinsim} sets the integrator to CF4, and uses the rotating frame.
-		These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
+		When comparing speed vs accuracy in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, the advantage that CF4 gives in terms of accuracy far outweighs its slower execution speed when compared to midpoint Euler methods.
+		% By default \emph{spinsim} sets the integrator to CF4, and uses the rotating frame.
+		% These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
 		\begin{figure}[h!]
@@
 	\subsection{Comparison to alternatives}
-		We ran the same error (using Equation \eqref{eq:error}) and execution time benchmarks on some alternative packages to compare \emph{spinsim}'s performance to theirs.
+		Using Equation \eqref{eq:error}, we ran the same error and execution time benchmarks on some alternative packages to compare \emph{spinsim}'s performance to theirs.
 		The packages compared were are listed in Table \ref{tab:external}.
@@
 		\end{table}
-
-		In each case, the step sizes of the alternative integrators were limited to a maximum value to obtain simulation results of different accuracies, and the maximum number of steps were modified in some cases to allow more steps to take place.
+		In each case, the step sizes of the alternative integrators were limited to a maximum value to obtain simulation results of different accuracies, and the maximum number of steps were modified in some cases to allow a larger number of steps to take place.
 		Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
 
-		Similarly to with the internal \emph{spinsim} benchmarks, the expected spin projection was evaluated in each case, but the states were compared to calculate a relative error.
+		Similarly to with the internal \emph{spinsim} benchmarks, the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error.
 		Again, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
-		Functions used for sampling were compiled in both \emph{spinsim} and \emph{QuTip}, and the time taken to complete a simulation was measured in both cases for a second simulation using the already compiled functions.
+		Functions used for sampling were compiled to \emph{LLVM} and \emph{cython} in \emph{spinsim} and \emph{QuTip} respectively.
+		in both cases, the time taken to complete a simulation was measured using a second simulation using the already compiled functions, to represent the use-case of sweeping through many simulations.
 
-		Each benchmark was run one simulation at a time.
-		However, it might be possible to increase the average speed of many benchmarks from \emph{Mathematica} and \emph{SciPy} packages using multithreading to run multiple benchmarks at a time.
+		The speed of only one simulation was measured for each benchmark.
+		However, it might be possible to increase the average speed of many benchmarks from \emph{Mathematica} and \emph{SciPy} packages by using multithreading to run multiple simulations at a time.
 		When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
-		Multithreading was also not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step consumes a day of computational time.
-		But to be fair, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8, which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor, which appears as dotted lines.
-		Results from \emph{spinsim} and \emph{QuTip} automatically run multithreaded, so this handicap is not plotted for these packages.
+		Multithreading was not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step already consumes over 11 hours of computational time.
+		Regardless, for a fair comparison, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8, which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor, which appears as dotted lines.
+		Simulations from \emph{spinsim} and \emph{QuTip} automatically run multithreaded, so this handicap is not plotted for these packages.
 
@@
 		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), compared highly procedural devices (being CPUs).
-		Speed benchmarks were performed using \texttt{sense.sim.benchmark}, by comparing evaluation speed of typical spin-one sensing experiments on different devices.
+		Speed benchmarks were performed using \texttt{neural-sense.sim.benchmark}, by comparing evaluation speed of typical spin-one sensing experiments on different devices.
 		This is shown in Figure \ref{fig:benchmark_device_aggregate}.
@@
 		Surprisingly, we found that the \emph{Ryzen 7 5800X} 8 core CPU was able to execute the benchmark faster than the \emph{Ryzen 9 5900X} 12 core CPU.
-		This can be explained by the fact that the \emph{Ryzen 7 5800X} was liquid cooled, rather than being air cooled, meaning it was likely able to boost to a higher core clock, and resist thermal throttling.
+		This can be explained by the fact that the \emph{Ryzen 7 5800X} was cooled by liquid rather than air, meaning it was likely able to boost to a higher core clock, and resist thermal throttling.
 
 		Figure \ref{fig:benchmark_device_aggregate} can be used by potential \emph{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
-		We would recommend Another factor not shown in the plot is the fact that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
+		Another factor not shown in the plot is the fact that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
 		In contrast, this does not happen when running a GPU based program, as it requires very little CPU utilisation to function.
@@
 		During the accuracy tests, it was confirmed that all possible modes of \emph{spinsim} agree with a standard \emph{SciPy} simulation up to an arbitrarily small error.
-		The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately.
+		The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately against \texttt{scipy.linalg.expm()} from \emph{SciPy}.
 		These tests and benchmarks were run as part of the \texttt{neural\_sense} package.
@@
 		This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
-		Another possible use case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
+		Another possible use-case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
 		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
@@
 
-Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group, particularly Hamish Taylor and Travis Hartley, who have started using \emph{spinsim} for their own projects and have given useful feedback of their user experience with the package.
+Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group.
+In particular, Hamish Taylor, Travis Hartley and Chris Bounds, who have started using \emph{spinsim} for their own projects and have given useful feedback of their user experience with the package.
 

### 2021-07-01 example.py

@@ -12,14 +12,14 @@ simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber
 
 results_larmor = simulator_larmor.evaluate(0e-3, 100e-3, 100e-9, 500e-9, spinsim.SpinQuantumNumber.HALF.plus_x)
 
-plt.figure()
-plt.plot(results_larmor.time, results_larmor.spin)
-plt.legend(["x", "y", "z"])
-plt.xlim(0e-3, 2e-3)
-plt.xlabel("time (s)")
-plt.ylabel("spin expectation (hbar)")
-plt.title("Spin projection for Larmor precession")
-plt.show()
+# plt.figure()
+# plt.plot(results_larmor.time, results_larmor.spin)
+# plt.legend(["x", "y", "z"])
+# plt.xlim(0e-3, 2e-3)
+# plt.xlabel("time (s)")
+# plt.ylabel("spin expectation (hbar)")
+# plt.title("Spin projection for Larmor precession")
+# plt.show()
 
 import spinsim
 import numpy as np
@@ -58,4 +58,4 @@ plt.ylabel("spin expectation (hbar)")
 plt.title("Spin projection for Rabi flopping")
 plt.draw()
 
-plt.show()
+# plt.show()

### 2021-07-01 spinsim/__init__.py

@@ -936,13 +936,13 @@ class Simulator:
             self.get_time_evolution_raw(sweep_parameters, time, time_end_points, time_step_integration, time_step_output, time_evolution_output)
 
         elif self.device == Device.CUDA:
-            time = cuda.device_array(time_index_max, np.float64)
-            time_evolution_output = cuda.device_array((time_index_max, self.spin_quantum_number.dimension, self.spin_quantum_number.dimension), np.complex128)
-
-            sweep_parameters_device = cuda.to_device(sweep_parameters)
-
-            blocks_per_grid = (time.size + (self.threads_per_block - 1)) // self.threads_per_block
             try:
+                time = cuda.device_array(time_index_max, np.float64)
+                time_evolution_output = cuda.device_array((time_index_max, self.spin_quantum_number.dimension, self.spin_quantum_number.dimension), np.complex128)
+
+                sweep_parameters_device = cuda.to_device(sweep_parameters)
+
+                blocks_per_grid = (time.size + (self.threads_per_block - 1)) // self.threads_per_block
                 self.get_time_evolution_raw[blocks_per_grid, self.threads_per_block](sweep_parameters_device, time, time_end_points, time_step_integration, time_step_output, time_evolution_output)
             except:
                 print("\033[31mspinsim error!!!\nnumba.cuda could not jit get_field function into a cuda device function.\033[0m\n")
@@ -952,13 +952,13 @@ class Simulator:
             time = time.copy_to_host()
         
         elif self.device == Device.ROC:
-            time = roc.device_array(time_index_max, np.float64)
-            time_evolution_output = roc.device_array((time_index_max, self.spin_quantum_number.dimension, self.spin_quantum_number.dimension), np.complex128)
-
-            sweep_parameters_device = roc.to_device(sweep_parameters)
-
-            blocks_per_grid = (time.size + (self.threads_per_block - 1)) // self.threads_per_block
             try:
+                time = roc.device_array(time_index_max, np.float64)
+                time_evolution_output = roc.device_array((time_index_max, self.spin_quantum_number.dimension, self.spin_quantum_number.dimension), np.complex128)
+
+                sweep_parameters_device = roc.to_device(sweep_parameters)
+
+                blocks_per_grid = (time.size + (self.threads_per_block - 1)) // self.threads_per_block
[…]

### 2021-07-02 article/article.tex
v0.4.3: Code cleaned and documentation updates

@@
 % (which we found to be $ K = 3\cdot 10^8 $ sample points for the 10GiB \emph{GeForce RTX 3080}).
-		We found that a the 10GiB \emph{GeForce RTX 3080} could run at full memory capacity with 300 million sample points for spin-one mode and 600 million sample points for spin-half.
+		We found that a the 10GiB \emph{GeForce RTX 3080} could run at full memory capacity with 60 million sample points for spin-one mode and 120 million sample points for spin-half.
 		% Comment on number of samples for cores or whatever physics is being done

### 2021-07-02 docs/source/conf.py

@@ -40,7 +40,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.2'
+release = '0.4.3'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-07-02 example.py

@@ -1,61 +1,63 @@
 import spinsim
-import numpy as np
 import matplotlib.pyplot as plt
 import math
 
+# Define field for spin system
 def get_field_larmor(time_sample, sweep_parameters, field_sample):
    field_sample[0] = 0              # Zero field in x direction
    field_sample[1] = 0              # Zero field in y direction
    field_sample[2] = math.tau*1000  # Split spin z eigenstates by 1kHz
 
+# Initialise simulator instance
 simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF)
-
+# Evaluate a simulation
 results_larmor = simulator_larmor.evaluate(0e-3, 100e-3, 100e-9, 500e-9, spinsim.SpinQuantumNumber.HALF.plus_x)
 
-# plt.figure()
-# plt.plot(results_larmor.time, results_larmor.spin)
-# plt.legend(["x", "y", "z"])
-# plt.xlim(0e-3, 2e-3)
-# plt.xlabel("time (s)")
-# plt.ylabel("spin expectation (hbar)")
-# plt.title("Spin projection for Larmor precession")
-# plt.show()
+# Plot results
+plt.figure()
+plt.plot(results_larmor.time, results_larmor.spin)
+plt.legend(["x", "y", "z"])
+plt.xlim(0e-3, 2e-3)
+plt.xlabel("time (s)")
+plt.ylabel("spin expectation (hbar)")
+plt.title("Spin projection for Larmor precession")
+plt.show()
 
 import spinsim
-import numpy as np
 import matplotlib.pyplot as plt
 import math
 
+# Define field for spin system
 def get_field_rabi(time_sample, sweep_parameters, field_sample):
-   # Dress atoms from the x direction, Rabi flopping at 1kHz
-   field_sample[0] = math.tau*2000*math.cos(sweep_parameters[0]*time_sample)
+   # Dress atoms from the x direction, Rabi flopping
+   field_sample[0] = 2*sweep_parameters[1]*math.cos(sweep_parameters[0]*time_sample)
    field_sample[1] = 0                    # Zero field in y direction
-   field_sample[2] = sweep_parameters[0]  # Split spin z eigenstates by 700kHz
[…]

### 2021-07-02 gaussian_example.py

@@ -4,16 +4,89 @@ import numpy as np
 import matplotlib.pyplot as plt
 import datetime as dtm
 
+# Find the time
 time_now_string = dtm.datetime.now().strftime("%Y%m%dT%H%M%S")
 
+# Define the field function
 def gaussian_pulse(time, sweep_parameters, pulse):
-    pulse[0] = (math.pi/math.sqrt(math.tau))*math.exp(-0.5*(time**2))
+    pulse[0] = math.pi/math.sqrt(math.tau)*math.exp(-0.5*(time**2))
     pulse[1] = 0.0
     pulse[2] = 0.0
 
-def cumulative_gaussian(t):
-    return 0.5*(1 + math.erf(t/math.sqrt(2.0)))
+# Initialise plots
+plt.figure()
+legend = []
+colours = ["r", "g", "b", "c", "m", "y"]
 
+# Calculate the analytic solution
+def cumulative_gaussian(t):
+    return 0.5*(1 + math.erf(t/math.sqrt(2.0))) - 0.5*(1 + math.erf(-5.0/math.sqrt(2.0)))
+
+time = np.arange(-5.0, 5.1, 2.0)
+state_analytic = np.asarray([[math.cos(0.5*math.pi*cumulative_gaussian(t)), -1j*math.sin(0.5*math.pi*cumulative_gaussian(t))] for t in time], dtype = np.complex128)
+
+# Initialise simulations
+simulator = spinsim.Simulator(gaussian_pulse, spinsim.SpinQuantumNumber.HALF)
+error = []
+time_steps = np.asarray([0.001, 0.005, 0.01, 0.05, 0.1, 0.25, 0.5, 1.0, 2.0])
+number_of_steps = 10 / time_steps
+plot_start_index = 4
+
+# Loop through simulations at different time steps
+for simulation_index, time_step in enumerate(time_steps):
+    # Simulate at a particular time step
+    result_simulated = simulator.evaluate(-5.0, 7.0, time_step, 2.0, np.asarray([1, 0], np.complex128))
+
+    # Calculate error
+    error += [np.sqrt(np.sum(np.abs(result_simulated.state - state_analytic)**2))/5]
+
+    # Plot spins
+    if simulation_index >= plot_start_index:
+        plt.plot(time, result_simulated.spin[:, 0], colours[simulation_index - plot_start_index] + "--o")
+        plt.plot(time, result_simulated.spin[:, 1], colours[simulation_index - plot_start_index] + "--x")
[…]

### 2021-07-02 spinsim/__init__.py

@@ -1,9 +1,6 @@
 """
 
 """
-
-# from . import utilities
-
 from enum import Enum
 import numpy as np
 import numba as nb
@@ -83,14 +80,16 @@ class IntegrationMethod(Enum):
     Commutator free, fourth order Magnus based integrator.
     """
 
-    MIDPOINT_SAMPLE = "midpoint_sample"
+    EULER = "euler"
     """
     Euler integration method.
     """
 
-    HALF_STEP = "half_step"
+    HEUN = "heun"
     """
-    Integration method from AtomicPy. Makes two Euler integration steps, one sampling the field from the start of the time step, one sampling the field from the end of the time step. The equivalent of the trapezoidal method.
+    Integration method from AtomicPy.
+    Makes two Euler integration steps, one sampling the field from the start of the time step, one sampling the field from the end of the time step.
+    The equivalent of the trapezoidal method.
     """
 
 class ExponentiationMethod(Enum):
@@ -111,17 +110,22 @@ class ExponentiationMethod(Enum):
 
     ANALYTIC = ("analytic", 0)
     """
-    Analytic expression of the matrix exponential. For spin half :obj:`SpinQuantumNumber.HALF` systems only.
+    Analytic expression of the matrix exponential.
+    For spin-half :obj:`SpinQuantumNumber.HALF` systems only.
+    See :obj:`Utilities.matrix_exponential_analytic()` for more information.
     """
 
     LIE_TROTTER = ("lie_trotter", 1)
     """
     Approximation using the Lie Trotter theorem, using the Pauli matrices and a single quadratic operator.
+    See :obj:`Utilities.matrix_exponential_lie_trotter()` for more information.
     """
 
     LIE_TROTTER_8 = ("lie_trotter_8", 2)
     """
     Approximation using the Lie Trotter theorem, using all basis elements of su(3).
+    For spin-one :obj:`SpinQuantumNumber.HALF` systems only.
+    See :obj:`Utilities.matrix_exponential_lie_trotter_8()` for more information.
     """
 
 class Device(Enum):
@@ -273,13 +277,16 @@ class Results:
     time : :obj:`numpy.ndarray` of :obj:`numpy.float64` (time_index)
         The times that `state` was evaluated at.
     time_evolution : :obj:`numpy.ndarray` of :obj:`numpy.float128` (time_index, y_index, x_index)
-        The evaluated time evolution operator between each time step. See :ref:`architecture` for some information.
[…]

### 2021-07-12 article/article.tex
Added most of James's sugestions to paper

@@
 \rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}
+
+\newcommand{\supervisordisagreement}[2]{\textcolor{green}{\texttt{{Supervisor disagreement!!!
+<<<<<<< Lincoln}}} \textcolor{blue}{#1} \textcolor{green}{\texttt{=======}} \textcolor{red}{#2} \textcolor{green}{\texttt{>>>>>>> James}}}
+\newcommand{\todo}[1]{\textcolor{green}{\texttt{[TODO: #1]}}}
+\newcommand{\note}[1]{\textcolor{green}{\texttt{[NOTE: #1]}}}
 
@@
 	In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz.
-	Standard integration methods require very small time steps in order to accurately depict these oscillations.
+	Standard integration methods require very small time-steps in order to accurately depict these oscillations.
 
@@
 		Here $ N $ is the number of levels in the quantum system.
-		Often we are considering systems with spin $ J $ of half or one.
+		Often we are considering systems with spin of half or one.
+		\supervisordisagreement{
 			Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
+		}{
+		Spin-half is the $ N = 2 $ case, and spin-one is the $ N = 3 $ case.
+		}
 		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of angular frequency.
@@
 		\end{align}
+		Here we exclude the identity so that the Hamiltonian is traceless, which corresponds to choosing a physically meaningless energy zero point.
 		It is well known that a charged spin-half system with magnetic moment $ \overrightarrow{\mu} $, and gyromagnetic ratio $ \gamma $, in a magnetic field $ \overrightarrow{B}(t) $, has Hamiltonian
@@
 		\end{align}
-
+		\supervisordisagreement{
 			Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices halved.
-		We exclude the identity so that the Hamiltonian is traceless, which we can do because it corresponds to choosing a physically meaningless energy zero point.
+		}{
+			Here $ J_x, J_y $ and $ J_z $ are spin operators
+			\begin{align}
+				J_x &= \frac12\begin{pmatrix}
+					0 & 1 \\
+					1 & 0
+				\end{pmatrix},
+				&J_y &= \frac12\begin{pmatrix}
+					0 & -i \\
+					i &  0
+				\end{pmatrix},
+				&\textrm{and }J_z &= \frac12\begin{pmatrix}
+					1 &  0 \\
+					0 & -1
+				\end{pmatrix},\label{eq:spin_half_operators}
+			\end{align}
+			equal to the Pauli matrices halved.
+		}
+		Because of the equivalence of the magnetic field components $ B_j(t) $ and the $ \omega_j(t) $, we henceforth refer to the latter as field functions.
 
@@
 		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
-		With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,
+		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,\todo{Describe this subspace better}
+		% With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,
 		\begin{align}
@@
 		Note that $ Q $ is proportional to $ Q_{zz} $\cite{hamley_spin-nematic_2012} and $ Q_0 $\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
-		These are the only operators necessary to simulate many spin-one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
+		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
 		The \emph{spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
@@
 		% DONT WRITE OUT, sigma
-		% \begin{align}
-		% 	J_x &= \frac12\begin{pmatrix}
-		% 		0 & 1 \\
-		% 		1 & 0
-		% 	\end{pmatrix},
-		% 	&J_y &= \frac12\begin{pmatrix}
-		% 		0 & -i \\
-		% 		i &  0
-		% 	\end{pmatrix},
-		% 	&\textrm{and }J_z &= \frac12\begin{pmatrix}
-		% 		1 &  0 \\
-		% 		0 & -1
-		% 	\end{pmatrix}.\label{eq:spin_half_operators}
-		% \end{align}
 
@@
 	\subsection{Unitary time evolution and the Magnus expansion}
-		It is possible to write $ \psi(t) $ in terms of a unitary transformation $ \mathcal{U}(t, t_0) $ of the state $ \psi(t_0) $, for any time $ t_0 $, that is, $ \psi(t) = \mathcal{U}(t, t_0)\psi(t_0) $.
+		Since $H(t)$ is Hermitian, it follows from Equation \eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
+		Therefore it is possible to write $ \psi(t) $ in terms of a unitary transformation $ \mathcal{U}(t, t_0) $ of the state $ \psi(t_0) $, for any time $ t_0 $, that is, $ \psi(t) = \mathcal{U}(t, t_0)\psi(t_0) $.
 		It then follows from Equation \eqref{eq:schroedinger} that $ \mathcal{U}(t, t_0) $ also follows a Schr\"{o}dinger equation,
@@
 		% Note that because $ \mathcal{U}(t, t_0) $ is unitary, the calculated value of $ \psi(t) $ using this method will not change in magnitude, conserving probability.
-		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a skew-Hermitian (also termed anti-Hermitian) matrix.
-		If the Hamiltonian is constant, then this exponential is % Check if continuity requirement on unitary
-		\begin{align}
-			\mathcal{U}(t, t_0) &= \exp(-i H\cdot(t - t_0)).\label{eq:exp_sol_of_constant}
+		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a anti-Hermitian (also termed skew-Hermitian) matrix.
+		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is \note{Should we use H, ie no argument, or H(t'), ie arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
+		\begin{align}
+			\mathcal{U}(t, t_0) &= \exp(-i (t - t_0) \mathcal{H}).\label{eq:exp_sol_of_constant}
 		\end{align}
@@
 		For a time varying Hamiltonian, the general solution for $ \mathcal{U}(t, t_0) $ is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
-		The Dyson series\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
-		While the Dyson series has been used numerically\cite{kalev_integral-free_2020}, it has only been so recently, in particular because once truncated, it is in general no longer unitary.
-
-		The Magnus series
-		\begin{align}
-			\mathcal{U}(t, t_0) &= \exp\left(\Omega(t, t_0)\right) = \exp\left(\sum_{m = 1}^\infty \Omega_m(t, t_0)\right)
-		\end{align}
-		explicitly preserves unitarity when truncated\cite{magnus_exponential_1954}.
-		The first terms in the Magnus series are\cite{blanes_magnus_2009}
+		The well known Dyson series\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
+		While the Dyson series has recently been used numerically\cite{kalev_integral-free_2020}, it is challenging to work with because once truncated, it is in general no longer unitary.
+
+		The Magnus series, in contrast, gives $ \mathcal{U}(t, t_0) $ in terms of an exponential of a series of anti-Hermitian operators, specifically
+		\begin{align}
+			\mathcal{U}(t, t_0) &= \exp\left(\Omega(t, t_0)\right) = \exp\left(\sum_{m = 1}^\infty \Omega_m(t, t_0)\right).
+		\end{align}
+		As such, the Magnus series explicitly preserves unitarity when truncated\cite{magnus_exponential_1954}.
+		The terms in the Magnus series are integrals over nested time commutators of the Hermitian matrix $ A(t') $, where, in the case of quantum mechanics, $ A(t') = -iH(t') $.
+		For instance, the first three terms are\cite{blanes_magnus_2009}
 		\begin{align}
@@
 		\end{align}
-		where$ [X, Y] = XY - YX $ is the commutator, and, in the case of quantum mechanics, $ A(t') = -iH(t') $.
-Note that, when truncated to first order, the magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_0^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation \eqref{eq:exp_sol_of_constant}, with $ H $ approximated to be constant with its average value.
+		where $ [X, Y] = XY - YX $ is the commutator.
+		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation \eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.
 
@@
 
-		A Magnus series over a time step $ T $ will be guaranteed to converge only if $ \int_{t_0}^{t_0 + T}\mathrm{d}t_1\|H(t_1)\| < \pi $\cite{blanes_magnus_2009}.
+		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi \approx 1.08686870\dots $\cite{blanes_magnus_2009}.
+		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < 1.08686870\dots $\cite{blanes_magnus_2009}.
+		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $\cite{blanes_magnus_2009}.
 		Furthermore, each subsequent term in the expansion increases in complexity rapidly.
-		For these reasons, the Magnus expansion is generally used as a time stepping method rather than a single step to solve the complete system.
-		Designing a Magnus based solver is a trade-off between the number of terms used in each expansion, and the number of time steps used.
-		Time stepping can be made from the fact that time evolution operators can be split into a product via
+		For these reasons, the Magnus expansion is generally used as a time-stepping method rather than a single step to solve the complete system.
+		Designing a Magnus-based solver is a trade-off between the number of terms used in each expansion, and the number of time-steps used.
+		Time stepping is based on the fact that time evolution operators can be split into a product via
 		\begin{align}
@@
 Standard bounds.
-		% Numerical solver takes only a few terms of the expansion. However, any long operator can be broken into a product. Cite Magnus papers. Designing a Magnus based integrator is a trade off.
-
-		Many unitary time stepping techniques have been developed based on the Magnus expansion\cite{auer_magnus_2018}.
-		Some of these techniques use Gauss-Legendre quadrature sampling and Baker–Campbell–Hausdorff formula to respectively avoid the integration and commutators of the Hamiltonian, producing simple expressions that can be used for unitary time stepping\cite{blanes_fourth-_2006}.
+		% Numerical solver takes only a few terms of the expansion. However, any long operator can be broken into a product. Cite Magnus papers. Designing a Magnus-based integrator is a trade off.
+
+		Many unitary time-stepping techniques have been developed based on the Magnus expansion\cite{auer_magnus_2018}.
+		Some of these techniques use Gauss-Legendre quadrature sampling and the Baker–Campbell–Hausdorff formula to respectively avoid the integration and time commutators of the Hamiltonian, producing simple expressions that can be used for unitary time-stepping\cite{blanes_fourth-_2006}.
 		% These take advantage of the Baker–Campbell–Hausdorff formula
@@
 		In particular, we use the commutator free, fourth order method (CF4) from Reference~\cite{auer_magnus_2018}.
-		Suppose we wish to evaluate a time step of $ \mathcal{U}(t + \mathrm{d}t, t) $ using the CF4 method.
+		Suppose we wish to evaluate a time-step of $ \mathcal{U}(t + \mathrm{d}t, t) $ using the CF4 method.
 		The Hamiltonians are sampled at times
@@
 		To approximate the limit in Equation \eqref{eq:lie_trotter}, $ n $ must be a large number.
-		We choose $ n $ to be of the form $ n = 2^\tau $, as powers of two are particularly effient large numbers to raise matrices to.
+		We choose $ n $ to be of the form $ n = 2^\tau $, as raising matrices to powers of two can be done efficiently by iterative squaring.
 		This can be done just by iterative squaring, which requires a small number of operations.
-		While there are some loose lower bounds for the number of squares $ \tau $ \cite{suzuki_generalized_1976}, using these to choose a value can cause floating point errors from over-squaring.
+		While there are some loose upper bounds for the $ n $ required to reach a desired accuracy for the matrix exponential\cite{suzuki_generalized_1976}, using these to choose a value of $ n $ can, in practice, cause floating-point errors from over-squaring.
 		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}\cite{virtanen_scipy_2020}.
@@
 		In addition to those introduced by the Lie-Trotter approximation, we find errors when manipulating matrices close to the identity.
-		This is a consequence of the diagonals of the matrices being close to 1, with the limited precision of floating point numbers being unable to represent these differences accurately.
+		Because $ n $ is very large, $ T $ is very close to the identity.
+		In particular, the limited precision of floating-point numbers is unable to represent the diagonal of $ T $ and its squares accurately.
 		Errors appear in two forms.
-		One is that iterative squaring of matrices close to the identity produces floating point cancellation errors.
-		This can be fixed by only working with the difference of the matrices from the identity when squaring.
+		One form is that iterative squaring of matrices close to the identity produces floating-point cancellation errors.
+		It can be avoided by working with the difference of the matrices from the identity when iteratively squaring.
 		That is, if $ A = I + a $, then instead of calculating the square $ S = I + s = A^2 $, we find $ s = (a + 2I)a $.
-		The other is that if we use this method, we must calculate $ T - I $ accurately, rather than $ T $, which cannot be done by simply subtracting the identity from Equation \eqref{eq:lie_trotter_4}.
-		This can be fixed by replacing the exponentials and trigonometric functions along the diagonal with specialised functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose\cite{hewlett-packard_hp_1994}.
+		The other form of error is that if we use this method, we must initially calculate $ T - I $ accurately, rather than $ T $.
+		This cannot be done by simply subtracting the identity from Equation \eqref{eq:lie_trotter_4}, as doing so would introduce cancellation error.
+		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialised implementations of functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose\cite{hewlett-packard_hp_1994}.
 		The identity is added to the result of the iterative residual squaring and the full exponential is returned.
@@
 		% Once $ T $ is calculated, it is then recursively squared $ \tau $ times to obtain $ E(\omega) $.
-		% In practice the calculations here are done by finding the differences of the matrices from the identity to avoid floating point cancellation errors from subtracting a small number from 1.
+		% In practice the calculations here are done by finding the differences of the matrices from the identity to avoid floating-point cancellation errors from subtracting a small number from 1.
 		% Three sentences rather than one
@@
 		Note that, the methods for both spin-half and spin-one use analytic forms of matrix exponentials so that $ T $ is unitary by construction; $ \mathcal{U}=T^n $ is then also unitary.
-		Simulations in \emph{spinsim} thus maintain unitarity and so conserve probability even over very large numbers of time steps.
+		Simulations in \emph{spinsim} thus maintain unitarity and so conserve probability even over very large numbers of time-steps.
 
 	\subsection{Discretisation and parallelisation}
-		Frequently we wish to sample the state at times $ t_k $ spaced more coarsely than the integration time step.
-		Consider discrete times $ t_k = t_0 + \mathrm{D}t\cdot k $ where $ \mathrm{D}t $ is the time step of the time-series, in contrast to $ \mathrm{d}t $, the time step of the integration.
+		Frequently we wish to sample the state at times $ t_k $ spaced more coarsely than the integration time-step.
+		Consider discrete times $ t_k = t_0 + \mathrm{D}t\cdot k $ where $ \mathrm{D}t $ is the time-step of the time-series, in contrast to $ \mathrm{d}t $, the time-step of the integration.
 		% The unitary operator $ \mathcal{U}_k $ 
@@
 
-		\emph{spinsim} splits the full simulation into small time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals massively in parallel on a GPU.
+		\emph{spinsim} splits the full simulation into time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals in parallel on a GPU.
 % check phrase "massive"
@@
 		% Within each parallel discretisation, we ...
-		Beyond discretisation for parallelisation, we discretise our time-evolution operator into individual integration time steps.
-		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time step $ \mathrm{d}t = \mathrm{D}t/L $.
-
-		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error}.
+		Beyond discretisation for parallelisation, we discretise our time-evolution operator into individual integration time-steps.
+		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time-step $ \mathrm{d}t = \mathrm{D}t/L $.
+
+		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error}\note{How do I reference a section if they don't have number labels in the finished article?
+Should I?}.
 		To choose an appropriate value of $ \mathrm{D}t $, users must consider three factors.
@@
 % (which we found to be $ K = 3\cdot 10^8 $ sample points for the 10GiB \emph{GeForce RTX 3080}).
-		We found that a the 10GiB \emph{GeForce RTX 3080} could run at full memory capacity with 60 million sample points for spin-one mode and 120 million sample points for spin-half.
+		We found that the 10GiB \emph{GeForce RTX 3080} could run at full memory capacity with 60 million sample points for spin-one mode and 120 million sample points for spin-half.
 		% Comment on number of samples for cores or whatever physics is being done
@@
 		% \end{align} % Just use middle product
-		% with $ \mathrm{d}t $ being the integration level time step.
-		% Note that the sampling time steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $.
+		% with $ \mathrm{d}t $ being the integration level time-step.
+		% Note that the sampling time-steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $.
 
 	\subsection{Dynamically rotating frame}
-		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantisation axis $ z $.
+		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantisation axis (which is the $ z $ axis when representing spin operators with the Pauli matrices).
 		Transforming from the lab (standard) frame of reference into one rotating around this axis by rotation operator $ R_{\omega_r}(t) = \exp(i\omega_r J_z t) $, the resulting system follows a new Hamiltonian
@@
 		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
-		This almost always done to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ H_r(t) $ on average make minor contributions to time evolution, and can be ignored.
+		This is almost always done to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ H_r(t) $ on average make minor contributions to time evolution, and can be ignored.
 		In some cases, this allows one to obtain analytic, but approximate, solutions to the quantum system.
@@
 		By our assumption that $ |\omega_r| \approx |\omega_z(t)| \ge |\omega_x(t)|, |\omega_y(t)|, |\omega_q(t)| $ for the duration we have entered the frame, then the rotating frame Hamiltonian will have a smaller norm than the lab frame Hamiltonian.
-		This will yield more accurate results when making discrete time steps by the integrator, as the distances stepped are smaller.
+		This will yield more accurate results when making discrete time-steps by the integrator, as the distances stepped are smaller.
 
@@
 		% If the rotating frame option is selected, the time-evolution operators $ \mathcal{U}_k $ are first calculated within a rotating frame of reference as $ \mathcal{U}^r_k $, which, in some situations, reduces the size of the field functions used in the calculation, increasing accuracy.
-		% The rotation speed of the rotating frame is calculated locally for each parallel time step $ \mathcal{U}_k $, and only for rotations around the $ z $ axis.
+		% The rotation speed of the rotating frame is calculated locally for each parallel time-step $ \mathcal{U}_k $, and only for rotations around the $ z $ axis.
 		% The rotating from field functions $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ are related to the field function $ \omega $ from the user input via
@@
 
-	% \subsubsection{Magnus based integration method}
+	% \subsubsection{Magnus-based integration method}
 	% 	The integration method used in \emph{spinsim} is the commutator free 4 (CF4) method from Auer et al\cite{auer_magnus_2018}, which based on the Magnus expansion.
-Each of the $ \mathcal{U}_k $ are split into products of time evolution operators between times separated by a smaller time step, that is,
+Each of the $ \mathcal{U}_k $ are split into products of time evolution operators between times separated by a smaller time-step, that is,
 
@@
 
-	% 	with $ \mathrm{d}t $ being the integration level time step. Note that the time steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $, where $ L\in\mathbb{N} $.
+	% 	with $ \mathrm{d}t $ being the integration level time-step. Note that the time-steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $, where $ L\in\mathbb{N} $.
 
@@
 		It then starts a loop to find each of the time-stepping operators $ u^k_l $.
-		% The code then loops over each integration time step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
+		% The code then loops over each integration time-step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
 		Within the loop, the integrator enters a device function to sample the user-provided field functions $ \omega_j(t) $ (device functions are GPU subroutines, and in practice all device functions here are compiled inline for speed).
@@
 		For a use-case example, an MRI experimenter might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
-		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.
+		To do this they could choose to set \texttt{sweep\_parameters = [x, y]},\linebreak and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.
 		This feature is demonstrated with examples in the documentation.
@@
 
-		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for).
-		This simulation involves continuously driving transitions in the system for 100ms, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
-		We first wanted to test the accuracy of the different integration techniques for various integration time steps.
-		Here we wanted to test the advantages of using a Magnus based integration method.
+		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}~\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for).
+		This simulation involves continuously driving transitions in the system for $ 100\,\mathrm{ms} $, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
+		We first wanted to test the accuracy of the different integration techniques for various integration time-steps.
+		Here we wanted to test the advantages of using a Magnus-based integration method.
 		Accuracy was calculated by taking the quantum state simulation evaluations of a typical quantum sensing experiment and finding the root mean squared (RMS) error from a baseline simulation run by \texttt{scipy.integrate.ivp\_solve()} as part of the \emph{SciPy} python package, via
@@
 		where $ j \in \{\frac12, 1\} $ is the spin quantum number of the system.
-		This baseline was computed in 2.4 hours (in comparison to order of 10ths of a second these \emph{spinsim} tests were executed in), and was also used for comparisons to other software packages.
-
-		Error vs time step plots are shown in Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error}.
+		This baseline was computed in 2.4 hours (in comparison to order of $ 100\,\mathrm{ms} $ of a second these \emph{spinsim} tests were executed in), and was also used for comparisons to other software packages.
+
+		Error vs time-step plots are shown in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error}.
 		In order to find how long a simulation method takes to complete for a given accuracy, we also measured the execution time for each of the simulations.
-		These plots are shown in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}.
-		The former sets of plots will be of interest to users choosing an appropriate time step for simulations, and the latter for estimating the execution time of such simulations.
+		These plots are shown in Figures \ref{fig:benchmark_spin_one_execution_error} and \ref{fig:benchmark_spin_half_execution_error}.
+		The former sets of plots will be of interest to users choosing an appropriate time-step for simulations, and the latter for estimating the execution time of such simulations.
 		In all of these comparisons, errors above $ 10^{-3} $ were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
-		Errors bellow $ 10^{-11} $ were also excluded, as this was the order of magnitude of the errors in the reference simulation.
-
-		The integration techniques tested were the Magnus based CF4, as well as two Euler based sampling methods.
-		A midpoint Euler method was chosen as the simplest (and fastest for a given integration time step) possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code.
+		Errors below $ 10^{-11} $ were also excluded, as this was the order of magnitude of the errors in the reference simulation.
+
+		The integration techniques tested were the Magnus-based CF4, as well as two Euler-based sampling methods.
+		A midpoint Euler method was chosen as the simplest (and fastest for a given integration time-step) possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code.
 		We benchmarked these methods both while using and not using the rotating frame option.
@@
 		From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \emph{spinsim} gives are accurate to those of \emph{SciPy}.
-		Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus based integration method is up to 3 orders of magnitude more accurate when compared the Euler based methods.
+		Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus-based integration method is up to 3 orders of magnitude more accurate when compared the Euler-based methods.
 		Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
@@
 			\caption{Speed and accuracy of the spin-one options of \emph{spinsim}.
-			A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
+			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
 			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
@@
 			\caption{Speed and accuracy of the spin-half options of \emph{spinsim}.
-			A simulation of a typical neural sensing experiment was run for every integration time step, for each of the possible integration techniques (Magnus based commutator free 4, and two Euler methods).
+			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
 			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
@@
 	\subsection{Comparison to alternatives}
-		Using Equation \eqref{eq:error}, we ran the same error and execution time benchmarks on some alternative packages to compare \emph{spinsim}'s performance to theirs.
-		The packages compared were are listed in Table \ref{tab:external}.
+		We ran the same error and execution time benchmarks on some alternative packages, listed in Table \ref{tab:external}, to compare \emph{spinsim}'s performance to theirs.
 		\begin{table}[h!]
@@
 		\end{table}
-		In each case, the step sizes of the alternative integrators were limited to a maximum value to obtain simulation results of different accuracies, and the maximum number of steps were modified in some cases to allow a larger number of steps to take place.
+		To obtain simulation results of different accuracies, the step sizes of the alternative integrators were limited to a maximum value.
+		In some cases, the maximum number of steps was modified in some cases to allow for the smaller step sizes.
+		% In each case, the step sizes of the alternative integrators were limited to a maximum value 
 		Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
 
-		Similarly to with the internal \emph{spinsim} benchmarks, the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error.
-		Again, we used the longest running \emph{SciPy} simulation as a ground truth for comparison, as the accuracy of \emph{Mathematica} plateaus at small time steps.
+		Similarly to the internal \emph{spinsim} benchmarks\note{section???}, the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error via Equation \eqref{eq:error}.
+		Again, we used the longest running \emph{SciPy} simulation as a baseline for comparison, as the accuracy of \emph{Mathematica} plateaus at small time-steps.
 		Functions used for sampling were compiled to \emph{LLVM} and \emph{cython} in \emph{spinsim} and \emph{QuTip} respectively.
@@
 		When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
-		Multithreading was not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time step already consumes over 11 hours of computational time.
-		Regardless, for a fair comparison, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8, which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor, which appears as dotted lines.
-		Simulations from \emph{spinsim} and \emph{QuTip} automatically run multithreaded, so this handicap is not plotted for these packages.
+		Multithreading was not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time-step already consumes over 11 hours of computational time.
+		Regardless, for a fair comparison, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8 (dotted line in Figures \ref{fig:benchmark_spin_one_execution_error} and \ref{fig:benchmark_spin_half_execution_error}), which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor.
+		Simulations from \emph{spinsim} and \emph{QuTip} automatically run multithreaded, so this comparison is not plotted for these packages.
 
@@
 			\caption{Speed vs accuracy of two alternative integration packages.
-			A simulation of a typical neural sensing experiment was run for every integration time step, for each of alternative packages (\texttt{qutip.sesolve()} from \emph{QuTip}, \texttt{NDSolve()} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
+			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of alternative packages (\texttt{qutip.sesolve()} from \emph{QuTip}, \texttt{NDSolve()} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
 			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
@@
 		Once the algorithm behind \emph{spinsim} was developed, we wanted to check its execution speed while running on various devices.
-		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), compared highly procedural devices (being CPUs).
-		Speed benchmarks were performed using \texttt{neural-sense.sim.benchmark}, by comparing evaluation speed of typical spin-one sensing experiments on different devices.
-		This is shown in Figure \ref{fig:benchmark_device_aggregate}.
-		The integration code was compiled by \texttt{numba} for multicore CPUs, CPUs running single threaded, and \emph{Nvidia Cuda} compatible GPUs, and run on different models of each of them.
+		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), and highly procedural devices (being CPUs).
+		Speed benchmarks were performed using \texttt{neural-sense.sim.benchmark}, by comparing the evaluation speed of typical spin-one sensing experiments on different devices.
+		Results are of these benchmarks are shown in Figure \ref{fig:benchmark_device_aggregate}.
+		The integration code was compiled by \texttt{numba} for multicore CPUs, CPUs running single threaded, and \emph{Nvidia Cuda} compatible GPUs.
+		The compiled code was then run on different models of each of these devices.
 		These test devices are given in Table \ref{tab:devices}.
@@
 			\begin{tabular}{l|l|l|l|l}
-				\textbf{Device}	&\textbf{Type}	&\textbf{RAM (GiB)}	&\textbf{Cores}	&\textbf{Cooling}\\
+				\textbf{Name}	&\textbf{Device}&\textbf{RAM (GiB)}	&\textbf{Cores}	&\textbf{Cooling}\\
 				\hline
@@
 			\caption{Evaluation speed of a simulation of a typical spin-one sensing experiment on both CPUs and GPUs.
-			Integration time step is set to 100ns.
+			Integration time-step is set to 100ns.
 			Transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
@@
 		So, in these cases, performance scales in proportion to thread count.
-		Moving from a single core processor to a high end GPU increases performance by well over an order of magnitude on three of the four computers tested on.
+		Moving from a single core processor to a high end GPU increases performance by well over an order of magnitude on three of the five computers used for testing.
 		Even the low end \emph{Quadro K620} was an improvement over the \emph{Core i7-6700} used by the same computer.
 		Execution speed vs number of cuda cores starts to plateau as the number of cores increases.
-		This happens because the time it takes to transfer memory from RAM to VRAM (dedicated graphics memory), which is independent on the number of cores of the GPU, becomes a comparable to the execution time of the simulator logic.
+		This happens because the time it takes to transfer memory from RAM to VRAM (dedicated graphics memory), which is independent on the number of cores of the GPU, becomes comparable to the execution time of the simulator logic.
 		However, there is still a large improvement from using the high end \emph{GeForce RTX 3070} to the \emph{GeForce RTX 3080}, with the latter simulating the experiment almost twice as fast as it would take to run the simulated experiment in the real world.
@@
 
-		Figure \ref{fig:benchmark_device_aggregate} can be used by potential \emph{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
-		Another factor not shown in the plot is the fact that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
+		Users can view \ref{fig:benchmark_device_aggregate} to decide on how much their current or future hardware will be able to take advantage of \emph{spinsim}'s parallelism.
+		% Figure \ref{fig:benchmark_device_aggregate} can be used by potential \emph{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
+		Another factor not shown in the plot is that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
 		In contrast, this does not happen when running a GPU based program, as it requires very little CPU utilisation to function.
@@
 	\subsection{Testing}
-		During the accuracy tests, it was confirmed that all possible modes of \emph{spinsim} agree with a standard \emph{SciPy} simulation up to an arbitrarily small error.
+		During the accuracy tests, it was confirmed that all possible modes of \emph{spinsim} agree with a baseline \emph{SciPy} simulation, as close as the user wants up to the error of $ 10^{-11} $ of that baseline.
+		Therefore, \emph{spinsim} can be trusted for accuracy.
 		The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately against \texttt{scipy.linalg.expm()} from \emph{SciPy}.
 		These tests and benchmarks were run as part of the \texttt{neural\_sense} package.
-		The simulator has also been used as part of the measurement protocol being developed there, and it has been tested as part of those algorithms as well.
+		The simulator has also been adopted by members of our lab, who have given advice on user experience.
 
@@
 \section{Operating system}
-Developed and tested on Windows 10.
-CPU functionality tested on MacOS Big Sur (note that modern Mac computers are not compatible with \emph{Cuda} software).
-All packages referenced in \emph{spinsim} are compatible with Linux, but functionality has not been tested.
+Developed and tested on \emph{Windows 10}.
+CPU functionality tested on \emph{MacOS 10.16 Big Sur} (note that \emph{MacOS 10.14 Mojave} and higher is not compatible with \emph{Cuda} hardware and software).
+The package (including \emph{Cuda} functionality) is in principle compatible with Linux, but functionality has not been tested.
 

### 2021-07-13 article/article.tex
Merged more of James's suggestions

@@
 \section{Title}
-spinsim: a GPU optimised simulator of spin-half and spin-one quantum systems
+Spinsim: a GPU optimized simulator of spin-half and spin-one quantum systems
 
@@
 \section{Abstract}
-	The \emph{spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
+	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
 	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelisation. 
 	Along with other optimisations, this allows for speed improvements of up to four orders of magnitude while keeping staying just as accurate.
-	\emph{spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
+	\emph{Spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
 	The initial use-case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
@@
 	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
-	The simplest spin system, spin-half (ie spin quantum number of $ \frac12 $, also referred to as a qubit), is quantised into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
-	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (ie spin quantum number of $ 1 $, also referred to as a quitrit), which is quantised into three quantum spin levels.
+	The simplest spin system, spin-half (ie spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
+	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (ie spin quantum number of $ 1 $, also referred to as a quitrit), which is quantized into three quantum spin levels.
 
@@
 	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of modelling all effects of the system.
-	However, these methods are not completely optimised for our use-case, and therefore come with some issues.
+	However, these methods are not completely optimized for our use-case, and therefore come with some issues.
 
@@
 	Examples include calculating colours for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
-	By finding ways to parallelise the problem of solving quantum spin systems, we can use the many cores of a GPU to our advantage in this context as well.
+	By finding ways to parallelize the problem of solving quantum spin systems, we can use the many cores of a GPU to our advantage in this context as well.
 
@@
 	\subsection{Quantum mechanics background}
-		The \emph{spinsim} package solves the time-dependent Schr\"{o}dinger equation
+		The \emph{Spinsim} package solves the time-dependent Schr\"{o}dinger equation
 		\begin{align}
@@
 		\end{align}
-		where the quantum state $ \psi(t) \in \mathbb{C}^N $ is assumed normalised, and the Hamiltonian $ H(t) \in \mathbb{C}^{N \times N} $ is Hermitian.
+		where the quantum state $ \psi(t) \in \mathbb{C}^N $ is assumed normalized, and the Hamiltonian $ H(t) \in \mathbb{C}^{N \times N} $ is Hermitian.
 		Here $ N $ is the number of levels in the quantum system.
 		Often we are considering systems with spin of half or one.
-		\supervisordisagreement{
 		Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
-		}{
-		Spin-half is the $ N = 2 $ case, and spin-one is the $ N = 3 $ case.
-		}
+		% \supervisordisagreement{
+		% 	Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
+		% }{
+		% Spin-half is the $ N = 2 $ case, and spin-one is the $ N = 3 $ case.
+		% }
 		We set $ \hbar = 1 $, so that the Hamiltonian has physical dimension of angular frequency.
@@
 		% $ \hbar = 1 $).
-In addition, rather than being represented by standard coordinates in $ \mathbb{C}^{N \times N} $, in \emph{spinsim} the Hamiltonian $ H(t) $ is instead represented with respect to a choice of basis for the corresponding Lie Algebra, $ \mathfrak{su}(N) $.
-For example, when set to spin-half mode, the \emph{spinsim} package solves the time dependent Schroedinger equation of the form
+In addition, rather than being represented by standard coordinates in $ \mathbb{C}^{N \times N} $, in \emph{Spinsim} the Hamiltonian $ H(t) $ is instead represented with respect to a choice of basis for the corresponding Lie Algebra, $ \mathfrak{su}(N) $.
+For example, when set to spin-half mode, the \emph{Spinsim} package solves the time dependent Schroedinger equation of the form
 
@@
 		\end{align}
-		\supervisordisagreement{
-			Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices halved.
-		}{
-			Here $ J_x, J_y $ and $ J_z $ are spin operators
-			\begin{align}
-				J_x &= \frac12\begin{pmatrix}
-					0 & 1 \\
-					1 & 0
-				\end{pmatrix},
-				&J_y &= \frac12\begin{pmatrix}
-					0 & -i \\
-					i &  0
-				\end{pmatrix},
-				&\textrm{and }J_z &= \frac12\begin{pmatrix}
-					1 &  0 \\
-					0 & -1
-				\end{pmatrix},\label{eq:spin_half_operators}
-			\end{align}
-			equal to the Pauli matrices halved.
-		}
+		Here $ J_x $, $ J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices\cite[(p169)]{j_j_sakurai_jun_john_modern_2011} halved.
+		% \supervisordisagreement{
+		% 	Here $ J_x, J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices halved.
+		% }{
+		% 	Here $ J_x, J_y $ and $ J_z $ are spin operators
+		% 	\begin{align}
+		% 		J_x &= \frac12\begin{pmatrix}
+		% 			0 & 1 \\
+		% 			1 & 0
+		% 		\end{pmatrix},
+		% 		&J_y &= \frac12\begin{pmatrix}
+		% 			0 & -i \\
+		% 			i &  0
+		% 		\end{pmatrix},
+		% 		&\textrm{and }J_z &= \frac12\begin{pmatrix}
+		% 			1 &  0 \\
+		% 			0 & -1
+		% 		\end{pmatrix},\label{eq:spin_half_operators}
+		% 	\end{align}
+		% 	equal to the Pauli matrices halved.
+		% }
 		Because of the equivalence of the magnetic field components $ B_j(t) $ and the $ \omega_j(t) $, we henceforth refer to the latter as field functions.
@@
 		In the spin-one case there is no standard basis of operators $ \mathcal{A}_j $.
-		Choices include the Gell-Mann matrices\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012}\cite{di_dipolequadrupole_2010}.
+		Choices include the Gell-Mann matrices\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012, di_dipolequadrupole_2010}.
 		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
-		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,\todo{Describe this subspace better}
+		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}
+
+		% This spin-one exponentiator evolves Hamiltonians spanned by $ J_x $, $ J_y $, $ J_z $ and $ Q $ which is sufficient for three level systems in arbitrary bias fields, but with single-photon coupling.
+		% An exponentiator capable of evolving an arbitrary spin-one Hamiltonian, for example with different coupling between the lower and upper pairs of states, or with two-photon coupling, is included in the package.
+
 		% With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,
@@
 		Note that $ Q $ is proportional to $ Q_{zz} $\cite{hamley_spin-nematic_2012} and $ Q_0 $\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
-		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems, including quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
-		The \emph{spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
+		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems in arbitrary bias fields, but with single-photon coupling.
+		This includes quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
+		The \emph{Spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
 		\begin{align}
@@
 
-		% Similarly, when \emph{spinsim} is set to spin-one mode, it can solve the Schroedinger equation of the form
+		% Similarly, when \emph{Spinsim} is set to spin-one mode, it can solve the Schroedinger equation of the form
 
@@
 		% fast and parallel function from wavefunctions
-		As well as integrating the Schr\"odinger equation, \emph{spinsim} also has the functionality to calculate the expected spin projection $ \langle \overrightarrow{J}\rangle (t) $ of a system from its state.
+		As well as integrating the Schr\"odinger equation, \emph{Spinsim} also has the functionality to calculate the expected spin projection $ \langle \overrightarrow{J}\rangle (t) $ of a system from its state.
 		In an experimental setting, one cannot measure the value of the state itself, and must instead measure observables such as spin projection.
@@
 		However, the Bloch equations cannot be used to compute $ \psi(t) $, and can only fully model spin-half systems (and spin-one systems approximated to spin-half).
-		Thus, with \emph{spinsim} we choose to solve the full Schr\"odinger equation instead.
+		Thus, with \emph{Spinsim} we choose to solve the full Schr\"odinger equation instead.
 
@@
 However, it can also be used to model the overall orientation of an ensemble of many quantum systems, like a BEC, for instance.
-\emph{spinsim} has the functionality to calculate the expected spin projection of a system from its state.
+\emph{Spinsim} has the functionality to calculate the expected spin projection of a system from its state.
 
 	\subsection{Unitary time evolution and the Magnus expansion}
-		Since $H(t)$ is Hermitian, it follows from Equation \eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
+		Since $H(t)$ is Hermitian, it follows from Equation~\eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
 		Therefore it is possible to write $ \psi(t) $ in terms of a unitary transformation $ \mathcal{U}(t, t_0) $ of the state $ \psi(t_0) $, for any time $ t_0 $, that is, $ \psi(t) = \mathcal{U}(t, t_0)\psi(t_0) $.
-		It then follows from Equation \eqref{eq:schroedinger} that $ \mathcal{U}(t, t_0) $ also follows a Schr\"{o}dinger equation,
+		It then follows from Equation~\eqref{eq:schroedinger} that $ \mathcal{U}(t, t_0) $ also follows a Schr\"{o}dinger equation,
 		\begin{align}
@@
 
-		Thus, to solve Equation \eqref{eq:schroedinger} for $ \psi(t) $ given a particular $ \psi(t_0) $, one only needs to solve Equation \eqref{eq:unitary_schroedinger} for $ \mathcal{U}(t, t_0) $.
+		Thus, to solve Equation~\eqref{eq:schroedinger} for $ \psi(t) $ given a particular $ \psi(t_0) $, one only needs to solve Equation~\eqref{eq:unitary_schroedinger} for $ \mathcal{U}(t, t_0) $.
 		% Note that because $ \mathcal{U}(t, t_0) $ is unitary, the calculated value of $ \psi(t) $ using this method will not change in magnitude, conserving probability.
 		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a anti-Hermitian (also termed skew-Hermitian) matrix.
-		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is \note{Should we use H, ie no argument, or H(t'), ie arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
+		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is % \note{Should we use H, ie no argument, or H(t'), ie arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
 		\begin{align}
@@
 		where $ [X, Y] = XY - YX $ is the commutator.
-		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation \eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.
+		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation~\eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.
 
@@
 		Evaluating matrix exponentials is a core part of the integration algorithm.
-		Rather than exponentiating the Hamiltonian directly as in Equation \eqref{eq:cf4_implementation}, \emph{spinsim} works with the field functions $ \omega_j(t) $.
+		Rather than exponentiating the Hamiltonian directly as in Equation~\eqref{eq:cf4_implementation}, \emph{Spinsim} works with the field functions $ \omega_j(t) $.
 		% as a vector representation of the Hamiltonian of the spin system being simulated, rather than generic matrix elements in an array.
 		% This allows for matrix exponentiators that take advantage of this representation.
-		% For all implementations of exponentiation, the \emph{spinsim} computes the matrix exponential
+		% For all implementations of exponentiation, the \emph{Spinsim} computes the matrix exponential
 		% % \begin{align}
@@
 		% \end{align}
-		% In practice, $ \omega $ is the Lie algebra (spin and quadrature) basis representation of $ \overline{H_1} $ or $ \overline{H_2} $ defined in Equations \eqref{eq:cf4_sample_1} and \eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation \eqref{eq:cf4_implementation}.
+		% In practice, $ \omega $ is the Lie algebra (spin and quadrature) basis representation of $ \overline{H_1} $ or $ \overline{H_2} $ defined in Equations~\eqref{eq:cf4_sample_1} and~\eqref{eq:cf4_sample_2}, which need to be exponentiated in Equation~\eqref{eq:cf4_implementation}.
 
@@
 		\end{align}
-		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method \cite{barthel_optimized_2020} allow us to write 
+		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method\cite{barthel_optimized_2020} allow us to write 
 		\begin{align}
@@
 		Matrix exponentiation is completed by raising $ T $ to an integer $ n $.
-		To approximate the limit in Equation \eqref{eq:lie_trotter}, $ n $ must be a large number.
+		To approximate the limit in Equation~\eqref{eq:lie_trotter}, $ n $ must be a large number.
 		We choose $ n $ to be of the form $ n = 2^\tau $, as raising matrices to powers of two can be done efficiently by iterative squaring.
@@
 		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}\cite{virtanen_scipy_2020}.
-		We found that the error minimised after a number of squares of $ \tau = 24 $.
+		We found that the error minimized after a number of squares of $ \tau = 24 $.
 		Thus, by default, $ n = 2^{24} $.
@@
 		The other form of error is that if we use this method, we must initially calculate $ T - I $ accurately, rather than $ T $.
-		This cannot be done by simply subtracting the identity from Equation \eqref{eq:lie_trotter_4}, as doing so would introduce cancellation error.
-		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialised implementations of functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose\cite{hewlett-packard_hp_1994}.
+		This cannot be done by simply subtracting the identity from Equation~\eqref{eq:lie_trotter_4}, as doing so would introduce cancellation error.
+		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialized implementations of functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose\cite{hewlett-packard_hp_1994}.
 		The identity is added to the result of the iterative residual squaring and the full exponential is returned.
@@
 		% This spin-one exponentiator cannot solve arbitrary spin-one quantum systems, as that would require the ability to exponentiate a point in the full, 8-dimensional Lie algebra of $ \mathfrak{su}(3) $, rather than just the 4-dimensional subspace spanned by the subalgebra $ \mathfrak{su}(2) $ spanned by $ \{J_x, J_y, J_z, Q\} $, and the single quadratic operator $ Q $.
-		This spin-one exponentiator evolves Hamiltonians spanned by $ J_x, J_y, J_z $ and $ Q $ which is sufficient for three level systems in arbitrary bias fields, but with single-photon coupling.
+		This spin-one exponentiator evolves Hamiltonians spanned by $ J_x $, $ J_y $, $ J_z $ and $ Q $ which is sufficient for three level systems in arbitrary bias fields, but with single-photon coupling.
 		An exponentiator capable of evolving an arbitrary spin-one Hamiltonian, for example with different coupling between the lower and upper pairs of states, or with two-photon coupling, is included in the package.
@@
 		Note that, the methods for both spin-half and spin-one use analytic forms of matrix exponentials so that $ T $ is unitary by construction; $ \mathcal{U}=T^n $ is then also unitary.
-		Simulations in \emph{spinsim} thus maintain unitarity and so conserve probability even over very large numbers of time-steps.
+		Simulations in \emph{Spinsim} thus maintain unitarity and so conserve probability even over very large numbers of time-steps.
 
@@
 		Hence, the time-evolution operators $ \mathcal{U}_k $ can be calculated in parallel.
-		% It allows \emph{spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
-
-		\emph{spinsim} splits the full simulation into time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals in parallel on a GPU.
+		% It allows \emph{Spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
+
+		\emph{Spinsim} splits the full simulation into time intervals $ [t_{k - 1}, t_{k}] $, and calculates time-evolution operators $ \mathcal{U}_k $ for these intervals in parallel on a GPU.
 % check phrase "massive"
 		% within small time intervals $ [t_{k - 1}, t_{k}] $, which are each calculated massively in parallel on a GPU.
-		When all the $ \mathcal{U}_k $ are calculated, the CPU then multiplies them together (a comparatively less demanding job than calculating them) using Equation \eqref{eq:integration_compilation} to determine the output samples $ \psi_k $ of the evolving state.
+		When all the $ \mathcal{U}_k $ are calculated, the CPU then multiplies them together (a comparatively less demanding job than calculating them) using Equation~\eqref{eq:integration_compilation} to determine the output samples $ \psi_k $ of the evolving state.
 
 		% Within each parallel discretisation, we ...
-		Beyond discretisation for parallelisation, we discretise our time-evolution operator into individual integration time-steps.
+		Beyond discretisation for parallelisation, we discretize our time-evolution operator into individual integration time-steps.
 		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time-step $ \mathrm{d}t = \mathrm{D}t/L $.
 
-		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error}\note{How do I reference a section if they don't have number labels in the finished article?
-Should I?}.
+		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error} in Section~\nameref{sec:accuracy}.
+% \note{How do I reference a section if they don't have number labels in the finished article?
+Should I?}
 		To choose an appropriate value of $ \mathrm{D}t $, users must consider three factors.
-		For the most benefit out of GPU parallelisation, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{spinsim}.
+		For the most benefit out of GPU parallelisation, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{Spinsim}.
 		Users should also make sure that $ \mathrm{D}t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \langle \overrightarrow{J}\rangle_k $ to be used in their further analysis.
@@
 		\end{align}
-		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
+		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite[(p336,338)]{j_j_sakurai_jun_john_modern_2011}.
 		This is almost always done to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ H_r(t) $ on average make minor contributions to time evolution, and can be ignored.
 		In some cases, this allows one to obtain analytic, but approximate, solutions to the quantum system.
-		Note that the RWA is never invoked by \emph{spinsim}, as doing this would reduce the accuracy of simulation results; although a problem already expressed in a rotating frame can of course be input by the user if desired.
-		In fact, because of the speed increase of \emph{spinsim} compared to alternatives, users who would have previously simulated their systems using the RWA due to speed concerns may now wish to use \emph{spinsim} to simulate beyond RWA effects that would previously have been missed.
+		Note that the RWA is never invoked by \emph{Spinsim}, as doing this would reduce the accuracy of simulation results; although a problem already expressed in a rotating frame can of course be input by the user if desired.
+		In fact, because of the speed increase of \emph{Spinsim} compared to alternatives, users who would have previously simulated their systems using the RWA due to speed concerns may now wish to use \emph{Spinsim} to simulate beyond RWA effects that would previously have been missed.
 
@@
 
-		A different rotating frame is entered by \emph{spinsim} for each time interval $ [t_{k - 1}, t_k] $.
+		A different rotating frame is entered by \emph{Spinsim} for each time interval $ [t_{k - 1}, t_k] $.
 		This dynamic application allows for the rotating frame to be used even during sweeps of the dominant term $ \omega_z(t) $ where it is only approximately constant locally.
@@
 		% In some cases, this allows for analytic solutions to the approximate quantum system to be obtained.
-		% Note that the RWA is \emph{not} invoked in \emph{spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
+		% Note that the RWA is \emph{not} invoked in \emph{Spinsim}, as doing this would reduce the accuracy of simulation results, defeating our purpose of using a rotating frame.
 		% % Can still benefit from the rotating frame ...
@@
 	% \subsubsection{Magnus-based integration method}
-	% 	The integration method used in \emph{spinsim} is the commutator free 4 (CF4) method from Auer et al\cite{auer_magnus_2018}, which based on the Magnus expansion.
+	% 	The integration method used in \emph{Spinsim} is the commutator free 4 (CF4) method from Auer et al\cite{auer_magnus_2018}, which based on the Magnus expansion.
 Each of the $ \mathcal{U}_k $ are split into products of time evolution operators between times separated by a smaller time-step, that is,
@@
 			\centering
-			\includegraphics[scale=0.475]{architecture.pdf}
-			\caption{The structure of \emph{spinsim}}
+			\includegraphics[scale=0.475]{architecture.png}
+			\caption{The structure of \emph{Spinsim}}
 			\label{fig:architecture}
 		\end{figure}
-		A visual summary of the structure of \emph{spinsim} is shown in Figure \ref{fig:architecture}.
-		The integrator in the \emph{spinsim} package calls a kernel (multithreaded function) to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the $ \mathcal{U}_k $.
+		A visual summary of the structure of \emph{Spinsim} is shown in Figure~\ref{fig:architecture}.
+		The integrator in the \emph{Spinsim} package calls a kernel (multithreaded function) to be run on a \emph{Cuda} capable \emph{Nvidia} GPU in parallel, with a different thread being allocated to each of the $ \mathcal{U}_k $.
 		Alternatively, the kernel can be run in parallel on a multicore CPU if a compatible GPU is not available.
@@
 Next, the matrix exponentials are taken within another device function.
-		Finally, $ u^k_l $ is premultiplied to $ \mathcal{U}^r_k $ (which is initialised to the identity), and the loop continues.
-
-		When the loop has finished, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation \eqref{eq:exit_rotating_frame}, and this is returned.
-		Once all threads have executed, using Equation \eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} = \psi(t_0) $.
+		Finally, $ u^k_l $ is premultiplied to $ \mathcal{U}^r_k $ (which is initialized to the identity), and the loop continues.
+
+		When the loop has finished, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation~\eqref{eq:exit_rotating_frame}, and this is returned.
+		Once all threads have executed, using Equation~\eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} = \psi(t_0) $.
 
 	\subsection{Compilation of integrator}
-		The \emph{spinsim} integrator is constructed and compiled just in time, using the \emph{Numba}\cite{lam_numba_2015} python package.
+		The \emph{Spinsim} integrator is constructed and compiled just in time, using the \emph{Numba}\cite{lam_numba_2015} python package.
 		This is achieved via the \texttt{numba.cuda.jit()} decorator, which compiles python functions into \emph{Nvidia Cuda}\cite{nickolls_scalable_2008} kernels using an LLVM\cite{lattner_llvm_2004} (Low Level Virtual Machine) compiler.
@@
 		Third, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU.
-		In particular, this allows for compatibility with products running \emph{Apple}'s \emph{MacOS}, which are incompatible with \emph{Cuda} devices.
+		In particular, this allows for compatibility with products running \emph{Apple}'s \emph{MacOS 10.14 Mojave} and later, which are incompatible with \emph{Cuda} devices and software.
 
@@
 
-		The \emph{spinsim} package is designed so that a single simulator instance can be used to execute many simulations, sweeping through parameters while not needing to be recompiled.
+		The \emph{Spinsim} package is designed so that a single simulator instance can be used to execute many simulations, sweeping through parameters while not needing to be recompiled.
 		This is done through the \texttt{sweep\_parameters[]} argument to the user-provided field functions $ \omega_j(t) $.
@@
 \section{Quality control}
-	\subsection{Evaluation of accuracy}
-		All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from Figure \ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
+	\subsection{Evaluation of accuracy}\label{sec:accuracy}
+		All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from Figure~\ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
 		Note that these benchmarks do not take into account the amount of time required to JIT compile simulation code for the first time (order of seconds), as we want to look at this in the limit of running many simulations while sweeping through a parameter that differs in each one.
 
-		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}~\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{spinsim} was written for).
+		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}~\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{Spinsim} was written for).
 		This simulation involves continuously driving transitions in the system for $ 100\,\mathrm{ms} $, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
@@
 		where $ j \in \{\frac12, 1\} $ is the spin quantum number of the system.
-		This baseline was computed in 2.4 hours (in comparison to order of $ 100\,\mathrm{ms} $ of a second these \emph{spinsim} tests were executed in), and was also used for comparisons to other software packages.
-
-		Error vs time-step plots are shown in Figures \ref{fig:benchmark_spin_one_step_error} and \ref{fig:benchmark_spin_half_step_error}.
+		This baseline was computed in 2.4 hours (in comparison to order of $ 100\,\mathrm{ms} $ of a second these \emph{Spinsim} tests were executed in), and was also used for comparisons to other software packages.
+
+		Error vs time-step plots are shown in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error}.
 		In order to find how long a simulation method takes to complete for a given accuracy, we also measured the execution time for each of the simulations.
-		These plots are shown in Figures \ref{fig:benchmark_spin_one_execution_error} and \ref{fig:benchmark_spin_half_execution_error}.
+		These plots are shown in Figures~\ref{fig:benchmark_spin_one_execution_error} and~\ref{fig:benchmark_spin_half_execution_error}.
 		The former sets of plots will be of interest to users choosing an appropriate time-step for simulations, and the latter for estimating the execution time of such simulations.
@@
 		The integration techniques tested were the Magnus-based CF4, as well as two Euler-based sampling methods.
-		A midpoint Euler method was chosen as the simplest (and fastest for a given integration time-step) possible sampling method, whereas a Heun Euler sampling method was used as a comparison to previous versions of this code.
+		A midpoint Euler method was chosen as the simplest (and fastest for a given integration time-step) possible sampling method, whereas a Heun-Euler sampling method was used as a comparison to previous versions of this code.
+		These are respectively labelled as the modified Euler method and the improved Euler method in Reference~\cite[p328]{suli_introduction_2003}.
 		We benchmarked these methods both while using and not using the rotating frame option.
@@
 
-		From Figures \ref{fig:benchmark_spin_one} and \ref{fig:benchmark_spin_half}, we find that overall, the results that \emph{spinsim} gives are accurate to those of \emph{SciPy}.
-		Figures \ref{fig:benchmark_spin_one_step_error}, and \ref{fig:benchmark_spin_half_step_error} show that using the Magnus-based integration method is up to 3 orders of magnitude more accurate when compared the Euler-based methods.
+		From Figure~\ref{fig:benchmark_spin}, we find that overall, the results that \emph{Spinsim} gives are accurate to those of \emph{SciPy}.
+		Figures~\ref{fig:benchmark_spin_one_step_error}, and~\ref{fig:benchmark_spin_half_step_error} show that using the Magnus-based integration method is up to 3 orders of magnitude more accurate when compared the Euler-based methods.
 		Also, using the rotating frame increased the accuracy here by 4 orders of magnitude for any individual integration method.
-		When comparing speed vs accuracy in Figures \ref{fig:benchmark_spin_one_execution_error}, and \ref{fig:benchmark_spin_half_execution_error}, the advantage that CF4 gives in terms of accuracy far outweighs its slower execution speed when compared to midpoint Euler methods.
-		% By default \emph{spinsim} sets the integrator to CF4, and uses the rotating frame.
+		When comparing speed vs accuracy in Figures~\ref{fig:benchmark_spin_one_execution_error}, and~\ref{fig:benchmark_spin_half_execution_error}, the advantage that CF4 gives in terms of accuracy far outweighs its slower execution speed when compared to midpoint Euler methods.
+		% By default \emph{Spinsim} sets the integrator to CF4, and uses the rotating frame.
 		% These can be modified using optional arguments when instantiating the \texttt{spinsim.Simulator} object.
@@
 			\begin{subfigure}[b]{0.475\textwidth}
-				\includegraphics[scale=0.475]{benchmark_spin_one_step_error.pdf}
-				% \caption{Accuracy of the spin-one options of \emph{spinsim}.}
+				\includegraphics[scale=0.475]{benchmark_spin_one_step_error.png}
+				% \caption{Accuracy of the spin-one options of \emph{Spinsim}.}
 				\caption{}
@@
 			\begin{subfigure}[b]{0.475\textwidth}
-				\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.pdf}
-				% \caption{Speed vs accuracy of the spin-one options of \emph{spinsim}.}
+				\includegraphics[scale=0.475]{benchmark_spin_one_execution_error.png}
+				% \caption{Speed vs accuracy of the spin-one options of \emph{Spinsim}.}
 				\caption{}
 				\label{fig:benchmark_spin_one_execution_error}
-			\end{subfigure}\
-			\caption{Speed and accuracy of the spin-one options of \emph{spinsim}.
+			\end{subfigure}
+			\vfill
+			\begin{subfigure}[b]{0.475\textwidth}
+				\includegraphics[scale=0.475]{benchmark_spin_half_step_error.png}
+				% \caption{Accuracy of the spin-half options of \emph{Spinsim}.}
+				\caption{}
+				\label{fig:benchmark_spin_half_step_error}
+			\end{subfigure}
+			\hfill
+			\begin{subfigure}[b]{0.475\textwidth}
+				\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.png}
+				% \caption{Speed vs accuracy of the spin-half options of \emph{Spinsim}.}
+				\caption{}
+				\label{fig:benchmark_spin_half_execution_error}
+			\end{subfigure}
+			\caption{Speed and accuracy of the spin-one and spin-half options of \emph{Spinsim}.
 			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
@@
 			Error is RMS error compared to a long running \emph{SciPy} baseline.}
-			\label{fig:benchmark_spin_one}
+			\label{fig:benchmark_spin}
 		\end{figure}
-		\begin{figure}[h!]
-			\begin{subfigure}[b]{0.475\textwidth}
-				\includegraphics[scale=0.475]{benchmark_spin_half_step_error.pdf}
-				% \caption{Accuracy of the spin-half options of \emph{spinsim}.}
-				\caption{}
-				\label{fig:benchmark_spin_half_step_error}
-			\end{subfigure}
-			\hfill
-			\begin{subfigure}[b]{0.475\textwidth}
-				\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.pdf}
-				% \caption{Speed vs accuracy of the spin-half options of \emph{spinsim}.}
-				\caption{}
-				\label{fig:benchmark_spin_half_execution_error}
-			\end{subfigure}
-			\caption{Speed and accuracy of the spin-half options of \emph{spinsim}.
-			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
-			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
-			Each technique was tested while both using and not using a transformation into a rotating frame.
-			Both execution time and error were recorded for each of the simulations.
-			Error is RMS error compared to a long running \emph{SciPy} baseline.}
-			\label{fig:benchmark_spin_half}
-		\end{figure}
+		% \begin{figure}[h!]
+		% 	\begin{subfigure}[b]{0.475\textwidth}
+		% 		\includegraphics[scale=0.475]{benchmark_spin_half_step_error.png}
+		% 		% \caption{Accuracy of the spin-half options of \emph{Spinsim}.}
+		% 		\caption{}
+		% 		\label{fig:benchmark_spin_half_step_error}
+		% 	\end{subfigure}
+		% 	\hfill
+		% 	\begin{subfigure}[b]{0.475\textwidth}
+		% 		\includegraphics[scale=0.475]{benchmark_spin_half_execution_error.png}
+		% 		% \caption{Speed vs accuracy of the spin-half options of \emph{Spinsim}.}
+		% 		\caption{}
+		% 		\label{fig:benchmark_spin_half_execution_error}
+		% 	\end{subfigure}
+		% 	\caption{Speed and accuracy of the spin-half options of \emph{Spinsim}.
+		% 	A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
+		% 	In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+		% 	Each technique was tested while both using and not using a transformation into a rotating frame.
+		% 	Both execution time and error were recorded for each of the simulations.
+		% 	Error is RMS error compared to a long running \emph{SciPy} baseline.}
+		% 	\label{fig:benchmark_spin_half}
+		% \end{figure}
 
 	\subsection{Comparison to alternatives}
-		We ran the same error and execution time benchmarks on some alternative packages, listed in Table \ref{tab:external}, to compare \emph{spinsim}'s performance to theirs.
+		We ran the same error and execution time benchmarks on some alternative packages, listed in Table~\ref{tab:external}, to compare \emph{Spinsim}'s performance to theirs.
 		\begin{table}[h!]
-			\caption{The software packages used for and verification of \emph{spinsim}.}
+			\caption{The software packages used for and verification of \emph{Spinsim}.}
 			\label{tab:external}
@@
 				\hline
-				spinsim														&\texttt{Simulator()}				&The best performing \emph{spinsim} configuration, using the CF4 integrator and the rotating frame mode. This was run both on CPU and GPU.
+				Spinsim													&\texttt{Simulator()}				&The best performing \emph{Spinsim} configuration, using the CF4 integrator and the rotating frame mode. This was run both on CPU and GPU.
 				\\
@@
 				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
-				Like \emph{spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\
+				Like \emph{Spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\
 				\hline
@@
 
-		Similarly to the internal \emph{spinsim} benchmarks\note{section???}, the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error via Equation \eqref{eq:error}.
+		Similarly to the internal \emph{Spinsim} benchmarks (see Section~\nameref{sec:accuracy}), the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error via Equation~\eqref{eq:error}.
 		Again, we used the longest running \emph{SciPy} simulation as a baseline for comparison, as the accuracy of \emph{Mathematica} plateaus at small time-steps.
-		Functions used for sampling were compiled to \emph{LLVM} and \emph{cython} in \emph{spinsim} and \emph{QuTip} respectively.
+		Functions used for sampling were compiled to \emph{LLVM} and \emph{cython} in \emph{Spinsim} and \emph{QuTip} respectively.
 		in both cases, the time taken to complete a simulation was measured using a second simulation using the already compiled functions, to represent the use-case of sweeping through many simulations.
@@
 		Multithreading was not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time-step already consumes over 11 hours of computational time.
-		Regardless, for a fair comparison, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8 (dotted line in Figures \ref{fig:benchmark_spin_one_execution_error} and \ref{fig:benchmark_spin_half_execution_error}), which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor.
-		Simulations from \emph{spinsim} and \emph{QuTip} automatically run multithreaded, so this comparison is not plotted for these packages.
-
-		From Figure \ref{fig:benchmark_external}, for any given error tolerance, \emph{spinsim} is over 3 orders of magnitude faster than \emph{Mathematica} and \emph{QuTip}, and 4 orders of magnitude more accurate than \emph{SciPy}.
-		In practice, this means that a 25 minute \emph{SciPy} simulation is reduced to 50ms, and a three week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic requirement for testing quantum sensing protocols) would take less than one minute in \emph{spinsim}.
+		Regardless, for a fair comparison, both \emph{Mathematica} and \emph{SciPy} results are plotted with an artificial reduction in execution time by a factor of 8 (dotted line in Figures~\ref{fig:benchmark_spin_one_execution_error} and~\ref{fig:benchmark_spin_half_execution_error}), which is an upper bound for the speed increase that could be obtained by running them parallel on an 8 core processor.
+		Simulations from \emph{Spinsim} and \emph{QuTip} automatically run multithreaded, so this comparison is not plotted for these packages.
+
+		From Figure~\ref{fig:benchmark_external}, for any given error tolerance, \emph{Spinsim} is over 3 orders of magnitude faster than \emph{Mathematica} and \emph{QuTip}, and 4 orders of magnitude more accurate than \emph{SciPy}.
+		In practice, this means that a 25 minute \emph{SciPy} simulation is reduced to 50ms, and a three week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic requirement for testing quantum sensing protocols) would take less than one minute in \emph{Spinsim}.
 		\begin{figure}[h!]
-			\includegraphics[scale=0.9]{benchmark_external_execution_error.pdf}
+			\centering
+			\includegraphics[scale=0.475]{benchmark_external_execution_error.png} % 0.9
 			\caption{Speed vs accuracy of two alternative integration packages.
@@
 	\subsection{Parallelisation performance}
-		Once the algorithm behind \emph{spinsim} was developed, we wanted to check its execution speed while running on various devices.
+		Once the algorithm behind \emph{Spinsim} was developed, we wanted to check its execution speed while running on various devices.
 		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), and highly procedural devices (being CPUs).
 		Speed benchmarks were performed using \texttt{neural-sense.sim.benchmark}, by comparing the evaluation speed of typical spin-one sensing experiments on different devices.
-		Results are of these benchmarks are shown in Figure \ref{fig:benchmark_device_aggregate}.
+		Results are of these benchmarks are shown in Figure~\ref{fig:benchmark_device_aggregate}.
 		The integration code was compiled by \texttt{numba} for multicore CPUs, CPUs running single threaded, and \emph{Nvidia Cuda} compatible GPUs.
 		The compiled code was then run on different models of each of these devices.
-		These test devices are given in Table \ref{tab:devices}.
+		These test devices are given in Table~\ref{tab:devices}.
 
@@
 			\centering
-			\includegraphics[scale=0.7]{benchmark_device_aggregate.pdf}
+			\includegraphics[scale=0.6]{benchmark_device_aggregate.png}
 			\caption{Evaluation speed of a simulation of a typical spin-one sensing experiment on both CPUs and GPUs.
@@
 
-		The results in Figure \ref{fig:benchmark_device_aggregate} show the benefit to using parallelisation when solving a spin system problem.
+		The results in Figure~\ref{fig:benchmark_device_aggregate} show the benefit to using parallelisation when solving a spin system problem.
 		Moving from the 6 core \emph{Core i7-8750H} CPU to the 12 core \emph{Ryzen 9 5900X} CPU doubles the execution speed, as does moving from the 384 core \emph{Quadro K620} GPU to the 768 core \emph{Quadro T1000} GPU.
@@
 
-		Users can view \ref{fig:benchmark_device_aggregate} to decide on how much their current or future hardware will be able to take advantage of \emph{spinsim}'s parallelism.
-		% Figure \ref{fig:benchmark_device_aggregate} can be used by potential \emph{spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
-		Another factor not shown in the plot is that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilise the entire CPU (as it should).
+		Users can view~\ref{fig:benchmark_device_aggregate} to decide on how much their current or future hardware will be able to take advantage of \emph{Spinsim}'s parallelism.
+		% Figure~\ref{fig:benchmark_device_aggregate} can be used by potential \emph{Spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
+		Another factor not shown in the plot is that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilize the entire CPU (as it should).
 		In contrast, this does not happen when running a GPU based program, as it requires very little CPU utilisation to function.
@@
 	\subsection{Testing}
-		During the accuracy tests, it was confirmed that all possible modes of \emph{spinsim} agree with a baseline \emph{SciPy} simulation, as close as the user wants up to the error of $ 10^{-11} $ of that baseline.
-		Therefore, \emph{spinsim} can be trusted for accuracy.
+		During the accuracy tests, it was confirmed that all possible modes of \emph{Spinsim} agree with a baseline \emph{SciPy} simulation, as close as the user wants up to the error of $ 10^{-11} $ of that baseline.
+		Therefore, \emph{Spinsim} can be trusted for accuracy.
 		The Lie Trotter matrix exponentiator was tested separately from the full system, as well as benchmarked separately against \texttt{scipy.linalg.expm()} from \emph{SciPy}.
@@
 
-		The kernel execution was profiled thoroughly, and changes were made to optimise VRAM and register usage and transfer.
+		The kernel execution was profiled thoroughly, and changes were made to optimize VRAM and register usage and transfer.
 		This was done specifically for the development hardware of the \emph{GeForce GTX 1070}, so one may get some performance increases by changing some GPU specific meta parameters when instantiating the \texttt{spinsim.Simulator} object.
 
-		A good way to confirm that \emph{spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
-		Otherwise, one can reproduce the benchmarks shown here using \texttt{neural\_sense.sim.benchmark}.
+		A good way to confirm that \emph{Spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
+		Otherwize, one can reproduce the benchmarks shown here using \texttt{neural\_sense.sim.benchmark}.
 
@@
 For \emph{Cuda} mode to function, one also needs to install the \emph{Nvidia Cuda} toolkit\cite{noauthor_cuda_2013}.
-If \emph{Cuda} is not available on the system, the simulator will automatically parallelise over multicore CPUs instead.
+If \emph{Cuda} is not available on the system, the simulator will automatically parallelize over multicore CPUs instead.
 
@@
 	\subsection{Use potential and limitations}
-		\emph{spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin-half or spin-one systems.
+		\emph{Spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin-half or spin-one systems.
 		This is immediately relevant to developing new quantum sensing protocols with spin-half and spin-one systems.
@@
 		Rubidium BECs can potentially be made sensitive enough to these tiny magnetic fields that they can be measured by them.
-		\emph{spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin-one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
+		\emph{Spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin-one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
 		The package is also now being used to simulate other BEC magnetometry experiments by the lab group.
@@
 		Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
-		A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs\cite{parashar_axon_2020}, which is something that \emph{spinsim} could be useful for.
-
-		\emph{spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
+		A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs\cite{parashar_axon_2020}, which is something that \emph{Spinsim} could be useful for.
+
+		\emph{Spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
 		This means that it would not be able to integrate large arrays of entangled states or interacting particles.
 		As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
-		In addition, \emph{spinsim} is currently designed to integrate the time evolution of pure states only.
+		In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only.
 		This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation\cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).
 
-		With these restrictions in mind, \emph{spinsim} could be used for some simplified simulations in various areas of NMR.
-		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14)\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{spinsim} could be used to simulate for spectroscopy experiments, for example.
-		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin-one nuclei\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+		With these restrictions in mind, \emph{Spinsim} could be used for some simplified simulations in various areas of NMR.
+		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14)\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{Spinsim} could be used to simulate for spectroscopy experiments, for example.
+		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{Spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin-one nuclei\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
 		This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
 		Another possible use-case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
-		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{spinsim} simulations of spins at different positions in space.
-		While this package offers some advantages over state of the art simulators in the field\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrised pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
+		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{Spinsim} simulations of spins at different positions in space.
+		While this package offers some advantages over state of the art simulators in the field\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrized pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
 
 	\subsection{Support}
-		Documentation for \emph{spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
+		Documentation for \emph{Spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
 		This documentation contains a thorough tutorial on how to use the package, and installation instructions.
 
-		For direct support with the \emph{spinsim} package, one can open an issue in the \emph{github} repository.
+		For direct support with the \emph{Spinsim} package, one can open an issue in the \emph{github} repository.
 		One can also use this contact to suggest extensions to the package.
-		\emph{spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
+		\emph{Spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
 
@@
 Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group.
-In particular, Hamish Taylor, Travis Hartley and Chris Bounds, who have started using \emph{spinsim} for their own projects and have given useful feedback of their user experience with the package.
+In particular, Hamish Taylor, Travis Hartley and Chris Bounds, who have started using \emph{Spinsim} for their own projects and have given useful feedback of their user experience with the package.
 

### 2021-07-14 docs/source/conf.py
v0.4.4: Added number_of_core parameter

@@ -40,7 +40,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.3'
+release = '0.4.4'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-07-14 spinsim/__init__.py

@@ -28,7 +28,7 @@ class SpinQuantumNumber(Enum):
         Eigenstates of the spin operators for quick reference.
     """
 
-    def __init__(self, value, dimension, label):
+    def __init__(self, value:float, dimension:int, label:str):
         super().__init__()
         self._value_ = value
         self.dimension = dimension
@@ -103,7 +103,7 @@ class ExponentiationMethod(Enum):
     index : :obj:`int`
         A reference number, used when compiling the integrator, where higher level objects like enums cannot be interpreted.
     """
-    def __init__(self, value, index):
+    def __init__(self, value:str, index:int):
         super().__init__()
         self._value_ = value
         self.index = index
@@ -136,7 +136,7 @@ class Device(Enum):
     .. _Supported Numpy features: http://numba.pydata.org/numba-doc/latest/reference/numpysupported.html
     .. _Supported CUDA Python features: http://numba.pydata.org/numba-doc/latest/cuda/cudapysupported.html
     """
-    def __init__(self, value, index):
+    def __init__(self, value:"str", index:int):
         super().__init__()
         self._value_ = value
         self.index = index
@@ -296,7 +296,7 @@ class Results:
         
         * **spin** (:obj:`numpy.ndarray` of :obj:`numpy.float64` (time_index, spatial_direction)) - The expected spin projection (Bloch vector) over time.
     """
-    def __init__(self, time, time_evolution, state, spin_calculator):
+    def __init__(self, time:np.ndarray, time_evolution:np.ndarray, state:np.ndarray, spin_calculator:callable):
         """
         Parameters
         ----------
@@ -324,7 +324,7 @@ class Results:
         self.state = state
         self.spin_calculator = spin_calculator
 
-    def __getattr__(self, attr_name):
+    def __getattr__(self, attr_name:str) -> np.ndarray:
         if attr_name == "spin":
             spin = self.spin_calculator(self.state)
             setattr(self, attr_name, spin)
@@ -346,6 +346,8 @@ class Simulator:
         That is, whether the integrator is compiled for a CPU or GPU.
         Defaults to :obj:`Device.CUDA` if the system it is being run on is Nvidia Cuda compatible, and defaults to :obj:`Device.CPU` otherwise.
         See :obj:`Device` for all options and more details.
+    number_of_threads : :obj:`int`
+        The number of CPU threads to use when running on a CPU device.
     get_time_evolution : :obj:`callable`
[…]

### 2021-07-16 article/article.tex
debugging

@@
 		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}~\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{Spinsim} was written for).
-		This simulation involves continuously driving transitions in the system for $ 100\,\mathrm{ms} $, while exposing it to a short 1ms pulsed signal that the system should be able to sense.
+		This simulation involves continuously driving transitions in the system for $ 100\,\mathrm{ms} $, while exposing it to a $ 1\,\mathrm{ms} $ pulsed signal that the system should be able to sense.
+		The system has the hamiltonian
+		\begin{align}
+			H(t) = \omega J_z + 2\Omega\cos(\omega t)J_x + \Omega_p p_\Omega(t - t_p) J_z,\label{eq:neural_pulse}
+		\end{align}
+		where $ \omega = 2\pi\cdot700\,\mathrm{kHz} $, $ \Omega = 2\pi\cdot1\,\mathrm{kHz} $,$ \Omega_p = 2\pi\cdot70\,\mathrm{Hz} $, $ t_p = 233\,\mathrm{ms} $ and $ p_\Omega(t) $ is a single cycle of a sine wave wth frequency $ \Omega $.
+
 		We first wanted to test the accuracy of the different integration techniques for various integration time-steps.
@@
 			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+			See Equation~\eqref{eq:neural_pulse}.
 			Each technique was tested while both using and not using a transformation into a rotating frame.
@@
 			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+			See Equation~\eqref{eq:neural_pulse}.
 			Both execution time and error were recorded for each of the simulations.
@@
 			Transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+			See Equation~\eqref{eq:neural_pulse}.
 			Evaluation time is determined by an average of 100 similar simulations for each device, where each individual simulation varies in dressing amplitude (transition frequency).}

### 2021-07-16 docs/source/conf.py

@@ -40,7 +40,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.3'
+release = '0.4.9'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-07-16 spinsim/__init__.py

@@ -28,7 +28,7 @@ class SpinQuantumNumber(Enum):
         Eigenstates of the spin operators for quick reference.
     """
 
-    def __init__(self, value, dimension, label):
+    def __init__(self, value:np.float64, dimension:int, label:str):
         super().__init__()
         self._value_ = value
         self.dimension = dimension
@@ -103,7 +103,7 @@ class ExponentiationMethod(Enum):
     index : :obj:`int`
         A reference number, used when compiling the integrator, where higher level objects like enums cannot be interpreted.
     """
-    def __init__(self, value, index):
+    def __init__(self, value:str, index:int):
         super().__init__()
         self._value_ = value
         self.index = index
@@ -136,7 +136,7 @@ class Device(Enum):
     .. _Supported Numpy features: http://numba.pydata.org/numba-doc/latest/reference/numpysupported.html
     .. _Supported CUDA Python features: http://numba.pydata.org/numba-doc/latest/cuda/cudapysupported.html
     """
-    def __init__(self, value, index):
+    def __init__(self, value:str, index:int):
         super().__init__()
         self._value_ = value
         self.index = index
@@ -296,7 +296,7 @@ class Results:
         
         * **spin** (:obj:`numpy.ndarray` of :obj:`numpy.float64` (time_index, spatial_direction)) - The expected spin projection (Bloch vector) over time.
     """
-    def __init__(self, time, time_evolution, state, spin_calculator):
+    def __init__(self, time:np.ndarray, time_evolution:np.ndarray, state:np.ndarray, spin_calculator:callable):
         """
         Parameters
         ----------
@@ -324,7 +324,7 @@ class Results:
         self.state = state
         self.spin_calculator = spin_calculator
 
-    def __getattr__(self, attr_name):
+    def __getattr__(self, attr_name:str) -> np.ndarray:
         if attr_name == "spin":
             spin = self.spin_calculator(self.state)
             setattr(self, attr_name, spin)
@@ -346,6 +346,8 @@ class Simulator:
         That is, whether the integrator is compiled for a CPU or GPU.
         Defaults to :obj:`Device.CUDA` if the system it is being run on is Nvidia Cuda compatible, and defaults to :obj:`Device.CPU` otherwise.
         See :obj:`Device` for all options and more details.
+    number_of_threads : :obj:`int`
+        The number of CPU threads to use when running on a CPU device.
     get_time_evolution : :obj:`callable`
[…]

### 2021-07-20 docs/source/conf.py
Updated plots

@@ -40,7 +40,7 @@ copyright = '2020, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.9'
+release = '0.4.16'
 
 
 # -- General configuration ---------------------------------------------------

### 2021-07-20 example.py

@@ -9,7 +9,7 @@ def get_field_larmor(time_sample, sweep_parameters, field_sample):
    field_sample[2] = math.tau*1000  # Split spin z eigenstates by 1kHz
 
 # Initialise simulator instance
-simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF)
+simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF, device = spinsim.Device.CPU)
 # Evaluate a simulation
 results_larmor = simulator_larmor.evaluate(0e-3, 100e-3, 100e-9, 500e-9, spinsim.SpinQuantumNumber.HALF.plus_x)
 
@@ -23,41 +23,41 @@ plt.ylabel("spin expectation (hbar)")
 plt.title("Spin projection for Larmor precession")
 plt.show()
 
-import spinsim
-import matplotlib.pyplot as plt
-import math
+# import spinsim
+# import matplotlib.pyplot as plt
+# import math
 
-# Define field for spin system
-def get_field_rabi(time_sample, sweep_parameters, field_sample):
-   # Dress atoms from the x direction, Rabi flopping
-   field_sample[0] = 2*sweep_parameters[1]*math.cos(sweep_parameters[0]*time_sample)
-   field_sample[1] = 0                    # Zero field in y direction
-   field_sample[2] = sweep_parameters[0]  # Split spin z eigenstates
-   field_sample[3] = 0                    # Zero quadratic shift, found in spin one systems
+# # Define field for spin system
+# def get_field_rabi(time_sample, sweep_parameters, field_sample):
+#    # Dress atoms from the x direction, Rabi flopping
+#    field_sample[0] = 2*sweep_parameters[1]*math.cos(sweep_parameters[0]*time_sample)
+#    field_sample[1] = 0                    # Zero field in y direction
+#    field_sample[2] = sweep_parameters[0]  # Split spin z eigenstates
+#    field_sample[3] = 0                    # Zero quadratic shift, found in spin one systems
 
-# Initialise simulator instance
[…]

### 2021-07-20 spinsim/__init__.py

@@ -617,7 +617,7 @@ class Simulator:
                 return
             transform_frame = transform_frame_lab
 
-        get_field_jit = jit_device(get_field)
+        get_field_jit = jit_device_template("(float64, float64[:], float64[:])")(get_field)
 
         if integration_method == IntegrationMethod.MAGNUS_CF4:
             @jit_device_template("(float64[:], float64, float64, float64, float64[:, :], float64, complex128[:])")
@@ -948,9 +948,9 @@ class Simulator:
         results : :obj:`Results`
             An object containing the results of the simulation.
         """
-        if math.fabs(time_step_output/time_step_integration - round(time_step_output/time_step_integration)) > 1e-6:
-            time_step_integration_old = time_step_integration
-            time_step_integration = time_step_output/round(max(time_step_output/time_step_integration, 1))
+        time_step_integration_old = time_step_integration
+        time_step_integration = time_step_output/round(max(time_step_output/time_step_integration, 1))
+        if math.fabs(time_step_output/time_step_integration_old - round(time_step_output/time_step_integration_old)) > 1e-6:
             print(f"\033[33mspinsim warning!!!\ntime_step_output ({time_step_output:8.4e}) not an integer multiple of time_step_integration ({time_step_integration_old:8.4e}). Resetting time_step_integration to {time_step_integration:8.4e}.\033[0m\n")
 
         time_end_points = np.asarray([time_start, time_end], np.float64)
@@ -1474,7 +1474,6 @@ class Utilities:
         if number_of_hypercubes < 0:
             number_of_hypercubes = 0
         trotter_precision = 4**number_of_hypercubes
-        # print(type(trotter_precision), trotter_precision)
 
         @jit_device
         def conj(z):

### 2021-07-20 article/article.tex
Updated plots
Article edits (plot references)

@@
 
-		To choose an appropriate value of $ \mathrm{d}t $, users can use the accuracy plots in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error} in Section~\nameref{sec:accuracy}.
+		To choose an appropriate value of $ \mathrm{d}t $, users can refer to the accuracy plots in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error} under \emph{\nameref{sec:accuracy}}.
 % \note{How do I reference a section if they don't have number labels in the finished article?
@@
 			\includegraphics[scale=0.475]{architecture.png}
-			\caption{The structure of \emph{Spinsim}}
+			\caption{
+				The mathematical and computational breakdown of \emph{Spinsim}.
+				The procedural problem of evaluating the state time series $ \psi_k $ is broken into the parallel problem of evaluating time-evolution operators $ \mathcal{U}_k $.
+				Each of the $ \mathcal{U}_k $ are found independently on a separate GPU thread.
+				The problem is brought into a dynamic rotating frame to increase numerical accuracy.
+				The $ U_k $ are broken further into time-stepping operators $ u_k $, each of which are evaluated using the Magnus CF4 method.
+				Matrix exponentials are evaluated using a Lie-Trotter based method, including a residual squaring technique to avoid over-squaring.
+			}
 			\label{fig:architecture}
@@
 
-		Similarly to the internal \emph{Spinsim} benchmarks (see Section~\nameref{sec:accuracy}), the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error via Equation~\eqref{eq:error}.
+		Similarly to the internal \emph{Spinsim} benchmarks (see \emph{\nameref{sec:accuracy}}), the expected spin projection was evaluated in each case, but only the states were compared to calculate a relative error via Equation~\eqref{eq:error}.
 		Again, we used the longest running \emph{SciPy} simulation as a baseline for comparison, as the accuracy of \emph{Mathematica} plateaus at small time-steps.
@@
 
-\textcolor{blue}{If the software resulted from funded research please give the funder and grant number.}
+% \textcolor{blue}{If the software resulted from funded research please give the funder and grant number.}
+AT acknowledges support through an Australian Government Research Training Program Scholarship.
+LDT acknowledges funding from the Australian Research Council Linkage Project LP200100082.
 

### 2021-07-20 article/article.tex
Mention scqubits
Remove linebreak

@@
 		For a use-case example, an MRI experimenter might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
-		To do this they could choose to set \texttt{sweep\_parameters = [x, y]},\linebreak and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.
+		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.% \linebreak
 		This feature is demonstrated with examples in the documentation.
@@
 				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
+				Some quantum mechanics simulation packages such as the recent \emph{scqubits}~\cite{groszkowski_scqubits_2021} use \emph{QuTip} for calculating time evolution.
 				Like \emph{Spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\

### 2021-07-23 article/article.tex
Paper: Info on James and Russ

@@
 4. School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
+	Present address: Q-CTRL Pty. Ltd.\\
 	Original conception of first version of code.\\
@@
 	% \texttt{AtomicPy}\cite{morris_qcmonkatomicpy_2018}
-	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schroedinger equation for quantum sensing spin systems.
+	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schr\"odinger equation for quantum sensing spin systems.
 	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of modelling all effects of the system.
@@
 
-	Second, the Schroedinger equation has the geometric property of being norm persevering.
+	Second, the Schr\"odinger equation has the geometric property of being norm persevering.
 	In other words, the time-evolution operator for a system between two points in time must be unitary.
-	As such, numerical solutions to the Schroedinger equation should also preserve this property.
+	As such, numerical solutions to the Schr\"odinger equation should also preserve this property.
 	For many numerical methods like those in the Runge Kutta family, the approximations used might not be norm preserving, and the evaluated quantum state may diverge towards an infinite norm, or converge to zero if run for many iterations.
@@
 	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
-	Examples include calculating colours for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
+	Examples include calculating colors for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
 	By finding ways to parallelize the problem of solving quantum spin systems, we can use the many cores of a GPU to our advantage in this context as well.
@@
 In addition, rather than being represented by standard coordinates in $ \mathbb{C}^{N \times N} $, in \emph{Spinsim} the Hamiltonian $ H(t) $ is instead represented with respect to a choice of basis for the corresponding Lie Algebra, $ \mathfrak{su}(N) $.
-For example, when set to spin-half mode, the \emph{Spinsim} package solves the time dependent Schroedinger equation of the form
+For example, when set to spin-half mode, the \emph{Spinsim} package solves the time dependent Schr\"odinger equation of the form
 
@@
 
-		% Similarly, when \emph{Spinsim} is set to spin-one mode, it can solve the Schroedinger equation of the form
+		% Similarly, when \emph{Spinsim} is set to spin-one mode, it can solve the Schr\"odinger equation of the form
 
@@
 	School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
-	Original conception of first version of code.\\
+	Present address: Q-CTRL Pty. Ltd.\\
+	Original conception of first version of code, with minor contributions to released packages.\\
 5. James Saunderson\\
@@
 AT acknowledges support through an Australian Government Research Training Program Scholarship.
-LDT acknowledges funding from the Australian Research Council Linkage Project LP200100082.
+JS is the recipient of an Australian Research Council Discovery Early Career Researcher Award (project number DE210101056) funded by the Australian Government.
+% JS acknowledges funding from the Australian Research Council Discovery Early Career Researcher Award (project number DE210101056) funded by the Australian Government..
+LDT acknowledges funding from the Australian Research Council Linkage Project (project number LP200100082).
 

### 2021-07-23 example.py

@@ -9,7 +9,7 @@ def get_field_larmor(time_sample, sweep_parameters, field_sample):
    field_sample[2] = math.tau*1000  # Split spin z eigenstates by 1kHz
 
 # Initialise simulator instance
-simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF, device = spinsim.Device.CPU)
+simulator_larmor = spinsim.Simulator(get_field_larmor, spinsim.SpinQuantumNumber.HALF)
 # Evaluate a simulation
 results_larmor = simulator_larmor.evaluate(0e-3, 100e-3, 100e-9, 500e-9, spinsim.SpinQuantumNumber.HALF.plus_x)
 
@@ -23,41 +23,41 @@ plt.ylabel("spin expectation (hbar)")
 plt.title("Spin projection for Larmor precession")
 plt.show()
 
-# import spinsim
-# import matplotlib.pyplot as plt
-# import math
+import spinsim
+import matplotlib.pyplot as plt
+import math
 
-# # Define field for spin system
-# def get_field_rabi(time_sample, sweep_parameters, field_sample):
-#    # Dress atoms from the x direction, Rabi flopping
-#    field_sample[0] = 2*sweep_parameters[1]*math.cos(sweep_parameters[0]*time_sample)
-#    field_sample[1] = 0                    # Zero field in y direction
-#    field_sample[2] = sweep_parameters[0]  # Split spin z eigenstates
-#    field_sample[3] = 0                    # Zero quadratic shift, found in spin one systems
+# Define field for spin system
+def get_field_rabi(time_sample, sweep_parameters, field_sample):
+   # Dress atoms from the x direction, Rabi flopping
+   field_sample[0] = 2*sweep_parameters[1]*math.cos(sweep_parameters[0]*time_sample)
+   field_sample[1] = 0                    # Zero field in y direction
+   field_sample[2] = sweep_parameters[0]  # Split spin z eigenstates
+   field_sample[3] = 0                    # Zero quadratic shift, found in spin one systems
 
-# # Initialise simulator instance
[…]

### 2021-11-08 article/article.tex
Article update 8

@@
 \section{Title}
-Spinsim: a GPU optimized simulator of spin-half and spin-one quantum systems
+% Spinsim: a GPU optimized simulator of spin-half and spin-one quantum systems
+Spinsim: a GPU optimized python package for simulating spin-half and spin-one quantum systems
 
@@
 	Present address: Q-CTRL Pty. Ltd.\\
-	Original conception of first version of code.\\
+	Original conception of first version, and advice on current version of code.\\
 5. Department of Electrical and Computer Systems Engineering, Monash University, Victoria 3800, Australia.\\
@@
 	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
-	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelisation. 
-	Along with other optimisations, this allows for speed improvements of up to four orders of magnitude while keeping staying just as accurate.
-	\emph{Spinsim} is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
-	The initial use-case for the package will be to simulate quantum sensing-based Bose Einstein condensate (BEC) experiments for the Monash University School of Physics and Astronomy spinor BEC lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
-	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin-one systems of nitrogen vacancy centres (NVCs) and BECs.
+	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelization. 
+	Along with other optimizations, this allows for speed improvements of up to four orders of magnitude while staying just as accurate, compared to industry standard packages.
+	It is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
+	The initial use-case for the \emph{Spinsim} will be to simulate quantum sensing-based ultracold atom experiments for the Monash University School of Physics \& Astronomy spinor Bose-Einstein condensate (spinor BEC) lab, but we anticipate it will be useful in simulating any range of spin-half or spin-one quantum systems with time dependent Hamiltonians that cannot be solved analytically.
+	These appear in the fields of nuclear magnetic resonance (NMR), nuclear quadrupole resonance (NQR) and magnetic resonance imaging (MRI) experiments and quantum sensing, and with the spin-one systems of nitrogen vacancy centres (NVCs), ultracold atoms, and BECs.
 
 \section{Keywords}
-Time dependent Schr\"odinger equation; Quantum; Physics; Spin one; Spin half; Integrator; Exponentiator; GPU; Parallel computing; Solver; python; numba;
+Time dependent Schr\"odinger equation; Quantum; Physics; Spin one; Spin half; Integrator; Exponentiator; GPU; Parallel computing; Solver; Python; Numba; Sensing;
 
@@
 \subsection{Motivation}
-	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing\cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
+	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing~\cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
 	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
@@
 	The design of sensing protocols requires many steps of verification, including simulation.
-	This is especially important, since running real experiments can be expensive and time consuming, and thus it is more practical to debug such protocols quickly and cheaply on a computer.
+	This is especially important, since running real experiments can be expensive and time consuming, so it is more practical to debug such protocols quickly and cheaply on a computer.
 	In general, any design of experiments using spin systems could benefit from a fast, accurate method of simulation.
 
-	% \texttt{AtomicPy}\cite{morris_qcmonkatomicpy_2018}
-	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package is based, and standard differential equation solvers (such as \emph{Mathematica}'s function \texttt{NDSolve}) to solve the Schr\"odinger equation for quantum sensing spin systems.
-	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of modelling all effects of the system.
+	% \texttt{AtomicPy}~\cite{morris_qcmonkatomicpy_2018}
+	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package, \emph{Spinsim}, is based, and standard differential equation solvers (such as \emph{Mathematica}'s~\cite{wolfram_research_inc_mathematica_2020} function \texttt{NDSolve}) to solve the Schr\"odinger equation for quantum sensing spin systems.
+	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of not modelling all effects in the system.
 	However, these methods are not completely optimized for our use-case, and therefore come with some issues.
@@
 	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
+	Given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
+	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
+	Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
+	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
+	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by three orders of magnitude.
 
@@
 	In other words, the time-evolution operator for a system between two points in time must be unitary.
-	As such, numerical solutions to the Schr\"odinger equation should also preserve this property.
-	For many numerical methods like those in the Runge Kutta family, the approximations used might not be norm preserving, and the evaluated quantum state may diverge towards an infinite norm, or converge to zero if run for many iterations.
+	As such, numerical solutions to the Schr\"odinger equation should also preserve norms.
+	For many numerical methods like those in the Runge Kutta family, the approximations used are in general not norm preserving, so the evaluated quantum state may diverge towards an infinite norm, or converge to zero if run for many iterations.
+	To avoid this, we use a geometric integration technique for our solver (see \emph{\nameref{sec:magnus}}).
 
@@
 	Standard integration methods require very small time-steps in order to accurately depict these oscillations.
-
-	Given the recent boom in machine learning, many research computers are now equipped with advanced graphics processing units (GPUs).
-	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
-	Examples include calculating colors for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
-	By finding ways to parallelize the problem of solving quantum spin systems, we can use the many cores of a GPU to our advantage in this context as well.
+	For this reason we use a fourth order Magnus expansion~\cite{magnus_exponential_1954,blanes_magnus_2009} based solver for our geometric integrator to make larger time-steps accurate (see \emph{\nameref{sec:magnus}}).
+	We also use a dynamically changing rotating frame to slow down the effective rotations in the system, and thus reduce the size of integration steps being done, making each step more accurate (see \emph{\nameref{sec:rotating_frame}}).
+
+	% By finding ways to parallelize the problem of solving quantum spin systems, we can use the many cores of a GPU to our advantage in this context as well.
+
+	\subsection{Recent literature}
+		While we benchmark \emph{Spinsim} only against industry standard integrators, we also note that application specific quantum numerical simulator packages are regularly being released.
+		However, none of these packages are designed specific to quantum sensing, and so these releases are not suitable for simulations highly accurate at high time resolutions required in that field.
+
+		In quantum optimal control (QOC), researchers look at how to design robust pulse sequences to control spin systems using machine learning techniques.
+		Particularly, this means that simulators used here require automatic differentiation~\cite{griewank_who_2012}, which \emph{Spinsim} does not currently support.
+		A main use of QOC is to design control sequences in quantum computers.
+		Many of these pulse sequences are trains of hard pulses (which are physically constant bursts of radiation), which, if using the accuracy reducing rotating wave approximation (RWA), can have simplified time evolution operators.
+		This paradigm, used in the recent \emph{Qulacs}~\cite{suzuki_qulacs_2021}, \emph{QOpt}~\cite{teske_qopt_2021} and \emph{QSim}~\cite{isakov_simulations_2021}, is not suitable for accurately simulating more complicated (especially when looking from the lab frame of reference) pulse shapes found in quantum sensing.
+		However, all of these packages do allow for simulating entanglement (important for quantum computing, but not for all sensing applications), which \emph{Spinsim} does not and, like \emph{Spinsim}, all have versions optimised for parallelisation (although \emph{QSim} does sacrifice accuracy here for the sake of speed again, by using single-precision floats).
+		Dalgaard and Motzoi~\cite{dalgaard_fast_2021} have recently proposed Magnus integration techniques for use in QOC, but have not provided any open source implementation to do so.
+
+		% Three qubit such packages were published recently, being \emph{PULSEE}~\cite{candoli_pulsee_2021}, \emph{QOpt}~\cite{teske_qopt_2021} and ~\cite{isakov_simulations_2021}.
+		% While primarily focusing on being a complete toolkit for NMR simulations and quantum control optimization respectively, both contain Schr\"odinger equation solvers.
+		% Furthermore, neither package can take advantage of GPU parallelization.
+
+		Another application of simulations of spin systems is nuclear magnetic resonance (NMR).
+		In this field, the simulator part of the \emph{PULSEE}~\cite{candoli_pulsee_2021} package uses up to the 3rd order Magnus expansion just once to solve the complete system, rather than using it many times as a time stepping method.
+		Nested integrals of commutators are numerically evaluated on a CPU using Euler integration.
+		This is likely to be slow (due to the Euler-integrated nested integrals of commutators) and inaccurate (due to using the expansion over a large time step), and potentially not even convergent in general (also due to the large time step); although it may suffice for the kinds of problems this NMR simulation package is looking at.
+
+		% Designed for optimising quantum control protocols, the \emph{QOpt} package works in the paradigm of a time series of instructions, rather than the analytic forms used in \emph{Spinsim}.
+		% Given the solid grid of time series, this package cannot take advantage of the commutator free Magnus based techniques that \emph{Spinsim} employs.
+		% It may be able to model hard pulse sequences accurately (prevalent in quantum control), but will likely not be as accurate when modelling a continuous magnetic environment of a spin system.
+
+		% Finally, also just recently, Dalgaard and Motzoi~\cite{dalgaard_fast_2021} propose the use of Magnus expansion based techniques for simulations in quantum control optimization.
+		% However, they do not provide an implementation of their work.
 
@@
 		\end{align}
-		Here $ J_x $, $ J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices\cite[(p169)]{j_j_sakurai_jun_john_modern_2011} halved.
+		Here $ J_x $, $ J_y $ and $ J_z $ are spin operators, equal to the Pauli matrices~\cite[(p169)]{j_j_sakurai_jun_john_modern_2011} halved.
 		% \supervisordisagreement{
@@
 		In the spin-one case there is no standard basis of operators $ \mathcal{A}_j $.
-		Choices include the Gell-Mann matrices\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases\cite{hamley_spin-nematic_2012, di_dipolequadrupole_2010}.
+		Choices include the Gell-Mann matrices~\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases~\cite{hamley_spin-nematic_2012, di_dipolequadrupole_2010}.
 		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
@@
 
-		Note that $ Q $ is proportional to $ Q_{zz} $\cite{hamley_spin-nematic_2012} and $ Q_0 $\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
+		Note that $ Q $ is proportional to $ J_z^2 $ (up to a change in energy zero point), and $ Q_{zz} $~\cite{hamley_spin-nematic_2012} and $ Q_0 $~\cite{di_dipolequadrupole_2010} from alternative quadrupole bases.
 		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems in arbitrary bias fields, but with single-photon coupling.
-		This includes quadratic Zeeman splitting described by the Breit-Rabi formula\cite{mockler_atomic_1961} important to experiments in our lab.
+		This includes quadratic Zeeman splitting described by the Breit-Rabi formula~\cite{mockler_atomic_1961} important to experiments in our lab.
 		The \emph{Spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
@@
 		\end{align}
-		Here the additional operators are those defined in\cite{di_dipolequadrupole_2010}.
+		Here the additional operators are those defined in~\cite{di_dipolequadrupole_2010}.
 Note that this is included for completeness, but has not been thoroughly tested, as our lab has no physical context for modelling the $ U_1, U_2, V_1 $ and $ V_2 $ operators.
@@
 		% The matrices $ J_x, J_y, J_z $ are regular spin operators, and $ Q $ is a quadrupole operator.
-Note that $ Q $ is proportional to $ Q_{zz} $ as defined by Hamley et al\cite{hamley_spin-nematic_2012}, and $ Q_0 $ as defined by Di et al\cite{di_dipolequadrupole_2010}.
+Note that $ Q $ is proportional to $ Q_{zz} $ as defined by Hamley et al~\cite{hamley_spin-nematic_2012}, and $ Q_0 $ as defined by Di et al~\cite{di_dipolequadrupole_2010}.
 		% INLINE Q DIAG. WHY WE'VE PICKED THESE FOUR. For ground state spin-one atoms in a magnetic field, ... Breit Rabi ... . COULD BE READILY EXTENDED TO INCLUDE FURTHER ELEMENTS OR TO HIGHER SPINS.
@@
 		If this is done for an ensemble of systems, the average spin projection over all systems will converge to the expected value as calculated here.
-		As an alternative to solving the Schr\"odinger equation, if one is only interested in the dynamics of the expected spin projection, one can instead solve for $ \langle \overrightarrow{J}\rangle (t) $ directly using the Bloch equations\cite{bloch_nuclear_1946}.
+		As an alternative to solving the Schr\"odinger equation, if one is only interested in the dynamics of the expected spin projection, one can instead solve for $ \langle \overrightarrow{J}\rangle (t) $ directly using the Bloch equations~\cite{bloch_nuclear_1946}.
 		These are three coupled real equations as compared to three coupled complex equations for the spin-one Schr\"odinger equation.
@@
 
-	\subsection{Unitary time evolution and the Magnus expansion}
+	\subsection{Unitary time evolution and the Magnus expansion}\label{sec:magnus}
 		Since $H(t)$ is Hermitian, it follows from Equation~\eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
@@
 		\end{align}
-		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series\cite{blanes_magnus_2009}, where
+		% The act of integrating a linear differential equation by exponentiation can be generalised for time dependent Hamiltonians using the Magnus Series~\cite{blanes_magnus_2009}, where
 		For a time varying Hamiltonian, the general solution for $ \mathcal{U}(t, t_0) $ is much more complex, because it encapsulates the full solution to the time-dependent Schr\"{o}dinger equation.
-		The well known Dyson series\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
-		While the Dyson series has recently been used numerically\cite{kalev_integral-free_2020}, it is challenging to work with because once truncated, it is in general no longer unitary.
+		The well known Dyson series~\cite{kalev_integral-free_2020} gives an explicit expression for $ \mathcal{U}(t, t_0) $ in terms of multiple time integrals over nested time commutators of $ H(t') $.
+		While the Dyson series has recently been used numerically~\cite{kalev_integral-free_2020}, it is challenging to work with because once truncated, it is in general no longer unitary.
 
@@
 		\end{align}
-		As such, the Magnus series explicitly preserves unitarity when truncated\cite{magnus_exponential_1954}.
+		As such, the Magnus series explicitly preserves unitarity when truncated~\cite{magnus_exponential_1954}.
 		The terms in the Magnus series are integrals over nested time commutators of the Hermitian matrix $ A(t') $, where, in the case of quantum mechanics, $ A(t') = -iH(t') $.
-		For instance, the first three terms are\cite{blanes_magnus_2009}
+		For instance, the first three terms are~\cite{blanes_magnus_2009}
 		\begin{align}
@@
 
-		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi \approx 1.08686870\dots $\cite{blanes_magnus_2009}.
-		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < 1.08686870\dots $\cite{blanes_magnus_2009}.
-		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $\cite{blanes_magnus_2009}.
+		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi \approx 1.08686870\dots $~\cite{blanes_magnus_2009}.
+		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < 1.08686870\dots $~\cite{blanes_magnus_2009}.
+		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $~\cite{blanes_magnus_2009}.
 		Furthermore, each subsequent term in the expansion increases in complexity rapidly.
@@
 
-		Many unitary time-stepping techniques have been developed based on the Magnus expansion\cite{auer_magnus_2018}.
-		Some of these techniques use Gauss-Legendre quadrature sampling and the Baker–Campbell–Hausdorff formula to respectively avoid the integration and time commutators of the Hamiltonian, producing simple expressions that can be used for unitary time-stepping\cite{blanes_fourth-_2006}.
+		Many unitary time-stepping techniques have been developed based on the Magnus expansion~\cite{auer_magnus_2018}.
+		Some of these techniques use Gauss-Legendre quadrature sampling and the Baker–Campbell–Hausdorff formula to respectively avoid the integration and time commutators of the Hamiltonian, producing simple expressions that can be used for unitary time-stepping~\cite{blanes_fourth-_2006}.
 		% These take advantage of the Baker–Campbell–Hausdorff formula
@@
 		For spin-half, the exponentiator is in an analytic form in $ \omega_x, \omega_y $ and $ \omega_z $. % ... yz, which follows directly from eqref
-		For spin-one, an exponentiator based on the Lie-Trotter product formula\cite{moler_nineteen_2003}
+		For spin-one, an exponentiator based on the Lie-Trotter product formula~\cite{moler_nineteen_2003}
 		% Explicitly, this formula is
@@
 		\end{align}
-		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method\cite{barthel_optimized_2020} allow us to write 
+		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method~\cite{barthel_optimized_2020} allow us to write 
 		\begin{align}
@@
 		\end{align}
-		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \mathrm{arctan}2(\omega_y, \omega_x) $ (where $ \mathrm{arctan}2(y, x) $ is the two argument arctangent\cite{organick_fortran_1966}), $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
+		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \mathrm{arctan}2(\omega_y, \omega_x) $ (where $ \mathrm{arctan}2(y, x) $ is the two argument arctangent~\cite{organick_fortran_1966}), $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
 		The element-wise analytic form of this is
@@
 		We choose $ n $ to be of the form $ n = 2^\tau $, as raising matrices to powers of two can be done efficiently by iterative squaring.
-		This can be done just by iterative squaring, which requires a small number of operations.
-		While there are some loose upper bounds for the $ n $ required to reach a desired accuracy for the matrix exponential\cite{suzuki_generalized_1976}, using these to choose a value of $ n $ can, in practice, cause floating-point errors from over-squaring.
-		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}\cite{virtanen_scipy_2020}.
+		% This can be done just by iterative squaring, which requires a small number of operations.
+		While there are some loose upper bounds for the $ n $ required to reach a desired accuracy for the matrix exponential~\cite{suzuki_generalized_1976}, using these to choose a value of $ n $ can, in practice, cause floating-point errors from over-squaring.
+		Instead, we tested the formula on $ 10^5 $ matrices for different values of $ \tau $, and compared them to results given by \texttt{scipy.linalg.expm()}, from the popular python library \emph{SciPy}~\cite{virtanen_scipy_2020}.
 		We found that the error minimized after a number of squares of $ \tau = 24 $.
@@
 		This cannot be done by simply subtracting the identity from Equation~\eqref{eq:lie_trotter_4}, as doing so would introduce cancellation error.
-		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialized implementations of functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose\cite{hewlett-packard_hp_1994}.
+		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialized implementations of functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose~\cite{hewlett-packard_hp_1994}.
 		The identity is added to the result of the iterative residual squaring and the full exponential is returned.
@@
 
-	\subsection{Discretisation and parallelisation}
+	\subsection{Discretization and parallelization}\label{sec:parallelization}
 		Frequently we wish to sample the state at times $ t_k $ spaced more coarsely than the integration time-step.
@@
 		Hence, the time-evolution operators $ \mathcal{U}_k $ can be calculated in parallel.
-		% It allows \emph{Spinsim} to use GPU parallelisation on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
+		% It allows \emph{Spinsim} to use GPU parallelization on the level of time sample points, so a speed up is achieved even if just a single simulation is run.
 
@@
 
-		% Within each parallel discretisation, we ...
-		Beyond discretisation for parallelisation, we discretize our time-evolution operator into individual integration time-steps.
+		% Within each parallel discretization, we ...
+		Beyond discretization for parallelization, we discretize our time-evolution operator into individual integration time-steps.
 		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time-step $ \mathrm{d}t = \mathrm{D}t/L $.
@@
 		To choose an appropriate value of $ \mathrm{D}t $, users must consider three factors.
-		For the most benefit out of GPU parallelisation, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{Spinsim}.
+		For the most benefit out of GPU parallelization, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{Spinsim}.
 		Users should also make sure that $ \mathrm{D}t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \langle \overrightarrow{J}\rangle_k $ to be used in their further analysis.
@@
 
-	\subsection{Dynamically rotating frame}
-		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantisation axis (which is the $ z $ axis when representing spin operators with the Pauli matrices).
+	\subsection{Dynamically rotating frame}\label{sec:rotating_frame}
+		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantization axis (which is the $ z $ axis when representing spin operators with the Pauli matrices).
 		Transforming from the lab (standard) frame of reference into one rotating around this axis by rotation operator $ R_{\omega_r}(t) = \exp(i\omega_r J_z t) $, the resulting system follows a new Hamiltonian
@@
 		\end{align}
-		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite[(p336,338)]{j_j_sakurai_jun_john_modern_2011}.
-		This is almost always done to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ H_r(t) $ on average make minor contributions to time evolution, and can be ignored.
+		It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures~\cite[(p336,338)]{j_j_sakurai_jun_john_modern_2011}.
+		This is almost always done to enable the rotating wave approximation (RWA), which is an assumption that the oscillatory components of $ H_r(t) $ on average make minor contributions to time evolution, and can be ignored.
 		In some cases, this allows one to obtain analytic, but approximate, solutions to the quantum system.
@@
 		% % Put up the top
-		% It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures\cite{j_j_sakurai_jun_john_modern_1994}.
+		% It is a common technique in solving quantum mechanical problems to enter rotating frames, and their more abstract counterparts of interaction pictures~\cite{j_j_sakurai_jun_john_modern_1994}.
 		% This is typically done in to enable the Rotating Wave Approximation (RWA), which is an assumption that the oscillatory components of $ \omega^r_x, \omega^r_y, \omega^r_z, $ and $ \omega^r_q $ on an average make minor contributions to time evolution, and can be ignored.
@@
 	% \subsubsection{Magnus-based integration method}
-	% 	The integration method used in \emph{Spinsim} is the commutator free 4 (CF4) method from Auer et al\cite{auer_magnus_2018}, which based on the Magnus expansion.
+	% 	The integration method used in \emph{Spinsim} is the commutator free 4 (CF4) method from Auer et al~\cite{auer_magnus_2018}, which based on the Magnus expansion.
 Each of the $ \mathcal{U}_k $ are split into products of time evolution operators between times separated by a smaller time-step, that is,
@@
 
-		Each thread begins with initialisation of variables, which includes moving into the rotating frame.
+		Each thread begins with initialization of variables, which includes moving into the rotating frame.
 		It then starts a loop to find each of the time-stepping operators $ u^k_l $.
@@
 	\subsection{Compilation of integrator}
-		The \emph{Spinsim} integrator is constructed and compiled just in time, using the \emph{Numba}\cite{lam_numba_2015} python package.
-		This is achieved via the \texttt{numba.cuda.jit()} decorator, which compiles python functions into \emph{Nvidia Cuda}\cite{nickolls_scalable_2008} kernels using an LLVM\cite{lattner_llvm_2004} (Low Level Virtual Machine) compiler.
+		The \emph{Spinsim} integrator is constructed and compiled just in time, using the \emph{Numba}~\cite{lam_numba_2015} python package.
+		This is achieved via the \texttt{numba.cuda.jit()} decorator, which compiles python functions into \emph{Nvidia Cuda}~\cite{nickolls_scalable_2008} kernels using an LLVM~\cite{lattner_llvm_2004} (Low Level Virtual Machine) compiler.
 		The particular device functions used are not predetermined, but are instead chosen based on user input to decide on a closure.
@@
 
-		This functionality is interfaced through an object of class \texttt{spinsim.Simulator}.
+		Customization and execution of the simulator is interfaced through an object of class \texttt{spinsim.Simulator}.
 		The \emph{Cuda} kernel is defined as per the user’s instructions on construction of the instance, and it is used by calling the method \texttt{spinsim.Simulator.evaluate()}.
 		Users are returned an instance of \texttt{spinsim.Results} including the time, state, time-evolution operator, and expected spin projection.
-		Note that the expected spin projection is calculated as a lazy parameter if needed, rather than returned by the simulator object.
+		Note that, to avoid making unnecessary calculations, the expected spin projection is calculated as a lazy parameter if needed rather than returned by the simulator object.
 
@@
 		They can then set the value for \texttt{sweep\_parameters[]} for a particular simulation each time \texttt{spinsim.Simulator.evaluate()} is called.
-		As \texttt{sweep\_parameters[]} is a \texttt{numpy.ndarray}\cite{harris_array_2020}, one can use this functionality to sweep many parameters using the same simulator object.
-		For a use-case example, an MRI experimenter might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
+		As \texttt{sweep\_parameters[]} is a \texttt{numpy.ndarray}~\cite{harris_array_2020}, one can use this functionality to sweep many parameters using the same simulator object.
+		For a use-case example, an MRI experimentalist might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
 		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.% \linebreak
@@
 				\hline
-				QuTip\cite{johansson_qutip_2013}						&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
+				QuTip~\cite{johansson_qutip_2013}						&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
 				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
 				Some quantum mechanics simulation packages such as the recent \emph{scqubits}~\cite{groszkowski_scqubits_2021} use \emph{QuTip} for calculating time evolution.
-				Like \emph{Spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\
+				Like \emph{Spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelization.\\
 				\hline
-				Mathematica\cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
-				This was chosen as it is popular with our lab group for simulating magnetometry experiments.\\
+				Mathematica~\cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
+				This was chosen as it has been historically popular with our lab group for simulating quantum sensing experiments.\\
 				\hline
-				SciPy\cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
+				SciPy~\cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
 				This was chosen as a comparison to a generic solver from within the python ecosystem.
@@
 			Error is RMS error compared to a long running \emph{SciPy} baseline.
-			The \emph{Mathematica} and \emph{SciPy} results are also shown with a speed up by a factor of 8 to represent the upper bound of hypothetical parallelisation across an 8 core CPU.}
+			The \emph{Mathematica} and \emph{SciPy} results are also shown with a speed up by a factor of 8 to represent the upper bound of hypothetical parallelization across an 8 core CPU.}
 			\label{fig:benchmark_external}
@@
 
-	\subsection{Parallelisation performance}
+	\subsection{Parallelization performance}
 		Once the algorithm behind \emph{Spinsim} was developed, we wanted to check its execution speed while running on various devices.
-		The main reason for this test was to quantify the speed increase of parallelisation by comparing execution speeds on highly parallel devices (being GPUs), and highly procedural devices (being CPUs).
+		The main reason for this test was to quantify the speed increase of parallelization by comparing execution speeds on highly parallel devices (being GPUs), and highly procedural devices (being CPUs).
 		Speed benchmarks were performed using \texttt{neural-sense.sim.benchmark}, by comparing the evaluation speed of typical spin-one sensing experiments on different devices.
@@
 		\begin{table}[h!]
-			\caption{Devices used in the parallelisation speed test.
+			\caption{Devices used in the parallelization speed test.
 			These devices are part of individual computers, which are separated here by horizontal lines.}
@@
 
-		The results in Figure~\ref{fig:benchmark_device_aggregate} show the benefit to using parallelisation when solving a spin system problem.
+		The results in Figure~\ref{fig:benchmark_device_aggregate} show the benefit to using parallelization when solving a spin system problem.
 		Moving from the 6 core \emph{Core i7-8750H} CPU to the 12 core \emph{Ryzen 9 5900X} CPU doubles the execution speed, as does moving from the 384 core \emph{Quadro K620} GPU to the 768 core \emph{Quadro T1000} GPU.
@@
 
-		Users can view~\ref{fig:benchmark_device_aggregate} to decide on how much their current or future hardware will be able to take advantage of \emph{Spinsim}'s parallelism.
-		% Figure~\ref{fig:benchmark_device_aggregate} can be used by potential \emph{Spinsim} users for finding the relative performance for devices of varying abilities of parallelisation.
+		Users can view Figure~\ref{fig:benchmark_device_aggregate} to decide on how much their current or future hardware will be able to take advantage of \emph{Spinsim}'s parallelism.
+		% Figure~\ref{fig:benchmark_device_aggregate} can be used by potential \emph{Spinsim} users for finding the relative performance for devices of varying abilities of parallelization.
 		Another factor not shown in the plot is that, in practice, running highly code parallel code on a CPU on a personal computer will severely limit the responsiveness of other applications, as it can utilize the entire CPU (as it should).
-		In contrast, this does not happen when running a GPU based program, as it requires very little CPU utilisation to function.
+		In contrast, this does not happen when running a GPU based program, as it requires very little CPU utilization to function.
 		This can be convenient when running simulations on a personal laptop or desktop, as other work on the computer does not have to halt while simulations are being run.
@@
 		A good way to confirm that \emph{Spinsim} is functioning properly after an installation is to run the tutorial code provided and compare the outputs.
-		Otherwize, one can reproduce the benchmarks shown here using \texttt{neural\_sense.sim.benchmark}.
+		Otherwise, one can reproduce the benchmarks shown here using \texttt{neural\_sense.sim.benchmark}.
 
@@
 \section{Additional system requirements}
-To use the (default) \emph{Nvidia Cuda} GPU parallelisation, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU\cite{noauthor_cuda_2012}.
-For \emph{Cuda} mode to function, one also needs to install the \emph{Nvidia Cuda} toolkit\cite{noauthor_cuda_2013}.
+To use the (default) \emph{Nvidia Cuda} GPU parallelization, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU~\cite{noauthor_cuda_2012}.
+For \emph{Cuda} mode to function, one also needs to install the \emph{Nvidia Cuda} toolkit~\cite{noauthor_cuda_2013}.
 If \emph{Cuda} is not available on the system, the simulator will automatically parallelize over multicore CPUs instead.
@@
 	Author of first version of code.\\
-3. Joel Hockstetter\\
+3. Joel Hochstetter\\
 	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
@@
 	\subsection{Use potential and limitations}
-		\emph{Spinsim} will be useful for any research group needing quick, accurate, and / or large numbers of simulations involving spin-half or spin-one systems.
-		This is immediately relevant to developing new quantum sensing protocols with spin-half and spin-one systems.
-		This package is being used in the context of Bose Einstein Condensate (BEC) magnetic sensing protocol design by our lab.
-
-		This project is to be able to measure neural signals using BECs.
-		The electrical pulses made by neurons are currently measured using electrical probes, which is intrusive and damages the cells.
-		We instead propose to sense the small magnetic fields that these electrical currents produce.
-		Rubidium BECs can potentially be made sensitive enough to these tiny magnetic fields that they can be measured by them.
-		\emph{Spinsim} was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin-one atoms interacting with the magnetic fields of the neurons, control signals, and noise.
-		The package is also now being used to simulate other BEC magnetometry experiments by the lab group.
-
-		Another example of spin based magnetic field sensing is the use of Nitrogen Vacancy Centres (NVCs).
-		These are spin-one structures found in diamond doped with Nitrogen atoms.
+		The \emph{Spinsim} package will be useful for any research group needing quick, accurate, and/or large numbers of simulations involving spin-half or spin-one systems.
+		In particular, the package can simulate a system with complicated (ie not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.
+		We stress that many application specific simulators are designed for the paradigm of using the RWA and/or hard pulse approximations~\cite{suzuki_qulacs_2021, teske_qopt_2021, isakov_simulations_2021}, which both sacrifice accuracy for the sake of speed.
+		While this is viable for some areas of physics research, when designing quantum sensing protocols, we need to take all effects of the spin system and surrounding lab environment into account.
+		Thus, \emph{Spinsim}'s primary use is to fill in this gap of simulators for use of developing new quantum sensing protocols with spin-half and spin-one systems, and so should be useful to many within the field of quantum sensing.
+		Moreover, \emph{Spinsim} is fast and accurate enough that there is no need to simplify the problem to compromise accuracy for speed.
+
+		The package was written for the context of testing a particular ultracold atom magnetic sensing protocol design.
+		This project aims to be able to measure neural signals using ultracold atoms.
+		Electrical pulses made by neurons are currently measured using electrical probes~\cite{mitterdorfer_potassium_2002}, which is intrusive and damages the cells.
+		We, and others in the field~\cite{barry_optical_2016, xu_wavelet-based_2016, parashar_axon_2020, webb_high_2021} instead propose to sense the small magnetic fields that these electrical currents produce.
+		Rubidium ultracold atom clouds can potentially be made sensitive enough to these small magnetic waveforms that we can use them as sensors.
+		The \emph{Spinsim} package was written to simulate possible measurement protocols for this, showing the behaviour of the array of spin-one atoms interacting with the magnetic fields of the neurons, control signals, and the lab environment.
+
+		So far, the package has also been used to produce simulations for four other new and conceptually distinct quantum sensing protocols from members of the Monash University School of Physics \& Astronomy spinor BEC lab.
+		Included in this were some honors projects, where \emph{Spinsim} allowed for many quick simulations in the limited time available.
+
+		Another example of spin based magnetic field sensing is the use of nitrogen vacancy centres (NVCs).
+		These are spin-one structures found in diamond, doped with Nitrogen atoms.
 		This leaves a vacancy in a position adjacent to the Nitrogen atom, which pairs of electrons occupy to obtain the spin-one properties.
-		Similar to BECs, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
-		A paper was only recently released covering simulation experiments of magnetic neural pulse sensing using NVCs\cite{parashar_axon_2020}, which is something that \emph{Spinsim} could be useful for.
-
-		\emph{Spinsim} is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
+		Similar to ultracold atoms, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
+		As work first started on \emph{Spinsim}, Parashar et al~\cite{parashar_axon_2020} published results on simulation experiments of magnetic neural pulse sensing using NVCs.
+		This is a field \emph{Spinsim} could be useful in.
+
+		The \emph{Spinsim} package is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
 		This means that it would not be able to integrate large arrays of entangled states or interacting particles.
 		As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
-		In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only.
-		This means that it may not be adequate for use in some Nuclear Magnetic Resonance (NMR) applications where relaxation\cite{veshtort_spinevolution_2006} is important (or other kinds of simulations involving decoherence).
+		In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only, meaning it is only accurate for the duration that the physical spin system is coherent.
+		While ultracold atoms can be coherent for tens of seconds, to the point where decoherence is negligible for most quantum sensing experiments, NVCs have a much shorter coherence time of up to $ 1\,\text{ms} $~\cite{degen_quantum_2017}, so fewer simulations are accurate while ignoring decoherence.
+		Not being able to model decoherence also means that \emph{Spinsim} may not be adequate for use in some nuclear magnetic resonance (NMR) applications where relaxation is important, such as those covered by \emph{SpinEvolution}~\cite{veshtort_spinevolution_2006}, for example.
 
 		With these restrictions in mind, \emph{Spinsim} could be used for some simplified simulations in various areas of NMR.
-		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and fewer that have spins of one (eg Lithium 6, Nitrogen 14)\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{Spinsim} could be used to simulate for spectroscopy experiments, for example.
-		The inclusion of a quadrupole operator means that, with the same level of simplifications, \emph{Spinsim} should be able to simulate Nuclear Quadrupole Resonance (NQR) spectroscopy for spin-one nuclei\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
+		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and some that have spins of one (eg Lithium 6, Nitrogen 14)~\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{Spinsim} could be used to simulate for spectroscopy experiments, for example.
+		The inclusion of a quadrupole operator means that \emph{Spinsim} should be able to simulate nuclear quadrupole resonance (NQR) spectroscopy for spin-one nuclei~\cite{bain_nqr_2004}, such as Nitrogen 14, provided a suitable coordinate system is chosen.
 		This technique measures energy level differences between levels split by electric field gradients, rather than static magnetic bias fields.
-		Another possible use-case could be for Magnetic Resonance Imaging (MRI) simulation and pulse sequence design.
-		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{Spinsim} simulations of spins at different positions in space.
-		While this package offers some advantages over state of the art simulators in the field\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrized pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
+		Another possible use-case could be for magnetic resonance imaging (MRI) simulation and pulse sequence design.
+		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence~\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{Spinsim} simulations of spins at different positions in space.
+		While this package offers some advantages over state of the art simulators in the field~\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrized pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
+
+		The field of Quantum Optimal Control (QOC) requires many simulations in order to optimize a pulse sequence to be robust to the noisy environment of the system, using machine learning techniques~\cite{dalgaard_fast_2021}.
+		The ability to automatically differentiate~\cite{griewank_who_2012} the simulator is important for this application.
+		This is not currently a feature of \emph{Spinsim}.
+		However, it could be added in the future, especially since it might also be helpful for some quantum sensing applications.
 
@@
 		One can also use this contact to suggest extensions to the package.
-		\emph{Spinsim} is planned to be maintained by the Monash University spinor BEC lab into the future.
+		\emph{Spinsim} is planned to be used and maintained by the Monash University School of Physics \& Astronomy spinor BEC lab into the future.
 
@@
 
-Thank you to the Monash University School of Physics and Astronomy spinor BEC lab group.
-In particular, Hamish Taylor, Travis Hartley and Chris Bounds, who have started using \emph{Spinsim} for their own projects and have given useful feedback of their user experience with the package.
+Thank you to the Monash University School of Physics \& Astronomy spinor BEC lab group.
+In particular, Hamish Taylor, Travis Hartley, Chris Bounds and Sam White, who have been using \emph{Spinsim} to simulate new ideas for quantum sensing protocols, and have given useful feedback of their user experience with the package.
 

### 2021-11-09 article/article.tex
Paper torture comments

@@
 	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by three orders of magnitude.
+	% Mention GPU in fewer words
 
@@
 	In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz.
+% Too specific
 	Standard integration methods require very small time-steps in order to accurately depict these oscillations.
@@
 
-	\subsection{Recent literature}
+	\subsection{Recent literature} % Recent relevant software? Recent software with similar functionality
 		While we benchmark \emph{Spinsim} only against industry standard integrators, we also note that application specific quantum numerical simulator packages are regularly being released.
@@
 
-	\subsection{Use potential and limitations}
+	\subsection{Applications}
 		The \emph{Spinsim} package will be useful for any research group needing quick, accurate, and/or large numbers of simulations involving spin-half or spin-one systems.
-		In particular, the package can simulate a system with complicated (ie not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.
+		In particular, the package can simulate a system with complicated (ie not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.% Frequency, amplitude and phase modulation; multiple tones; narrow-band interference; Radiation in control Hamiltonian; interesting polarisation
 		We stress that many application specific simulators are designed for the paradigm of using the RWA and/or hard pulse approximations~\cite{suzuki_qulacs_2021, teske_qopt_2021, isakov_simulations_2021}, which both sacrifice accuracy for the sake of speed.
@@
 		Included in this were some honors projects, where \emph{Spinsim} allowed for many quick simulations in the limited time available.
+% People who have not used quantum computation before have managed to do this
 
@@
 		Not being able to model decoherence also means that \emph{Spinsim} may not be adequate for use in some nuclear magnetic resonance (NMR) applications where relaxation is important, such as those covered by \emph{SpinEvolution}~\cite{veshtort_spinevolution_2006}, for example.
+% Too much negativity; Long and adiabatic pulse sequences; simulate in the lab frame, end up with bloch-seigert shifts; targeted at individual quanta, separate regime
 

### 2021-11-16 article/article.tex
Merged changes from Josh and Joel

@@
 2. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
-	Present address: Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
+	Present address: Vienna Center for Quantum Science and Technology (VCQ), Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
 	Author of first version of code.\\
 3. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
-	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
+	Present address: Department of Applied Mathematics and Theoretical Physics, Centre for Mathematical Sciences, University of Cambridge, Cambridge, UK.\\
 	Optimization and extension to spin-one of first version of code.\\
@@
 \section{Abstract}
-	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shroedinger equation.
+	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shr\"odinger equation.
 	It makes use of \texttt{numba.cuda}, which is an \emph{LLVM} (Low Level Virtual Machine) compiler for \emph{Nvidia Cuda} compatible systems using GPU parallelization. 
-	Along with other optimizations, this allows for speed improvements of up to four orders of magnitude while staying just as accurate, compared to industry standard packages.
+	Along with other optimizations, this allows for speed improvements from 3 to 4 orders of magnitude while staying just as accurate, compared to industry standard packages. % Mention which ones?
 	It is available for installation on \emph{PyPI}, and the source code is available on \emph{github}.
@@
 	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
-	The simplest spin system, spin-half (ie spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
-	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (ie spin quantum number of $ 1 $, also referred to as a quitrit), which is quantized into three quantum spin levels.
+	The simplest spin system, spin-half (i.e.spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
+	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (i.e.spin quantum number of $ 1 $, also referred to as a quitrit), which is quantized into three quantum spin levels.
 
@@
 	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
-	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by three orders of magnitude.
+	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by up to 4 orders of magnitude.
 	% Mention GPU in fewer words
@@
 		\begin{align}
-			i\hbar\frac{\mathrm{d}\psi(t)}{\mathrm{d}t} &= H(t)\psi(t),\label{eq:schroedinger}
+			i\hbar\frac{\text{d}\psi(t)}{\text{d}t} &= H(t)\psi(t),\label{eq:schroedinger}
 		\end{align}
@@
 		Here $ N $ is the number of levels in the quantum system.
-		Often we are considering systems with spin of half or one.
-		Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
+		Often we are considering systems with spin of half ($ N = 2 $ case) or one ($ N = 3 $).
+		% Spin-half is the $ N = 2 $ case, and spin-one is $ N = 3 $.
 		% \supervisordisagreement{
@@
 
-		Rather than parametrizing the problem in terms of the matrix elements of $ H(t) $, we consider time varying real coefficients in a linear combination of fixed operators,
+		Rather than parametrizing the problem in terms of the matrix elements of $ H(t) $, we consider time varying real coefficients in a linear combination of a basis of fixed operators,
 		\begin{align}
@@
 		Here we exclude the identity so that the Hamiltonian is traceless, which corresponds to choosing a physically meaningless energy zero point.
-		It is well known that a charged spin-half system with magnetic moment $ \overrightarrow{\mu} $, and gyromagnetic ratio $ \gamma $, in a magnetic field $ \overrightarrow{B}(t) $, has Hamiltonian
+		It is well known~\cite[(p74)]{j_j_sakurai_jun_john_modern_2011} that a charged spin-half system with magnetic moment $ \overrightarrow{\mu} $, and gyromagnetic ratio $ \gamma $, in a magnetic field $ \overrightarrow{B}(t) $, has Hamiltonian
 		\begin{align}
@@
 		% }
-		Because of the equivalence of the magnetic field components $ B_j(t) $ and the $ \omega_j(t) $, we henceforth refer to the latter as field functions.
-
-		In the spin-one case there is no standard basis of operators $ \mathcal{A}_j $.
+		Motivated by this, we define our basis for the spin-half model with $ \mathcal{A}_1 = J_x $, $ \mathcal{A}_2 = J_y $ and $ \mathcal{A}_3 = J_z $.
+		Additionally, because of the equivalence of the magnetic field components $ B_j(t) $ and the $ \omega_j(t) $, we henceforth refer to the latter as field functions.
+
+		In the spin-one case there is no universal standard basis of operators $ \mathcal{A}_j $.
 		Choices include the Gell-Mann matrices~\cite{gell-mann_symmetries_1962}, and multiple dipole-quadrupole bases~\cite{hamley_spin-nematic_2012, di_dipolequadrupole_2010}.
 		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
-		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}
+		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \text{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}
 
@@
 
-		% With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \mathrm{diag}(1, -2, 1)/3 $,
+		% With this in mind, we choose to represent the Hamiltonian a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x, J_y $ and $ J_z $, and a single quadrupole operator $ Q = \text{diag}(1, -2, 1)/3 $,
 		\begin{align}
@@
 		The $ J_x $, $ J_y $, $ J_z $ and $ Q $ are the only operators necessary to simulate many spin-one quantum systems in arbitrary bias fields, but with single-photon coupling.
-		This includes quadratic Zeeman splitting described by the Breit-Rabi formula~\cite{mockler_atomic_1961} important to experiments in our lab.
+		This includes quadratic Zeeman splitting described by the Breit-Rabi formula~\cite{mockler_atomic_1961}, important to experiments in our lab.
 		The \emph{Spinsim} simulator can also be configured to solve a general spin-one system by setting the Hamiltonian to an arbitrary point in $ \mathfrak{su}(3) $ using the full quadrupole basis, which extends the possible Hamiltonian to
@@
 		% \begin{align}
-		% 	\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
+		% 	\frac{\text{d}}{\text{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z) \psi(t),
 		% \end{align}
@@
 		% \begin{align}
-		% 	\frac{\mathrm{d}}{\mathrm{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
+		% 	\frac{\text{d}}{\text{d}t}\psi(t) = -i 2\pi (f_x(t) J_x + f_y(t) J_y + f_z(t) J_z + f_q(t) Q) \psi(t).
 		% \end{align}
@@
 		\begin{align}
-			i\hbar\frac{\mathrm{d}\mathcal{U}(t, t_0)}{\mathrm{d}t} &= H(t)\mathcal{U}(t, t_0).\label{eq:unitary_schroedinger}
+			i\hbar\frac{\text{d}\mathcal{U}(t, t_0)}{\text{d}t} &= H(t)\mathcal{U}(t, t_0).\label{eq:unitary_schroedinger}
 		\end{align}
@@
 		Since $ \mathcal{U}(t, t_0) $ is unitary, it can be written as a matrix exponential of a anti-Hermitian (also termed skew-Hermitian) matrix.
-		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is % \note{Should we use H, ie no argument, or H(t'), ie arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
+		If the Hamiltonian is a of constant value $ H(t) = \mathcal{H} $, then this exponential is % \note{Should we use H, i.e.no argument, or H(t'), i.e.arbitrary argument, to represent constancy?} % Check if continuity requirement on unitary
 		\begin{align}
@@
 		\begin{align}
-			\Omega_1(t, t_0) &= \int_0^t\mathrm{d}t_1A(t_1)\\
-			\Omega_2(t, t_0) &= \frac12\int_{t_0}^t\mathrm{d}t_1\int_{t_0}^{t_1}\mathrm{d}t_2[A(t_1), A(t_2)]\\
-			\Omega_3(t, t_0) &= \frac16\int_{t_0}^t\mathrm{d}t_1\int_{t_0}^{t_1}\mathrm{d}t_2\int_{t_0}^{t_2}\mathrm{d}t_3\left([A(t_1), [A(t_2), A(t_3)]] + [A(t_3), [A(t_2), A(t_1)]]\right),
+			\Omega_1(t, t_0) &= \int_0^t\text{d}t_1A(t_1),\\
+			\Omega_2(t, t_0) &= \frac12\int_{t_0}^t\text{d}t_1\int_{t_0}^{t_1}\text{d}t_2[A(t_1), A(t_2)],\\
+			\Omega_3(t, t_0) &= \frac16\int_{t_0}^t\text{d}t_1\int_{t_0}^{t_1}\text{d}t_2\int_{t_0}^{t_2}\text{d}t_3\left([A(t_1), [A(t_2), A(t_3)]] + [A(t_3), [A(t_2), A(t_1)]]\right),
 		\end{align}
 		where $ [X, Y] = XY - YX $ is the commutator.
-		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\mathrm{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation~\eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.
+		Note that, when truncated to first order, the Magnus expansion $ \mathcal{U}(t, t_0) = \exp\left(\int_{t_0}^t\text{d}t_1\left(-iH(t_1)\right)\right) $ reduces to Equation~\eqref{eq:exp_sol_of_constant}, with $ H(t) $ approximated by its average value over the interval $ [t_0, t] $.
 
@@
 		% Here each $ \Omega_m(t) $ are integrals over time commutators of $ H(t') $.
-		% $ \Omega_1(t) $, for example, is $ \Omega_1(t) = H_\mathrm{av}t $, where $ H_\mathrm{av} $ is the average value of $ H $ over the interval being integrated over, which is the solution for when $ H $ is constant in time.
+		% $ \Omega_1(t) $, for example, is $ \Omega_1(t) = H_\text{av}t $, where $ H_\text{av} $ is the average value of $ H $ over the interval being integrated over, which is the solution for when $ H $ is constant in time.
 		% The terms $ \Omega_m(t) $ for $ m > 1 $ are corrections to this approximation.
@@
 
-		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi \approx 1.08686870\dots $~\cite{blanes_magnus_2009}.
-		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < 1.08686870\dots $~\cite{blanes_magnus_2009}.
-		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\mathrm{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $~\cite{blanes_magnus_2009}.
+		Convergence of the Magnus series for $ \mathcal{U}(t, t_0) $ is not in general guaranteed, but it is under the condition that $ \int_{t_0}^t\text{d}t_1\|H(t_1)\|_2 < \xi \approx 1.08686870\dots $~\cite{blanes_magnus_2009}.
+		% The loosest bound discovered for the convergence of a general Magnus series for $ \mathcal{U}(t, t_0) $ is $ \int_{t_0}^t\text{d}t_1\|H(t_1)\| < 1.08686870\dots $~\cite{blanes_magnus_2009}.
+		% A Magnus series for $ \mathcal{U}(t, t_0) $ will be guaranteed to converge if $ \int_{t_0}^t\text{d}t_1\|H(t_1)\| < \xi = 1.08686870\dots $~\cite{blanes_magnus_2009}.
 		Furthermore, each subsequent term in the expansion increases in complexity rapidly.
@@
 		In particular, we use the commutator free, fourth order method (CF4) from Reference~\cite{auer_magnus_2018}.
-		Suppose we wish to evaluate a time-step of $ \mathcal{U}(t + \mathrm{d}t, t) $ using the CF4 method.
+		Suppose we wish to evaluate a time-step of $ \mathcal{U}(t + \delta t, t) $ using the CF4 method.
 		The Hamiltonians are sampled at times
 		\begin{align}
-			t_1 &= t + \frac12 \left(1 - \frac{1}{\sqrt{3}}\right)\mathrm{d}t\quad\text{and}\\
-			t_2 &= t + \frac12 \left(1 + \frac{1}{\sqrt{3}}\right)\mathrm{d}t,
+			t_1 &= t + \frac12 \left(1 - \frac{1}{\sqrt{3}}\right)\delta t\quad\text{and}\\
+			t_2 &= t + \frac12 \left(1 + \frac{1}{\sqrt{3}}\right)\delta t,
 		\end{align} % maybe not rm d
@@
 		\begin{align}
-			\mathcal{U}(t + \mathrm{d}t, t) \approx \exp(-i\overline{H}_2\mathrm{d}t)\exp(-i\overline{H}_1\mathrm{d}t)\label{eq:cf4_implementation}
+			\mathcal{U}(t + \delta t, t) = \exp(-i\overline{H}_2\,\delta t)\exp(-i\overline{H}_1\,\delta t) + \mathcal{O}(\delta t^5),\label{eq:cf4_implementation}
 		\end{align}% \approx? Unitary? End with sentence
@@
 
-	\subsection{Lie-Trotter based Exponentiator}
+	\subsection{Lie-Trotter based exponentiator}
 		Evaluating matrix exponentials is a core part of the integration algorithm.
@@
 		An advantage of the Lie-Trotter approach is that $ \exp(-iA_k/n) $ has known analytic forms for the Lie algebra basis elements $ A_k $.
-		Hence the unitary time-evolution operator is approximated by $ U = \exp(-iHt) \approx T^n $ where
+		Hence the unitary time-evolution operator is approximated by $ U = \exp(-iH\,\delta t) = T^n + \mathcal{O}(\delta t^3) $, where
 		\begin{align}
@@
 		\end{align}
-		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method~\cite{barthel_optimized_2020} allow us to write 
+		In fact, commutation relations between the Lie basis operators and the leapfrog splitting method~\cite{barthel_optimized_2020} allow us to instead write 
 		\begin{align}
@@
 		\end{align}
-		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \mathrm{arctan}2(\omega_y, \omega_x) $ (where $ \mathrm{arctan}2(y, x) $ is the two argument arctangent~\cite{organick_fortran_1966}), $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
+		Here $ z = \omega_z/n $, $q = \omega_q/n $, $ \Phi = \sqrt{\omega_x^2 + \omega_y^2}/n $, $ \phi = \text{arctan}2(\omega_y, \omega_x) $ (where $ \text{arctan}2(y, x) $ is the two argument arctangent~\cite{organick_fortran_1966}), $ D_{z,q} = zJ_z + qQ $ and $ J_\phi = \cos(\phi) J_x + \sin(\phi) J_y $.
 		The element-wise analytic form of this is
@@
 		This cannot be done by simply subtracting the identity from Equation~\eqref{eq:lie_trotter_4}, as doing so would introduce cancellation error.
-		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialized implementations of functions such as $ \mathrm{expm}1(x) = \exp(x) - 1 $, designed for this purpose~\cite{hewlett-packard_hp_1994}.
+		It can be avoided by replacing the exponentials and trigonometric functions along the diagonal with specialized implementations of functions such as $ \text{expm}1(x) = \exp(x) - 1 $, designed for this purpose~\cite{hewlett-packard_hp_1994}.
 		The identity is added to the result of the iterative residual squaring and the full exponential is returned.
@@
 		% % Choice of n. n is large number, integer, power of 2. Efficiently by iterated squaring. Reference. % Revisit!!!
-		% Here $ z = 2^{-\tau}\frac{\omega_z}{2} $, $ q = 2^{-\tau}\frac{\omega_q}{6} $, $ \phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2} $, and $ \phi = \mathrm{atan}2(\omega_y, \omega_x) $.
+		% Here $ z = 2^{-\tau}\frac{\omega_z}{2} $, $ q = 2^{-\tau}\frac{\omega_q}{6} $, $ \phi = 2^{-\tau}\sqrt{\omega_x^2 + \omega_y^2} $, and $ \phi = \text{atan}2(\omega_y, \omega_x) $.
 		% Once $ T $ is calculated, it is then recursively squared $ \tau $ times to obtain $ E(\omega) $.
@@
 		Frequently we wish to sample the state at times $ t_k $ spaced more coarsely than the integration time-step.
-		Consider discrete times $ t_k = t_0 + \mathrm{D}t\cdot k $ where $ \mathrm{D}t $ is the time-step of the time-series, in contrast to $ \mathrm{d}t $, the time-step of the integration.
+		Consider discrete times $ t_k = t_0 + \Delta t\cdot k $ where $ \Delta t $ is the time-step of the time-series, in contrast to $ \delta t $, the time-step of the integration.
 		% The unitary operator $ \mathcal{U}_k $ 
@@
 		Beyond discretization for parallelization, we discretize our time-evolution operator into individual integration time-steps.
-		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time-step $ \mathrm{d}t = \mathrm{D}t/L $.
-
-		To choose an appropriate value of $ \mathrm{d}t $, users can refer to the accuracy plots in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error} under \emph{\nameref{sec:accuracy}}.
+		Each of the $ \mathcal{U}_k $ is further split into products $ u^k_{L-1} \cdots u^k_0 $ of $ L $ time-evolution operators, now separated by the integration time-step $ \delta t = \Delta t/L $.
+
+		To choose an appropriate value of $ \delta t $, users can refer to the accuracy plots in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error} under \emph{\nameref{sec:accuracy}}.
 % \note{How do I reference a section if they don't have number labels in the finished article?
 Should I?}
-		To choose an appropriate value of $ \mathrm{D}t $, users must consider three factors.
-		For the most benefit out of GPU parallelization, users should choose $ \mathrm{D}t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{Spinsim}.
-		Users should also make sure that $ \mathrm{D}t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \langle \overrightarrow{J}\rangle_k $ to be used in their further analysis.
+		To choose an appropriate value of $ \Delta t $, users must consider three factors.
+		For the most benefit out of GPU parallelization, users should choose $ \Delta t $ so that the number of time samples $ K $ is at least as large as the number of GPU cores available for \emph{Spinsim}.
+		Users should also make sure that $ \Delta t $ represents a large enough sample rate for the state $ \psi_k $ or expected spin projection $ \langle \overrightarrow{J}\rangle_k $ to be used in their further analysis.
 		Finally, if $ K $ is too large, then the GPU will run out of memory on compilation, which will raise an exception.
@@
 		% \begin{align}
-		% 	\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \mathrm{d}t) \cdots \mathcal{U}(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) \mathcal{U}(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+		% 	\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \delta t) \cdots \mathcal{U}(t_{k-1} + 2\delta t, t_{k-1} + \delta t) \mathcal{U}(t_{k-1} + \delta t, t_{k-1})\\
 		% 	\mathcal{U}_k &= u^k_{L-1} \cdots u^k_0,\quad\text{where}\\
-		% 	u^k_{l} &= \mathcal{U}(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
+		% 	u^k_{l} &= \mathcal{U}(t_0 + (k - 1)\Delta t + (l + 1)\delta t, t_0 + (k - 1)\Delta t + l\delta t)
 		% \end{align} % Just use middle product
-		% with $ \mathrm{d}t $ being the integration level time-step.
-		% Note that the sampling time-steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $.
+		% with $ \delta t $ being the integration level time-step.
+		% Note that the sampling time-steps are related to each other by $ \Delta t = L\delta t $.
 
@@
 		This dynamic application allows for the rotating frame to be used even during sweeps of the dominant term $ \omega_z(t) $ where it is only approximately constant locally.
-		Here we choose $ \omega_r = \omega_z(t_{k - 1} + \mathrm{D}t/2) $ as an approximate average value of $ \omega_z(t) $ over the duration.
+		Here we choose $ \omega_r = \omega_z(t_{k - 1} + \Delta t/2) $ as an approximate average value of $ \omega_z(t) $ over the duration.
 		The calculated time-evolution operator $ \mathcal{U}_k^r $ is then transformed back to the lab frame as
 		\begin{align}
-			\mathcal{U}_k &= R_{\omega_r}(-\mathrm{D}t)\mathcal{U}_k^r.\label{eq:exit_rotating_frame}
+			\mathcal{U}_k &= R_{\omega_r}(-\Delta t)\mathcal{U}_k^r.\label{eq:exit_rotating_frame}
 		\end{align}
@@
 
-		% Where $ \omega_r = \omega_z(t_k + \frac12\mathrm{D}t) $ is sampled the midpoint value of the fields over the interval $ [t_{k - 1}, t_k] $.
+		% Where $ \omega_r = \omega_z(t_k + \frac12\Delta t) $ is sampled the midpoint value of the fields over the interval $ [t_{k - 1}, t_k] $.
 		% This, assuming that a midpoint sample is representative of an average value over the time interval, decreases the magnitude of $ \omega_z(t) $, while leaving the other field components at an equivalent magnitude.
@@
 		% \begin{align}
-		% 	\mathcal{U}_k &= \exp(-i \omega_r J_z \mathrm{D}t) \mathcal{U}^r_k.
-		% \end{align}
-		% Specifically, this relationship is $ \mathcal{U}_k = \mathrm{diag}\left(\exp\left(-i \frac12 \omega_r \mathrm{D}t\right), \exp\left(i \frac12 \omega_r \mathrm{D}t\right)\right) $ for spin-half, and $ \mathcal{U}_k = \mathrm{diag}(\exp(-i \omega_r \mathrm{D}t), 0, \exp(i \omega_r \mathrm{D}t)) $ for spin-one.
+		% 	\mathcal{U}_k &= \exp(-i \omega_r J_z \Delta t) \mathcal{U}^r_k.
+		% \end{align}
+		% Specifically, this relationship is $ \mathcal{U}_k = \text{diag}\left(\exp\left(-i \frac12 \omega_r \Delta t\right), \exp\left(i \frac12 \omega_r \Delta t\right)\right) $ for spin-half, and $ \mathcal{U}_k = \text{diag}(\exp(-i \omega_r \Delta t), 0, \exp(i \omega_r \Delta t)) $ for spin-one.
 
@@
 	% 	\begin{align}
-	% 		\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \mathrm{d}t) \cdots \mathcal{U}(t_{k-1} + 2\mathrm{d}t, t_{k-1} + \mathrm{d}t) \mathcal{U}(t_{k-1} + \mathrm{d}t, t_{k-1})\\
+	% 		\mathcal{U}(t_k, t_{k-1}) &= \mathcal{U}(t_k, t_k - \delta t) \cdots \mathcal{U}(t_{k-1} + 2\delta t, t_{k-1} + \delta t) \mathcal{U}(t_{k-1} + \delta t, t_{k-1})\\
 	% 		\mathcal{U}_k &= u^k_{L-1} \cdots u^k_0\textrm{, where}\\
-	% 		u^k_{L-1} &= \mathcal{U}(t_0 + (k - 1)\mathrm{D}t + (l + 1)\mathrm{d}t, t_0 + (k - 1)\mathrm{D}t + l\mathrm{d}t)
-	% 	\end{align}
-
-	% 	with $ \mathrm{d}t $ being the integration level time-step. Note that the time-steps are related to each other by $ \mathrm{D}t = L\mathrm{d}t $, where $ L\in\mathbb{N} $.
+	% 		u^k_{L-1} &= \mathcal{U}(t_0 + (k - 1)\Delta t + (l + 1)\delta t, t_0 + (k - 1)\Delta t + l\delta t)
+	% 	\end{align}
+
+	% 	with $ \delta t $ being the integration level time-step. Note that the time-steps are related to each other by $ \Delta t = L\delta t $, where $ L\in\mathbb{N} $.
 
 		% The CF4 method is used to calculate each individual $ u^k_l $.
-Let the fine sample time be given by $ t_I = l\mathrm{d}t + t_k $.
+Let the fine sample time be given by $ t_I = l\delta t + t_k $.
 Then as part of the CF4 method, the field functions are sampled at particular times based on the second order Gauss-Legendre quadrature, given by
@@
 		% \begin{align}
-		% 	t_1 &= t_I + \frac12 \mathrm{d}t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
-		% 	t_2 &= t_I + \frac12 \mathrm{d}t\left(1 + \frac{1}{\sqrt{3}}\right).
+		% 	t_1 &= t_I + \frac12 \delta t\left(1 - \frac{1}{\sqrt{3}}\right)\textrm{, and}\\
+		% 	t_2 &= t_I + \frac12 \delta t\left(1 + \frac{1}{\sqrt{3}}\right).
 		% \end{align}
@@
 		% 	\omega_1 =& (\omega_{1,x}, \omega_{1,y}, \omega_{1,z}, \omega_{1,q})\\
-		% 	=& 2 \pi \mathrm{d}t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, and}\\
+		% 	=& 2 \pi \delta t \left(\frac{3 + 2 \sqrt{3}}{12} f(t_1) + \frac{3 - 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, and}\\
 		% 	\omega_2 =& (\omega_{2,x}, \omega_{2,y}, \omega_{2,z}, \omega_{2,q})\\
-		% 	=& 2 \pi \mathrm{d}t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, so}\\
+		% 	=& 2 \pi \delta t \left(\frac{3 - 2 \sqrt{3}}{12} f(t_1) + \frac{3 + 2 \sqrt{3}}{12} f(t_2)\right)\textrm{, so}\\
 		% 	u =& \exp(-i \left( \omega_{2,x} J_x + \omega_{2,y} J_y + \omega_{2,z} J_z + \omega_{2,q} Q\right))\\
@@
 		It then starts a loop to find each of the time-stepping operators $ u^k_l $.
-		% The code then loops over each integration time-step $ \mathrm{d}t $ to calculate the integration time-evolution operators $ u^k_l $.
+		% The code then loops over each integration time-step $ \delta t $ to calculate the integration time-evolution operators $ u^k_l $.
 		Within the loop, the integrator enters a device function to sample the user-provided field functions $ \omega_j(t) $ (device functions are GPU subroutines, and in practice all device functions here are compiled inline for speed).
@@
 		When the loop has finished, $ \mathcal{U}^r_k $ is transformed to $ \mathcal{U}_k $ as in Equation~\eqref{eq:exit_rotating_frame}, and this is returned.
-		Once all threads have executed, using Equation~\eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\mathrm{init}} = \psi(t_0) $.
+		Once all threads have executed, using Equation~\eqref{eq:integration_compilation}, the state $ \psi_k $ is calculated in a (CPU) \texttt{numba.jit()}ed function from the $ \mathcal{U}_k $ and an initial condition $ \psi_{\text{init}} = \psi(t_0) $.
 
 	\subsection{Compilation of integrator}
-		The \emph{Spinsim} integrator is constructed and compiled just in time, using the \emph{Numba}~\cite{lam_numba_2015} python package.
+		The \emph{Spinsim} integrator is constructed and compiled just-in-time (JIT), using the \emph{Numba}~\cite{lam_numba_2015} python package.
 		This is achieved via the \texttt{numba.cuda.jit()} decorator, which compiles python functions into \emph{Nvidia Cuda}~\cite{nickolls_scalable_2008} kernels using an LLVM~\cite{lattner_llvm_2004} (Low Level Virtual Machine) compiler.
@@
 		The default settings should be optimal for most users, although tuning the values of \emph{Cuda} meta-parameters \texttt{max\_registers} and \texttt{threads\_per\_block} could improve performance for different GPUs.
-		Third, just in time compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU.
+		Third, JIT compilation also allows the user to select a target device other than \emph{Cuda} for compilation, so the simulator can run, using the same algorithm, on a multicore CPU in parallel instead of a GPU.
 		In particular, this allows for compatibility with products running \emph{Apple}'s \emph{MacOS 10.14 Mojave} and later, which are incompatible with \emph{Cuda} devices and software.
@@
 		For a use-case example, an MRI experimentalist might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
-		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.% \linebreak
+		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}. % \linebreak
 		This feature is demonstrated with examples in the documentation.
@@
 		Benchmarks were performed using \texttt{neural-sense.sim.benchmark} (where \texttt{neural-sense}~\cite{alexander-tritt-monash_alexander-tritt-monashneural-sense_2020} is the quantum sensing package that \emph{Spinsim} was written for).
-		This simulation involves continuously driving transitions in the system for $ 100\,\mathrm{ms} $, while exposing it to a $ 1\,\mathrm{ms} $ pulsed signal that the system should be able to sense.
-		The system has the hamiltonian
+		This simulation involves continuously driving transitions in the system for $ 100\,\text{ms} $, while exposing it to a $ 1\,\text{ms} $ pulsed signal that the system should be able to sense.
+		The system has the Hamiltonian
 		\begin{align}
@@
 		\end{align}
-		where $ \omega = 2\pi\cdot700\,\mathrm{kHz} $, $ \Omega = 2\pi\cdot1\,\mathrm{kHz} $,$ \Omega_p = 2\pi\cdot70\,\mathrm{Hz} $, $ t_p = 233\,\mathrm{ms} $ and $ p_\Omega(t) $ is a single cycle of a sine wave wth frequency $ \Omega $.
+		where $ \omega = 2\pi\cdot700\,\text{kHz} $, $ \Omega = 2\pi\cdot1\,\text{kHz} $,$ \Omega_p = 2\pi\cdot70\,\text{Hz} $, $ t_p = 233\,\text{ms} $ and $ p_\Omega(t) $ is a single cycle of a sine wave wth frequency $ \Omega $.
 
@@
 		where $ j \in \{\frac12, 1\} $ is the spin quantum number of the system.
-		This baseline was computed in 2.4 hours (in comparison to order of $ 100\,\mathrm{ms} $ of a second these \emph{Spinsim} tests were executed in), and was also used for comparisons to other software packages.
+		This baseline was computed in 2.4 hours (in comparison to order of $ 100\,\text{ms} $ these \emph{Spinsim} tests were executed in), and was also used for comparisons to other software packages.
 
@@
 		The former sets of plots will be of interest to users choosing an appropriate time-step for simulations, and the latter for estimating the execution time of such simulations.
-		In all of these comparisons, errors above $ 10^{-3} $ were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
+		% In all of these comparisons, errors above $ 10^{-3} $ were counted as a failed simulation, as the maximum possible error for a quantum state saturates given that it is a point on a unit complex sphere.
+		In all of these comparisons, errors above $ 10^{-3} $ were counted as a failed simulation, as quantum states cannot be arbitrarily far away from each other given that they are points on a unit complex sphere.
 		Errors below $ 10^{-11} $ were also excluded, as this was the order of magnitude of the errors in the reference simulation.
@@
 			\caption{Speed and accuracy of the spin-one and spin-half options of \emph{Spinsim}.
-			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
-			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+			A simulation of a typical sensing experiment for our lab was run for every integration time-step, for each of the possible integration techniques (Magnus-based commutator free 4, and two Euler methods).
+			In the simulation, transitions are continuously driven in the spin system for a duration of $ 100 \,\text{ms} $, and an additional small signal is injected for $ 1\,\text{ms} $.
 			See Equation~\eqref{eq:neural_pulse}.
@@
 		However, it might be possible to increase the average speed of many benchmarks from \emph{Mathematica} and \emph{SciPy} packages by using multithreading to run multiple simulations at a time.
-		When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
+		% When this was attempted using \emph{Mathematica}, the kernels crashed as the 32GiB of RAM was not enough to run them all at once.
+		We attempted doing 8 way multithreading (on an 8 core \emph{Ryzen 7 5800X}) with \emph{Mathematica}, but the solver crashed due to insufficient RAM (of $ 32\,\text{GiB} $).
 		Multithreading was not attempted using \emph{SciPy}, due to the fact that running the full set of benchmarks of only a single simulation per integration time-step already consumes over 11 hours of computational time.
@@
 		From Figure~\ref{fig:benchmark_external}, for any given error tolerance, \emph{Spinsim} is over 3 orders of magnitude faster than \emph{Mathematica} and \emph{QuTip}, and 4 orders of magnitude more accurate than \emph{SciPy}.
-		In practice, this means that a 25 minute \emph{SciPy} simulation is reduced to 50ms, and a three week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic requirement for testing quantum sensing protocols) would take less than one minute in \emph{Spinsim}.
+		In practice, this means that a 25 minute \emph{SciPy} simulation is reduced to 50ms, and a three week long \emph{SciPy} batch simulation of 1000 separate systems (a realistic situation for testing quantum sensing protocols) would take less than one minute in \emph{Spinsim}.
+		Note that while the three week long \emph{SciPy} example could be parallelised over a computer cluster, saving some, \emph{Spinsim} allows users to avoid the need for using clusters and, given that a single \emph{SciPy} simulation still takes 25 minutes to run, the \emph{Spinsim} batch would still be faster.
 		\begin{figure}[h!]
@@
 			\caption{Speed vs accuracy of two alternative integration packages.
-			A simulation of a typical neural sensing experiment was run for every integration time-step, for each of alternative packages (\texttt{qutip.sesolve()} from \emph{QuTip}, \texttt{NDSolve()} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
-			In the simulation, transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+			A simulation of a typical sensing experiment for our lab was run for every integration time-step, for each of alternative packages (\texttt{qutip.sesolve()} from \emph{QuTip}, \texttt{NDSolve()} from \emph{Mathematica}, and \texttt{scipy.integrate.ivp\_solve()} from \emph{SciPy}).
+			In the simulation, transitions are continuously driven in the spin system for a duration of $ 100\,\text{ms} $, and an additional small signal is injected for $ 1\,\text{ms} $.
 			See Equation~\eqref{eq:neural_pulse}.
@@
 			\includegraphics[scale=0.6]{benchmark_device_aggregate.png}
-			\caption{Evaluation speed of a simulation of a typical spin-one sensing experiment on both CPUs and GPUs.
-			Integration time-step is set to 100ns.
-			Transitions are continuously driven in the spin system for a duration of 100ms, and an additional small signal is injected for 1ms.
+			\caption{Evaluation speed of a simulation of a typical spin-one sensing experiment for our lab on both CPUs and GPUs.
+			Integration time-step is set to $ 100\,\text{ns} $.
+			Transitions are continuously driven in the spin system for a duration of $ 100\,\text{ms} $, and an additional small signal is injected for $ 1\,\text{ms} $.
 			See Equation~\eqref{eq:neural_pulse}.
@@
 	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
-	Present address: Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
+	Present address: Vienna Center for Quantum Science and Technology (VCQ), Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
 	Author of first version of code.\\
@@
 	School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
-	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
+	Present address: Department of Applied Mathematics and Theoretical Physics, Centre for Mathematical Sciences, University of Cambridge, Cambridge, UK.\\
 	Optimization and extension to spin-one of first version of code.\\
@@
 		The \emph{Spinsim} package will be useful for any research group needing quick, accurate, and/or large numbers of simulations involving spin-half or spin-one systems.
-		In particular, the package can simulate a system with complicated (ie not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.% Frequency, amplitude and phase modulation; multiple tones; narrow-band interference; Radiation in control Hamiltonian; interesting polarisation
+		In particular, the package can simulate a system with complicated (i.e.not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.
+% Frequency, amplitude and phase modulation; multiple tones; narrow-band interference; Radiation in control Hamiltonian; interesting polarisation
 		We stress that many application specific simulators are designed for the paradigm of using the RWA and/or hard pulse approximations~\cite{suzuki_qulacs_2021, teske_qopt_2021, isakov_simulations_2021}, which both sacrifice accuracy for the sake of speed.
@@
 	\subsection{Support}
-		Documentation for \emph{Spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs}}.
+		Documentation for \emph{Spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs} (https://spinsim.readthedocs.io/en/latest/)}.
 		This documentation contains a thorough tutorial on how to use the package, and installation instructions.

### 2022-04-08 docs/source/conf.py
v 0.5.0. Added interpolator

@@ -36,11 +36,11 @@ sys.path.append(os.path.abspath("../../../"))
 # -- Project information -----------------------------------------------------
 
 project = 'spinsim'
-copyright = '2020, Monash University'
+copyright = '2022, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.4.16'
+release = '0.5.0'
 
 
 # -- General configuration ---------------------------------------------------

### 2022-04-08 example.py

@@ -1,3 +1,4 @@
+# Example 1:
 import spinsim
 import matplotlib.pyplot as plt
 import math
@@ -23,6 +24,7 @@ plt.ylabel("spin expectation (hbar)")
 plt.title("Spin projection for Larmor precession")
 plt.show()
 
+# Example 2:
 import spinsim
 import matplotlib.pyplot as plt
 import math

### 2022-04-08 gaussian_example.py

@@ -71,7 +71,7 @@ legend += ["Analytic"]
 plt.legend(legend, loc = "lower left")
 plt.xlabel("Time (standard deviations)")
 plt.ylabel("Spin")
-plt.title("{}\nGaussian pulse at various numbers of steps".format(time_now_string))
+plt.title("Gaussian pulse at various numbers of steps")
 plt.savefig("gaussian_pulse.png")
 plt.savefig("gaussian_pulse.pdf")
 plt.show()
@@ -81,7 +81,7 @@ plt.figure()
 plt.loglog(number_of_steps, error, "-rx")
 plt.xlabel("Number of steps")
 plt.ylabel("Error")
-plt.title("{}\nError in integrating Gaussian pulse".format(time_now_string))
+plt.title("Error in integrating Gaussian pulse")
 plt.savefig("gaussian_pulse_error.png")
 plt.savefig("gaussian_pulse_error.pdf")
 plt.show()
@@ -130,7 +130,7 @@ plt.legend(
         "Pulse sample points"
     ]
 )
-plt.title("{}\nSample points for integrating Gaussian pulse".format(time_now_string))
+plt.title("Sample points for integrating Gaussian pulse")
 plt.savefig("gaussian_pulse_sample.png")
 plt.savefig("gaussian_pulse_sample.pdf")
 plt.show()

### 2022-04-08 interpolator_example.py

@@ -1,0 +1,57 @@
+import spinsim
+import matplotlib.pyplot as plt
+import math
+import numpy as np
+
+# Generate noise
+time_sampled = np.arange(0, 100e-3, 1e-3)
+larmor_sampled = np.random.randn(time_sampled.size)
+
+# Generate the interpolator
+larmor_interpolator = spinsim.generate_interpolation_sampler(time_sampled, larmor_sampled)
+def get_field_larmor_interpolator(time_sample, user_parameters, field_sample):
+  # We can vary the noise amplitude per simulation using user_parameters
+  noise_amplitude = user_parameters[0]
+  field_sample[2] = math.tau*(200 + noise_amplitude*larmor_interpolator(time_sample))
+
+  field_sample[0] = 0
+  field_sample[1] = 0
+  field_sample[3] = 0
+
+# Simulate the system with first without noise, then with noise
+simulator_larmor_interpolator = spinsim.Simulator(get_field_larmor_interpolator, spinsim.SpinQuantumNumber.ONE)
+results_larmor = simulator_larmor_interpolator.evaluate(0, 100e-3, 1e-6, 10e-6, spinsim.SpinQuantumNumber.ONE.plus_x, [0])
+results_larmor_interpolator = simulator_larmor_interpolator.evaluate(0, 100e-3, 1e-6, 10e-6, spinsim.SpinQuantumNumber.ONE.plus_x, [50])
+
+# Visualise the interpolation
+larmor_interpolator_plot = spinsim.generate_interpolation_sampler(time_sampled, larmor_sampled, device = spinsim.Device.CPU)
+time_plot = np.arange(0, 100e-3, 100e-6)
+larmor_plot = np.zeros(time_plot.size)
+for time_index in range(time_plot.size):
+  larmor_plot[time_index] = 200 + 50*larmor_interpolator_plot(time_plot[time_index])
+
+# Plot
+plt.figure()
+plt.plot(time_sampled, 200 + 50*larmor_sampled, "r.", label = "\"Recorded\" amplitudes")
+plt.plot(time_plot, larmor_plot, "b-", label = "Interpolated amplitudes")
+plt.xlabel("Time (s)")
+plt.ylabel("Z field amplitude (Hz)")
+plt.legend()
+plt.ylim(0, 400)
+plt.title("Noisy Larmor interpolation\nField timeseries")
+plt.savefig("interpolation_example_1_timeseries.png")
[…]

### 2022-04-08 spinsim/__init__.py

@@ -270,7 +270,7 @@ class Device(Enum):
 
 class Results:
     """
-    The results of a an evaluation of the integrator.
+    The results of an evaluation of the integrator.
 
     Attributes
     ----------
@@ -622,6 +622,25 @@ class Simulator:
         if integration_method == IntegrationMethod.MAGNUS_CF4:
             @jit_device_template("(float64[:], float64, float64, float64, float64[:, :], float64, complex128[:])")
             def get_field_integration_magnus_cf4(sweep_parameters, time_fine, time_coarse, time_step_integration, field_sample, rotating_wave, rotating_wave_winding):
+                field_sample[0, 0] = 0
+                field_sample[0, 1] = 0
+                field_sample[0, 2] = 0
+                field_sample[1, 0] = 0
+                field_sample[1, 1] = 0
+                field_sample[1, 2] = 0
+                if lie_dimension > 3:
+                    field_sample[0, 3] = 0
+                    field_sample[1, 3] = 0
+                    if lie_dimension > 4:
+                        field_sample[0, 4] = 0
+                        field_sample[0, 5] = 0
+                        field_sample[0, 6] = 0
+                        field_sample[0, 7] = 0
+                        field_sample[1, 4] = 0
+                        field_sample[1, 5] = 0
+                        field_sample[1, 6] = 0
+                        field_sample[1, 7] = 0
+                
                 time_sample = ((time_fine + 0.5*time_step_integration*(1 - 1/sqrt3)) - time_coarse)
                 rotating_wave_winding[0] = cmath.exp(1j*rotating_wave*time_sample)
                 time_sample += time_coarse
@@ -643,16 +662,26 @@ class Simulator:
                 field_sample[2, 0] = time_step_integration*(w0*field_sample[0, 0] + w1*field_sample[1, 0])
                 field_sample[2, 1] = time_step_integration*(w0*field_sample[0, 1] + w1*field_sample[1, 1])
                 field_sample[2, 2] = time_step_integration*(w0*field_sample[0, 2] + w1*field_sample[1, 2])
-                if dimension > 2:
+                if lie_dimension > 3:
                     field_sample[2, 3] = time_step_integration*(w0*field_sample[0, 3] + w1*field_sample[1, 3])
+                    if lie_dimension > 4:
[…]

### 2022-04-08 article/article.tex
Updates to paper introduction and applications

@@
 \usepackage{graphicx, subcaption}
+
+% Cross referencing headings
+\makeatletter
+\def\ttl@useclass#1#2{%
+	\@ifstar
+		{\ttl@labeltrue\@dblarg{#1{#2}}}% {\ttl@labelfalse#1{#2}[]}%
+		{\ttl@labeltrue\@dblarg{#1{#2}}}}
+\makeatother
+
 \graphicspath{ {images/} }
@@
 
-\section{(1) Overview}
+\section*{(1) Overview}
 
@@
 
-\section{Title}
+\section*{Title}
 % Spinsim: a GPU optimized simulator of spin-half and spin-one quantum systems
@@
 
-\section{Paper Authors}
+\section*{Paper Authors}
 1. Tritt, Alex;\\
@@
 
-\section{Paper Author Roles and Affiliations}
+\section*{Paper Author Roles and Affiliations}
 1. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
@@
 
-\section{Abstract}
+\section*{Abstract}
 	The \emph{Spinsim} \emph{python} package simulates spin-half and spin-one quantum mechanical systems following a time dependent Shr\"odinger equation.
@@
 
-\section{Keywords}
+\section*{Keywords}
 Time dependent Schr\"odinger equation; Quantum; Physics; Spin one; Spin half; Integrator; Exponentiator; GPU; Parallel computing; Solver; Python; Numba; Sensing;
 
-\section{Introduction}
-\subsection{Motivation}
+\section*{Introduction}
+\subsection*{Motivation}
 	Ultracold rubidium atoms have proven their effectiveness in state of the art technologies in quantum sensing~\cite{degen_quantum_2017}, the use of quantum mechanics to make precise measurements of small signals.
-	The rotation of these atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
-	The simplest spin system, spin-half (i.e.spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
-	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (i.e.spin quantum number of $ 1 $, also referred to as a quitrit), which is quantized into three quantum spin levels.
+	These atoms can be modelled as quantum spin systems, which is the quantum mechanical model for objects with angular momentum.
+	The simplest spin system, spin-half (i.e.
+spin quantum number of $ \frac12 $, also referred to as a qubit), is quantized into just two quantum spin levels, and this describes the motion of some fundamental particles such as electrons.
+	However, systems more practical for sensing, such as ultracold rubidium atoms, are more accurately described as a spin-one quantum system (i.e.
+spin quantum number of $ 1 $, also referred to as a qutrit), which is quantized into three quantum spin levels.
 
@@
 	In the past, the spinor Bose Einstein condensate (spinor BEC) lab at Monash University used an in-house, \emph{cython} based script, on which this package, \emph{Spinsim}, is based, and standard differential equation solvers (such as \emph{Mathematica}'s~\cite{wolfram_research_inc_mathematica_2020} function \texttt{NDSolve}) to solve the Schr\"odinger equation for quantum sensing spin systems.
-	Spin one systems are sometimes approximated to spin-half for a faster execution time, at the cost of not modelling all effects in the system.
 	However, these methods are not completely optimized for our use-case, and therefore come with some issues.
@@
 	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
-	Given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
-	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
-	Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
-	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
+	A crude method often used to combat this involves approximating spin-one systems as spin-half for a faster execution time, at the cost of not modelling all effects in the system.
+	With \emph{Spinsim}, this is something we would like to avoid.
+
+	% However, given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
+	% Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
+	% Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
+
+	One option not explored by these generic methods is parallelisation, specifically across graphics processing unit (GPU) cores.
+	While there do already exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
 	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by up to 4 orders of magnitude.
-	% Mention GPU in fewer words
 
@@
 	Third, our system (and similar spin systems) can be very oscillatory.
-	In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz.
+	% In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz.
 % Too specific
@@
 
-	\subsection{Recent literature} % Recent relevant software? Recent software with similar functionality
+	\subsection*{Comparison to recent specialized packages} % Recent relevant software? Recent software with similar functionality
 		While we benchmark \emph{Spinsim} only against industry standard integrators, we also note that application specific quantum numerical simulator packages are regularly being released.
-		However, none of these packages are designed specific to quantum sensing, and so these releases are not suitable for simulations highly accurate at high time resolutions required in that field.
-
-		In quantum optimal control (QOC), researchers look at how to design robust pulse sequences to control spin systems using machine learning techniques.
+		However, none of these packages are designed specific to quantum sensing, and so these releases are not suitable for simulations highly accurate at high time resolutions required in this field.
+		See \emph{\nameref{sec:applications}} for use cases where \emph{Spinsim} is advantageous.
+
+		One application of simulations of spin systems is nuclear magnetic resonance (NMR).
+		In this field, the simulator part of the \emph{PULSEE}~\cite{candoli_pulsee_2021} package uses up to the 3rd order Magnus expansion just once to solve the complete system, rather than using it many times as a time stepping method.
+		Nested integrals of commutators are numerically evaluated on a CPU using Euler integration.
+		This is likely to be slow (due to the Euler-integrated nested integrals of commutators) and inaccurate (due to using the expansion over a large time step), and potentially not even convergent in general (also due to the large time step); although it may suffice for the kinds of problems this NMR simulation package is looking at.
+		This is an application that would benefit from \emph{Spinsim}'s speed.
+
+		An application of spin system simulation that would benefit to a lesser extent is quantum optimal control (QOC).
+		In QOC, researchers look at how to design robust pulse sequences to control spin systems using machine learning techniques.
 		Particularly, this means that simulators used here require automatic differentiation~\cite{griewank_who_2012}, which \emph{Spinsim} does not currently support.
@@
 		Many of these pulse sequences are trains of hard pulses (which are physically constant bursts of radiation), which, if using the accuracy reducing rotating wave approximation (RWA), can have simplified time evolution operators.
-		This paradigm, used in the recent \emph{Qulacs}~\cite{suzuki_qulacs_2021}, \emph{QOpt}~\cite{teske_qopt_2021} and \emph{QSim}~\cite{isakov_simulations_2021}, is not suitable for accurately simulating more complicated (especially when looking from the lab frame of reference) pulse shapes found in quantum sensing.
-		However, all of these packages do allow for simulating entanglement (important for quantum computing, but not for all sensing applications), which \emph{Spinsim} does not and, like \emph{Spinsim}, all have versions optimised for parallelisation (although \emph{QSim} does sacrifice accuracy here for the sake of speed again, by using single-precision floats).
+		This paradigm, used in the recent \emph{Qulacs}~\cite{suzuki_qulacs_2021}, \emph{QOpt}~\cite{teske_qopt_2021} and \emph{QSim}~\cite{isakov_simulations_2021}, is not suitable for accurately simulating more complicated (especially when looking from the lab frame of reference) pulse shapes found in quantum Sensing.
+		However, all of these packages do allow for simulating entanglement (important for quantum computing, but not for all sensing applications), which \emph{Spinsim} does not and, like \emph{Spinsim}, all have versions optimised for parallelisation (although \emph{QSim} does sacrifice accuracy here for the sake of speed, by using single-precision floats).
 		Dalgaard and Motzoi~\cite{dalgaard_fast_2021} have recently proposed Magnus integration techniques for use in QOC, but have not provided any open source implementation to do so.
@@
 
-		Another application of simulations of spin systems is nuclear magnetic resonance (NMR).
-		In this field, the simulator part of the \emph{PULSEE}~\cite{candoli_pulsee_2021} package uses up to the 3rd order Magnus expansion just once to solve the complete system, rather than using it many times as a time stepping method.
-		Nested integrals of commutators are numerically evaluated on a CPU using Euler integration.
-		This is likely to be slow (due to the Euler-integrated nested integrals of commutators) and inaccurate (due to using the expansion over a large time step), and potentially not even convergent in general (also due to the large time step); although it may suffice for the kinds of problems this NMR simulation package is looking at.
-
 		% Designed for optimising quantum control protocols, the \emph{QOpt} package works in the paradigm of a time series of instructions, rather than the analytic forms used in \emph{Spinsim}.
@@
 
-\section{Implementation and architecture}
-	% \subsection{Mathematical methods}
-	\subsection{Quantum mechanics background}
+\section*{Implementation and architecture}
+	% \subsection*{Mathematical methods}
+	\subsection*{Quantum mechanics background}
 		The \emph{Spinsim} package solves the time-dependent Schr\"{o}dinger equation
@@
 		In general, we can choose any basis from the 8-dimensional Lie algebra $ \mathfrak{su}(3) $, which is the vector space of traceless Hermitian operators that can generate transformations (from the corresponding Lie group $ SU(3) $) in the spin-one system.
-		We focus on a particular subfamily of of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \text{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}
+		We focus on a particular subfamily of spin-one systems for which the Hamiltonian is a linear combination of matrices from a 4-dimensional subspace of $ \mathfrak{su}(3) $, consisting of the spin matrices $ J_x $, $ J_y $ and $ J_z $, (labelled $ L_x $, $ L_y $ and $ L_z $ in Reference~\cite{hamley_spin-nematic_2012}) and a single quadrupole operator $ Q = \text{diag}(1, -2, 1)/3 $,% \todo{Describe this subspace better}
 
@@
 
-	\subsection{Unitary time evolution and the Magnus expansion}\label{sec:magnus}
+	\subsection*{Unitary time evolution and the Magnus expansion}\label{sec:magnus}
 		Since $H(t)$ is Hermitian, it follows from Equation~\eqref{eq:schroedinger} that $\|\psi(t)\|^2 = \|\psi(t_0)\|^2$ for all $t$.
@@
 
-	\subsection{Lie-Trotter based exponentiator}
+	\subsection*{Lie-Trotter based exponentiator}
 		Evaluating matrix exponentials is a core part of the integration algorithm.
@@
 
-	\subsection{Discretization and parallelization}\label{sec:parallelization}
+	\subsection*{Discretization and parallelization}\label{sec:parallelization}
 		Frequently we wish to sample the state at times $ t_k $ spaced more coarsely than the integration time-step.
@@
 		To choose an appropriate value of $ \delta t $, users can refer to the accuracy plots in Figures~\ref{fig:benchmark_spin_one_step_error} and~\ref{fig:benchmark_spin_half_step_error} under \emph{\nameref{sec:accuracy}}.
-% \note{How do I reference a section if they don't have number labels in the finished article?
+% \note{How do I reference a section* if they don't have number labels in the finished article?
 Should I?}
@@
 
-	\subsection{Dynamically rotating frame}\label{sec:rotating_frame}
+	\subsection*{Dynamically rotating frame}\label{sec:rotating_frame}
 		Hamiltonians which have dominant and slowly-varying terms induce rotations around a primary axis, which is usually chosen to be the quantization axis (which is the $ z $ axis when representing spin operators with the Pauli matrices).
@@
 
-	% \subsubsection{Magnus-based integration method}
+	% \subsubsection*{Magnus-based integration method}
 	% 	The integration method used in \emph{Spinsim} is the commutator free 4 (CF4) method from Auer et al~\cite{auer_magnus_2018}, which based on the Magnus expansion.
@@
 
-% \subsection{Software architecture}
-	\subsection{Integrator architecture}
+% \subsection*{Software architecture}
+	\subsection*{Integrator architecture}
 		\begin{figure}[h!]
@@
 
-	\subsection{Compilation of integrator}
+	\subsection*{Compilation of integrator}
 		The \emph{Spinsim} integrator is constructed and compiled just-in-time (JIT), using the \emph{Numba}~\cite{lam_numba_2015} python package.
@@
 
-\section{Quality control}
-	\subsection{Evaluation of accuracy}\label{sec:accuracy}
+\section*{Quality control}
+	\subsection*{Evaluation of accuracy}\label{sec:accuracy}
 		All accuracy benchmarks were run in \emph{Cuda} mode, on the desktop computer with the \emph{Ryzen 7 5800X} and \emph{GeForce RTX 3080}, which from Figure~\ref{fig:benchmark_device_aggregate} are the fastest CPU and GPU from the devices tested.
@@
 
-	\subsection{Comparison to alternatives}
+	\subsection*{Comparison to alternatives}
 		We ran the same error and execution time benchmarks on some alternative packages, listed in Table~\ref{tab:external}, to compare \emph{Spinsim}'s performance to theirs.
@@
 
-	\subsection{Parallelization performance}
+	\subsection*{Parallelization performance}
 		Once the algorithm behind \emph{Spinsim} was developed, we wanted to check its execution speed while running on various devices.
@@
 
-	\subsection{Testing}
+	\subsection*{Testing}
 		During the accuracy tests, it was confirmed that all possible modes of \emph{Spinsim} agree with a baseline \emph{SciPy} simulation, as close as the user wants up to the error of $ 10^{-11} $ of that baseline.
@@
 
-\section{(2) Availability}
+\section*{(2) Availability}
 \vspace{0.5cm}
-\section{Operating system}
+\section*{Operating system}
 Developed and tested on \emph{Windows 10}.
@@
 
-\section{Programming language}
+\section*{Programming language}
 Python (3.7 or greater)
 
-\section{Additional system requirements}
+\section*{Additional system requirements}
 To use the (default) \emph{Nvidia Cuda} GPU parallelization, one needs to have a \emph{Cuda} compatible \emph{Nvidia} GPU~\cite{noauthor_cuda_2012}.
@@
 
-\section{Dependencies}
+\section*{Dependencies}
 numba (0.50.1 or greater)\\
@@
 
-\section{List of contributors}
+\section*{List of contributors}
 
@@
 
-\section{Software location:}
+\section*{Software location:}
 
@@
 
-\section{Language}
+\section*{Language}
 
@@
 
-\section{(3) Reuse potential}
-
-	\subsection{Applications}
+\section*{(3) Reuse potential}
+
+	\subsection*{Applications}\label{sec:applications}
 		The \emph{Spinsim} package will be useful for any research group needing quick, accurate, and/or large numbers of simulations involving spin-half or spin-one systems.
@@
 		We stress that many application specific simulators are designed for the paradigm of using the RWA and/or hard pulse approximations~\cite{suzuki_qulacs_2021, teske_qopt_2021, isakov_simulations_2021}, which both sacrifice accuracy for the sake of speed.
-		While this is viable for some areas of physics research, when designing quantum sensing protocols, we need to take all effects of the spin system and surrounding lab environment into account.
+		While this is viable for some areas of physics research, when designing quantum sensing protocols we need to take all effects of the spin system and surrounding lab environment into account.
 		Thus, \emph{Spinsim}'s primary use is to fill in this gap of simulators for use of developing new quantum sensing protocols with spin-half and spin-one systems, and so should be useful to many within the field of quantum sensing.
@@
 
-		So far, the package has also been used to produce simulations for four other new and conceptually distinct quantum sensing protocols from members of the Monash University School of Physics \& Astronomy spinor BEC lab.
-		Included in this were some honors projects, where \emph{Spinsim} allowed for many quick simulations in the limited time available.
+		% So far, the package has also been used to produce simulations for four other new and conceptually distinct quantum sensing protocols from members of the Monash University School of Physics \& Astronomy spinor BEC lab.
+		% Included in this were some honors projects, where \emph{Spinsim} allowed for many quick simulations in the limited time available.
 % People who have not used quantum computation before have managed to do this
 
-		Another example of spin based magnetic field sensing is the use of nitrogen vacancy centres (NVCs).
-		These are spin-one structures found in diamond, doped with Nitrogen atoms.
-		This leaves a vacancy in a position adjacent to the Nitrogen atom, which pairs of electrons occupy to obtain the spin-one properties.
+		% Another example of spin based magnetic field sensing is the use of nitrogen vacancy centres (NVCs).
+		Aside from cold atom based sensors, \emph{Spinsim} could be used to simulate sensors made from nitrogen vacancy centres (NVCs).
+		These are spin-one structures found in diamond doped with Nitrogen atoms.
+		% This leaves a vacancy in a position adjacent to the Nitrogen atom, which pairs of electrons occupy to obtain the spin-one properties.
 		Similar to ultracold atoms, NVCs can be placed and addressed in 2D arrays in order to take many samples in one measurement.
@@
 
-		The \emph{Spinsim} package is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
-		This means that it would not be able to integrate large arrays of entangled states or interacting particles.
-		As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
-		In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only, meaning it is only accurate for the duration that the physical spin system is coherent.
-		While ultracold atoms can be coherent for tens of seconds, to the point where decoherence is negligible for most quantum sensing experiments, NVCs have a much shorter coherence time of up to $ 1\,\text{ms} $~\cite{degen_quantum_2017}, so fewer simulations are accurate while ignoring decoherence.
-		Not being able to model decoherence also means that \emph{Spinsim} may not be adequate for use in some nuclear magnetic resonance (NMR) applications where relaxation is important, such as those covered by \emph{SpinEvolution}~\cite{veshtort_spinevolution_2006}, for example.
+		% The \emph{Spinsim} package is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
+		% This means that it would not be able to integrate large arrays of entangled states or interacting particles.
+		% As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
+		% In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only, meaning it is only accurate for the duration that the physical spin system is coherent.
+		% While ultracold atoms can be coherent for tens of seconds, to the point where decoherence is negligible for most quantum sensing experiments, NVCs have a much shorter coherence time of up to $ 1\,\text{ms} $~\cite{degen_quantum_2017}, so fewer simulations are accurate while ignoring decoherence.
+		% Not being able to model decoherence also means that \emph{Spinsim} may not be adequate for use in some nuclear magnetic resonance (NMR) applications where relaxation is important, such as those covered by \emph{SpinEvolution}~\cite{veshtort_spinevolution_2006}, for example.
 % Too much negativity; Long and adiabatic pulse sequences; simulate in the lab frame, end up with bloch-seigert shifts; targeted at individual quanta, separate regime
 
-		With these restrictions in mind, \emph{Spinsim} could be used for some simplified simulations in various areas of NMR.
+		With some restrictions of not being able to model mixed states, \emph{Spinsim} could be used for simulations in various areas of NMR.
 		There are many atomic nuclei with spins of half (eg protons, Carbon 13) and, and some that have spins of one (eg Lithium 6, Nitrogen 14)~\cite{fuller_nuclear_1976}, which, if relaxation and interactions between systems are not important for the application, \emph{Spinsim} could be used to simulate for spectroscopy experiments, for example.
@@
 		MRI uses measures the response of spins of an array of spin-half protons to a spatially varying pulse sequence~\cite{mckinnon_physics_1998}, which essentially just corresponds to many separate \emph{Spinsim} simulations of spins at different positions in space.
-		While this package offers some advantages over state of the art simulators in the field~\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrized pulse sequence definitions and geometric integrator, again, the lack of interacting particles and decoherence features are may limit its use in this area.
+		This package offers some advantages over state of the art simulators in the field~\cite{kose_fast_2019}, with its use of quantum mechanics over classical mechanics, and its absence of rotating wave approximations, its parametrized pulse sequence definitions and geometric integrator.
 
@@
 
-	\subsection{Support}
+	\subsection*{Support}
 		Documentation for \emph{Spinsim} is available on \href{https://spinsim.readthedocs.io/en/latest/}{\emph{Read the Docs} (https://spinsim.readthedocs.io/en/latest/)}.
-		This documentation contains a thorough tutorial on how to use the package, and installation instructions.
+		This documentation contains a thorough tutorial of examples on how to use the package, and installation instructions.
 
@@
 
-\section{Acknowledgements}
-
-Thank you to the Monash University School of Physics \& Astronomy spinor BEC lab group.
-In particular, Hamish Taylor, Travis Hartley, Chris Bounds and Sam White, who have been using \emph{Spinsim} to simulate new ideas for quantum sensing protocols, and have given useful feedback of their user experience with the package.
-
-\section{Funding statement}
+\section*{Acknowledgements}
+
+Thank you to past and present members the Monash University School of Physics \& Astronomy spinor BEC lab group.
+In particular, Chris Bounds, Hamish Taylor, Travis Hartley, and Sam White, who have been using \emph{Spinsim} to simulate new ideas for quantum sensing protocols, and have given useful feedback of their user experience with the package.
+
+\section*{Funding statement}
 
@@
 
-\section{Competing interests}
+\section*{Competing interests}
 

### 2022-04-11 docs/source/conf.py
Version 1.0.0

@@ -40,7 +40,7 @@ copyright = '2022, Monash University'
 author = 'Alexander Tritt'
 
 # The full version, including alpha/beta/rc tags
-release = '0.5.0'
+release = '1.0.0'
 
 
 # -- General configuration ---------------------------------------------------

### 2022-04-11 spinsim/utilities_old/__init__.py

@@ -1,78 +1,0 @@
-"""
-Some device functions for doing maths and interpolation with :mod:`numba.cuda`.
-"""
-
-import math
-import numpy as np
-import numba as nb
-from numba import cuda
-
-from . import scalar
-from . import spin_half
-from . import spin_one
-
-#@cuda.jit(device = True, inline = True)
-def interpolate_source_linear(source, time_sample, time_step_source, source_sample):
-    """
-    Samples the source using linear interpolation.
-
-    Parameters
-    ----------
-    source : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index, time_source_index)
-        The input source of the environment of the spin system. In units of Hz.
-    time_sample : `float`
-        The time to be sampled.
-    time_step_source : `float`
-        The time step between source samples.
-    source_sample : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index)
-        The interpolated value of source.
-    """
-    time_sample = time_sample/time_step_source
-    time_index_source = int(time_sample)
-    time_sample -= time_index_source
-
-    time_index_source_next = time_index_source + 1
-    if time_index_source_next > source.shape[0] - 1:
-        time_index_source_next = source.shape[0] - 1
-
-    for spacial_index in range(source.shape[1]):
-        source_sample[spacial_index] = (time_sample*(source[time_index_source_next, spacial_index] - source[time_index_source, spacial_index]) + source[time_index_source, spacial_index])
-
-#@cuda.jit(device = True, inline = True)
-def interpolate_source_cubic(source, time_sample, time_step_source, source_sample):
-    """
-    Samples the source using cubic interpolation.
-
-    Parameters
-    ----------
-    source : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index, time_source_index)
-        The input source of the environment of the spin system. In units of Hz.
-    time_sample : `float`
-        The time to be sampled.
-    time_step_source : `float`
-        The time step between source samples.
-    source_sample : :class:`numpy.ndarray` of :class:`numpy.double` (spatial_index)
-        The interpolated value of source.
-    """
-    time_sample = time_sample/time_step_source
-    time_index_source = int(time_sample)
-    time_sample -= time_index_source
-
-    time_index_source_next = time_index_source + 1
-    if time_index_source_next > source.shape[0] - 1:
-        time_index_source_next = source.shape[0] - 1
[…]

### 2022-04-11 spinsim/utilities_old/scalar.py

@@ -1,54 +1,0 @@
-"""
-Some device functions for doing complex scalar maths with :mod:`numba.cuda`.
-"""
-
-import math
-import numpy as np
-import numba as nb
-from numba import cuda
-
-#@cuda.jit(device = True, inline = True)
-def conj(z):
-    """
-    Conjugate of a complex number.
-
-    .. math::
-        \\begin{align*}
-        (a + ib)^* &= a - ib\\\\
-         a, b &\\in \\mathbb{R}
-        \\end{align*}
-
-    Parameters
-    ----------
-    z : :class:`numpy.cdouble`
-        The complex number to take the conjugate of.
-    
-    Returns
-    -------
-    cz : :class:`numpy.cdouble`
-        The conjugate of z.
-    """
-    return (z.real - 1j*z.imag)
-
-#@cuda.jit(device = True, inline = True)
-def complex_abs(z):
-    """
-    The absolute value of a complex number.
-
-    .. math::
-        \\begin{align*}
-        |a + ib| &= \\sqrt{a^2 + b^2}\\\\
-         a, b &\\in \\mathbb{R}
-        \\end{align*}
-    
-    Parameters
-    ----------
-    z : :class:`numpy.cdouble`
-        The complex number to take the absolute value of.
-    
-    Returns
-    -------
-    az : :class:`numpy.double`
-        The absolute value of z.
-    """
-    return math.sqrt(z.real**2 + z.imag**2)

### 2022-04-11 spinsim/utilities_old/spin_half.py

@@ -1,525 +1,0 @@
-"""
-Some device functions for doing spin one maths with :mod:`numba.cuda`.
-"""
-
-import math
-import numpy as np
-import numba as nb
-from numba import cuda
-from . import scalar
-
-# Important constants
-cuda_debug = False
-sqrt2 = math.sqrt(2)
-sqrt3 = math.sqrt(3)
-machine_epsilon = np.finfo(np.float64).eps*1000  # When to decide that vectors are parallel
-# trotter_cutoff = 52
-
-#@cuda.jit(device = True, inline = True)
-def matrix_exponential_analytic(source_sample, result):
-    """
-    Calculates a :math:`su(2)` matrix exponential based on its analytic form.
-
-    Assumes the exponent is an imaginary  linear combination of :math:`su(2)`, being,
-
-    .. math::
-        \\begin{align*}
-            A &= -i(x F_x + y F_y + z F_z),
-        \\end{align*}
-    
-    with
-
-    .. math::
-        \\begin{align*}
-            F_x &= \\frac{1}{2}\\begin{pmatrix}
-                0 & 1 \\\\
-                1 & 0
-            \\end{pmatrix},&
-            F_y &= \\frac{1}{2}\\begin{pmatrix}
-                0 & -i \\\\
-                i &  0
-            \\end{pmatrix},&
-            F_z &= \\frac{1}{2}\\begin{pmatrix}
-                1 &  0  \\\\
-                0 & -1 
-            \\end{pmatrix}
-        \\end{align*}
-
-    Then the exponential can be calculated as
-
-    .. math::
-        \\begin{align*}
-            \\exp(A) &= \\exp(-ix F_x - iy F_y - iz F_z)\\\\
-            &= \\begin{pmatrix}
-                \\cos(\\frac{r}{2}) - i\\frac{z}{r}\\sin(\\frac{r}{2}) & -\\frac{y + ix}{r}\\sin(\\frac{r}{2})\\\\
-                 \\frac{y - ix}{r}\\sin(\\frac{r}{2}) & \\cos(\\frac{r}{2}) + i\\frac{z}{r}\\sin(\\frac{r}{2})
-            \\end{pmatrix}
-        \\end{align*}
-
-    with :math:`r = \\sqrt{x^2 + y^2 + z^2}`.
-
[…]

### 2022-04-11 spinsim/utilities_old/spin_one.py

@@ -1,910 +1,0 @@
-"""
-Some device functions for doing spin one maths with :mod:`numba.cuda`.
-"""
-
-import math
-import numpy as np
-import numba as nb
-from numba import cuda
-from . import scalar
-
-# Important constants
-cuda_debug = False
-sqrt2 = math.sqrt(2)
-sqrt3 = math.sqrt(3)
-machine_epsilon = np.finfo(np.float64).eps*1000  # When to decide that vectors are parallel
-# trotter_cutoff = 52
-
-#@cuda.jit(device = True, inline = True)
-def matrix_exponential_lie_trotter(source_sample, result, trotter_cutoff):
-    """
-    Calculates a matrix exponential based on the Lie Product Formula,
-
-    .. math::
-        \\exp(A + B) = \\lim_{c \\to \\infty} \\left(\\exp\\left(\\frac{1}{c}A\\right) \\exp\\left(\\frac{1}{c}B\\right)\\right)^c.
-
-    Assumes the exponent is an imaginary  linear combination of a subspace of :math:`su(3)`, being,
-
-    .. math::
-        \\begin{align*}
-            A &= -i(x F_x + y F_y + z F_z + q F_q),
-        \\end{align*}
-    
-    with
-
-    .. math::
-        \\begin{align*}
-            F_x &= \\frac{1}{\\sqrt{2}}\\begin{pmatrix}
-                0 & 1 & 0 \\\\
-                1 & 0 & 1 \\\\
-                0 & 1 & 0
-            \\end{pmatrix},&
-            F_y &= \\frac{1}{\\sqrt{2}}\\begin{pmatrix}
-                0 & -i &  0 \\\\
-                i &  0 & -i \\\\
-                0 &  i &  0
-            \\end{pmatrix},\\\\
-            F_z &= \\begin{pmatrix}
-                1 & 0 &  0 \\\\
-                0 & 0 &  0 \\\\
-                0 & 0 & -1
-            \\end{pmatrix},&
-            F_q &= \\frac{1}{3}\\begin{pmatrix}
-                1 &  0 & 0 \\\\
-                0 & -2 & 0 \\\\
-                0 &  0 & 1
-            \\end{pmatrix}
[…]
